### 2011-12-06 paper2/paper2.tex
initial port from svn repository - no further modifications made

% gjilguid2e.tex
% V2.0 released 1998 December 18
% V2.1 released 2003 October 7 -- Gregor Hutton, updated the web address for the style files.

%\documentclass[extra,mreferee]{gji}
\documentclass[extra]{gji}

\bibliographystyle{gji}
\usepackage{timet}
\usepackage[dvips]{graphicx}

\title{Relocating a cluster of earthquakes using a single station}
\author[D.J. Robinson, M. Sambridge, R. Snieder and J Hauser]
  {David J. Robinson$^{1,2}$, Malcolm Sambridge$^{1}$, Roel Snieder$^{3}$, J\"urg Hauser$^{4}$ \\
  $^1$ Research School of Earth Sciences, Australian National
    University, Canberra ACT \emph{0200}, Australia, E-mail: david.robinson@anu.edu.au \\
$^2$  Risk Research Group, Geoscience Australia, GPO Box \emph{383} Canberra ACT \emph{2601} Australia, E-mail: david.robinson@ga.gov.au\\
$^3$ Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines, Golden CO \emph{80401-1887}, USA \\
$^4$ Earthquakes and the Environment Program, NORSAR,Kjeller, Norway}

\date{Received 2010 Month Day; in original form 2010 Month Day}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\volume{200}
\pubyear{2010}

%\def\LaTeX{L\kern-.36em\raise.3ex\hbox{{\small A}}\kern-.15em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}
%\def\LATeX{L\kern-.36em\raise.3ex\hbox{{\Large A}}\kern-.15em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}
% Authors with AMS fonts and mssymb.tex can comment out the following
% line to get the correct symbol for Geophysical Journal International.
\let\leqslant=\leq

\newtheorem{theorem}{Theorem}[section]

\begin{document}

\label{firstpage}

\maketitle

\begin{summary}
(Type abstract here)
\end{summary}

\begin{keywords}
 Probability distributions; Earthquake source observations; Seismicity and tectonics; Wave scattering and diffraction
\end{keywords}

\section{Introduction}

Earthquake location is important for many applications. It assists
our understanding of seismic activity by indicating regions of
relatively higher seismicity such as major lithospheric plate
boundaries \citep[e.g., ][]{dr_Sykes67a, dr_Isacks68a,
dr_Stein02a} or local active source zones
\citep[e.g., ][]{dr_Gutenberg44a, dr_Giardini03a}.
Earthquake locations are required for  magnitude determination
\citep[e.g., ][]{dr_Richter35a, dr_Gutenberg45a}, computing
moment tensors \citep[e.g., ][]{dr_Sipkin02a} and
seismological studies of the Earth's interior
\citep[e.g., ][]{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a,
dr_Kennett04a}. They are needed to
understand strong motion and seismic attenuation
\citep[e.g., ][]{dr_Toro97a, dr_Campbell03a}
 and model earthquake hazard or risk
\citep[e.g., ][]{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
The accuracy required in earthquake location depends on the application.
For example, imaging the structure of a fracture system from microseismicity
requires greater detail than determining whether a $M_w=7.5$ earthquake
occurs offshore for tsunami warning purposes. This paper focuses
on reducing the uncertainty on the locations of a cluster of events, particularly
when they are recorded by a small number of stations.

Absolute location describes the location of an earthquake
with respect to some global reference such as latitude, longitude (or
easting/northing) and depth. Uncertainties associated with absolute locations
are influenced by source to station distances, the number of
stations and their geometry, quality of signal and accuracy of
the velocity model used in computing travel times. Errors in absolute location are typically of the
order of several km because they are susceptible to uncertainty in the velocity
structure along the entire path between the source and receiver.
For example, \citet{dr_Shearer99a} states that location uncertainty
in the ISC and PDE catalogues are generally around 25\,km horizontally and
at least 25\,km in depth.\footnote{Here the depth uncertainties of 25\,km assume the use
of depth dependent phases such as $pP$. Without such phases the uncertainty is higher.}
  These locations are created using global seismic networks.
\citet{dr_Bondar04a} demonstrate
that at the local scale, absolute locations are accurate to within 5\,km with a 95\%
confidence level when local networks meet a number of station
related criteria. Such errors are too large for many applications, particularly
those focussed on the study of micro seismicity and imaging
rupture surfaces from aftershock sequences.

Relative earthquake location involves locating a group of earthquakes with
respect to one another and was first introduced by \citet{dr_Douglas67a}
who developed the technique commonly known as joint hypocenter
determination.\footnote{\citet{dr_Douglas67a} originally used the term
joint epicentre determination. However, he was solving for hypocentre.}
In principle, relative locations can be
computed by differencing absolute locations. However, \citet{dr_Pavlis92a}
shows that inadequate knowledge of velocity structure leads to
systematic biases when relative positions are computed in this way.
This is confirmed by \citet{dr_Richards06a}
who state that inaccuracies in the travel time model are one of
two primary error sources in absolute earthquake location. The other
error source is erroneous arrival picks. To reduce errors from the travel
time model, relative location techniques compute locations
directly from travel time differences between two waveforms
\citep[e.g., ][]{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}.
By doing so, they remove errors
associated with unknown lateral velocity variations outside the
local region, because such variations influence all waveforms in
the same manner \citep{dr_Shearer99a}.

Reported uncertainties
for event locations from relative techniques are  around 15 to 75\,m in
local settings with good station coverage
\citep[e.g., ][]{dr_Ito85a, dr_Got94a, dr_Waldhauser99a,dr_Waldhauser08a}.
Here, `good coverage' implies multiple
stations distributed across a broad range of azimuthal directions.
Precise relative location techniques have been applied to a
diverse range of problems. For example, the location of active
fault planes \citep[e.g., ][]{dr_Deichmann92a, dr_Got94a,
dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a}, studying rupture mechanics
\citep[e.g., ][]{dr_Rubin99a, dr_Rubin02a}, interpreting magma
movement in volcanoes \citep[e.g., ][]{dr_Fremont87a} and monitoring
pumping induced seismicity \citep[e.g., ][]{dr_Lees98a,
dr_Ake05a}. \citet{dr_Poupinet84a},
\citet{dr_Bokelmann00a} and  \citet{dr_Rubin02b} apply relative
location techniques to identify earthquake doublets, events that have near identical
locations. \citet{dr_Poupinet84a} use these doublets to measure
temporal variation in crustal velocity, \citet{dr_Bokelmann00a}
use them to identify systematic temporal variations in seismic
anisotropy and \citet{dr_Rubin02b} describes how they are useful for
correcting time-dependent station delays.

In traditional approaches to absolute and relative location
only early onset body waves, typically $P$ and/or $S$ waves, are used.
The data utilised may be the direct arrival times; the travel time difference computed
between direct arrivals of two waveforms; or the time differences
inferred from time-lagged cross correlation of relatively small windows
around the body wave arrivals.
 In all three cases, the majority of the
waveform is discarded. Furthermore, obtaining high accuracy with these techniques
requires multiple stations with good azimuthal coverage.
In this paper we demonstrate that it is possible to
significantly reduce location uncertainty when few stations are
available by using more of the waveform.

Coda refers to  later arriving waves in the seismogram that arise from
scattering  \citep{dr_Aki69a,dr_Snieder99a,dr_Snieder06a}.
Typically, the coda waves are ignored in most seismological
applications due to the complexity involved in modeling their
generation. In this
paper we develop an approach for locating earthquakes using coda waves.
\citet{dr_Snieder05a} demonstrate that the
coda of two earthquakes can be used to estimate the separation between
them. Their technique is based on the interference pattern between
the coda waves and is known as coda wave interferometry (CWI).
Unlike travel time techniques, CWI
 does not require multiple stations or good azimuthal coverage.
In fact, it is possible to obtain estimates of separation using a single
station \citep{dr_Robinson07b}. This makes CWI particularly interesting
for regions where station density is low such as intraplate areas.
Our technique can be used on coda waves alone or in combination with
travel times. We demonstrate that the use of coda waves improves
the location of a cluster of events when the recording situation
is poor and we show that it is possible to obtain accurate relative locations with as
little as one station.

\section{Theory}

\citet{dr_Snieder05a} introduce a CWI based estimator of source
separation $\delta_{CWI}$ between two earthquakes
\begin{equation}
\label{eq:Theory-dcwi_g_sigmat}
\delta_{CWI}^2 = g(\alpha,\beta)\sigma_\tau^2,
\end{equation}
where $\sigma_\tau$ is the standard deviation of the travel time perturbation
between the coda waves of two earthquakes,
and $\alpha$ and $\beta$ are the near source $P$ and $S$ wave velocities,
respectively. The function $g$ depends on the type of excitation
(explosion, point force, double couple) and on the direction of
source displacement relative to the point force or double
couple. For example, for two double couple sources displaced in the
fault plane,
\begin{equation}
\label{eq:LitReview-g-3d-dc}
g(\alpha,\beta) = 7
\frac{\left(\frac{2}{\alpha^6}+\frac{3}{\beta^6}\right)}{\left(\frac{6}{\alpha^8}+\frac{7}{\beta^8}\right)},
\end{equation}
whereas, for two point sources in a 2D acoustic medium
\begin{equation}
\label{eq:LitReview-g-2d-ps} g(\alpha,\beta) = 2 \alpha^2
\end{equation}
\citep{dr_Snieder05a}. The
$\sigma_\tau$ in eq. (\ref{eq:Theory-dcwi_g_sigmat}) is related to $R_{max}$, the maximum of the cross correlation between
the coda of the two waveforms and hence can be computed directly from the recorded data.
In this paper we use the autocorrelation
approach of \citet{dr_Robinson10b} when relating these parameters
and we apply a restricted time lag search when evaluating $R_{max}$. These extensions
to the original technique of \citet{dr_Snieder05a} increase the range of applicability
of CWI by 50\%.

\citet{dr_Robinson10b} show that coda waves provide
only probabilistic constraints on source separation and
introduce a Bayesian approach for describing the probability
of true separation given the CWI data. Their approach is
summarised by
\begin{equation}
\label{eq:-bayesian-noisyform}
P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN}) \propto P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)
\times P(\widetilde{\delta}_t)
\end{equation}
where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the posterior function
indicating the probability of true separation $\widetilde{\delta}_t$ given the noisy CWI separation
estimates $\widetilde{\delta}_{CWIN}$; $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
is the likelihood function representing the forward model between the
desired separation $\widetilde{\delta}_t$ and the data $\widetilde{\delta}_{CWIN}$; and
$P(\widetilde{\delta}_t)$ is the prior function accounting for all a-priori information.
The tilde above the separation parameters in eq. (\ref{eq:-bayesian-noisyform})
indicates the use of a wavelength normalised separation parameter
\begin{equation}
\label{eq-normalisation-eqn}
\widetilde{\delta} = \frac{\delta}{\lambda_{d}},
\end{equation}
which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$) with
respect to dominant wavelength $\lambda_{d}$.
In this paper we consider a uniform prior which gives emphasis to the recorded data.
The algorithm for computing the noisy
likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by \citet{dr_Robinson10b}
and summarised in Appendix \ref{sec-Appendix-noisylikelihood}. With these two pieces
in place we can compute the posterior $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
(or PDF) for the separation between any pair of events directly from their coda waves.

We seek a probability density function (PDF) which links
 individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
and describes the location of multiple events with maximum identifying
 the most probable combination of locations.
More importantly however, the PDF will
quantify location uncertainty and provide information
on the degree to which individual events are constrained
 by the data. For convenience, we begin with three earthquakes having locations
$\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian formulation we write
\begin{equation}
\label{eq-Bayes-three-locations}
P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3| \mathbf{d}) \propto P( \mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)
\times P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3),
\end{equation}
where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$, $P(\mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
and $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
likelihood and prior functions, respectively. In eq. (\ref{eq-Bayes-three-locations})
$\mathbf{d}$ represents observations that constrain the locations. They can be any combination
of travel times, geodetic information  or CWI separation estimations. For example, if coda waves are used
we have $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN})$ and
$P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the wavelength normalised separation estimates.
Alternatively, if we use CWI and travel time data we may write
$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}, \mathbf{t}_{DD})$ and
$P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{t}_{DD}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
where $\mathbf{t}_{DD}$ represent travel time differences.
In this derivation and in Sec. \ref{sec:benchmarking} we focus on the constraints imposed by coda waves, whereas in
Sec. \ref{sec:CalaverasLoc-CWIandTT} we demonstrate how
CWI and travel time data can be combined.

For three earthquakes we have likelihoods;
$P(\widetilde{\delta}_{CWIN,12}|\mathbf{e}_1, \mathbf{e}_2)$,
$P(\widetilde{\delta}_{CWIN,13}|\mathbf{e}_1, \mathbf{e}_3)$
and
$P(\widetilde{\delta}_{CWIN,23}|\mathbf{e}_2, \mathbf{e}_3)$.
In writing
these likelihoods we have replaced the conditional term on separation
$\widetilde{\delta}_t$ with the locations (e.g. $\mathbf{e}_1$ and $\mathbf{e}_2$).
This can be done because
knowledge of location translates to separation.\footnote{Note that the reverse
can not be said. That is, knowledge of separation between a single event pair
does not translate to location but rather places a non-unique constraint on
location.}
Furthermore, since the pairwise functions are independent the joint
likelihood becomes
\begin{equation}
\begin{array}{l}
\label{eq:-joint-likelihood4three}
P(\widetilde{\mathbf{\delta}}_{CWIN} | \mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) =
P(\widetilde{\delta}_{CWIN,12} | \mathbf{e}_1, \mathbf{e}_2) \\
\hspace{2em} \times P(\widetilde{\delta}_{CWIN,13} | \mathbf{e}_1, \mathbf{e}_3)
\times  P(\widetilde{\delta}_{CWIN,23} | \mathbf{e}_2, \mathbf{e}_3).
\end{array}
\end{equation}
Similarly, we note that earthquake locations are independent and the
joint prior becomes
\begin{equation}
\label{eq:-joint-prior4three}
P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) = P((\mathbf{e}_1) \times P(\mathbf{e}_2) \times P(\mathbf{e}_3).
\end{equation}
Combining eqs. (\ref{eq:-joint-likelihood4three}) and (\ref{eq:-joint-prior4three})
gives the joint posterior function
\begin{equation}
\label{eq-3eqposterior}
\begin{array}{l}
P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^3 P(\mathbf{e}_i) \\
\hspace{4em}  \times \displaystyle \prod_{i=1}^2 \prod_{j=i+1}^3 P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
\end{array}
\end{equation}
for three events. A detailed understanding of the location of a single event (e.g. $\mathbf{e}_2$) is obtained by computing the
marginal
\begin{equation}
\label{eq:-E2-marginal}
P(\mathbf{e}_2) = \int \int P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1 d\mathbf{e}_3
\end{equation}
where the intergral is taken over all plausible locations for $\mathbf{e}_1$ and $\mathbf{e}_3$.
Alternatively, we can compute the marginal for a single event coordinate
by integrating the posterior over all events and remaining coordinates
for the chosen earthquake. Evaluation of $c$ in eq. (\ref{eq-3eqposterior}) involves finding the value which
normalises the posterior function to unit area over all plausible locations.
In many applications the constant of
proportionality $c$ is not important. For example, it is not required
when seeking the combination of locations which maximise
 the posterior function, nor in Bayesian sampling algorithms such as Markov-chain Monte-Carlo
techniques which require evaluation of a function proportional to the PDF.

By following the same argument we get the posterior function
\begin{equation}
\begin{array}{l}
\label{posterior-n-events}
P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^n P(\mathbf{e}_i) \\
\hspace{4em} \displaystyle  \times \prod_{i=1}^{n-1} \prod_{j=i+1}^n P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
\end{array}
\end{equation}
for $n$ events. When evaluating eq. (\ref{posterior-n-events}) over a range of locations
it is necessary to compute and multiply many numbers close to zero.
This is because the PDFs tend to zero as
the locations get less likely (i.e. near the boundaries of the plausible region).
Such calculations are prone to truncation errors so we
work with the negative logarithm
\begin{equation}
\label{eq:-negative-log-part1}
L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n) = -ln\left[ P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN} )  \right]
\end{equation}
or
\begin{equation}
\begin{array}{l}
\label{eq:-negative-log}
L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n) =
-ln\left[ c \right] - \displaystyle \sum_{i=1}^n ln\left[P(\mathbf{e}_i)\right] \\
\hspace{3em} - \displaystyle \sum_{i=1}^{n-1} \sum_{j=i+1}^n ln\left[P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)\right].
\end{array}
\end{equation}
The logarithm improves numerical stability by replacing products with summations. The negative assists with
optimisation, many algorithms for which are designed to minimise an objective function.

The event locations $\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n$
are defined by coordinates $\hat{x}$, $\hat{y}$ and $\hat{z}$
where the hat $\hat{.}$ indicates use of
a local coordinate system. We choose a local coordinate system
which removes ambiguity associated with transformations of the coordinate system,
such as translations and rotations, that do not change the distance between events.
In defining this coordinate system we fix the first event at the origin,
\begin{equation}
\label{eq:coord-const1}
\mathbf{e}_1 = (0,0,0),
\end{equation}
the second event on the positive $\hat{x}$-axis
\begin{equation}
\label{eq:coord-const2}
\mathbf{e}_2 = (\hat{x}_2, 0, 0), \hat{x}_2>0
\end{equation}
the third on the $\hat{x}-\hat{y}$ plane
\begin{equation}
\label{eq:coord-const3}
\mathbf{e}_3 = (\hat{x}_3,\hat{y}_3,0), \hat{y}_3>0
\end{equation}
and the fourth to
\begin{equation}
\label{eq:coord-const4}
\mathbf{e}_4 = (\hat{x}_4,\hat{y}_4,\hat{z}_4), \hat{z}_4>0.
\end{equation}
This coordinate system reduces translational (constraint \ref{eq:coord-const1})
and rotational (constraints \ref{eq:coord-const2} to \ref{eq:coord-const4}) non-uniqueness
without loss of generality. It is necessary to work with a local coordinate
system when using coda waves alone because the CWI technique constrains only event separation
between earthquakes. The inclusion of travel times in Sec. \ref{sec:CalaverasLoc-CWIandTT}
allows us to move to a global reference system.

In summary, the posterior $P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN})$ and its negative
logarithm $L$ describe the joint probability of multiple event locations given the observed coda waves.
The most likely set of locations is given by the minimum of $L$.   In this paper we use the Polak-Ribiere
technique \citep{dr_Press87a} to optimise $L$. The Polak-Ribiere
technique is a particular choice of conjugate gradient method. It uses the
derivatives of $L$ to guide the optimisation procedure. We derive the derivatives in Appendix \ref{sec-Appendix-derivatives_ofL}.

\subsection{Synthetic experiments}
\label{sec:benchmarking}

We use synthetic examples in 2D with 50 earthquakes to test the performance of the optimisation
routine.

\subsection{2D synthetic experiments}

Actual locations are created by
randomly selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq \hat{x} \leq 50$ and $-50 \leq \hat{y} \leq 50$.
These are indicated with triangles in Fig. \ref{fig-2D50eq-relocation_eg1}.
 We assume a local velocity of $v=3300\,$ms$^{-1}$ between all
event pairs and a dominant frequency of 2.5$\,$Hz to represent waveform data filtered between 1 and 5$\,$Hz.
The CWI data are defined by the positive bounded Gaussian with statistics
$\bar{\mu}_N$ and $\bar{\sigma}_N$. A hypothetical CWI mean is created by setting
\begin{equation}
\label{eq:hypothetical-CWI-mean-optichapt}
\bar{\mu}_N = \mu_1 \left( \widetilde{\delta}_t \right)
\end{equation}
using eq. (\ref{eq:mu1}). This assumption ensures that
the sample mean of hypothetical separation estimates is consistent with known CWI
biases \citep{dr_Robinson10b}. In example 1 we use $\bar{\sigma}_N=0.02$ between all event pairs.
Application of our optimisation procedure on the hypothetical CWI data yields the circles
in Fig. \ref{fig-2D50eq-relocation_eg1}. The optimisation does not lead to the correct
solution due to the addition of noise $\bar{\sigma}_N=0.02$ on the hypothetical
CWI data. The average coordinate error
is 2.0\,m which is small compared to the noise of $\bar{\sigma}_N=0.02$ which for
$v_s=3300$\,ms$^{-1}$ and $f_{dom}=2.5$\,Hz corresponds to roughly 25\,m.
\begin{figure}
\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise $\bar{\sigma}_N=0.02$.
Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg1}
\end{figure}

\begin{figure}
\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
\caption{Example 3 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise
$\bar{\sigma}_N= 2 \sigma_{1to5Hz}(\delta_t)$.
 Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg3}
\end{figure}
\citet{dr_Robinson10b} demonstrates that the noise on CWI estimates is often larger than 0.02 and that it increases
with event separation. Consequently, example 1 is overly simplistic because we fix
$\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase the uncertainty and introduce a distance
dependance into the hypothetical $\bar{\sigma}_N$ by defining
$\bar{\sigma}_N=\sigma_{1to5Hz}(\delta_t)$, where $\sigma_{1to5Hz}(\delta_t)$ is the half-width of
the errorbars for a synthetic acoustic experiment
with filtering between 1 and 5\,Hz \citep[see Fig4(b) of ][]{dr_Robinson10b}.
Repeating the optimisation leads
to the circles in Fig. \ref{fig-2D50eq-relocation_eg3} which have an average coordinate error of 2.8\,m.

Conjugate gradient based optimisation techniques are susceptible to the presence of local minima.
This is because they use the slope of the target function to explore the solution space.
We explore the impact of local minima for our CWI location problem by beginning
the optimisation from 25 different randomly chosen starting positions. In this case we observe no differences
in the solution for neither examples 1 or 2.

We can draw three observations from the error structure in Figs. \ref{fig-2D50eq-relocation_eg1} and
\ref{fig-2D50eq-relocation_eg3}. Firstly, we note that the location errors depicted
by grey bars in each figure increase between examples 1 and 2 with the
introduction of larger noise. Secondly, the errors are larger for
events at greater distances from the center. This is because events near the center of the cluster are
constrained by links from all angles, whereas those
on the outside are moderated by links from a limited number of directions. This observation is analogous
to problems associated with poor azimuthal coverage in common triangulation problems such as individual earthquake location
from limited travel time data, or GPS positioning with few satellites. Our third observation is that the location errors appear to
be circular, despite our attempt to correct for rotational non-uniqueness with the local coordinate system.

The local coordinate system works by constraining the location of the first three
earthquakes. Earthquake 1 is fixed at the origin, earthquake 2 on the positive $\hat{x}$-axis and earthquake 3
has $\hat{y}>0$. As the number of events increases the strength of this constraint on later events
becomes weaker allowing small rotations of events with respect to each other.
That is, even though the rotational freedom of the cluster is in principal
removed by the constraints imposed on the events (see eqs. \ref{eq:coord-const1} to \ref {eq:coord-const4}) we observe that
in practice the effects of noise means that the rotational non-uniqueness
reappears. This is because the `easiest' way data noise can propagate is into
the direction which is least constrained by the data. It is the same phenomena as in
linear inversion where noise creates large spurious model changes in directions
of the eigenvectors with the smallest singular values \citep[e.g ][]{dr_Aster05a}.
Unfortunately, there is no obvious way to overcome this issue when using coda
waves alone since the constraints are based on separation. Fortunately however, combining coda waves with
measurements of travel times alleviates this problem and facilitate the removal of a local coordinate system
altogether.

Despite these observations about the error structure however, we gain confidence in the
optimisation procedure due to its stability for different starting locations and
because of the small average coordinate errors of 2.0\,m and 2.8\,m
for examples 1 and 2, respectively.

\subsubsection{The impact of reduced linkage}

A set of earthquakes and their corresponding coda wave estimates of separation can be thought of as
a network. In this network the earthquakes are nodes and the constraints are branches or links
which join them together. Synthetic examples 1 and 2 use 100\% direct linkage between event pairs. That is, there is a constraint
between each earthquake and all other events. In reality, we might expect that the separation between some
pairs will not be constrained by CWI data due to poor signal to noise ratio in the coda for common stations.
Obviously, the less stations that record an event the more likely it is that links
between it and other events will be broken.
In such cases the probabilistic distance constraint between a pair of
events may only exist indirectly through multiple pairs. In this section we
consider the impact of reduced linkage between event pairs. In example 3, we repeat example 2
using 90\%, 80\%, ..., 10\% of the links. As with the above examples, we undertake the
optimisation with 25 randomly chosen starting locations.

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

In Figs. \ref{fig:optimisationresults-2Dsynth}(a) and (b) we examine the performance of the optimisation statistically. In particular,
we plot the maximum $\Delta_{max}$ and mean $\Delta_\mu$ of the coordinate difference as a function of increasing linkage.
We show the statistics for the `best' optimisation solution (black) and for the solution space
when all 25 optimisations are considered (grey). In this case the best solution is determined
by the set of event locations which lead to the smallest value of $L$.
We observe similar errors in the best solution for all cases when at least 30\% of the
branches are used. The errors increase drastically when only 10\% or 20\% of the constraints are included.
Interestingly, this breakdown around 20\% to 30\% coincides with the point where the average number of branches
required to link each pair reaches 2 (see Fig.\ref{fig:optimisationresults-2Dsynth}(c)). Since the average number of branches can be computed
in advance it can be used as an indication of the potential stability of the inversion prior
to optimisation. An earlier breakdown is observed when all 25 solutions
are considered collectively. For example, the
maximum coordinate error $\Delta_{max}$ is significantly higher than that for the best solution for all
cases with 60\% of the constraints or less. This observation suggests that
the optimisation is susceptible to the presence of local minima and that a range of starting points
should be considered.

Interestingly, we note that some of the optimisations chains
fail to converge after 1200 iterations when the linkage is 60\% or lower and all
fail when then linkage is 20\% or lower. Despite their failure to converge however, many of the
solutions remain relatively close to the actual solutions. The derivatives used in the conjugate gradient method
depend on events connected by CWI measurements. Consequently,
earthquakes that are only connected via other events do not `communicate' with each other
directly. To some extent, this should be taken care of during the iterative process where location information
can spread to events which have no direct links. However, the
lack of connection through the gradient could prevent convergence in extreme cases, or more likely
slow the procedure down. This could explain why some
examples do not converge after 1200 iterations.
\citet{dr_VanDecar94a} show that gradient damping acts
slowly through iterative least-squares, because
 every cell in one iteration communicates only with its neighbours, and they demonstrate that this can be
fixed with preconditioning in some cases. Their findings suggest that it may be possible to improve
the convergence (stability and/or speed) of the CWI optimisation by preconditioning.

\subsubsection{3D synthetic examples with reduced linkage}

In this section we expand the optimisation routine to 3D and repeat example 3 of the 2D case.
We randomly pick a set of actual event locations for 50 earthquakes with
$-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case we assume a local velocity
of $v=3300\,$ms$^{-1}$ between all event pairs and a dominant frequency of 2.5$\,$Hz to represent
 waveform data filtered between 1 and 5$\,$Hz.
The hypothetical CWI mean is created using eq. \ref{eq:hypothetical-CWI-mean-optichapt}
which ensures consistency between the sample mean of hypothetical separation estimates and CWI
biases. We use a standard deviation for the noisy CWI estimates
of $\bar{\sigma}_N = \sigma_{1to5Hz}$ and perform the optimisation using 10\%,
20\%, ..., 100\% of the direct links.
In each case we repeat the
optimisation 25 times using randomly chosen starting locations. The results are
summarised in Fig. \ref{fig:optimisationresults-3Dsynth}.

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
when all or best optimisation result(s) are considered, respectively.}
\label{fig:optimisationresults-3Dsynth}
\end{figure}

As in the 2D example we observe a consistency of the optimisation procedure when the number of direct links used
is high. That is, when 70\% of the direct constraints are considered all optimisation results (grey) are consistent with
the best solution (black). Furthermore, the best solution appears to constrain the event locations down to 30\%
of the direct links. There is however, one notable difference between the 3D and 2D results.
In 2D the final iteration was typically close to the actual solution
when the optimisation chain failed to converge after 1200 iterations. Contrastingly,
in 3D the optimisation appears to converge to the correct solution or fail completely, leading to a set locations which
in no way resemble the actual solution. This is depicted in Fig. \ref{fig:optimisationresults-3Dsynth}
by the absence of the grey and black lines below 60\% and 30\% of the constraints, respectively.
The reason for this difference may be due to the increased number of degrees
of freedom in 3D requiring a greater number of iterations to converge. Nevertheless, the accurate convergence of the best
solution for cases with 30\% or more of the links is encouraging for the potential
of coda wave optimisation to constrain earthquake location more generally.

\subsubsection{Summary of findings}

In summary, the synthetic examples demonstrate the ability of coda wave data to constrain event location
using optimisation. The optimisation error is influenced by the
noise on CWI estimates with greater $\bar{\sigma}_N$ leading to larger
errors in the solutions. When 70\% or more of the direct branches are used the
optimiser is stable with no observable difference in the solution for 25 randomly chosen starting
locations. As the direct linkage reduces to 50\% the optimisation becomes less stable and the best solution
from 25 random starting locations is required to find the optimal solution. Finally, as the number of links decrease
below 30\% the best solution also fails to converge to a useful result.

\section{Relocating Earthquakes on the Calaveras Fault}
\label{sec:CalaverasLoc-CWIonly}

In this section we consider real
earthquakes and undertake a complete coda wave analysis beginning with waveform selection, filtering, pairwise application
of CWI and optimisation.
\begin{itemize}
\item Introduce the Calaveras Fault and provide a brief background of why it is chosen here (Figure \ref{fig:-eqopti-California-Calaveras})
\item Discuss Catalogue Locations - hypoDD locations and CWI locations
(Figure \ref{fig-69Calaverasevents_eg1})
\begin{itemize}
\item mention difference between hypoDD inversions when 68 or
308 earthquakes considered but don't show figure (i.e. difference in coordinates for
the two solutions is roughly 2\,m)
\item provide details on CWI application - waveform selection, filtering etc.
\end{itemize}
\item Discuss comparison between CWI and catalogue locations - first order performance of CWI and clustering
\item Discuss comparison between CWI and hypoDD locations - second order result and streaks.
\end{itemize}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
\caption{Elevation in California showing location
of the 308 event Calaveras cluster (black star) and 805 seismic stations (red triangles).}
\label{fig:-eqopti-California-Calaveras}
\end{figure}

\begin{figure*}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

\subsection{Dependance on the number of stations}

\begin{itemize}
\item Explain issues associated with poor station coverage - superimpose
the three SWSZ (i.e. Australian) stations onto  Figure
\ref{fig:-eqopti-California-Calaveras}
\item Show setup for consideration of fewer stations (Table
\ref{tab:Calaveras-stationremoval}
and Figure \ref{fig:-eqopti-Calaveras-substations})
\item Show the results (Figures \ref{fig-68Calaveras_CWIxyloc-statremove}
to \ref{fig-68Calaveras_hypoDDyzloc-statremove} and Figure \ref{fig-statremoval_summarystats})
\item Discuss the better performance of CWI with fewer stations
\item Question/Discuss why hypoDD continues to suggest streaks with 2 or 3 stations - there must be regularization
\end{itemize}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
\caption{Location of the 10 stations (red triangles) used to relocate the Calaveras events.
Stations are removed one at a time according to the order in Table \ref{tab:Calaveras-stationremoval} and the events
relocated (see Figures \ref{fig-68Calaveras_CWIxyloc-statremove} to \ref{fig-68Calaveras_hypoDDyzloc-statremove}).
The 304 Calaveras events are indicated with black circles.}
\label{fig:-eqopti-Calaveras-substations}
\end{figure}

\begin{table}
\caption{Stations considered when exploring the effect of reduced station coverage.}
\label{tab:Calaveras-stationremoval}
\begin{tabular}{|r|l|}
\hline
Number of & Station Names\\
Stations  & \\
\hline
10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
6  & CCO, JCB, JST, CMH, HSP, JAL \\
5  & CCO, JCB, JST, CMH, HSP \\
4  & CCO, JCB, JST, CMH \\
3  & CCO, JCB, JST \\
2  & CCO, JCB \\
1  & CCO \\
\hline
\end{tabular}
\end{table}

\begin{figure*}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
\caption{....}
\label{fig-CWIreducesstats}
\end{figure*}

\begin{figure*}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
\caption{....}
\label{fig-HYPODDreducesstats}
\end{figure*}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

\section{Combining travel time and CWI constraints}
\label{sec:CalaverasLoc-CWIandTT}
\begin{itemize}
\item Pose the problem
\item Introduce the idea of a travel time based separation PDF with mean event locations from hypoDD outputs and
some measure of uncertainty (we will consider three levels of uncertainty as in paper1).
\item Explain how to combine the CWI based posterior with these new travel time based separation PDFs
\item Show the derivatives of the travel time based separation PDF
\item Undertake the combined inversion show/discuss findings (Figure \ref{fig-68Calaverasevents_ttandcoda1} )
\end{itemize}

\begin{figure*}
\noindent\includegraphics{diags/CalaverasLoc5.eps}
\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
\label{fig-68Calaverasevents_ttandcoda1}
\end{figure*}

\subsection{Combining CWI and travel times when the travel times constrain a limited number of events}

\begin{itemize}
\item Explain the idea of a temporary deployment of stations i.e. for aftershocks
\item Discuss Omori formula and the $M_s$7.8 Hokkaido-Nansei-Oki earthquake
\citep[Figure \ref{fig:Omorifigure},]{dr_Utsu95a}
\item Show/Discuss results (Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1})
\end{itemize}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
\caption{Cumulative number of aftershocks for the Hokkaido-Nansei-Oki, Japan
$M_s=7.8$ earthquake of 12 July 1993 according to the best fitting modified Omori Formula
\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost dashed signify aftershocks occurring before, during and
after the deployment of a temporary array installed 7 days after the main shock and left for
65 days.}
\label{fig:Omorifigure}
\end{figure}

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc6.eps}
\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
relocation only (i.e. no CWI) using ........}
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}

\section{Conclusions}
\begin{itemize}
\item Emphasise strengths of the CWI relocation (i.e. with small number of stations,
linking temporary deployments with catalogue locations)
\item Discuss potential applications e.g. intraplate/downhole/tunnel monitoring etc.
\end{itemize}

\begin{acknowledgments}
(Text here)
\end{acknowledgments}

\bibliography{../../refs/drrefs}

\appendix

\section{The noisy likelihood}
\label{sec-Appendix-noisylikelihood}

The noisy likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
used in eq. (\ref{eq:-bayesian-noisyform}) is given by
\begin{equation}
\begin{array}{l}
\label{eq-likelihood-int}
P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
\hspace{3em} \times \int_0^\infty
B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
d\widetilde{\delta}_{CWI}
\end{array}
\end{equation}
where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
of noise,
\begin{equation}
\label{eq:Adefn}
A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
\end{equation}
\begin{equation}
B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
\end{equation}
\begin{equation}
\label{eq:Cdefn}
C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
\end{equation}
\begin{equation}
D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
\end{equation}
and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
\begin{equation}
\label{eq-cummulative-Gaussian}
\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
\end{equation}
\citep{dr_Robinson10b}. The parameters $\mu_1$ and $\sigma_1$ used in
eq. (\ref{eq:Adefn}) are defined by the expresions
\begin{equation}
\label{eq:mu1}
\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
\end{equation}
and
\begin{equation}
\label{eq:sigma1}
\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
\end{equation}
with coefficients $a_1$ to $a_5$ and $c$ defined in Table \ref{tab-const4-mu1-sigma1}.
The parameters $\bar{\mu}_N$ and $\bar{\sigma}_N$ used in
eq. (\ref{eq:Cdefn}) are obtained by finding the values which minimise the
difference in a least squares sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
computed from the waveforms and the
positively bounded Gaussian density function
\begin{equation}
\label{eq-likelihood-noisydata-pdf-orig}
\begin{array}{l}
P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
\end{array}
\end{equation}
with $\widetilde{\delta}_{CWIN} \geq 0$.

\begin{table}
\caption{Coefficients for eqs. (\ref{eq:mu1}) and (\ref{eq:sigma1}).}
\label{tab-const4-mu1-sigma1}
\begin{tabular}{|c|c|}
\hline
$\mu_1(\widetilde{\delta}_t)$ & $\sigma_1(\widetilde{\delta}_t)$ \\
\hline
$a1 = 0.4661$ & $a1 = 0.1441$\\
$a2 = 48.9697$ & $a2 = 101.0376$\\
$a3 = 2.4693$ & $a3 = 120.3864$\\
$a4 = 4.2467$ & $a4 = 2.8430$\\
$a5 = 1.1619$ & $a5 = 6.0823$ \\
     & $c = 0.017$ \\
\hline
\end{tabular}
\end{table}

\section{Derivatives}
\label{sec-Appendix-derivatives_ofL}

The derivatives of $L(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$
\begin{equation}
\frac{\partial L}{\partial \hat{x}_1},
\frac{\partial L}{\partial \hat{y}_1},
 \frac{\partial L}{\partial \hat{z}_1},
\frac{\partial L}{\partial \hat{x}_2},
\frac{\partial L}{\partial \hat{y}_2},
\frac{\partial L}{\partial \hat{z}_2},
...,
\frac{\partial L}{\partial \hat{x}_N},
\frac{\partial L}{\partial \hat{y}_N},
\frac{\partial L}{\partial \hat{z}_N}
\end{equation}
are required by the Polak-Ribiere algorithm. These are used to guide the optimisation procedure
towards the values of $(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$ which
minimise $L$.

The equations for the derivatives are convoluted so we
build them gradually. We start with an expression for $\delta_t$, the wavelength normalised separation between two events
$\mathbf{e}_p= (\hat{x}_p,\hat{y}_p,\hat{z}_p)$ and $\mathbf{e}_q = (\hat{x}_q,\hat{y}_q,\hat{z}_q)$
\begin{equation}
\label{eq:deltat4chapt6deriv}
\delta_t = \frac{f_{dom}}{v_s}\sqrt{(\hat{x}_p-\hat{x}_q)^2 + (\hat{y}_p-\hat{y}_q)^2 +  (\hat{z}_p-\hat{z}_q)^2},
\end{equation}
where $f_{dom}$ is the dominant frequency of the waveforms and $v_s$ is the velocity between the events. Expression
\ref{eq:deltat4chapt6deriv} has derivatives
\begin{equation}
\label{eq-partial-xyz1}
\begin{array}{l}
\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p} = \frac{f_{dom}^2 (\hat{x}_p-\hat{x}_q)}{v_s^2 \widetilde{\delta}_t},
\frac{\partial \widetilde{\delta}_t}{\partial \hat{y}_p} = \frac{f_{dom}^2 (\hat{y}_p-\hat{y}_q)}{v_s^2 \widetilde{\delta}_t}, \\
\frac{\partial \widetilde{\delta}_t}{\partial \hat{z}_p} = \frac{f_{dom}^2 (\hat{z}_p-\hat{z}_q)}{v_s^2 \widetilde{\delta}_t},
\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_q} = \frac{f_{dom}^2 (\hat{x}_q-\hat{x}_p)}{v_s^2 \widetilde{\delta}_t}, \\
\frac{\partial \widetilde{\delta}_t}{\partial \hat{y}_q} = \frac{f_{dom}^2 (\hat{y}_q-\hat{y}_p)}{v_s^2 \widetilde{\delta}_t},
\frac{\partial \widetilde{\delta}_t}{\partial \hat{z}_q} = \frac{f_{dom}^2 (\hat{z}_q-\hat{z}_p)}{v_s^2 \widetilde{\delta}_t}.
\end{array}
\end{equation}
For brevity we focus the following derivation in terms of $\hat{x}_p$. The remaining terms for $\mathbf{e}_p$
(i.e. $\hat{y}_p$ and $\hat{z}_p$) can be computed
by following the same procedure. The derivatives for $\mathbf{e}_q$ can be attained by exploiting the symmetry
\begin{equation}
\label{eq:ep2eq-deriv-symmetry}
\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_q} = - \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}.
\end{equation}

The chain rule gives
\begin{equation}
\frac{\partial \mu_1}{\partial \hat{x}_p} = \frac{\partial \mu_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}
\end{equation}
where differentiating eq. (\ref{eq:mu1}) gives
\begin{equation}
\label{eq-dmu1-by-dx1}
\frac{\partial \mu_1}{\partial \widetilde{\delta}_t} = a_1 \frac{a_2 a_4 \widetilde{\delta}_t^{a_4-1} +a_3 a_5 \widetilde{\delta}_t^{a_5-1}}
{\left(a_2 \widetilde{\delta}_t^{a_4} +a_3 \widetilde{\delta}_t^{a_5} +1 \right)^2}.
\end{equation}
Similarly, we have
\begin{equation}
\frac{\partial \sigma_1}{\partial \hat{x}_p} = \frac{\partial \sigma_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}
{\partial \hat{x}_p}
\end{equation}
where $\frac{\partial \sigma_1}{\partial \widetilde{\delta}_t}$ has the identical form as \ref{eq-dmu1-by-dx1} with different constants
$a_1,a_2,...,a_5$ (see table \ref{tab-const4-mu1-sigma1}).

The cumulative Gaussian distribution function \ref{eq-cummulative-Gaussian} is
\begin{equation}
\Phi_{\mu_1,\sigma_1}(0) = \frac{1}{\sigma_1 \sqrt{2 \pi}}
\int_{-\infty}^0 e^{  \frac{-(s-\mu_1)^2}{2\sigma_1^2}  } ds
\end{equation}
which has derivative
\begin{equation}
\frac{\partial \Phi_{\mu_1,\sigma_1}(0)}{\partial \hat{x}_p} =
\frac{ \sigma_1 \int_{-\infty}^0 \frac{\partial g}{\partial \hat{x}_p} e^g ds -
\frac{\partial \sigma_1}{\partial \hat{x}_p} \int_{-\infty}^0 e^g ds}
{\sigma_1^2 \sqrt{2 \pi}}
\end{equation}
where
\begin{equation}
g = \frac{-(s-\mu_1)^2}{2 \sigma_1^2}
\end{equation}
and
\begin{equation}
\frac{\partial g}{\partial \hat{x}_p} = \frac{4 \sigma_1^2 (s-\mu_1) \frac{\partial \mu_1}{\partial \hat{x}_p}
+ 4\sigma_1 \frac{\partial \sigma_1}{\partial \hat{x}_p}(s-\mu_1)^2}
{4 \sigma_1^4}.
\end{equation}

Now, we have all the pieces to compute the derivatives of $A=A(\delta_t)$ and $B = B(\delta_t,\delta_{CWI})$ as follows
\begin{equation}
\frac{\partial A} {\partial \hat{x}_p} =
-\frac{ -\frac{\partial  \Phi_{\mu_1,\sigma_1}(0)}{\partial \hat{x}_p} \sigma_1 +
 \left(1- \Phi_{\mu_1,\sigma_1}(0) \right) \frac{\partial \sigma_1}{\partial \hat{x}_p}}
{\left(1- \Phi_{\mu_1,\sigma_1}(0) \right)^2 \sigma_1^2 \sqrt{2 \pi}}
\end{equation}
and
\begin{equation}
\frac{\partial B} {\partial \hat{x}_p} = e^h \frac{\partial h}{\partial \hat{x}_p}
\end{equation}
where
\begin{equation}
h =  \frac{-(\delta_{CWI}-\mu_1)^2}{2 \sigma_1^2}
\end{equation}
and
\begin{equation}
\frac{\partial h}{\partial \hat{x}_p} = \frac{
4 \sigma_1^2 (\delta_{CWI}-\mu_1) \frac{\partial \mu_1}{\partial \hat{x}_p}
+ 4(\delta_{CWI}-\mu_1)^2 \sigma_1 \frac{\partial \sigma_1}{\partial \hat{x}_p} }
{4 \sigma_1^4}.
\end{equation}
Finally, we can differentiate the likelihood for an individual event pair
\begin{equation}
\begin{array}{l}
\frac{\partial P(\delta_{CWIN}|\widetilde{\delta}_t)} {\partial \hat{x}_p}  =
\frac{\partial A(\widetilde{\delta}_t)}{\partial \hat{x}_p} C(\bar{\mu}_N, \bar{\sigma}_N) \\
\hspace{2em} \times \int_0^\infty B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
d\widetilde{\delta}_{CWI} \\
\hspace{2em} + A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N) \\
\hspace{2em} \times \int_0^\infty
\frac{\partial B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})} {\partial \hat{x}_p}
D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
d\widetilde{\delta}_{CWI}
\end{array}
\end{equation}
and for the logarithm we have
\begin{equation}
\frac{ \partial \ln \left[ P(\delta_{CWIN}|\delta_t) \right] } {\partial \hat{x}_p}
= \frac{1}{P(\delta_{CWIN}|\delta_t)} \frac{\partial P(\delta_{CWIN}|\delta_t)}{\partial \hat{x}_p}.
\end{equation}

Thus, it follows that the derivative of $L$ with respect to $\hat{x}_p$ is given by
%\begin{equation}
%\label{eq-derivative-Lstar-cwionly22}
%\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} =
%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p}
%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
%\end{equation}
\begin{equation}
\label{eq-derivative-Lstar-cwionly}
\begin{array}{ll}
\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} = &
- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p} \\
 & + \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
\end{array}
\end{equation}
%
%\iftwocol{\begin{eqnarray} \frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} &  = &\\
%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p} \\
%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
%\end{eqnarray}}
%{\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} =
%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p}
%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}}
%\end{equation}
for a uniform prior. The change of sign in the middle (i.e. to addition) accounts for the change in
order of the events under the conditional. Its inclusion here assumes the correct use of
$\partial \widetilde{\delta}_t / \partial \hat{x}_p$
or
$\partial \widetilde{\delta}_t / \partial \hat{x}_q$
when evaluating the left and right hand terms of the summation. The derivatives shown in this section
appear complicated but are in practice trivial to compute numerically.
Confidence in their accuracy is enhanced in the following sections by demonstrating that
the optimisation procedure converges to the correct solution for a number of synthetic problems
in 2 and 3 dimensions.

\clearpage

\begin{figure*}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

\begin{figure*}
\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
\caption{HypoDD (SVD) with reduced stations.}
\label{fig-HYPODDreducesstats}
\end{figure*}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

\begin{figure*}
\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
\label{fig-69Calaverasevents_eg1}
\end{figure*}

%\bsp % ``This paper has been produced using the Blackwell
     %   Publishing GJI \LaTeXe\ class file.''

\label{lastpage}

\end{document}

### 2011-12-06 paper2/paper2_jgr.tex
initial port from svn repository - no further modifications made

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified March 2009
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
%
% For more information on using the AGUTeX macro package,
% see agudocs.tex or agudocs.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to author.help@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: set the \documentclass
%
% The three options for article format are: two-column (default),
% draft, for initial article submission; and galley for narrow
% single columns.
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS
% The draft option produces double spaced output
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS

% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below)

\documentclass[draft,jgrga]{agutex}
\bibliographystyle{agufull08}
%\usepackage{rotating}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% optional article formats author might want to use

% To produce a galley version:
% \documentclass[galley,jgrga]{AGUTeX}

% To produce a two columned version:
% \documentclass[jgrga]{AGUTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To print your article using PostScript fonts, uncomment this:
% \usepackage{agu-ps}
% You many need to edit the top of agu-ps to use the names of the PS
% fonts on your system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To Create numbered lines:

% If you don't already have lineno.sty, you can download it from
% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
% (or google lineno.sty ctan), available at TeX Archive Network (CTAN).
% Take care that you always use the latest version.

% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:

% \usepackage{lineno}
% \linenumbers*[1]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables
%

% When submitting articles through the GEMS system:
% COMMENT OUT ANY COMMANDS THAT INCLUDE GRAPHICS.
% (See FIGURES section near the end of the file)

%  Figures and Tables should be placed at the end of the article,
%  after the references.
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
  \usepackage[dvips]{graphicx}
%
%    Uncomment the following command to allow illustrations to print
%    when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
\authorrunninghead{ROBINSON ET AL.}

% Shorter version of title entered in capital letters:
\titlerunninghead{EARTHQUAKE LOCATION USING CODA WAVES}

% Author mailing address: please repeat this command for
% each author and alphabetize authors:

\authoraddr{D. J. Robinson,
Research School of Earth Sciences, Australian National University, Canberra, ACT, 0200, Australia.
 (david.robinson@anu.edu.au) and
Risk Research Group, Geoscience Australia, GPO Box 378, Canberra, ACT, 2601, Australia.
 (david.robinson@ga.gov.au)}

\authoraddr{M. Sambridge,
Research School of Earth Sciences, Australian National University, Canberra, ACT, 0200, Australia.
 (malcolm.sambridge@anu.edu.au)}

\authoraddr{R. Snieder,
Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines,
    Golden CO 80401, USA.
 (rsnieder@mines.edu)}

\authoraddr{J. Hauser,
NORSAR, Postboks 53, Instituttveien 25, N-2027 Kjeller, Norge}

%\authoraddr{J. R. McConnell, Division of Hydrologic
%Sciences, 123 Main Street, Desert Research Institute, Reno, NV
%89512, USA.}

%\authoraddr{E. Mosley-Thompson, Department of Geography,
%Ohio State University, 123 Orange Boulevard, Columbus, OH 43210,
%USA.}

%\authoraddr{R. Williams, Department of Space Sciences, University of
%Michigan, 123 Brown Avenue, Ann Arbor, MI 48109, USA.}

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

\title{Relocating a cluster of earthquakes using coda waves from a single station}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
% You may use \\ to break the title over several lines.

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

%Use \author{\altaffilmark{}} and \altaffiltext{}

% \altaffilmark will produce footnote;
% matching altaffiltext will appear at bottom of page.
% May use \\ to start a new line.

\authors{D. J. ROBINSON, \altaffilmark{1,} \altaffilmark{2}
M. SAMBRIDGE,  \altaffilmark{1}
R. SNIEDER \altaffilmark{3}
and J. HAUSER \altaffilmark{1,} \altaffilmark{4}}
%E. Mosley-Thompson, \altaffilmark{2} R. Williams, \altaffilmark{3}
%and J. R. McConnell\altaffilmark{4}}

\altaffiltext{1}{Research School of Earth Sciences, The Australian National University}

\altaffiltext{2}{Risk Research Group, Geoscience Australia}

\altaffiltext{3}{Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines}

\altaffiltext{4}{Earthquakes and the Environment Program, NORSAR}

%\altaffiltext{1}{Department of Hydrology and Water Resources,
%University of Arizona, Tucson, Arizona, USA.}

%\altaffiltext{2}{Department of Geography, Ohio State University,
%Columbus, Ohio, USA.}

%\altaffiltext{3}{Department of Space Sciences, University of
%Michigan, Ann Arbor, Michigan, USA.}

%\altaffiltext{4}{Division of Hydrologic Sciences, Desert Research
%Institute, Reno, Nevada, USA.}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

% >> Do NOT include any \begin...\end commands within
% >> the body of the abstract.

\begin{abstract}
(Type abstract here)
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%

% The body of the article must start with a \begin{article} command
%
% \end{article} must follow the references section, before the figures
%  and tables.

\begin{article}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\section{Introduction}
\begin{itemize}
\item Brief discussion of existing earthquake location techniques - first arrivals - need for good station coverage etc.
\item Non-technical overview of CWI (\citealp{dr_Snieder05a}; \citealp{dr_Snieder06a})
\item Comment how CWI pairwise separation does not require azimuthal station coverage \citep{dr_Robinson07b}
\item Mention probabilistic version for CWI based separation (ref \textbf{paper1})
\end{itemize}

\section{Theory}
\begin{itemize}
\item Key CWI formulae from \citet{dr_Snieder05a},
\citet{dr_Snieder06a} and \textbf{paper1}
\item Formulation of the misfit function $L$ (i.e. extract from Thesis Chapter 5)
\item Discuss minimization of $L$ using Polak-Ribiere conjugate gradient method
\item Derivation of Derivatives
\end{itemize}

\section{Benchmarking}
\begin{itemize}
\item Introduce 2D synthetic studies (relocating 50 earthquakes) and show results for cases with
two different uncertainty levels (Figures \ref{fig-2D50eq-relocation_eg1} and
\ref{fig-2D50eq-relocation_eg3})
\item Explain CWI constraints in terms of a network of points
\item Repeat the relocations with reduced pairwise linkage and show results
(Figure \ref{fig:optimisationresults-2Dsynth})
\item Discuss process of repeating optimisation with 25 randomly chosen starting locations
 and compare results to the best optimisation chain - i.e. stability of the inversion.
\item \textbf{Malcolm and Roel - at this stage I am not planning to include detailed pictures of the 2D
inversions and discuss rotational error structure. I don't think it is needed in this paper but I welcome your thoughts}
\item Repeat the experiment in 3D and show results
(Figure \ref{fig:optimisationresults-3Dsynth})
\item Discuss differences between the 2D and 3D versions -i.e. failed convergence (in 3D) versus slow convergence (in 2D)
\end{itemize}

\section{Relocating Earthquakes on the Calaveras Fault}
\begin{itemize}
\item Introduce the Calaveras Fault and provide a brief background of why it is chosen here (Figure \ref{fig:-eqopti-California-Calaveras})
\item Discuss Catalogue Locations - hypoDD locations and CWI locations
(Figure \ref{fig-69Calaverasevents_eg1})
\begin{itemize}
\item mention difference between hypoDD inversions when 68 or
308 earthquakes considered but don't show figure (i.e. difference in coordinates for
the two solutions is roughly 2\,m)
\item provide details on CWI application - waveform selection, filtering etc.
\end{itemize}
\item Discuss comparison between CWI and catalogue locations - first order performance of CWI and clustering
\item Discuss comparison between CWI and hypoDD locations - second order result and streaks.
\end{itemize}

\section{Dependance on the number of stations}

\begin{itemize}
\item Explain issues associated with poor station coverage - superimpose
the three SWSZ (i.e. Australian) stations onto  Figure
\ref{fig:-eqopti-California-Calaveras}
\item Show setup for consideration of fewer stations (Table
\ref{tab:Calaveras-stationremoval}
and Figure \ref{fig:-eqopti-Calaveras-substations})
\item Show the results (Figures \ref{fig-68Calaveras_CWIxyloc-statremove}
to \ref{fig-68Calaveras_hypoDDyzloc-statremove} and Figure \ref{fig-statremoval_summarystats})
\item Discuss the better performance of CWI with fewer stations
\item Question/Discuss why hypoDD continues to suggest streaks with 2 or 3 stations - there must be regularization
\end{itemize}

\section{Combining travel time and CWI constraints}

\begin{itemize}
\item Pose the problem
\item Introduce the idea of a travel time based separation PDF with mean event locations from hypoDD outputs and
some measure of uncertainty (we will consider three levels of uncertainty as in paper1).
\item Explain how to combine the CWI based posterior with these new travel time based separation PDFs
\item Show the derivatives of the travel time based separation PDF
\item Undertake the combined inversion show/discuss findings (Figure \ref{fig-68Calaverasevents_ttandcoda1} )
\end{itemize}

\section{Combining CWI and travel times when the travel times constrain a limited number of events}

\begin{itemize}
\item Explain the idea of a temporary deployment of stations i.e. for aftershocks
\item Discuss Omori formula and the $M_s$7.8 Hokkaido-Nansei-Oki earthquake
(Figure \ref{fig:Omorifigure}; \citealp{dr_Utsu95a})
\item Show/Discuss results (Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1})
\end{itemize}

\section{Conclusions}
\begin{itemize}
\item Emphasise strengths of the CWI relocation (i.e. with small number of stations,
linking temporary deployments with catalogue locations)
\item Discuss potential applications e.g. intraplate/downhole/tunnel monitoring etc.
\end{itemize}

%%% End of body of article:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
%%%%%%%%%%%%%%%%%
% Geophysical Research Letters only allows an appendix without a letter.
%% You can get this result with
%  \section*{Appendix}
%  or
%  \section*{Appendix: Title}
%%%%%%%%%%%%%%%%%
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing  \appendix
%
% \section{Here Is Appendix Title}
% will print
% Appendix A: Here Is Appendix Title
%
% \section*{Appendix}
% will print
% Appendix
%
% \section*{Appendix: Here Is Appendix Title}
% will print
% Appendix: Here Is Appendix Title
%
% For only 1 appendix \appendix \section{Appendix} is preferred.
% which will print
% Appendix A

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second Term & second definition.
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

\begin{acknowledgments}
(Text here)
\end{acknowledgments}

%% ------------------------------------------------------------------------ %%
%
%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% Or,
%
% If you use BiBTeX for your References, please produce your .bbl
% file and copy the contents into your paper here.
%
% Follow these steps:
% 1. Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Comment out the old \bibliographystyle and \bibliography commands.
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file, but asks that you
% copy in the contents of your .bbl file here.
\bibliography{../../refs/drrefs}
% DR ... \begin{thebibliography}{}

%\bibitem[{\textit{Kilby}(2008)}]{jskilby}
%Kilby, J. S. (2008), Invention of the integrated circuit, {\it IEEE
%Trans. Electron Devices,} \textit{23}, 648--650.

%\bibitem[{\textit{Kilby et al.}(2008)}]{jskilbye}
%Kilby, J. S., S. Smith, and R. Jones (2008), Invention of the
%integrated circuit, {\it IEEE Trans. Electron Devices,} \textit{23},
%648--650.

% DR ... \end{thebibliography}

%Reference citation examples:

%...as shown by \textit{Kilby} [2008].
%...has been shown [\textit{Kilby et al.}, 2008].

%...as shown by \cite{jskilby}.
%...has been shown \citep{jskilbye}.

%% ------------------------------------------------------------------------ %%
%
%  END ARTICLE
%
%% ------------------------------------------------------------------------ %%

\end{article}

%% Enter Figures and Tables here:

% When submitting articles through the GEMS system:
% COMMENT OUT ANY COMMANDS THAT INCLUDE GRAPHICS.

% Figure captions go below this illustration; Table captions go above tables

% ONE-COLUMN figure/table, including eps graphics
%
% \begin{figure}
% \noindent\includegraphics[width=20pc]{samplefigure.eps}
% \caption{Caption text here}
% \end{figure}
% \end{document}
%
% \begin{table}
% \caption{}
% \end{table}
%
% ---------------
% TWO-COLUMN figure/table
%
% \begin{figure*}
% \noindent\includegraphics[width=39pc]{samplefigure.eps}
% \caption{Caption text here}
% \end{figure*}
%
% \begin{table*}
% \caption{Caption text here}
% \end{table*}
%
% see below for how to make landscape figures or tables

%%% End the article here:
% Put the figures here....
\clearpage
\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise $\bar{\sigma}_N=0.02$.
Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
\caption{Example 3 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise
$\bar{\sigma}_N= 2 \sigma_{1to5Hz}(\delta_t)$.
 Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg3}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
when all or best optimisation result(s) are considered, respectively.}
\label{fig:optimisationresults-3Dsynth}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
\caption{Elevation in California showing location
of the 308 event Calaveras cluster (black star) and 805 seismic stations (red triangles).}
\label{fig:-eqopti-California-Calaveras}
\end{figure}

\begin{figure}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
\caption{Location of the 10 stations (red triangles) used to relocate the Calaveras events.
Stations are removed one at a time according to the order in Table \ref{tab:Calaveras-stationremoval} and the events
relocated (see Figures \ref{fig-68Calaveras_CWIxyloc-statremove} to \ref{fig-68Calaveras_hypoDDyzloc-statremove}).
The 304 Calaveras events are indicated with black circles.}
\label{fig:-eqopti-Calaveras-substations}
\end{figure}

\begin{figure}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
\caption{....}
\label{fig-CWIreducesstats}
\end{figure}

\begin{figure}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
\caption{....}
\label{fig-HYPODDreducesstats}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc5.eps}
\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
(after \citealp{dr_Waldhauser08a}), Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m (after \citealp{dr_Shearer97a}). }
\label{fig-68Calaverasevents_ttandcoda1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
\caption{Cumulative number of aftershocks for the Hokkaido-Nansei-Oki, Japan
$M_s=7.8$ earthquake of 12 July 1993 according to the best fitting modified Omori Formula
\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost dashed signify aftershocks occurring before, during and
after the deployment of a temporary array installed 7 days after the main shock and left for
65 days.}
\label{fig:Omorifigure}
\end{figure}

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc6.eps}
\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
relocation only (i.e. no CWI) using ........}
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}

\clearpage
\begin{table}
\caption{Stations considered when exploring the effect of reduced station coverage.}
\label{tab:Calaveras-stationremoval}
\begin{tabular}{|r|l|}
\hline
Number of & Station Names\\
Stations  & \\
\hline
10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
6  & CCO, JCB, JST, CMH, HSP, JAL \\
5  & CCO, JCB, JST, CMH, HSP \\
4  & CCO, JCB, JST, CMH \\
3  & CCO, JCB, JST \\
2  & CCO, JCB \\
1  & CCO \\
\hline
\end{tabular}
\end{table}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%  SECTION HEADS

 ---------------
 Level 1 head

 Use the \section{} command to identify level 1 heads;
 type the appropriate head wording between the curly
 brackets, as shown below.

 Capitalize the first letter of each word (expect for
 prepositions, conjunctions, and articles that are
 three or fewer letters).

 Do not hyphenate level 1 heads. To break lines,
 type \protect\\ where you want the break to occur.
 AGU prefers the inverted triangle, breaking before
 prepositions, conjunctions, and articles, if possible.

An example:
\section{Level 1 Head: Introduction}

 ---------------
 Level 2 head

 Use the \subsection{} command to identify level 2 heads.

 Capitalize the first letter of each word (expect for
 prepositions, conjunctions, and articles that are
 three or fewer letters).

 Do not hyphenate level 1 heads. To break lines,
 type \protect\\ where you want the break to occur.
 AGU prefers the inverted triangle, breaking before
 prepositions, conjunctions, and articles, if possible.

\subsection{Level 2 Head} An example.

 ---------------
 Level 3 head

 Use the \subsubsection{} command to identify level 3 heads

 Capitalize only the first letter of the first word, acronyms,
 first letter of proper nouns, and first letter of first word
 after a colon.

 Hyphenation is permitted in level 3 heads, if needed.

\subsubsection{Level 3 Head} An example.

\subsubsubsection{Level 4 Head} An example.

%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%

% Do not use bulleted lists; enumerated lists are okay.
 \begin{enumerate}
 \item
 \item
 \item
 \end{enumerate}

%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.

 Math coded inside display math mode \[ ...\]
 will not be numbered e.g.:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered e.g.:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
% BREAK THE EQUATIONS INTO TWO OR MORE LINES
% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
% using double backslashes (\\).

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

If you don't want an equation number, use the star form:
\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

% There is another multiline equation environment:
% \begin{aguleftmath}...\end{aguleftmath}
% The equation is aligned left and the second line indents to
% the width of a paragraph indent (AGU style)

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%
% To reset the equation counter, place the setcounter{equation}
% command in front of your equation(s).
%\setcounter{equation}{0}

% Set the equation counter to 0 if the next
% number needed is 1 or set it to 7 if the
% next number needed is 8, etc.
%
% The \setcounter{equation} command does affect
% equations appearing later in the manuscript.

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Landscape figure and table examples
%
% ---------------
% Landscape (broadside) figure/table
% (These objects will not display properly in draft mode, use galley.)
%
% ONE-COLUMN landscape figure and table
%
% \begin{landscapefigure}
% \includegraphics[height=.75\mycolumnwidth,width=42pc]{samplefigure.eps}
% \caption{Caption text here}
% \end{landscapefigure}
%
% \begin{landscapetable}
% \caption{Caption text here}
% \begin{tabular*}{\hsize}{@{\extracolsep{\fill}}lcccc}
% \tableline
% ....
% \tableline\\
% \multicolumn5l{(a) Algorithms from Numerical Recipes}\\
% \end{tabular*}
% \tablenotetext{}{}
% \tablecomments{}
% \end{landscapetable}
%
% FULL-PAGE landscape figures and tables
%
% \begin{figure*}[p]
% \begin{landscapefigure*}
% illustration here
% \caption{caption here}
% \end{landscapefigure*}
% \end{figure*}
%
% \begin{table}[p]
% \begin{landscapetable*}
% \caption{}
% \begin{tabular*}{\textheight}{@{\extracolsep{\fill}}lccrrrcrrr}
% ....
% \end{tabular*}
% \begin{tablenotes}
% ...
% \end{tablenotes}
% \end{landscapetable*}
% \end{table}
%

### 2011-12-06 paper2/diags/CalaverasMap/matlab/plot_map.m

@@ -1,0 +1,56 @@
+% The purpose of this script is to plot a map of the events and stations
+
+%====================================
+% Define desired figures
+figure_switch = 1;
+%   1 => compute small figure with subset of stations only (FAST)
+%   2 => also compute large figure with all stations (SLOW)
+%====================================
+
+fsize = 16;
+
+
+% Load the earthquakes
+load hypoDD.reloc
+figure
+plot(hypoDD(:,3), hypoDD(:,2), 'ko','markersize',2,'markerfacecolor','k')
+hold on
+
+s = importdata('station_subset.dat');
+[n m] =size(s.data)
+for i = 1:n
+    plot(s.data(i,2), s.data(i,1), 'k^','markersize',7,'markerfacecolor','k')
+    tmp =s.textdata(i);
+    text(s.data(i,2)-0.025, s.data(i,1)+0.015,tmp{1}(3:end),'fontsize',fsize)
+end
+%set(gca,'ylim',[37 37.5],'xlim',[-121.9 -121.5])
+set(gca,'xlim',[-121.9,-121.5],'ylim',[37,37.4])
+set(gca,'ytick', [37:0.1:37.4],'xtick',[-121.9:0.1:-121.5])
+
+ylabel('Latitude','fontsize',fsize)
+xlabel('Longitude','fontsize',fsize)
+set(gca,'fontsize',fsize)
+%axis equal
+
+% Let's put on a scale bar
+[s, alpha12, alpha21] = vincenty_inverse(37.35,-121.65,37.35,-121.53705)
+plot([-121.65 -121.53705],[37.35 37.35],'k','linewidth',2)
+text(mean([-121.65 -121.53705])-0.015,37.36,'10km','fontsize',fsize)
+
+print -depsc Calaveras_substationmap.eps
+
+if figure_switch ==2
+    figure
+    plot(hypoDD(:,3), hypoDD(:,2), 'ko','markersize',2,'markerfacecolor','k')
+    hold on
+
+    s = importdata('station.dat');
+    [n m] =size(s.data)
+    for i = 1:n
+        plot(s.data(i,2), s.data(i,1), 'r^','markersize',7,'markerfacecolor','r')
+        tmp =s.textdata(i);
+        text(s.data(i,2)-0.01, s.data(i,1)+0.01,tmp{1}(3:end))
+    end
+    %set(gca,'ylim',[37 37.5],'xlim',[-121.9 -121.5])
+    axis equal
+end

### 2011-12-06 paper2/diags/build_OmoriFigure.m

@@ -1,0 +1,42 @@
+function [] = build_OmoriFigure()
+
+% The purpose of this function is to build the Omori figure...
+
+tstart = 7;
+tdays = 65;
+tend = tstart+tdays; 
+ttotal = 1000;
+
+Nstart =  Cumm_Omori(tstart)
+Nend = Cumm_Omori(tend)
+Ntotal = Cumm_Omori(ttotal)
+
+prop_recorded = (Nend-Nstart)/Ntotal
+
+t1 = [0:tstart];
+N1 = Cumm_Omori(t1);
+plot(t1,N1,'k--','linewidth',4)
+
+t2 = [tstart:tend];
+N2 = Cumm_Omori(t2);
+hold on
+plot(t2,N2,'k','linewidth',4)
+
+t3 = [tend:100];
+N3 = Cumm_Omori(t3);
+plot(t3,N3,'k--','linewidth',4)
+
+fsize = 16;
+set(gca,'fontsize',fsize)
+xlabel('time (days)','fontsize',fsize)
+ylabel('Cummulative number of aftershocks','fontsize',fsize)
+
+print -depsc OmoriFigure.eps
+
+function [N] = Cumm_Omori(t)
+% Assume the following values
+K = 906.5;
+c = 1.433; 
+p = 1.256;
+
+N = K *( c^(1-p) - (t+c).^(1-p))/(p-1);

### 2011-12-06 paper2/diags/extra_hypoDD/dt.cc

@@ -1,0 +1,3520 @@
+# 77218 126189 0.021999 
+NCCCOa 0.002643 0.937 P 
+# 126189 126389 -0.002003 
+NCCSC 0.001487 0.752 P 
+NCCADa 0.031378 0.725 P 
+NCJCB 0.028081 0.724 P 
+NCJHL 0.020495 0.738 P 
+# 126389 215747 -0.023998 
+NCCSC -0.005856 0.751 P 
+NCCMH -0.005813 0.839 P 
+NCCADa -0.004093 0.800 P 
+NCJST -0.011004 0.791 P 
+NCHSP -0.003261 0.772 P 
+NCJHL -0.008583 0.731 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+NCJRR 0.065577 0.710 P 
+# 22271 30076454 -0.027002 
+NCCCOa -0.023903 0.823 P 
+# 21644 35109 0.052002 
+NCCCOa 0.039738 0.822 P 
+# 23190 42559 0.041000 
+NCCCOa 0.033461 0.710 P 
+# 23190 54084 -0.010000 
+NCCCOa -0.019628 0.862 P 
+# 42559 54084 -0.051000 
+NCCCOa -0.053419 0.721 P 
+# 22280 62514 0.015002 
+NCCCOa 0.013193 0.749 P 
+# 32049 62514 -0.010998 
+NCCCOa -0.010430 0.919 P 
+# 42643 62514 -0.052998 
+NCCCOa -0.043646 0.744 P 
+# 17842 62520 -0.020000 
+NCCCOa -0.033167 0.710 P 
+# 35109 67820 0.030997 
+NCCCOa 0.031302 0.970 P 
+# 23190 77218 -0.000999 
+NCCCOa -0.002993 0.876 P 
+# 42559 77218 -0.041999 
+NCCCOa -0.038710 0.734 P 
+# 54084 77218 0.009001 
+NCCCOa 0.016518 0.777 P 
+# 23190 101361 0.008000 
+NCCCOa -0.001325 0.964 P 
+# 42559 101361 -0.033000 
+NCCCOa -0.034886 0.746 P 
+# 54084 101361 0.018001 
+NCCCOa 0.018338 0.872 P 
+# 77218 101361 0.009000 
+NCCCOa 0.001529 0.872 P 
[…]

### 2011-12-06 paper2/diags/extra_hypoDD/subsample_hypoDDdata_to_stations.m

@@ -1,0 +1,196 @@
+function [] = subsample_hypoDDdata_to_stations()
+
+outputdir = './';
+
+%% get the events of interest
+% load the events of interest for which we get CWI data for the station CCO
+path2eventsoi ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/CalaverasMultiSim/CWI/stat1/events_oi.txt';
+copyfile(path2eventsoi)
+load events_oi.txt
+% Now split these into those that use travel time for all stations (eventlist_allstat)
+% and those that use info from CCO only (eventlis_substat). 
+eventlist_allstat = events_oi(23:end);
+eventlis_substat = events_oi(1:22);
+
+
+%
+% This function is used to subsample the hypoDD data to desired stations
+% (i.e. number_of_stats stations are sub-sampled from 
+% ../../CWI/importantstats.txt). A new set of subsampled hypoDD input files
+% are saved to outputdir. This function assumes that the input files have 
+% already been sub-sampled to the deisred events (for details see
+% subsample_hypoDDdata_to_69eq.m).
+%
+inputdatadir = ['/export/storage/davidr/sandpit/davidr/thesis_version2', ...
+                '/diags/eq_location_optimisation/CalaverasMultiSim/HYPODD2/',...
+                'runs/orig_68eqonly/'];
+
+%=============================================================
+% Read in the station data
+%s = importdata('../../CWI/importantstats.txt');
+% s = importdata('importantstats.txt');
+% importantstats_tmp = s.textdata(6:end);
+% importantstats_data_tmp = s.data;
+% importantstats = importantstats_tmp(1:number_of_stats);
+% importantstats_data = importantstats_data_tmp(1:number_of_stats,:);
+
+importantstats = {  'NCCAD','NCCCO','NCCMH','NCCSC','NCHSP','NCJAL', ... 
+                    'NCJCB','NCJHL','NCJRR','NCJST'};
+
+
+% ============================================================
+% Sub-sample the station file
+% ..... No need to do this because station file already copied over
+% ..... we copy the one with 10 stations
+
+
+
+% ============================================================
+% Sub-sample the dt.cc file
+events_rep1 = create_ttimefile('dt.cc',inputdatadir,outputdir,importantstats,eventlist_allstat,eventlis_substat);
+
+%===================================================
[…]

### 2011-12-06 paper2/diags/plot_2Dsynth_example1.m

@@ -1,0 +1,73 @@
+datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
+
+if strcmp(filesep,'/')
+    error('You must be on Windows to get the Latex Interpreter for these figures')
+end
+
+opttype = 'fortran'; % 'fortran' or 'matlab'
+load([datadir,'randsearch_',opttype,'.mat'])
+[sorted_x2, ind]=sort(xend(2,:));
+
+[nevnts, nrand] = size(xend);
+
+% Have a quick look at the solution space
+figure
+colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'}
+colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'}
+for i = 1:nevnts
+    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',10);
+    hold on
+    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',10);
+    hold on
+    plot([xend(i,:) E(i,1)], [yend(i,:) E(i,2)],'Color',[0.5 0.5 0.5],'linewidth',2)
+end
+plot([ 0 0], get(gca,'ylim'),'k')
+plot(get(gca,'xlim'),[0 0],'k')
+legend([h2,h1],{'Actual Location','Optimisation Soln'},'Location','NorthWest') 
+
+
+
+figure
+colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
+colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
+ind = find(f<-127.38);
+for i = 1:nevnts
+    h1 = plot(E(i,1), E(i,2), 'ko', 'markerfacecolor','w','markersize',10);
+    hold on
+    %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
+    for j = 1:length(ind)
+        h2 = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
+        hold on
+        plot([xend(i,ind(j)) E(i,1)], [yend(i,ind(j)) E(i,2)],'Color',[0.7 0.7 0.7],'linewidth',2,'markersize',10)
+    end
+end
[…]

### 2011-12-06 paper2/diags/plot_2Dsynth_example3.m

@@ -1,0 +1,73 @@
+datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
+
+if strcmp(filesep,'/')
+    error('You must be on Windows to get the Latex Interpreter for these figures')
+end
+
+opttype = 'fortran'; % 'fortran' or 'matlab'
+load([datadir,'randsearch_',opttype,'.mat'])
+[sorted_x2, ind]=sort(xend(2,:));
+
+[nevnts, nrand] = size(xend);
+
+% Have a quick look at the solution space
+figure
+colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'}
+colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'}
+for i = 1:nevnts
+    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',10);
+    hold on
+    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',10);
+    hold on
+    plot([xend(i,:) E(i,1)], [yend(i,:) E(i,2)],'Color',[0.5 0.5 0.5],'linewidth',2)
+end
+plot([ 0 0], get(gca,'ylim'),'k')
+plot(get(gca,'xlim'),[0 0],'k')
+legend([h2,h1],{'Actual Location','Optimisation Soln'},'Location','NorthWest') 
+
+
+
+figure
+colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
+colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
+ind = find(f<-127.38);
+for i = 1:nevnts
+    h1 = plot(E(i,1), E(i,2), 'ko', 'markerfacecolor','w','markersize',10);
+    hold on
+    %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
+    for j = 1:length(ind)
+        h2 = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
+        hold on
+        plot([xend(i,ind(j)) E(i,1)], [yend(i,ind(j)) E(i,2)],'Color',[0.7 0.7 0.7],'linewidth',2,'markersize',10)
+    end
+end
[…]

### 2011-12-06 paper2/diags/plot_calaveras_loc1.m

@@ -1,0 +1,1136 @@
+% The purpose of this script is to plot the Calaveras earthquake locations
+% IMPORTANT NOTE
+% .... This version (i.e. plot_calaveras_loc1.m utilises hypoDD with
+% .... LSQR method........
+
+%% Machine check - must be on notebook for best figure
+if strcmp(filesep,'/')
+    error('ERROR: must be on notebook for best figure quality')
+end
+
+%% Figure setup
+
+colorswitch = 'bw';  %'c'=>color OR 'bw'=>black/white
+switch colorswitch
+    case 'bw'
+        c1 = [0.7, 0.7, 0.7];   % background event - edge colour
+        c2 = 'k';               % event of interest - edge and face color
+        c3 = 'w';               % background event - face colour
+    case 'c'
+        c1 = 'b';               % background event - edge colour
+        c2 = 'r';               % event of interest - edge and face color
+        c3 = 'b';               % background event - face colour
+end
+
+
+
+plot_struct.xlimits = [-500 500];
+plot_struct.ylimits = [-500 500];
+plot_struct.zlimits = [-2000 2000];
+plot_struct.axes_posy = [5,3,6,6];
+plot_struct.xtickspots = [-250 0 250];
+plot_struct.ytickspots = [-250 0 250];
+plot_struct.ztickspots = [-1000 0 1000];
+plot_struct.zticklabels =[-1000, 0, 1000];
+plot_struct.fsize = 10;
+plot_struct.msize = 2;
+
+awidth = 3; % width of axis in centimeters
+aheight = 3; % height of axis in centimeters
+hgap = 0.2; % horizontal gap in centimeters
+vgap = 0.2; % vertical gap in centimeters
+ax_start = 1.7;
+ay_start = 0.7;
+
+
+%% Load inputdata
+events_oi = load('../../../thesis_version2/diags/eq_location_optimisation/events_oi.txt');
+
+CatLoc = load('../../../thesis_version2/diags/eq_location_optimisation/Calaveras_cat_locations.txt'); 
+[n m] = size(CatLoc); 
+CatLoc_68 = [];
[…]

### 2011-12-06 paper2/diags/plot_calaveras_loc2.m

@@ -1,0 +1,818 @@
+% The purpose of this script is to plot the Calaveras earthquake locations
+% IMPORTANT NOTE
+% .... This version (i.e. plot_calaveras_loc2.m utilises hypoDD with
+% .... SVD ........
+
+%% Machine check - must be on notebook for best figure
+if strcmp(filesep,'/')
+    error('ERROR: must be on notebook for best figure quality')
+end
+
+%% Figure setup
+
+colorswitch = 'bw';  %'c'=>color OR 'bw'=>black/white
+switch colorswitch
+    case 'bw'
+        c1 = [0.7, 0.7, 0.7];   % background event - edge colour
+        c2 = 'k';               % event of interest - edge and face color
+        c3 = 'w';               % background event - face colour
+    case 'c'
+        c1 = 'b';               % background event - edge colour
+        c2 = 'r';               % event of interest - edge and face color
+        c3 = 'b';               % background event - face colour
+end
+
+
+
+plot_struct.xlimits = [-500 500];
+plot_struct.ylimits = [-500 500];
+plot_struct.zlimits = [-2000 2000];
+plot_struct.axes_posy = [5,3,6,6];
+plot_struct.xtickspots = [-250 0 250];
+plot_struct.ytickspots = [-250 0 250];
+plot_struct.ztickspots = [-1000 0 1000];
+plot_struct.zticklabels =[-1000, 0, 1000];
+plot_struct.fsize = 10;
+plot_struct.msize = 2;
+
+awidth = 3; % width of axis in centimeters
+aheight = 3; % height of axis in centimeters
+hgap = 0.2; % horizontal gap in centimeters
+vgap = 0.2; % vertical gap in centimeters
+ax_start = 1.7;
+ay_start = 0.7;
+
+
+%% Load inputdata
+events_oi = load('../../../thesis_version2/diags/eq_location_optimisation/events_oi.txt');
+
+CatLoc = load('../../../thesis_version2/diags/eq_location_optimisation/Calaveras_cat_locations.txt'); 
+[n m] = size(CatLoc); 
+CatLoc_68 = [];
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/aprod.f

@@ -1,0 +1,60 @@
+c Multiply a matrix by a vector
+c  Version for use with sparse matrix specified by
+c  output of subroutine sparse for use with LSQR
+
+	subroutine aprod(mode, m, n, x, y, leniw, lenrw, iw, rw)
+
+	implicit none
+
+c	Parameters:
+	integer	mode		! ==1: Compute  y = y + a*x
+				! 	y is altered without changing x
+				! ==2: Compute  x = x + a(transpose)*y
+				!	x is altered without changing y
+	integer	m, n		! Row and column dimensions of a
+	real	x(n), y(m)	! Input vectors
+	integer	leniw, lenrw
+	integer	iw(leniw)	! Integer work vector containing:
+				! iw[1]  Number of non-zero elements in a
+				! iw[2:iw[1]+1]  Row indices of non-zero elements
+				! iw[iw[1]+2:2*iw[1]+1]  Column indices
+	real	rw(lenrw)	! [1..iw[1]] Non-zero elements of a
+
+c	Local variables:
+	integer i1
+	integer j1
+	integer k
+	integer kk
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/aprod.f,v 1.5 2001/02/02 21:30:44 julian Exp julian $"/
+	save rcsid
+
+c	set the ranges the indices in vector iw
+
+	kk=iw(1)
+	i1=1
+	j1=kk+1
+
+c	main iteration loop
+
+	do 100 k = 1,kk
+
+	if (mode.eq.1) then
+
+c	compute  y = y + a*x
+
+	y(iw(i1+k)) = y(iw(i1+k)) + rw(k)*x(iw(j1+k))
+
+	else
+
+c	compute  x = x + a(transpose)*y
+
+	x(iw(j1+k)) = x(iw(j1+k)) + rw(k)*y(iw(i1+k))
+
+	endif
+
+  100	continue
+
+	return
+	end

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/cluster1.f

@@ -1,0 +1,194 @@
+	subroutine cluster1(log, nev, ndt,
+     &	idata, minobs_cc, minobs_ct,
+     &	dt_c1, dt_c2, ev_cusp,
+     &	clust, noclust, nclust)
+
+	implicit none
+
+	include'hypoDD.inc'
+
+c	Parameters:
+	integer		log		! Log-file identifier
+	integer		nev		! No. of events
+	integer		ndt		! No. of data
+	integer		idata
+	integer		minobs_cc	! Min. obs./pair for ccor. data
+	integer		minobs_ct	! Min. obs./pair for cat. data
+	integer		dt_c1(MAXDATA)	! [1..ndt] Event keys
+	integer		dt_c2(MAXDATA)	! [1..ndt] Event keys
+	integer		ev_cusp(MAXEVE)	! [1..nev] Event keys
+	integer		clust(MAXCL,MAXEVE) ! [1..nclust,1..] Event keys
+					! clust[i,1] = Size of ith cluster
+	integer		noclust(MAXEVE)	! [1..MAXEVE] Event keys
+					! noclust[1] = No. of keys
+	integer		nclust		! No. of cllusters
+
+c	Local variables:
+	integer		acli(MAXEVE)
+	integer		acl(MAXEVE)
+	integer		apair_n((MAXEVE*(MAXEVE-1))/2)
+	integer		i
+	integer		ia
+	integer		icusp(MAXEVE)	! [1..nev] Event keys
+	integer		ifindi
+	integer		ii
+	integer		j
+	integer		k
+	integer		kk
+	integer		n
+	integer		nn
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/hypoDD/RCS/cluster1.f,v 1.12 2001/02/17 01:20:49 julian Exp $"/
+	save rcsid
+
+      write(*,'("clustering ...  ")')
+      write(log,'(/,"~ clustering ...  ")')
+
+c     Set up event-pair arrays
+      k = 0
+      do i=2,nev
+         do j=1,i-1		!lower triangle of matrix
+            k = k+1
+            apair_n(k) = 0
+         enddo
+      enddo
+
+      do i=1,nev
+         icusp(i) = ev_cusp(i)
+      enddo
+      call sorti(nev, icusp)
+
+      do i=1, ndt
+         j = ifindi(nev, icusp, dt_c1(i))
+         k = ifindi(nev, icusp, dt_c2(i))
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/delaz2.f

@@ -1,0 +1,99 @@
+c Compute distance and azimuth on a sphere
+c changes by Felix Waldhauser (fw)
+
+	subroutine delaz2(alat, alon, blat, blon, del, dist, az)
+
+	implicit none
+
+	doubleprecision	alat, alon	! Coordinates of first point
+	real		blat, blon	! Coordinates of second point
+	real		del		! Sentral angle (degrees)
+	real		dist		! Distance (km)
+	real		az		! Azimuth from a to b (degrees)
+
+C	Local variables:
+	doubleprecision	acol, bcol
+	doubleprecision	azr
+	doubleprecision	blatr, blonr
+	doubleprecision	colat
+	doubleprecision	cosdel
+	doubleprecision	delr
+	doubleprecision	flat
+	doubleprecision	geoa
+	doubleprecision	geob
+	doubleprecision	rad
+	doubleprecision	radius
+	doubleprecision alatr, alonr
+	doubleprecision diflon
+	doubleprecision pi2
+	doubleprecision tana, tanb
+cfw	real		xtop, xden	! see comments below
+	doubleprecision top, den
+
+c	Built-in functions: Declarations not needed
+	doubleprecision dtan
+	doubleprecision	datan
+	doubleprecision	dsin
+	doubleprecision	dcos
+	doubleprecision	dacos
+
+c	doubleprecision top,den
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/delaz2.f,v 1.6 2001/02/09 01:48:17 julian Exp julian $"/
+	save rcsid
+
+	data pi2/1.570796d0/
+	data rad/1.745329d-02/
+	data flat/.993231d0/
+
+c-----convert to radians
+	alatr=alat*rad
+	alonr=alon*rad
+	blatr=blat*rad
+	blonr=blon*rad
+c-----convert latitudes to geocentric colatitudes
+	tana=flat*dtan(alatr)
+	geoa=datan(tana)
+	acol=pi2-geoa
+	tanb=flat*dtan(blatr)
+	geob=datan(tanb)
+	bcol=pi2-geob
+c-----calculate delta
+	diflon=blonr-alonr
+	cosdel=dsin(acol)*dsin(bcol)*dcos(diflon)+dcos(acol)*
+     &	dcos(bcol)
+	delr=dacos(cosdel)
+c-----calculate azimuth from a to b
+
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/dtres.f

@@ -1,0 +1,71 @@
+	subroutine dtres(log, ndt, stdim, nsrc,
+     &	dt_dt, dt_idx,
+     &	dt_ista, dt_ic1, dt_ic2,
+     &	src_cusp, src_t, tmp_ttp, tmp_tts,
+     &	dt_cal, dt_res)
+
+	implicit none
+
+	include'hypoDD.inc'
+
+c	Parameters:
+	integer		log		! Log-file identifier
+	integer		ndt		! No. of data
+	integer		stdim		! Column dimenson of arrays tmp_tt[ps]
+	integer		nsrc		! No. of sources
+	real		dt_dt(MAXDATA)	! [1..ndt] Observed time differences
+	integer		dt_idx(MAXDATA)	! [1..ndt]
+	integer		dt_ista(MAXDATA)! [1..ndt] Station indices
+	integer		dt_ic1(MAXDATA)	! [1..ndt] Event indices
+	integer		dt_ic2(MAXDATA)	! [1..ndt] Event indices
+	integer		src_cusp(MAXEVE)! [1..nsrc] Event keys
+	real		src_t(MAXEVE)	! [1..nsrc] Event times
+	real		tmp_ttp(stdim,MAXEVE)! [1.., 1..nsrc]
+	real		tmp_tts(stdim,MAXEVE)! [1.., 1..nsrc]
+	real		dt_cal(MAXDATA)	! [1..ndt] Theoretical time differences
+	real		dt_res(MAXDATA)	! [1..ndt] Time-difference residuals
+
+c	Local variables:
+	integer		i
+	real		tt1, tt2
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/dtres.f,v 1.12 2001/03/09 22:17:32 dinger Exp julian $"/
+	save rcsid
+
+      write(log,'("~ getting residual vector...")')
+
+      if (nsrc.eq.1) then
+c        Single source
+         do i=1,ndt
+            dt_res(i) = dt_dt(i)
+         enddo
+      else
+c        Mulitple sources
+	 tt1 = 0.0
+	 tt2 = 0.0
+         do i=1,ndt
+            if (dt_idx(i).eq.1 .or. dt_idx(i).eq.3) then
+c              P phase
+               tt1 = tmp_ttp(dt_ista(i),dt_ic1(i)) -
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/getdata.f

@@ -1,0 +1,609 @@
+c Read in data
+
+	subroutine getdata(
+     &	log, fn_cc, fn_ct, fn_sta, fn_eve, fn_srcpar,
+     &	idata, iphase, ncusp, icusp,
+     &  maxdist,maxsep_ct,maxsep_cc,
+     &	noisef_dt, mod_nl, mod_ratio, mod_v, mod_top,
+     &	ev_date, ev_time, ev_cusp, ev_lat, ev_lon, ev_dep,
+     &	ev_mag, ev_herr, ev_zerr, ev_res,
+     &	sta_lab, sta_lat, sta_lon,
+     &	dt_sta, dt_dt, dt_qual, dt_c1, dt_c2, dt_idx,
+     &	dt_ista, dt_ic1, dt_ic2,dt_offs,
+     &	nev, nsta, ndt, nccp, nccs, nctp, ncts,
+     &	tmp_xp, tmp_yp, tmp_zp, tmp_ttp, tmp_tts)
+
+	implicit none
+
+	include 'hypoDD.inc'
+
+c	Parameters:
+	doubleprecision	atoangle	! ASCII-to-angle function
+	integer		log
+	character*80	fn_cc, fn_ct, fn_sta, fn_eve, fn_srcpar
+	integer		idata
+	integer		iphase
+	integer		ncusp		! No. of events to relocate
+	integer		icusp(MAXEVE)	! [1..ncusp] Keys of events to relocate
+	real		maxdist
+	real		maxsep_ct
+	real		maxsep_cc
+	real		noisef_dt
+	integer		mod_nl
+	real		mod_ratio
+	real		mod_v(MAXLAY)	! [1..MAXLAY]
+	real		mod_top(MAXLAY)	! [1..MAXLAY]
+	integer		ev_date(MAXEVE)	! [1..MAXEVE]
+	integer		ev_time(MAXEVE)	! [1..MAXEVE]
+	integer		ev_cusp(MAXEVE)	! [1..nev] Event keys
+	real		ev_lat(MAXEVE)	! [1..nev]
+	real		ev_lon(MAXEVE)	! [1..nev]
+	real		ev_dep(MAXEVE)	! [1..nev]
+	real		ev_mag(MAXEVE)	! [1..nev]
+	real		ev_herr(MAXEVE)	! [1..nev]
+	real		ev_zerr(MAXEVE)	! [1..nev]
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/getinp.f

@@ -1,0 +1,223 @@
+c Get input parameters
+
+	subroutine getinp (maxev,maxlyr,log,fn_inp,
+     &	fn_cc, fn_ct, fn_sta, fn_eve,
+     &	fn_loc, fn_reloc, fn_res, fn_stares, fn_srcpar,
+     &	idata, iphase,
+     &	minobs_cc, minobs_ct,
+     &	amaxres_cross, amaxres_net, amaxdcc, amaxdct,
+     &	noisef_dt, maxdist,
+     &	awt_ccp, awt_ccs, awt_ctp, awt_cts, adamp,
+     &	istart, maxiter, isolv, niter, aiter,
+     &	mod_nl, mod_ratio, mod_v, mod_top,
+     &	iclust, ncusp, icusp)
+
+	implicit none
+
+c	Parameters:
+	integer		maxev		! Array dimension
+	integer		maxlyr		! Array dimension
+	integer		log		! Log-file identifier
+	character	fn_inp*80	! File of control info.
+	character	fn_cc*80	! File of cross-corr. times
+	character	fn_ct*80	! File of catalog times
+	character	fn_sta*80	! Station file
+	character	fn_eve*80	! Event file
+	character	fn_loc*80	! Output file of original locs.
+	character	fn_reloc*80	! Output file of final locs.
+	character	fn_res*80	! Output residual file
+	character	fn_stares*80	! Output station file
+	character	fn_srcpar*80	! Output source-parameter file
+	integer		idata		! 0: Synthetics
+					! 1: Cross-correlation
+					! 2: Catalog
+					! 3: Both
+	integer		iphase		! 1: P; 2: S; 3: Both
+	integer		minobs_cc	! Min. obs./pair for ccor. data
+	integer		minobs_ct	! Min. obs./pair for cat. data
+	real		amaxres_cross(10)! [1..niter] Ccor. res. thresh.
+	real		amaxres_net(10)	! [1..niter] Cat. res. thresh.
+	real		amaxdcc(10)	! [1..niter] Ccor. link-dist. limit
+	real		amaxdct(10)	! [1..niter] Cat. link-dist. limit
+	real		noisef_dt	! Synthetic noise
+	real		maxdist		! Max. cluster-station distance
+	real		awt_ccp(10)	! [1..niter] Wts. for ccor. P
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/hypoDD.f

@@ -1,0 +1,969 @@
+      program hypoDD
+
+c Author: Felix Waldhauser, felixw@ldeo.columbia.edu
+c Version 1.1 - 10/2004 - FW 
+c
+c started 03/1999 
+c 01-03/2001  clean up & bug fixes by Bruce Julian, Fred Klein, Keith
+c             Richards-Dinger, Felix Waldhauser 
+c 10/2004     Version 1.1: fixed errors listed in BugList to V 1.0.
+c
+c Purpose:
+c Program to determine high-resolution hypocenter locations using the
+c double-difference algorithm. hypoDD incorporates catalog and/or cross
+c correlation P- and/or S-wave relative travel-time measurements.
+c Residuals between observed and theoretical travel time differences
+c (or double-differences = DD) are minimized for pairs
+c of earthquakes at each station while linking together all observed
+c event/station pairs. A least squares solution (SVD or LSQR) is found
+c by iteratively adjusting the vector difference between hypocentral pairs.
+c
+c References:
+c For a detailed description of the algorithm see:
+c    Waldhauser, F. and W.L. Ellsworth, A double-difference earthquake
+c    location algorithm: Method and application to the northern Hayward
+c    fault, Bull. Seismol. Soc. Am., 90, 1353-1368, 2000.
+c
+c For a user guide to hypoDD see USGS open-file report: 
+c    Waldhauser, F., HypoDD: A computer program to compute double-difference 
+c    earthquake locations,  U.S. Geol. Surv. open-file report , 01-113, 
+c    Menlo Park, California, 2001.
+c
+c The code is continuously being updated and improved, so feel
+c free to send me an occasional request for the newest version:
+c felixw@ldeo.columbia.edu  
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/lsfit_lsqr.f

@@ -1,0 +1,371 @@
+	subroutine lsfit_lsqr(log, iter, ndt, nev, nsrc,
+     &	damp, mod_ratio,
+     &	idata, ev_cusp, src_cusp,
+     &	dt_res, dt_wt,
+     &	dt_ista, dt_ic1, dt_ic2,
+     &	src_dx, src_dy, src_dz, src_dt, src_ex, src_ey, src_ez, src_et,
+     &	exav, eyav, ezav, etav, dxav, dyav, dzav, dtav,
+     &	rms_cc, rms_ct, rms_cc0, rms_ct0,
+     &	rms_ccold, rms_ctold, rms_cc0old, rms_ct0old,
+     &	tmp_xp, tmp_yp, tmp_zp, dt_idx, acond)
+
+	implicit none
+
+	include'hypoDD.inc'
+
+c	Parameters:
+	integer		log		! Log-file identifier
+	integer		iter
+	integer		ndt
+	integer		nev
+	integer		nsrc
+	real		damp
+	real		mod_ratio
+	integer		idata
+	integer		ev_cusp(MAXEVE)	! [1..nev] Event keys
+	integer		src_cusp(MAXEVE)! [1..nev] Event keys
+	real		dt_res(MAXDATA)	! [1..ndt]
+	real		dt_wt(MAXDATA)	! [1..ndt]
+	integer		dt_ista(MAXDATA)! [1..ndt]
+	integer		dt_ic1(MAXDATA)	! [1..ndt]
+	integer		dt_ic2(MAXDATA)	! [1..ndt]
+	real		src_dx(MAXEVE)	! [1..nev]
+	real		src_dy(MAXEVE)	! [1..nev]
+	real		src_dz(MAXEVE)	! [1..nev]
+	real		src_dt(MAXEVE)	! [1..nev]
+	real		src_ex(MAXEVE)	! [1..nev]
+	real		src_ey(MAXEVE)	! [1..nev]
+	real		src_ez(MAXEVE)	! [1..nev]
+	real		src_et(MAXEVE)	! [1..nev]
+	real		exav
+	real		eyav
+	real		ezav
+	real		etav
+	real		dxav
+	real		dyav
+	real		dzav
+	real		dtav
+	real		rms_cc
+	real		rms_ct
+	real		rms_cc0
+	real		rms_ct0
+	real		tmp_xp(MAXSTA,MAXEVE)! [1.., 1..nev]
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/lsfit_svd.f

@@ -1,0 +1,359 @@
+	subroutine lsfit_svd(log, iter, ndt, nev, nsrc, damp, mod_ratio,
+     &	idata, ev_cusp, src_cusp,
+     &	dt_res, dt_wt,
+     &	dt_ista, dt_ic1, dt_ic2,   
+     &	src_dx, src_dy, src_dz, src_dt, src_ex, src_ey, src_ez, src_et,
+     &	exav, eyav, ezav, etav, dxav, dyav, dzav, dtav,
+     &	rms_cc, rms_ct, rms_cc0, rms_ct0,
+     &	rms_ccold, rms_ctold, rms_cc0old, rms_ct0old,
+     &	tmp_xp, tmp_yp, tmp_zp, dt_idx)
+
+	implicit none
+
+	include 'hypoDD.inc'
+
+c	Parameters:
+	integer		log
+	integer		iter
+	integer		ndt
+	integer		nev
+	integer		nsrc
+	real		damp
+	real		mod_ratio
+	integer		idata
+	integer		ev_cusp(MAXEVE)	! (1..MAXEVE)
+	integer		src_cusp(MAXEVE)	! (1..MAXEVE)
+	real		dt_res(MAXDATA)	! (1..MAXDATA)
+	real		dt_wt(MAXDATA)	! (1..MAXDATA)
+	integer		dt_ista(MAXDATA)	! (1..MAXDATA)
+	integer		dt_ic1(MAXDATA)	! (1..MAXDATA)
+	integer		dt_ic2(MAXDATA)	! (1..MAXDATA)
+	real		src_dx(MAXEVE)	! (1..MAXEVE)
+	real		src_dy(MAXEVE)	! (1..MAXEVE)
+	real		src_dz(MAXEVE)	! (1..MAXEVE)
+	real		src_dt(MAXEVE)	! (1..MAXEVE)
+	real		src_ex(MAXEVE)	! (1..MAXEVE)
+	real		src_ey(MAXEVE)	! (1..MAXEVE)
+	real		src_ez(MAXEVE)	! (1..MAXEVE)
+	real		src_et(MAXEVE)	! (1..MAXEVE)
+	real		exav
+	real		eyav
+	real		ezav
+	real		etav
+	real		dxav
+	real		dyav
+	real		dzav
+	real		dtav
+	real		rms_cc
+	real		rms_ct
+	real		rms_cc0
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/partials.f

@@ -1,0 +1,109 @@
+	subroutine partials(fn_srcpar,
+     &	nsrc, src_cusp, src_lat, src_lon, src_dep,
+     &	nsta, sta_lab, sta_lat, sta_lon,
+     &	mod_nl, mod_ratio, mod_v, mod_top,
+     &	tmp_ttp, tmp_tts,
+     &	tmp_xp, tmp_yp, tmp_zp)
+
+	implicit none
+
+	include'hypoDD.inc'
+
+c	Parameters:
+	character	fn_srcpar*80	! Source-parameter file
+	integer		nsrc		! No. of sources
+	integer		src_cusp(MAXEVE)! [1..nsrc]
+	doubleprecision	src_lat(MAXEVE)	! [1..nsrc]
+	doubleprecision	src_lon(MAXEVE)	! [1..nsrc]
+	real		src_dep(MAXEVE)	! [1..nsrc]
+	integer		nsta		! No. of stations
+	character	sta_lab(MAXSTA)*7! [1..nsta]
+	real		sta_lat(MAXSTA)	! [1..nsta]
+	real		sta_lon(MAXSTA)	! [1..nsta]
+	integer		mod_nl		! No. of layers
+	real		mod_ratio	! Vp/Vs
+	real		mod_v(MAXLAY)	! [1..mod_nl]
+	real		mod_top(MAXLAY)	! [1..mod_nl]
+	real		tmp_ttp(MAXSTA,MAXEVE)! [1..nsta,1..nsrc]
+	real		tmp_tts(MAXSTA,MAXEVE)! [1..nsta,1..nsrc]
+	real		tmp_xp(MAXSTA,MAXEVE)! [1..nsta,1..nsrc]
+	real		tmp_yp(MAXSTA,MAXEVE)! [1..nsta,1..nsrc]
+	real		tmp_zp(MAXSTA,MAXEVE)! [1..nsta,1..nsrc]
+
+c	Local variables:
+	real		ain
+	real		az
+	real		del
+	real		dist
+	integer		i, j, k
+	integer		iunit		! Output unit number
+	real		pi
+	integer		trimlen
+        real            vs(MAXLAY)
+
+	parameter(pi=3.141593)
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/partials.f,v 1.7 2001/02/17 23:54:57 julian Exp julian $"/
+	save rcsid
+
+      iunit = 0
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/ran.f

@@ -1,0 +1,26 @@
+c Pseudo-random number generator
+c Numerical Recipes, p. 274
+
+	subroutine ran(jlo, jhi, j)
+
+	implicit none
+
+c	Parameters:
+	real	jlo, jhi	! Limit values (changed)
+	real	j
+
+c	Local variables:
+	integer	im, ia, ic
+	real	jran
+
+	parameter (im= 714025, ia= 4096, ic= 150889)
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/ran.f,v 1.4 2001/02/06 03:04:35 julian Exp julian $"/
+	save rcsid
+
+      jhi=jhi-1.0
+      jran= mod(jran*ia+ic,im)         ! generator
+      j= jlo+((jhi-jlo+1)*jran)/im
+      return
+      end

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/refract.f

@@ -1,0 +1,169 @@
+c Find "refracted" ray with smallest travel time
+
+	subroutine refract (nl, v, vsq, thk, jl, tkj, delta,
+     &	kk, tref, xovmax)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer	nl
+	real	v(MAXLAY)
+	real	vsq(MAXLAY)
+	real	thk(MAXLAY)
+	integer	jl
+	real	tkj
+	integer	kk
+	real	tref
+	real	xovmax
+
+c       For refracted rays in a layered earth model, refract
+c  determines the fastest travel time, tref, the layer
+c  in which the fastest ray is refracted, kk, the
+c  critical distance for refraction in that layer,
+c  didjkk, and an upper bound on delta for which a
+c  direct ray can be a first arrival, xovmax.  Refract
+c  allows for the possibility of low velocity layers.
+c       Note that there may not be a refracted ray, either because
+c  all layers below the event layer are low velocity layers or
+c  because for all layers below the event layer which are not low
+c  velocity layers the critical distance exceeds delta.  In such
+c  cases tref, didjkk, and xovmax are set very large, kk is set to
+c  zero, and refract returns to the calling program.
+c
+c  input:  nl - number of layers
+c        v(l) - velocity of layer l
+c      vsq(l) - v(l) ** 2
+c      thk(l) - thickness of layer l
+c          jl - event layer
+c         tkj - depth of event in event layer
+c       delta - horizontal distance between event and receiver
+c
+c  output:   kk - refracting layer for fastest refracted ray
+c          tref - travel time of fastest refracted ray
+c        didjkk - critical distance for refraction in layer kk
+c        xovmax - an upper bound on delta for which the direct ray can
+c                       be the first arrival
+c  internal arrays:
+c
+c       tr(m) - travel time for refraction in layer m
+c     tinj(m) - traveltime intercept
+c      tid(m) - terms in travel time intercept which are
+c                     independent of tkj
+c     didj(m) - critical distance
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/resstat.f

@@ -1,0 +1,197 @@
+c Calculate residual statistics
+
+	subroutine resstat(log, idata, ndt, nev, d, w, idx,
+     &	rms_cc, rms_ct, rms_cc0, rms_ct0,
+     &	rms_ccold, rms_ctold, rms_cc0old, rms_ct0old,
+     &                   dum)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer	log
+	integer	idata
+	integer	ndt
+	integer	nev
+	real	d(MAXDATA)	! (1..ndt)
+	real	w(MAXDATA)	! (1..ndt)
+	integer	idx(MAXDATA)	! (1..ndt)
+	real	rms_cc
+	real	rms_ct
+	real	rms_cc0
+	real	rms_ct0
+	real	rms_ccold
+	real	rms_ctold
+	real	rms_cc0old
+	real	rms_ct0old
+	real	dum
+
+c	Local variables:
+	real	av_cc
+	real	av_cc0
+	real	av_ct
+	real	av_ct0
+	real	dav
+	real	dav0
+	real	dav1
+	real	dav1old
+	real	davold
+	real	dvar
+	real	dvar1
+	real	dvar1old
+	real	dvarold
+	real	f
+	real	f_cc
+	real	f_ct
+	integer	i, j
+	real	s
+	real	s1
+	real	ss
+	real	ss1
+	real	sw
+	real	sw_cc
+	real	sw_ct
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/resstat.f,v 1.10 2001/03/07 04:43:09 felix Exp julian $"/
+	save rcsid
+
+c--- get rms:
+      rms_cc0old= rms_cc0
+      rms_ct0old= rms_ct0
+      rms_ccold= rms_cc
+      rms_ctold= rms_ct
+      j= 0
+      sw_cc= 0
+      sw_ct= 0
+      do i= 1,ndt
+         if(idx(i).le.2) then
+             sw_cc= sw_cc + w(i)
+             j= j+1
+         else
+             sw_ct= sw_ct + w(i)
+         endif
+      enddo
+      f_cc= j/sw_cc  ! factor to scale weights for rms value
+      f_ct= (ndt-j)/sw_ct  ! factor to scale weights for rms value
+
+      rms_cc0= 0
+      rms_ct0= 0
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/skip.f

@@ -1,0 +1,273 @@
+	subroutine skip(log, kiter, minwght,
+     &	ndt, nev, nsrc, nsta,
+     &	ev_cusp, ev_date, ev_time, ev_mag,
+     &	ev_lat, ev_lon, ev_dep, ev_x, ev_y, ev_z,
+     &	ev_herr, ev_zerr, ev_res,
+     &	src_cusp, src_lat, src_lon, src_dep,
+     &	src_lat0, src_lon0,
+     &	src_x, src_y, src_z, src_t, src_x0, src_y0, src_z0, src_t0,
+     &	sta_lab, sta_lat, sta_lon, sta_dist, sta_az,
+     &	sta_rmsc, sta_rmsn, sta_np, sta_ns, sta_nnp, sta_nns,
+     &	dt_sta, dt_c1, dt_c2, dt_idx, dt_dt, dt_qual, dt_cal,
+     &	dt_ista, dt_ic1, dt_ic2,
+     &	dt_res, dt_wt, dt_offs,
+     &	tmp_ttp, tmp_tts, tmp_xp, tmp_yp, tmp_zp, nct, ncc)
+
+	implicit none
+
+	include'hypoDD.inc'
+
+c	Parameters:
+	integer		log
+	integer		kiter
+	real		minwght
+	integer		ndt
+	integer		nev
+	integer		nsrc
+	integer		nsta
+	integer		ev_cusp(MAXEVE)	! [1..MAXEVE]
+	integer		ev_date(MAXEVE)	! [1..MAXEVE]
+	integer		ev_time(MAXEVE)	! [1..MAXEVE]
+	real		ev_mag(MAXEVE)	! [1..MAXEVE]
+	real		ev_lat(MAXEVE)	! [1..MAXEVE]
+	real		ev_lon(MAXEVE)	! [1..MAXEVE]
+	real		ev_dep(MAXEVE)	! [1..MAXEVE]
+	real		ev_x(MAXEVE)	! [1..MAXEVE]
+	real		ev_y(MAXEVE)	! [1..MAXEVE]
+	real		ev_z(MAXEVE)	! [1..MAXEVE]
+	real		ev_herr(MAXEVE)	! [1..MAXEVE]
+	real		ev_zerr(MAXEVE)	! [1..MAXEVE]
+	real		ev_res(MAXEVE)	! [1..MAXEVE]
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/tiddid.f

@@ -1,0 +1,96 @@
+c Compute intercept times and critical distances for "refracted" rays
+
+	subroutine tiddid (jl, nl, v, vsq, thk, tid, did)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer	jl
+	integer	nl
+	real	v(MAXLAY)	! (1..nl)
+	real	vsq(MAXLAY)	! (1..nl)
+	real	thk(MAXLAY)	! (1..nl)
+	real	tid(20)	! (1..20)
+	real	did(20)	! (1..20)
+
+c       Determines the travel time intercept and critical
+c  distance for a seismic ray in a layered earth model
+c  originating at the top of layer jl, refracting in
+c  layer m, and terminating at the top of layer 1.
+c
+c  input:       jl - event layer
+c               nl - number of layers
+c             v(l) - velocity of layer l
+c           vsq(l) - velocity squared
+c           thk(l) - thickness of layer l
+c  output:
+c           tid(m) - travel time intercept for
+c                      refraction in layer m
+c           did(m) - critical distance
+
+c	Local variables:
+	real	did1, did2
+	real	dimm
+	integer	j1
+	integer	l
+	integer	m
+	integer	m1
+	real	sqt
+	real	tid1, tid2
+	real	tim
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/tiddid.f,v 1.7 2001/02/13 23:50:58 julian Exp julian $"/
+	save rcsid
+
+      j1=jl+1
+      do 23174m=j1,nl
+      tid(m)=0.
+      did(m)=0.
+      tid1=0.
+      tid2=0.
+      did1=0.
+      did2=0.
+      m1=m-1
+      do 23176l=1,m1
+      if(.not.(vsq(m).le.vsq(l)))goto 23178
+
+c   if m is a low velocity layer, set tid and did to
+c   very large values
+
+      tid(m)=100000.
+      did(m)=100000.
+      goto 23179
+23178 continue
+      sqt=sqrt(vsq(m)-vsq(l))
+      tim=thk(l)*sqt/(v(l)*v(m))
+      dimm=thk(l)*v(l)/sqt
+      if(.not.(l.lt.jl))goto 23180
+
+c   sum for layers above event layer
+
+      tid1=tid1+tim
+      did1=did1+dimm
+      goto 23181
+23180 continue
+
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/trialsrc.f

@@ -1,0 +1,90 @@
+
+	subroutine trialsrc(istart, sdc0_lat, sdc0_lon, sdc0_dep,
+     &	nev, ev_cusp, ev_lat, ev_lon, ev_dep,
+     &	nsrc, src_cusp, src_lat0, src_lon0,
+     &	src_x0, src_y0, src_z0, src_t0,
+     &	src_lat, src_lon, src_dep,
+     &	src_x, src_y, src_z, src_t)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer		istart
+	real		sdc0_lat	! Cluster center
+	real		sdc0_lon	! Cluster center
+	real		sdc0_dep	! Cluster center
+	integer		nev		! No. of events
+	integer		ev_cusp(MAXEVE)	! [1..nev]
+	real		ev_lat(MAXEVE)	! [1..nev]
+	real		ev_lon(MAXEVE)	! [1..nev]
+	real		ev_dep(MAXEVE)	! [1..nev]
+	integer		nsrc		! No of trial sources
+	integer		src_cusp(MAXEVE)! [1..nev]
+	real		src_lat0(MAXEVE)! [1..nev]
+	real		src_lon0(MAXEVE)! [1..nev]
+	real		src_x0(MAXEVE)	! [1..nev]
+	real		src_y0(MAXEVE)	! [1..nev]
+	real		src_z0(MAXEVE)	! [1..nev]
+	real		src_t0(MAXEVE)	! [1..nev]
+	doubleprecision	src_lat(MAXEVE)	! [1..nev]
+	doubleprecision	src_lon(MAXEVE)	! [1..nev]
+	real		src_dep(MAXEVE)	! [1..nev]
+	real		src_x(MAXEVE)	! [1..nev]
+	real		src_y(MAXEVE)	! [1..nev]
+	real		src_z(MAXEVE)	! [1..nev]
+	real		src_t(MAXEVE)	! [1..nev]
+
+c	Local variables:
+	integer	i
+	real	x, y
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/trialsrc.f,v 1.8 2001/02/19 00:42:25 julian Exp julian $"/
+	save rcsid
+
+c     Set up parameters for initial inversion
+      if (istart.eq.1) then
+c        Cluster center as initial trial source
+         nsrc = 1
+         do i=1,nev
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/ttime.f

@@ -1,0 +1,120 @@
+c Determine the fastest traveltime between a source
+c at depth=depth(km) and a receiver at distance=delta(km).
+
+	subroutine ttime(delta, depth, nl, v, top, t, ain)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	real	delta
+	real	depth
+	integer	nl
+	real	v(MAXLAY)
+	real	top(MAXLAY)
+	real	t
+	real	ain
+
+c	Local variables:
+	integer	jl
+	integer	kk
+	real	tdir
+	real	thk(20)
+	real	tkj
+	real	tref
+	real	u
+	real	vsq(20)
+	real	x
+	real	xovmax
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/ttime.f,v 1.5 2001/02/13 23:50:58 julian Exp julian $"/
+	save rcsid
+
+c	compile and link for S
+c	f77 -c ttime.f
+c	ld -r -dn ttime.o
+c	mv a.out ttime.o
+
+c	subroutine direct1 is used to compute the direct ray
+c	traveltime and sine of takeoff angle.
+
+c	subroutine refract is used to compute the fastest
+c	refracted ray traveltime.  It calls subroutine tiddid.
+
+c	subroutine vmodel extract needed information from the
+c	layered velocity model.
+
+c	input:
+c	delta	epicentral distance in km
+c	depth	focal depth of source in km
+c	nl	number of layers in velocity model
+c	v	velocity in each layer
+c	top	depth to top of layer
+
+c	output:
+c	t	minimum traveltime
+c	ain	angle of emergence at source
+
+
+c	call vmodel to set-up model and locate source in it
+
+	call vmodel(nl,v,top,depth,vsq,thk,jl,tkj)
+
+c  output:
+c      vsq(l) - v(l) ** 2
+c      thk(l) - thickness of layer l
+c          jl - event layer
+c         tkj - depth of event in event layer
+
+c	call refract to find fastest refracted arrival
+
+	call refract(nl,v,vsq,thk,jl,tkj,delta,
+     &			kk,tref,xovmax)
+
+c  output:   kk - refracting layer for fastest refracted ray
+c          tref - travel time of fastest refracted ray
+c        xovmax - an upper bound on delta for which the direct ray
+c                 can be the first arrival
+
+
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/vmodel.f

@@ -1,0 +1,65 @@
+c Extract needed information from the layered velocity model.
+
+	subroutine vmodel(nl, v, top, depth, vsq, thk, jl, tkj)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer	nl
+	real	v(MAXLAY)
+	real	vsq(MAXLAY)
+	real	top(MAXLAY)
+	real	depth
+	real	thk(MAXLAY)
+	integer	jl
+	real	tkj
+
+c  input:     nl - number of layers
+c           v(l) - velocity of layer l
+c	     top - depth to top of layer l
+c          depth - depth of event
+
+c         vsq(l) = v(l) ** 2
+c         thk(l) - thickness of layer l
+c             jl - event layer
+c            tkj - depth of event from top of event layer
+
+c	Local variables:
+	integer	i
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/vmodel.f,v 1.5 2001/02/13 23:50:58 julian Exp julian $"/
+	save rcsid
+
+c	compute square of layer velocity
+	do 10 i=1,nl
+   10	vsq(i)=v(i)*v(i)
+
+c	determine layer thickness and
+c	find layer containing event,
+
+	jl=nl
+
+	do 20 i=1,nl
+
+c	Important note:  if (depth.lt.top(i)) will
+c	lead to incorrect results for traveltime
+	if (depth.le.top(i)) then
+	jl=i-1
+	goto 25
+	endif
+   20	continue
+   25	continue
+
+	do 30 i=1,nl-1
+   30	thk(i)=top(i+1)-top(i)
+
+c	compute depth from top of layer to source
+
+	tkj=depth-top(jl)
+
+	return
+c *****	end of subroutine vmodel *****
+	end

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/hypoDD/weighting.f

@@ -1,0 +1,224 @@
+c 10/04/00 determines a priori weights and re-weights them ....
+
+	subroutine weighting(log, ndt, mbad, amcusp, idata, kiter, ineg,
+     &	maxres_cross, maxres_net, maxdcc, maxdct, minwght,
+     &	wt_ccp, wt_ccs, wt_ctp, wt_cts,
+     &	dt_c1, dt_c2, dt_idx, dt_qual, dt_res, dt_offs,
+     &	dt_wt)
+
+	implicit none
+
+	include "hypoDD.inc"
+
+c	Parameters:
+	integer	log
+	integer	ndt
+	integer	mbad
+	integer	amcusp(1000)
+	integer	idata
+	integer	kiter
+	integer	ineg
+	real	maxres_cross
+	real	maxres_net
+	real	maxdcc
+	real	maxdct
+	real	minwght
+	real	wt_ccp
+	real	wt_ccs
+	real	wt_ctp
+	real	wt_cts
+	integer	dt_c1(MAXDATA)		! (1..MAXDATA)
+	integer	dt_c2(MAXDATA)		! (1..MAXDATA)
+	integer	dt_idx(MAXDATA)		! (1..MAXDATA)
+	real	dt_qual(MAXDATA)		! (1..MAXDATA)
+	real	dt_res(MAXDATA)		! (1..MAXDATA)
+	real	dt_offs(MAXDATA)		! (1..MAXDATA)
+	real	dt_wt(MAXDATA)		! (1..MAXDATA)
+
+c	Local variables:
+	character	dattim*25
+	real	dt_tmp(MAXDATA)
+	integer	i, j, k
+	real	mad_cc
+	real	mad_ct
+	real	maxres_cc
+	real	maxres_ct
+	real	med_cc
+	real	med_ct
+	integer	ncc
+	integer	nct
+	integer	nncc
+	integer	nnct
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/src/hypoDD/RCS/weighting.f,v 1.12 2001/03/08 18:51:27 klein Exp julian $"/
+	save rcsid
+        call datetime(dattim)
+
+c synthetics:
+      if(idata.eq.0) then
+            do i=1,ndt
+               dt_wt(i)=1 	
+            enddo
+      endif
+
+c--- get a priori data weights:
+c intial (a priori) weights:
+c s=linspace(0.0,100.0,101); ss= (s/100).^2; plot(s/100,ss); % coherency
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/cluster.f

@@ -1,0 +1,187 @@
+
+      subroutine cluster(log, mev, mcl, npair, minobs,
+     & ic1, ic2, in, icusp, acl, acli, apair_n,
+     & clust, noclust, nclust)
+
+	implicit none
+
+c	Parameters:
+	integer		log
+	integer		mev
+	integer		mcl
+	integer		npair
+	integer		minobs
+	integer		ic1(*)		! (1..mpair)
+	integer		ic2(*)		! (1..mpair)
+	integer		in(*)		! (1..mpair)
+	integer		icusp(*)	! (1..mev)
+	integer		acl(*)		! (1..mev)
+	integer		acli(*)		! (1..mev)
+	character	apair_n((mev**2-mev)/2)*1
+	integer		clust(mcl,*)	! (a..mcl, 1..mev)
+	integer		noclust(*)	! (1..mev)
+	integer		nclust
+
+c	Local variables:
+	integer		iev
+	integer		nev
+	integer		i
+	integer		j
+	integer		k
+	integer		kk
+	integer		n
+	integer		ii
+	integer		nn
+	integer		ia
+	integer		ifindi
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/ph2dt/RCS/cluster.f,v 1.10 2001/03/08 18:25:10 klein Exp $"/
+	save rcsid
+
+      write(*,'("clustering ...  ")')
+
+
+      iev= 0
+      do i=1,npair
+        do j=1,iev
+          if(ic1(i).eq.icusp(j)) goto 10
+        enddo
+        iev= iev+1
+        icusp(iev)= ic1(i)
+        do j=1,iev
+          if(ic2(i).eq.icusp(j)) goto 10
+        enddo
+        iev= iev+1
+        icusp(iev)= ic2(i)
+10      continue
+      enddo
+      nev= iev
+      call sorti(nev,icusp)
+
+      do i=1,npair
+         j= ifindi(nev,icusp,ic1(i))
+         k= ifindi(nev,icusp,ic2(i))
+         if(k.gt.j) then   !map into lower triangle
+            kk= k
+            k= j
+            j= kk
+         endif
+         if(in(i).ge.minobs) then
+            apair_n(((j-1)**2-(j-1))/2+k)= '1'
+         else
+            apair_n(((j-1)**2-(j-1))/2+k)= '0'
+         endif
+
+      enddo
+
+      do i=1,nev
+         acl(i)= nev+1
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/datetime.f

@@ -1,0 +1,17 @@
+c Current date and time, as a character string
+c (This version merely returns a string of blanks)
+
+	subroutine datetime(dattim)
+
+	implicit none
+
+c	Parameters:
+	character	dattim*20
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/ph2dt/RCS/datetime.f,v 1.6 2001/02/06 22:27:25 julian Exp $"/
+	save rcsid
+
+      dattim = '                    '
+      return
+      end ! of subroutine datetime

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/delaz.f

@@ -1,0 +1,102 @@
+c Compute distance and azimuth on a sphere
+
+	subroutine delaz(alat, alon, blat, blon, del, dist, az)
+
+c	computes distance and azimuth from a to b
+c	a and b are in decimal degrees and n-e coordinates
+c	del -- delta in degrees
+c	dist -- distance in km
+c	az -- azimuth from a to b clockwise from north in degrees
+
+c	Original author:  Bruce Julian
+c	new values for radius used (from Edi Kissling)
+
+	implicit none
+
+c	Parameters:
+	real	alat, alon	! Coordinates of first point
+	real	blat, blon	! Coordinates of second point
+	real	del		! Central angle (degrees)
+	real	dist		! Distance (km)
+	real	az		! Azimuth from a to b (degrees)
+
+	real	xtop
+	real	xden
+
+c	Local variables:
+	doubleprecision	acol, bcol
+	doubleprecision	azr
+	doubleprecision	blatr, blonr
+	doubleprecision	colat
+	doubleprecision	cosdel
+	doubleprecision	delr
+	doubleprecision	flat
+	doubleprecision	geoa
+	doubleprecision	geob
+	doubleprecision	rad
+	doubleprecision	radius
+	doubleprecision alatr, alonr
+	doubleprecision diflon
+	doubleprecision pi2
+	doubleprecision tana, tanb
+
+c	Built-in functions:  Declarations not needed
+	doubleprecision dtan
+	doubleprecision	datan
+	doubleprecision	dsin
+	doubleprecision	dcos
+	doubleprecision	dacos
+
+c	doubleprecision top,den
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/ph2dt/RCS/delaz.f,v 1.6 2001/02/08 23:34:01 julian Exp $"/
+	save rcsid
+
+	data pi2/1.570796d0/
+	data rad/1.745329d-02/
+	data flat/.993231d0/
+
+c-----convert to radians
+	alatr=alat*rad
+	alonr=alon*rad
+	blatr=blat*rad
+	blonr=blon*rad
+c-----convert latitudes to geocentric colatitudes
+	tana=flat*dtan(alatr)
+	geoa=datan(tana)
+	acol=pi2-geoa
+	tanb=flat*dtan(blatr)
+	geob=datan(tanb)
+	bcol=pi2-geob
+c-----calculate delta
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/indexx.f

@@ -1,0 +1,66 @@
+	subroutine indexx(n, arrin, indx)
+
+	implicit none
+
+c	Parameters:
+	integer	n
+	real	arrin(n)
+	integer	indx(n)
+
+c	Local variables:
+	integer	i
+	integer	indxt
+	integer	ir
+	integer	j
+	integer	l
+	real	q
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/ph2dt/RCS/indexx.f,v 1.6 2001/03/09 01:33:11 dinger Exp $"/
+	save rcsid
+
+      if (n.lt.1) then
+         return
+      else if (n.eq.1) then
+         indx(1) = 1
+         return
+      endif
+
+      DO 11 J=1,N
+        INDX(J)=J
+11    CONTINUE
+      L=N/2+1
+      IR=N
+10    CONTINUE
+        IF(L.GT.1)THEN
+          L=L-1
+          INDXT=INDX(L)
+          Q=ARRIN(INDXT)
+        ELSE
+          INDXT=INDX(IR)
+          Q=ARRIN(INDXT)
+          INDX(IR)=INDX(1)
+          IR=IR-1
+          IF(IR.EQ.1)THEN
+            INDX(1)=INDXT
+            RETURN
+          ENDIF
+        ENDIF
+        I=L
+        J=L+L
+20      IF(J.LE.IR)THEN
+          IF(J.LT.IR)THEN
+            IF(ARRIN(INDX(J)).LT.ARRIN(INDX(J+1)))J=J+1
+          ENDIF
+          IF(Q.LT.ARRIN(INDX(J)))THEN
+            INDX(I)=INDX(J)
+            I=J
+            J=J+J
+          ELSE
+            J=IR+1
+          ENDIF
+        GO TO 20
+        ENDIF
+        INDX(I)=INDXT
+      GO TO 10
+      END

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/ph2dt.f

@@ -1,0 +1,710 @@
+       program ph2dt
+
+c Author: Felix Waldhauser, felixw@ldeo.columbia.edu
+c Version 1.1 - 10/2004 - FW
+c
+c started 03/1999
+c 01-03/2001  clean up & bug fixes by Bruce Julian, Fred Klein, Keith
+c             Richards-Dinger, Felix Waldhauser
+c 10/2004     Version 1.1: fixed errors listed in BugList to V 1.0.
+c
+c Purpose:
+c Reads and filters absolute travel-time data from network catalogs
+c to form travel-time data for pairs of earthquakes. Control file or
+c interactive input of parameters to optimize linkage between events 
+c (i.e. optimize quality and minimize number of links between events).
+c See hypoDD user guide for information on how to use ph2dt.
+
+c For a user guide to ph2dt see USGS open-file report:
+c
+
+c--Reads the input file specified om the command line (ph2dt ph2dt.inp)
+c  to get the input station and phase file names, and the numerical parameters.
+c--Writes the files (input files to hypoDD):
+c  dt.ct	the travel times for the common stations for close 
+c               earthquake pairs
+c  event.dat	earthquake list in dd format
+c  event.sel	selected earthquake list in dd format (should be the same 
+c               as event.dat)
+c  ph2dt.log	log file
+c--Most earthquake selection (dates, magnitudes, etc) happens before ph2dt 
+c  processes phase to differential time data.
+c--Use the files events.select to select events by ID (one per line).
+c--FWK 2/9/01
+
+c The standard input format (free format) is:
+c#  yr  mn dy hr mn  sc      lat      lon      dep  mag  eh  ez  res  id
+c sta  t-t  wght pha
+c e.g.:
+c# 1997  6 13 13 44 37.33  49.2424 -123.6192   3.42 3.43 0.0 0.0 0.0  1
+c NAB      4.871   1    P
+c BIB      5.043   0.5  P
+c SHB      7.043   1    S
+c WPB      8.934   1    P
+
+c See hypoDD user guide for a description of the parameters.
+
+	implicit none
+
+	include 'ph2dt.inc'
+
+	real		a_dist(MOBS)
+	real		alat
+	real		alon
+	real		aoffs(MEV)
[…]

### 2011-12-06 paper2/diags/runs2/HYPODD_code/src/ph2dt/trimlen.f

@@ -1,0 +1,17 @@
+c Length of character string, excluding trailing blanks
+
+	integer function trimlen(t)
+
+	implicit none
+
+c	Parameter:
+	character t*(*)
+
+	character rcsid*150
+	data rcsid /"$Header: /home1/crhet/julian/HYPODD/ph2dt/RCS/trimlen.f,v 1.1 2001/02/03 02:55:40 julian Exp $"/
+	save rcsid
+
+      do 1 trimlen=LEN(t),1,-1
+    1    if(t(trimlen:trimlen).ne.' ')RETURN
+      trimlen=1
+      end ! of integer function trimlen

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/batchsubsamplestations.m

@@ -1,0 +1,12 @@
+% This is a batch script to subsample the stations..
+
+
+
+
+
+station_counts = 1:10;
+
+for i = 1:length(station_counts)
+    disp(['Doing directory ', num2str(i), ' of ', num2str(length(station_counts))])
+    subsample_hypoDDdata_to_stations(['stat',num2str(station_counts(i))],station_counts(i))
+end

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/example_68eq_calaveras1/example_68eq_calaveras1.m

@@ -1,0 +1,208 @@
+%% This script sets up example 1 and runs it
+
+% Load, subsample and save the CWI_data
+
+tic
+%Calaveras EXAMPLE - 10eq 
+fdom = 2.5;
+vs = 2728.3;  % vs = 3300;
+
+path2eventsoi ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/events_oi.txt';
+copyfile(path2eventsoi)
+load events_oi.txt
+
+hypoDD_loc68= load('/export/storage/davidr/sandpit/davidr/concluding_papers/paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/orig_68eqonly/hypoDD.reloc');
+E = [];
+count = 1;
+for i = 1:length(events_oi);
+    ind = find(events_oi(i)==hypoDD_loc68(:,1));
+    if ~isempty(ind)
+        E(count,:) = hypoDD_loc68(ind,5:7);
+        sigmaE(count,:) = hypoDD_loc68(ind,8:10);
+        count = count+1;
+    end 
+end
+
+% events_oi = [events_oi(1:2); events_oi(5); events_oi(3:4); events_oi(6:end)];
+[nE,tmp] = size(E);
+nrand = 1;
+npar = nE*3;%-3-2-1;
+
+%USING REAL EVENTS CALAVERAS
+path2CWIstat_data ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/revised_2dacoustics_1to5Hz/Calaveras_CWI_stat.mat';
+%events_oi = [101361,102139,102776,105327];
+[CWI_stat_small,CWI_stat_large] = subsample_CWI_stats(path2CWIstat_data,events_oi(:,1));
+CWI_stat = CWI_stat_large;
+CWI_stat = [CWI_stat,vs*ones(size(CWI_stat_large,1),1)];
+% Now let's pull out all the contsraints with "large" mun
+ind = find(CWI_stat(:,6)>0.1);
+CWI_stat(ind,3:9) = [-99999*ones(length(ind),7)];
+save CWI_stat.txt CWI_stat -ascii
+
+
+% Travel time constraints
+ttconst = zeros(nE,7);
+ttconst_pointer = ones(nE,1);
+%ttconst_pointer(1:8) = [1, 1,1,1,1,1,1,1];
+%ttconst_pointer(1:nE) = ones(nE,1);
+%ttconst_pointer = ones(nE,1);
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/example_68eq_calaveras2/example_68eq_calaveras2.m

@@ -1,0 +1,208 @@
+%% This script sets up example 1 and runs it
+
+% Load, subsample and save the CWI_data
+
+tic
+%Calaveras EXAMPLE - 10eq 
+fdom = 2.5;
+vs = 2728.3;  % vs = 3300;
+
+path2eventsoi ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/events_oi.txt';
+copyfile(path2eventsoi)
+load events_oi.txt
+
+hypoDD_loc68= load('/export/storage/davidr/sandpit/davidr/concluding_papers/paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat5/hypoDD.reloc');
+E = [];
+count = 1;
+for i = 1:length(events_oi);
+    ind = find(events_oi(i)==hypoDD_loc68(:,1));
+    if ~isempty(ind)
+        E(count,:) = hypoDD_loc68(ind,5:7);
+        sigmaE(count,:) = hypoDD_loc68(ind,8:10);
+        count = count+1;
+    end 
+end
+
+% events_oi = [events_oi(1:2); events_oi(5); events_oi(3:4); events_oi(6:end)];
+[nE,tmp] = size(E);
+nrand = 1;
+npar = nE*3;%-3-2-1;
+
+%USING REAL EVENTS CALAVERAS
+path2CWIstat_data ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/revised_2dacoustics_1to5Hz/Calaveras_CWI_stat.mat';
+%events_oi = [101361,102139,102776,105327];
+[CWI_stat_small,CWI_stat_large] = subsample_CWI_stats(path2CWIstat_data,events_oi(:,1));
+CWI_stat = CWI_stat_large;
+CWI_stat = [CWI_stat,vs*ones(size(CWI_stat_large,1),1)];
+% Now let's pull out all the contsraints with "large" mun
+ind = find(CWI_stat(:,6)>0.1);
+CWI_stat(ind,3:9) = [-99999*ones(length(ind),7)];
+save CWI_stat.txt CWI_stat -ascii
+
+
+% Travel time constraints
+ttconst = zeros(nE,7);
+ttconst_pointer = ones(nE,1);
+%ttconst_pointer(1:8) = [1, 1,1,1,1,1,1,1];
+%ttconst_pointer(1:nE) = ones(nE,1);
+%ttconst_pointer = ones(nE,1);
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/example_68eq_calaveras3/example_68eq_calaveras3.m

@@ -1,0 +1,208 @@
+%% This script sets up example 1 and runs it
+
+% Load, subsample and save the CWI_data
+
+tic
+%Calaveras EXAMPLE - 10eq 
+fdom = 2.5;
+vs = 2728.3;  % vs = 3300;
+
+path2eventsoi ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/events_oi.txt';
+copyfile(path2eventsoi)
+load events_oi.txt
+
+hypoDD_loc68= load('/export/storage/davidr/sandpit/davidr/concluding_papers/paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat7/hypoDD.reloc');
+E = [];
+count = 1;
+for i = 1:length(events_oi);
+    ind = find(events_oi(i)==hypoDD_loc68(:,1));
+    if ~isempty(ind)
+        E(count,:) = hypoDD_loc68(ind,5:7);
+        sigmaE(count,:) = hypoDD_loc68(ind,8:10);
+        count = count+1;
+    end 
+end
+
+% events_oi = [events_oi(1:2); events_oi(5); events_oi(3:4); events_oi(6:end)];
+[nE,tmp] = size(E);
+nrand = 1;
+npar = nE*3;%-3-2-1;
+
+%USING REAL EVENTS CALAVERAS
+path2CWIstat_data ='/export/storage/davidr/sandpit/davidr/thesis_version2/diags/revised_2dacoustics_1to5Hz/Calaveras_CWI_stat.mat';
+%events_oi = [101361,102139,102776,105327];
+[CWI_stat_small,CWI_stat_large] = subsample_CWI_stats(path2CWIstat_data,events_oi(:,1));
+CWI_stat = CWI_stat_large;
+CWI_stat = [CWI_stat,vs*ones(size(CWI_stat_large,1),1)];
+% Now let's pull out all the contsraints with "large" mun
+ind = find(CWI_stat(:,6)>0.1);
+CWI_stat(ind,3:9) = [-99999*ones(length(ind),7)];
+save CWI_stat.txt CWI_stat -ascii
+
+
+% Travel time constraints
+ttconst = zeros(nE,7);
+ttconst_pointer = ones(nE,1);
+%ttconst_pointer(1:8) = [1, 1,1,1,1,1,1,1];
+%ttconst_pointer(1:nE) = ones(nE,1);
+%ttconst_pointer = ones(nE,1);
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat2/dt.cc

@@ -1,0 +1,2486 @@
+# 32049 77218 -0.014999 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCJCB 0.006964 0.707 P 
+# 42643 101361 -0.047999 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCJCB 0.003616 0.942 P 
+# 126189 126389 -0.002003 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCJCB 0.008203 0.811 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 17842 23190 0.039000 
+NCJCB 0.009186 0.729 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 22280 32049 0.026000 
+NCJCB 0.022360 0.726 P 
+# 23190 32049 0.014000 
+NCJCB 0.022291 0.846 P 
+# 21644 35109 0.052002 
+NCJCB 0.039524 0.882 P 
+# 23190 42559 0.041000 
+NCJCB 0.033132 0.910 P 
+# 32049 42559 0.027000 
+NCJCB 0.011293 0.735 P 
+# 23190 42643 0.056000 
+NCJCB 0.057359 0.804 P 
+# 32049 42643 0.042000 
+NCJCB 0.034861 0.799 P 
+# 42559 42643 0.015000 
+NCJCB 0.024308 0.752 P 
+# 21644 54084 0.039999 
+NCJCB 0.041856 0.706 P 
+# 22280 54084 0.002000 
+NCJCB -0.019694 0.756 P 
+# 23190 54084 -0.010000 
+NCJCB -0.020351 0.911 P 
+# 32049 54084 -0.024000 
+NCJCB -0.042594 0.816 P 
+# 42559 54084 -0.051000 
+NCJCB -0.053812 0.830 P 
+# 22280 62514 0.015002 
+NCJCB 0.012073 0.773 P 
+# 23190 62514 0.003002 
+NCJCB 0.011881 0.832 P 
+# 32049 62514 -0.010998 
+NCJCB -0.010342 0.981 P 
+# 42559 62514 -0.037998 
+NCJCB -0.021477 0.738 P 
+# 42643 62514 -0.052998 
+NCJCB -0.045010 0.818 P 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat3/dt.cc

@@ -1,0 +1,4270 @@
+# 32049 77218 -0.014999 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCJCB 0.006964 0.707 P 
+# 42643 101361 -0.047999 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCJST 0.002636 0.974 P 
+NCJCB 0.003616 0.942 P 
+# 126189 126389 -0.002003 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCJST 0.006475 0.720 P 
+NCJCB 0.008203 0.811 P 
+# 126389 215747 -0.023998 
+NCJST -0.011004 0.791 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 22271 30076454 -0.027002 
+NCJST -0.019191 0.899 P 
+# 17842 23190 0.039000 
+NCJCB 0.009186 0.729 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 17842 32049 0.052999 
+NCJST 0.036114 0.785 P 
+# 22280 32049 0.026000 
+NCJST 0.026570 0.778 P 
+NCJCB 0.022360 0.726 P 
+# 23190 32049 0.014000 
+NCJST 0.014785 0.806 P 
+NCJCB 0.022291 0.846 P 
+# 21644 35109 0.052002 
+NCJCB 0.039524 0.882 P 
+# 23190 42559 0.041000 
+NCJST 0.034098 0.838 P 
+NCJCB 0.033132 0.910 P 
+# 32049 42559 0.027000 
+NCJCB 0.011293 0.735 P 
+# 23190 42643 0.056000 
+NCJCB 0.057359 0.804 P 
+# 32049 42643 0.042000 
+NCJST 0.039327 0.704 P 
+NCJCB 0.034861 0.799 P 
+# 42559 42643 0.015000 
+NCJCB 0.024308 0.752 P 
+# 17842 54084 0.028999 
+NCJST 0.005004 0.706 P 
+# 21644 54084 0.039999 
+NCJCB 0.041856 0.706 P 
+# 22280 54084 0.002000 
+NCJCB -0.019694 0.756 P 
+# 23190 54084 -0.010000 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat4/dt.cc

@@ -1,0 +1,5062 @@
+# 32049 77218 -0.014999 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCJCB 0.006964 0.707 P 
+# 42643 101361 -0.047999 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCCMH 0.002954 0.972 P 
+NCJST 0.002636 0.974 P 
+NCJCB 0.003616 0.942 P 
+# 126189 126389 -0.002003 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCCMH -0.015197 0.707 P 
+NCJST 0.006475 0.720 P 
+NCJCB 0.008203 0.811 P 
+# 126389 215747 -0.023998 
+NCCMH -0.005813 0.839 P 
+NCJST -0.011004 0.791 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 22271 30076454 -0.027002 
+NCJST -0.019191 0.899 P 
+# 17842 23190 0.039000 
+NCJCB 0.009186 0.729 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 17842 32049 0.052999 
+NCCMH 0.040486 0.813 P 
+NCJST 0.036114 0.785 P 
+# 22280 32049 0.026000 
+NCJST 0.026570 0.778 P 
+NCJCB 0.022360 0.726 P 
+# 23190 32049 0.014000 
+NCJST 0.014785 0.806 P 
+NCJCB 0.022291 0.846 P 
+# 21644 35109 0.052002 
+NCCMH 0.039164 0.934 P 
+NCJCB 0.039524 0.882 P 
+# 23190 42559 0.041000 
+NCJST 0.034098 0.838 P 
+NCJCB 0.033132 0.910 P 
+# 32049 42559 0.027000 
+NCJCB 0.011293 0.735 P 
+# 23190 42643 0.056000 
+NCJCB 0.057359 0.804 P 
+# 32049 42643 0.042000 
+NCCMH 0.049603 0.824 P 
+NCJST 0.039327 0.704 P 
+NCJCB 0.034861 0.799 P 
+# 42559 42643 0.015000 
+NCCMH 0.005979 0.754 P 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat5/dt.cc

@@ -1,0 +1,6127 @@
+# 17842 42643 0.094999 
+NCHSP 0.064937 0.841 P 
+# 32049 77218 -0.014999 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCJCB 0.006964 0.707 P 
+# 42643 101361 -0.047999 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCCMH 0.002954 0.972 P 
+NCJST 0.002636 0.974 P 
+NCJCB 0.003616 0.942 P 
+NCHSP -0.000537 0.947 P 
+# 126189 126389 -0.002003 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCCMH -0.015197 0.707 P 
+NCJST 0.006475 0.720 P 
+NCJCB 0.008203 0.811 P 
+# 126389 215747 -0.023998 
+NCCMH -0.005813 0.839 P 
+NCJST -0.011004 0.791 P 
+NCHSP -0.003261 0.772 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 22271 30076454 -0.027002 
+NCJST -0.019191 0.899 P 
+NCHSP -0.007810 0.910 P 
+# 17842 23190 0.039000 
+NCJCB 0.009186 0.729 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 17842 32049 0.052999 
+NCCMH 0.040486 0.813 P 
+NCJST 0.036114 0.785 P 
+NCHSP 0.031069 0.806 P 
+# 22280 32049 0.026000 
+NCJST 0.026570 0.778 P 
+NCJCB 0.022360 0.726 P 
+NCHSP 0.023139 0.772 P 
+# 23190 32049 0.014000 
+NCJST 0.014785 0.806 P 
+NCJCB 0.022291 0.846 P 
+# 21644 35109 0.052002 
+NCCMH 0.039164 0.934 P 
+NCJCB 0.039524 0.882 P 
+NCHSP 0.040087 0.952 P 
+# 23190 42559 0.041000 
+NCJST 0.034098 0.838 P 
+NCJCB 0.033132 0.910 P 
+NCHSP 0.033510 0.873 P 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat6/dt.cc

@@ -1,0 +1,6941 @@
+# 17842 42643 0.094999 
+NCHSP 0.064937 0.841 P 
+# 32049 77218 -0.014999 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCJCB 0.006964 0.707 P 
+# 42643 101361 -0.047999 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCCMH 0.002954 0.972 P 
+NCJST 0.002636 0.974 P 
+NCJCB 0.003616 0.942 P 
+NCHSP -0.000537 0.947 P 
+# 126189 126389 -0.002003 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCCMH -0.015197 0.707 P 
+NCJST 0.006475 0.720 P 
+NCJCB 0.008203 0.811 P 
+# 126389 215747 -0.023998 
+NCCMH -0.005813 0.839 P 
+NCJST -0.011004 0.791 P 
+NCHSP -0.003261 0.772 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 22271 30076454 -0.027002 
+NCJST -0.019191 0.899 P 
+NCJAL -0.020570 0.792 P 
+NCHSP -0.007810 0.910 P 
+# 17842 23190 0.039000 
+NCJCB 0.009186 0.729 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 17842 32049 0.052999 
+NCCMH 0.040486 0.813 P 
+NCJST 0.036114 0.785 P 
+NCHSP 0.031069 0.806 P 
+# 22280 32049 0.026000 
+NCJST 0.026570 0.778 P 
+NCJCB 0.022360 0.726 P 
+NCJAL 0.025385 0.795 P 
+NCHSP 0.023139 0.772 P 
+# 23190 32049 0.014000 
+NCJST 0.014785 0.806 P 
+NCJCB 0.022291 0.846 P 
+# 21644 35109 0.052002 
+NCCMH 0.039164 0.934 P 
+NCJCB 0.039524 0.882 P 
+NCJAL 0.035221 0.766 P 
+NCHSP 0.040087 0.952 P 
+# 23190 42559 0.041000 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/stat8/dt.cc

@@ -1,0 +1,7620 @@
+# 17842 42643 0.094999 
+NCCSC 0.084108 0.854 P 
+NCHSP 0.064937 0.841 P 
+# 32049 77218 -0.014999 
+NCCSC -0.005540 0.846 P 
+NCJCB -0.026794 0.841 P 
+# 17842 101361 0.047000 
+NCCSC 0.035959 0.814 P 
+NCJCB 0.006964 0.707 P 
+# 35109 101361 0.005998 
+NCCSC -0.010594 0.724 P 
+# 42643 101361 -0.047999 
+NCCSC -0.047928 0.895 P 
+NCJCB -0.059432 0.789 P 
+# 32049 126189 0.007000 
+NCCSC -0.002995 0.856 P 
+NCJCB -0.023065 0.883 P 
+# 77218 126189 0.021999 
+NCCSC 0.002377 0.987 P 
+NCCMH 0.002954 0.972 P 
+NCJST 0.002636 0.974 P 
+NCJCB 0.003616 0.942 P 
+NCHSP -0.000537 0.947 P 
+# 77218 126389 0.019997 
+NCCSC 0.005203 0.741 P 
+# 126189 126389 -0.002003 
+NCCSC 0.001487 0.752 P 
+NCJCB 0.028081 0.724 P 
+# 77218 215747 -0.004002 
+NCCMH -0.015197 0.707 P 
+NCJST 0.006475 0.720 P 
+NCJCB 0.008203 0.811 P 
+# 126389 215747 -0.023998 
+NCCSC -0.005856 0.751 P 
+NCCMH -0.005813 0.839 P 
+NCJST -0.011004 0.791 P 
+NCHSP -0.003261 0.772 P 
+# 101361 30069222 0.044000 
+NCJCB 0.061813 0.750 P 
+# 22271 30076454 -0.027002 
+NCJST -0.019191 0.899 P 
+NCJAL -0.020570 0.792 P 
+NCHSP -0.007810 0.910 P 
+# 17842 23190 0.039000 
+NCCSC 0.035502 0.767 P 
+NCJCB 0.009186 0.729 P 
+# 21644 23190 0.049999 
+NCCSC 0.028716 0.781 P 
+# 22280 23190 0.012000 
+NCJCB 0.000414 0.767 P 
+# 17842 32049 0.052999 
+NCCSC 0.039789 0.805 P 
+NCCMH 0.040486 0.813 P 
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/subsample_hypoDDdata_to_68eq.m

@@ -1,0 +1,122 @@
+function [dtct_data] = subsample_hypoDDdata_to_68eq()
+% This function locates the 69 earthquakes of interest then loads all of the 
+% hypoDD input data from */orig_69eqonly and sub-samples it to events of
+% interest. 
+
+inputdatadir = './orig_example2/';
+outputdir = './orig_68eqonly/';
+
+%===================================================
+% Find the events of interest
+
+events_oi = load('../../../events_oi.txt');
+nE = length(events_oi);
+events_oi'
+%===================================================
+% Now let us load in the event data 
+% allevents = load([inputdatadir,'event.dat']);
+% [c, ind_allevents, iindevents_oi] = intersect(allevents(:,end), events_oi);
+% events69eq = allevents(ind_allevents,:);
+% %save([outputdir,'event.dat'],'events69eq','-ascii');
+% [n m] = size(events69eq);
+% fid = fopen([outputdir,'event.dat'],'w');
+% for i = 1:n
+%     fprintf(fid, '%d%d%d%d%d%d%d%d%d%d\n', events69eq(i,:)); % write the evnt pair line to file
+% end
+% fclose(fid)
+
+fid = fopen([inputdatadir,'event.dat']);
+event_data = textscan(fid, '%s', 'delimiter', '\n');
+fclose(fid)
+fid = fopen([outputdir,'event.dat'],'w');
+for i = 1:length(event_data{1})
+    tmp = event_data{1}(i);
+    tmp2 = str2num(tmp{1}); 
+    ind1 = find(tmp2(end) == events_oi)
+    if ~isempty(ind1)
+        %fprintf(fid, '%8.0f %8.0f %7.4f %9.4f %5.3f %3.1f %4.2f %4.2f %4.2f %f \n', tmp2); % write the evnt pair line to file
+        fprintf(fid, '%s \n', tmp{1})
+    end
+end
+fclose(fid)
+
+
+%===================================================
+% Now let us copy over the station data
+% i.e. no need to sub-sample it
+copyfile([inputdatadir,'station.dat'],[outputdir,'station.dat'])
+
+%===================================================
+% Now let us have a look at the Calaveras.pha file used by ph2dt
+% First read in all the data
+create_phasefile('Calaveras.pha',inputdatadir,outputdir,events_oi)
+
+%===================================================
+% Now let us have a look at th dt.cc file 
+% First read in all the data
+create_ttimefile('dt.cc',inputdatadir,outputdir,events_oi)
+
+
[…]

### 2011-12-06 paper2/diags/runs2/Hypodd_SVD/HYPODD2/runs/subsample_hypoDDdata_to_stations.m

@@ -1,0 +1,163 @@
+function [] = subsample_hypoDDdata_to_stations(outputdir, number_of_stats)
+%
+% This function is used to subsample the hypoDD data to desired stations
+% (i.e. number_of_stats stations are sub-sampled from 
+% ../../CWI/importantstats.txt). A new set of subsampled hypoDD input files
+% are saved to outputdir. This function assumes that the input files have 
+% already been sub-sampled to the deisred events (for details see
+% subsample_hypoDDdata_to_69eq.m).
+%
+
+inputdatadir = './orig_68eqonly/';
+
+%=============================================================
+% Read in the station data
+s = importdata('../../CWI/importantstats.txt');
+importantstats_tmp = s.textdata(6:end);
+importantstats_data_tmp = s.data;
+importantstats = importantstats_tmp(1:number_of_stats);
+importantstats_data = importantstats_data_tmp(1:number_of_stats,:);
+
+
+% ============================================================
+% Sub-sample the station file
+fid = fopen([inputdatadir,'station.dat']);
+station_data = textscan(fid, '%s', 'delimiter', '\n');
+fclose(fid);
+fid = fopen([outputdir,filesep,'station.dat'],'w');
+for i = 1:length(station_data{1})
+    tmp = station_data{1}(i);
+    statname1 = tmp{1}(1:6);
+    for j = 1:length(importantstats)
+        statname2 = ['NC',importantstats{j},' '];
+        if strcmp(statname1,statname2)
+            fprintf(fid, '%s \n', tmp{1});
+        end
+    end
+ %   if ~isempty(ind1)
+        %fprintf(fid, '%8.0f %8.0f %7.4f %9.4f %5.3f %3.1f %4.2f %4.2f %4.2f %f \n', tmp2); % write the evnt pair line to file
+  %      fprintf(fid, '%s \n', tmp{1})
+  %  end
+end
+fclose(fid);
+
+% ============================================================
+% Sub-sample the dt.cc file
+events_rep1 = create_ttimefile('dt.cc',inputdatadir,outputdir,importantstats);
+
+%===================================================
+% Now let us have a look at the Calaveras.pha file used by ph2dt
+% First read in all the data
+events_rep2 = create_phasefile('Calaveras.pha',inputdatadir,outputdir,importantstats)
+
+% ============================================================
[…]

### 2011-12-06 paper2/paper2.tex
brought the new (hypoDD SVD based) figures into the main document - ensured paper compiles under the new git repository

@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+\noindent\includegraphics[width = 20pc]{diags/ressummary_2Dsynth50eq.eps}
 \caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+\noindent\includegraphics[width = 20pc]{diags/ressummary_3Dsynth50eq.eps}
 \caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
@@
 
+%%=======================================================================================
+% This is the original figure using HypoDD with LSQR
+%\begin{figure*}
+%\includegraphics{diags/CalaverasLoc1.eps}
+%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
+%308 events (column 2) and CWI example 1 (column 3).
+%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
+%blue events are shown for the purpose of orientation only.}
+%\label{fig-69Calaverasevents_eg1}
+%\end{figure*}
+
+% Now we have the SVD version 
 \begin{figure*}
-\includegraphics{diags/CalaverasLoc1.eps}
+\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
 \caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
@@
 \end{figure*}
+%%=======================================================================================
 
@@
 
+%%=========================================================================
+% this is the original version using hypoDD with LSQ
+%\begin{figure*}
+%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
+%\caption{....}
+%\label{fig-HYPODDreducesstats}
+%\end{figure*}
+
+% This is the version using hypoDD with SVD
 \begin{figure*}
-\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
-\caption{....}
+\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
+\caption{HypoDD (SVD) with reduced stations.}
 \label{fig-HYPODDreducesstats}
 \end{figure*}
-
+%%=========================================================================
+
+%%=========================================================================
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
+%\caption{Statistics on coordinate differences for reduced station inversions. Differences
+%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
+%locations for all 308 events. The top subplot illustrates the number of constrainable
+%events in the CWI and hypoDD inversions as a function of the stations considered.}
+%\label{fig-statremoval_summarystats}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
+\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
 \caption{Statistics on coordinate differences for reduced station inversions. Differences
@@
 \end{figure}
+%%=========================================================================
 
@@
 
-\begin{figure*}
-\noindent\includegraphics{diags/CalaverasLoc5.eps}
-\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
-levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
-\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
-column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
-\label{fig-68Calaverasevents_ttandcoda1}
-\end{figure*}
+%%=========================================================================
+% This is the original version using hypoDD with LSQ
+% This is only makes sense for LSQR so we remove it from this manuscript
+%\begin{figure*}
+%\noindent\includegraphics{diags/CalaverasLoc5.eps}
+%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
+%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
+%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
+%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
+%\label{fig-68Calaverasevents_ttandcoda1}
+%\end{figure*}
+%%=========================================================================
 
@@
 
-\begin{figure}
-\noindent\includegraphics{diags/CalaverasLoc6.eps}
-\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
-22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
-are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
-relocation only (i.e. no CWI) using ........}
-\label{fig-68Calaverasevents_ttsubsetandcoda1}
-\end{figure}
+%%=========================================================================
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics{diags/CalaverasLoc6.eps}
+%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
+%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
+%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
+%relocation only (i.e. no CWI) using ........}
+%\label{fig-68Calaverasevents_ttsubsetandcoda1}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
+\begin{figure*}
+\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
+\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
+\label{fig-69Calaverasevents_eg1}
+\end{figure*}
+%%=========================================================================
 
@@
 
-\begin{figure*}
-\includegraphics{diags/CalaverasLoc1.eps}
-\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-308 events (column 2) and CWI example 1 (column 3).
-Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
-blue events are shown for the purpose of orientation only.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\caption{HypoDD (SVD) with reduced stations.}
-\label{fig-HYPODDreducesstats}
-\end{figure*}
-
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
-\caption{Statistics on coordinate differences for reduced station inversions. Differences
-are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-locations for all 308 events. The top subplot illustrates the number of constrainable
-events in the CWI and hypoDD inversions as a function of the stations considered.}
-\label{fig-statremoval_summarystats}
-\end{figure}
-
-\begin{figure*}
-\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure*}
-
 %\bsp % ``This paper has been produced using the Blackwell

### 2012-07-12 paper2/paper2.tex
updated my contact details

@@
     University, Canberra ACT \emph{0200}, Australia, E-mail: david.robinson@anu.edu.au \\
-$^2$  Risk Research Group, Geoscience Australia, GPO Box \emph{383} Canberra ACT \emph{2601} Australia, E-mail: david.robinson@ga.gov.au\\
+$^2$  Risk Analysis Methods, Geoscience Australia, GPO Box \emph{383} Canberra ACT \emph{2601} Australia, E-mail: david.robinson@ga.gov.au\\
 $^3$ Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines, Golden CO \emph{80401-1887}, USA \\

### 2012-07-17 paper2/paper2.tex
some big changes done at GA

@@
 our understanding of seismic activity by indicating regions of
-relatively higher seismicity such as major lithospheric plate
-boundaries \citep[e.g., ][]{dr_Sykes67a, dr_Isacks68a,
-dr_Stein02a} or local active source zones
-\citep[e.g., ][]{dr_Gutenberg44a, dr_Giardini03a}.
-Earthquake locations are required for  magnitude determination
-\citep[e.g., ][]{dr_Richter35a, dr_Gutenberg45a}, computing
-moment tensors \citep[e.g., ][]{dr_Sipkin02a} and
-seismological studies of the Earth's interior
-\citep[e.g., ][]{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a,
-dr_Kennett04a}. They are needed to
-understand strong motion and seismic attenuation
+relatively higher seismicity such as lithospheric plate boundaries
+\citep[e.g., ][]{dr_Sykes67a, dr_Isacks68a, dr_Stein02a} or local
+active source zones \citep[e.g., ][]{dr_Gutenberg44a,
+dr_Giardini03a}. Earthquake locations are required for  magnitude
+determination \citep[e.g., ][]{dr_Richter35a, dr_Gutenberg45a},
+computing moment tensors \citep[e.g., ][]{dr_Sipkin02a} and
+seismological studies of the Earth's interior \citep[e.g.,
+][]{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a, dr_Kennett04a}. They
+are needed to understand strong motion and seismic attenuation
 \citep[e.g., ][]{dr_Toro97a, dr_Campbell03a}
@@
 \citep[e.g., ][]{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
-The accuracy required in earthquake location depends on the application.
-For example, imaging the structure of a fracture system from microseismicity
-requires greater detail than determining whether a $M_w=7.5$ earthquake
-occurs offshore for tsunami warning purposes. This paper focuses
-on reducing the uncertainty on the locations of a cluster of events, particularly
-when they are recorded by a small number of stations.
-
-Absolute location describes the location of an earthquake
-with respect to some global reference such as latitude, longitude (or
-easting/northing) and depth. Uncertainties associated with absolute locations
-are influenced by source to station distances, the number of
-stations and their geometry, quality of signal and accuracy of
-the velocity model used in computing travel times. Errors in absolute location are typically of the
-order of several km because they are susceptible to uncertainty in the velocity
-structure along the entire path between the source and receiver.
-For example, \citet{dr_Shearer99a} states that location uncertainty
-in the ISC and PDE catalogues are generally around 25\,km horizontally and
-at least 25\,km in depth.\footnote{Here the depth uncertainties of 25\,km assume the use
-of depth dependent phases such as $pP$. Without such phases the uncertainty is higher.}
+
+The accuracy required in earthquake location depends on the
+application. For example, imaging the structure of a fracture system
+from microseismicity requires greater detail than determining
+whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning
+purposes. This paper focuses on reducing the uncertainty on the
+locations of a cluster of events when they are recorded by a small
+number of stations.
+
+Absolute location describes the location of an earthquake with
+respect to a global reference such as latitude, longitude (or
+easting/northing) and depth. Uncertainties associated with absolute
+locations are influenced by source to station distances, the number
+of stations and their geometry, quality of signal and accuracy of
+the velocity model used in computing travel times. Uncertainties in
+absolute location are typically of the order of several km because
+they are susceptible to uncertainty in the velocity structure along
+the entire path between the source and receiver. For example,
+\citet{dr_Shearer99a} states that location uncertainty in the ISC
+and PDE catalogues are generally around 25\,km horizontally and at
+least 25\,km in depth.\footnote{Here the depth uncertainties of
+25\,km assume the use of depth dependent phases such as $pP$.
+Without such phases the uncertainty is higher.}
   These locations are created using global seismic networks.
-\citet{dr_Bondar04a} demonstrate
-that at the local scale, absolute locations are accurate to within 5\,km with a 95\%
-confidence level when local networks meet a number of station
-related criteria. Such errors are too large for many applications, particularly
-those focussed on the study of micro seismicity and imaging
-rupture surfaces from aftershock sequences.
-
-Relative earthquake location involves locating a group of earthquakes with
-respect to one another and was first introduced by \citet{dr_Douglas67a}
-who developed the technique commonly known as joint hypocenter
-determination.\footnote{\citet{dr_Douglas67a} originally used the term
-joint epicentre determination. However, he was solving for hypocentre.}
-In principle, relative locations can be
-computed by differencing absolute locations. However, \citet{dr_Pavlis92a}
-shows that inadequate knowledge of velocity structure leads to
-systematic biases when relative positions are computed in this way.
-This is confirmed by \citet{dr_Richards06a}
-who state that inaccuracies in the travel time model are one of
-two primary error sources in absolute earthquake location. The other
-error source is erroneous arrival picks. To reduce errors from the travel
-time model, relative location techniques compute locations
-directly from travel time differences between two waveforms
-\citep[e.g., ][]{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}.
-By doing so, they remove errors
-associated with unknown lateral velocity variations outside the
-local region, because such variations influence all waveforms in
+\citet{dr_Bondar04a} demonstrate that at the local scale, absolute
+locations are accurate to within 5\,km with a 95\% confidence level
+when local networks meet a number of station related criteria. Such
+errors are too large for many applications, particularly those
+focussed on imaging rupture surfaces from aftershock sequences.
+
+Relative earthquake location involves locating a group of
+earthquakes with respect to one another and was first introduced by
+\citet{dr_Douglas67a} who developed the technique commonly known as
+joint hypocenter determination.\footnote{\citet{dr_Douglas67a}
+originally used the term joint epicentre determination. However, he
+was solving for hypocentre.} In principle, relative locations can be
+computed by differencing absolute locations. However,
+\citet{dr_Pavlis92a} shows that inadequate knowledge of velocity
+structure leads to systematic biases when relative positions are
+computed in this way. To reduce errors from unknown velocity
+structure, relative location techniques compute locations directly
+from travel time differences between two waveforms \citep[e.g.,
+][]{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
+so, they remove errors associated with velocity variations outside
+the local region, because such variations influence all waveforms in
 the same manner \citep{dr_Shearer99a}.
 
-Reported uncertainties
-for event locations from relative techniques are  around 15 to 75\,m in
-local settings with good station coverage
-\citep[e.g., ][]{dr_Ito85a, dr_Got94a, dr_Waldhauser99a,dr_Waldhauser08a}.
-Here, `good coverage' implies multiple
-stations distributed across a broad range of azimuthal directions.
-Precise relative location techniques have been applied to a
-diverse range of problems. For example, the location of active
-fault planes \citep[e.g., ][]{dr_Deichmann92a, dr_Got94a,
-dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a}, studying rupture mechanics
-\citep[e.g., ][]{dr_Rubin99a, dr_Rubin02a}, interpreting magma
-movement in volcanoes \citep[e.g., ][]{dr_Fremont87a} and monitoring
-pumping induced seismicity \citep[e.g., ][]{dr_Lees98a,
-dr_Ake05a}. \citet{dr_Poupinet84a},
-\citet{dr_Bokelmann00a} and  \citet{dr_Rubin02b} apply relative
-location techniques to identify earthquake doublets, events that have near identical
-locations. \citet{dr_Poupinet84a} use these doublets to measure
-temporal variation in crustal velocity, \citet{dr_Bokelmann00a}
-use them to identify systematic temporal variations in seismic
-anisotropy and \citet{dr_Rubin02b} describes how they are useful for
-correcting time-dependent station delays.
+Reported location uncertainties from relative techniques are  around
+15 to 75\,m in local settings with good station coverage
+\citep[e.g., ][]{dr_Ito85a, dr_Got94a,
+dr_Waldhauser99a,dr_Waldhauser08a}. Here, `good coverage' implies
+multiple stations distributed across a broad range of azimuthal
+directions. Relative location techniques have been applied to a
+diverse range of problems including: location of active fault planes
+\citep[e.g., ][]{dr_Deichmann92a, dr_Got94a, dr_Waldhauser99a,
+dr_Waldhauser02a, dr_Shearer05a}; studying rupture mechanics
+\citep[e.g., ][]{dr_Rubin99a, dr_Rubin02a}; interpreting magma
+movement in volcanoes \citep[e.g., ][]{dr_Fremont87a}; and
+monitoring pumping induced seismicity \citep[e.g., ][]{dr_Lees98a,
+dr_Ake05a}. \citet{dr_Poupinet84a}, \citet{dr_Bokelmann00a} and
+\citet{dr_Rubin02b} apply relative location techniques to identify
+earthquake doublets, events that have near identical locations.
 
@@
 paper we develop an approach for locating earthquakes using coda waves.
-\citet{dr_Snieder05a} demonstrate that the
-coda of two earthquakes can be used to estimate the separation between
-them. Their technique is based on the interference pattern between
-the coda waves and is known as coda wave interferometry (CWI).
-Unlike travel time techniques, CWI
+
+\citet{dr_Snieder05a} demonstrate that the coda of two earthquakes
+can be used to estimate the separation between them. Their
+technique, known as coda wave interferometry (CWI), is based on the
+interference pattern between the coda waves. Unlike travel time
+techniques, CWI
  does not require multiple stations or good azimuthal coverage.
@@
 \section{Theory}
+\label{sec:theory}
 
@@
 \end{equation}
-\citep{dr_Snieder05a}. The
-$\sigma_\tau$ in eq. (\ref{eq:Theory-dcwi_g_sigmat}) is related to $R_{max}$, the maximum of the cross correlation between
-the coda of the two waveforms and hence can be computed directly from the recorded data.
-In this paper we use the autocorrelation
-approach of \citet{dr_Robinson10b} when relating these parameters
-and we apply a restricted time lag search when evaluating $R_{max}$. These extensions
-to the original technique of \citet{dr_Snieder05a} increase the range of applicability
-of CWI by 50\%.
-
-\citet{dr_Robinson10b} show that coda waves provide
-only probabilistic constraints on source separation and
-introduce a Bayesian approach for describing the probability
-of true separation given the CWI data. Their approach is
-summarised by
+\citep{dr_Snieder05a}.
+
+The $\sigma_\tau$ in eq. (\ref{eq:Theory-dcwi_g_sigmat}) is related
+to $R_{max}$, the maximum of the cross correlation between the coda
+of the two waveforms and hence can be computed directly from the
+recorded data. In this paper we use the autocorrelation approach of
+\citet{dr_Robinson11a} when relating these parameters and we apply a
+restricted time lag search when evaluating $R_{max}$. These
+extensions to the original technique of \citet{dr_Snieder05a}
+increase the range of applicability of CWI by 50\%.
+
+\citet{dr_Robinson11a} show that coda waves provide only
+probabilistic constraints on source separation and introduce a
+Bayesian approach for describing the probability of true separation
+given the CWI data. Their approach is summarised by
 \begin{equation}
@@
 \end{equation}
-which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$) with
-respect to dominant wavelength $\lambda_{d}$.
-In this paper we consider a uniform prior which gives emphasis to the recorded data.
-The algorithm for computing the noisy
-likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by \citet{dr_Robinson10b}
-and summarised in Appendix \ref{sec-Appendix-noisylikelihood}. With these two pieces
-in place we can compute the posterior $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-(or PDF) for the separation between any pair of events directly from their coda waves.
+which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$)
+with respect to dominant wavelength $\lambda_{d}$. In this paper we
+consider a uniform prior which gives emphasis to the recorded data.
+The algorithm for computing the noisy likelihood
+$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
+\citet{dr_Robinson11a} and summarised in Appendix
+\ref{sec-Appendix-noisylikelihood}. With these two pieces in place
+we can compute the posterior
+$P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ (or PDF) for the
+separation between any pair of events directly from their coda
+waves.
 
@@
  individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-and describes the location of multiple events with maximum identifying
+to describe the location of multiple events with maximum identifying
  the most probable combination of locations.
@@
 on the degree to which individual events are constrained
- by the data. For convenience, we begin with three earthquakes having locations
-$\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian formulation we write
+ by the data.
+
+For convenience, we begin with three earthquakes having locations
+$\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian
+formulation we write
 \begin{equation}
@@
 \end{equation}
-where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$, $P(\mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
-and $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
-likelihood and prior functions, respectively. In eq. (\ref{eq-Bayes-three-locations})
-$\mathbf{d}$ represents observations that constrain the locations. They can be any combination
-of travel times, geodetic information  or CWI separation estimations. For example, if coda waves are used
-we have $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
-where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the wavelength normalised separation estimates.
-Alternatively, if we use CWI and travel time data we may write
-$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}, \mathbf{t}_{DD})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{t}_{DD}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$
-where $\mathbf{t}_{DD}$ represent travel time differences.
-In this derivation and in Sec. \ref{sec:benchmarking} we focus on the constraints imposed by coda waves, whereas in
-Sec. \ref{sec:CalaverasLoc-CWIandTT} we demonstrate how
-CWI and travel time data can be combined.
+where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$,
+$P(\mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ and
+$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
+likelihood and prior functions, respectively. In eq.
+(\ref{eq-Bayes-three-locations}) $\mathbf{d}$ represents
+observations that constrain the locations. They can be any
+combination of travel times, geodetic information  or CWI
+separations. For example, if coda waves are used we have
+$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 |
+\widetilde{\mitbf{\delta}}_{CWIN})$ and
+$P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2,
+\mathbf{e}_3)$ where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the
+wavelength normalised separation estimates. Alternatively, if we use
+CWI and travel time data we may write $P(\mathbf{e}_1, \mathbf{e}_2,
+\mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN},
+\mathbf{\Delta}_{TT})$ and
+$P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{\Delta}_{TT}|\mathbf{e}_1,
+\mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
+travel time differences. In this derivation and in Sec.
+\ref{sec:benchmarking} we focus on the constraints imposed by coda
+waves, whereas in Sec. \ref{sec:CalaverasLoc-CWIandTT} we
+demonstrate how CWI and travel time data can be combined.
 
@@
 
-We use synthetic examples in 2D with 50 earthquakes to test the performance of the optimisation
-routine.
+We use synthetic examples in 2D and 3D with 50 earthquakes to test
+the performance of the optimisation routine.
 
@@
 \end{equation}
-using eq. (\ref{eq:mu1}). This assumption ensures that
-the sample mean of hypothetical separation estimates is consistent with known CWI
-biases \citep{dr_Robinson10b}. In example 1 we use $\bar{\sigma}_N=0.02$ between all event pairs.
-Application of our optimisation procedure on the hypothetical CWI data yields the circles
-in Fig. \ref{fig-2D50eq-relocation_eg1}. The optimisation does not lead to the correct
-solution due to the addition of noise $\bar{\sigma}_N=0.02$ on the hypothetical
-CWI data. The average coordinate error
-is 2.0\,m which is small compared to the noise of $\bar{\sigma}_N=0.02$ which for
-$v_s=3300$\,ms$^{-1}$ and $f_{dom}=2.5$\,Hz corresponds to roughly 25\,m.
+using eq. (\ref{eq:mu1}). This assumption ensures that the sample
+mean of hypothetical separation estimates is consistent with known
+CWI biases \citep{dr_Robinson11a}. In example 1 we use
+$\bar{\sigma}_N=0.02$ between all event pairs. Application of our
+optimisation procedure on the hypothetical CWI data yields the
+circles in Fig. \ref{fig-2D50eq-relocation_eg1}. The optimisation
+does not lead to the correct solution due to the addition of noise
+$\bar{\sigma}_N=0.02$ on the hypothetical CWI data. The average
+coordinate error is 2.0\,m which is small compared to the noise of
+$\bar{\sigma}_N=0.02$ which for $v_s=3300$\,ms$^{-1}$ and
+$f_{dom}=2.5$\,Hz corresponds to roughly 25\,m.
 \begin{figure}
 \includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise $\bar{\sigma}_N=0.02$.
-Actual and optimisation event locations
-are shown in blue and red circles, respectively.}
-\label{fig-2D50eq-relocation_eg1}
+\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
+optimisation event locations are shown in triangles and circles,
+respectively.} \label{fig-2D50eq-relocation_eg1}
 \end{figure}
@@
  Actual and optimisation event locations
-are shown in blue and red circles, respectively.}
+are shown in triangles and circles, respectively.}
 \label{fig-2D50eq-relocation_eg3}
 \end{figure}
-\citet{dr_Robinson10b} demonstrates that the noise on CWI estimates is often larger than 0.02 and that it increases
-with event separation. Consequently, example 1 is overly simplistic because we fix
-$\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase the uncertainty and introduce a distance
-dependance into the hypothetical $\bar{\sigma}_N$ by defining
-$\bar{\sigma}_N=\sigma_{1to5Hz}(\delta_t)$, where $\sigma_{1to5Hz}(\delta_t)$ is the half-width of
-the errorbars for a synthetic acoustic experiment
-with filtering between 1 and 5\,Hz \citep[see Fig4(b) of ][]{dr_Robinson10b}.
-Repeating the optimisation leads
-to the circles in Fig. \ref{fig-2D50eq-relocation_eg3} which have an average coordinate error of 2.8\,m.
-
-Conjugate gradient based optimisation techniques are susceptible to the presence of local minima.
-This is because they use the slope of the target function to explore the solution space.
-We explore the impact of local minima for our CWI location problem by beginning
-the optimisation from 25 different randomly chosen starting positions. In this case we observe no differences
-in the solution for neither examples 1 or 2.
-
-We can draw three observations from the error structure in Figs. \ref{fig-2D50eq-relocation_eg1} and
-\ref{fig-2D50eq-relocation_eg3}. Firstly, we note that the location errors depicted
-by grey bars in each figure increase between examples 1 and 2 with the
-introduction of larger noise. Secondly, the errors are larger for
-events at greater distances from the center. This is because events near the center of the cluster are
-constrained by links from all angles, whereas those
-on the outside are moderated by links from a limited number of directions. This observation is analogous
-to problems associated with poor azimuthal coverage in common triangulation problems such as individual earthquake location
-from limited travel time data, or GPS positioning with few satellites. Our third observation is that the location errors appear to
-be circular, despite our attempt to correct for rotational non-uniqueness with the local coordinate system.
-
-The local coordinate system works by constraining the location of the first three
-earthquakes. Earthquake 1 is fixed at the origin, earthquake 2 on the positive $\hat{x}$-axis and earthquake 3
-has $\hat{y}>0$. As the number of events increases the strength of this constraint on later events
-becomes weaker allowing small rotations of events with respect to each other.
-That is, even though the rotational freedom of the cluster is in principal
-removed by the constraints imposed on the events (see eqs. \ref{eq:coord-const1} to \ref {eq:coord-const4}) we observe that
-in practice the effects of noise means that the rotational non-uniqueness
-reappears. This is because the `easiest' way data noise can propagate is into
-the direction which is least constrained by the data. It is the same phenomena as in
-linear inversion where noise creates large spurious model changes in directions
-of the eigenvectors with the smallest singular values \citep[e.g ][]{dr_Aster05a}.
-Unfortunately, there is no obvious way to overcome this issue when using coda
-waves alone since the constraints are based on separation. Fortunately however, combining coda waves with
-measurements of travel times alleviates this problem and facilitate the removal of a local coordinate system
+\citet{dr_Robinson11a} demonstrates that the noise on CWI estimates
+is often larger than 0.02 and that it increases with event
+separation. Consequently, example 1 is overly simplistic because we
+fix $\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase
+the uncertainty and introduce a distance dependance into the
+hypothetical $\bar{\sigma}_N$ by defining
+$\bar{\sigma}_N=\sigma_{1to5Hz}(\delta_t)$, where
+$\sigma_{1to5Hz}(\delta_t)$ is the half-width of the errorbars for a
+synthetic acoustic experiment with filtering between 1 and 5\,Hz
+\citep[see Fig4(b) of ][]{dr_Robinson11a}. Repeating the
+optimisation leads to the circles in Fig.
+\ref{fig-2D50eq-relocation_eg3} which have an average coordinate
+error of 2.8\,m.
+
+Conjugate gradient based optimisation techniques are susceptible to
+the presence of local minima. This is because they use the slope of
+the target function to explore the solution space. We explore the
+impact of local minima for our CWI location problem by beginning the
+optimisation from 25 randomly chosen starting positions. We observe
+no differences in the solution for either example.
+
+We can draw three observations from the error structure in Figs.
+\ref{fig-2D50eq-relocation_eg1} and \ref{fig-2D50eq-relocation_eg3}.
+Firstly, the location errors depicted by grey bars increase between
+examples 1 and 2 with the introduction of larger noise. Secondly,
+the errors are larger for events at greater distances from the
+center. This is because events near the center of the cluster are
+constrained by links from all angles, whereas those on the outside
+are moderated by links from a limited number of directions. This
+observation is analogous to problems associated with poor azimuthal
+coverage in common triangulation problems such as individual
+earthquake location from limited travel time data, or GPS
+positioning with few satellites. Our third observation is that the
+location errors appear to be circular, despite our attempt to
+correct for rotational non-uniqueness with the local coordinate
+system.
+
+The local coordinate system works by constraining the location of
+the first three earthquakes. Earthquake 1 is fixed at the origin,
+earthquake 2 on the positive $\hat{x}$-axis and earthquake 3 has
+$\hat{y}>0$. As the number of events increases the strength of this
+constraint on later events becomes weaker allowing small rotations
+of events with respect to each other. That is, even though the
+rotational freedom of the cluster is in principal removed by the
+constraints imposed on the events (see eqs. \ref{eq:coord-const1} to
+\ref {eq:coord-const4}) we observe that in practice the presence of
+noise allows the rotational non-uniqueness to reappear. This is
+because the `easiest' way data noise can propagate is into the
+direction which is least constrained by the data. The same phenomena
+is observed in linear inversion where noise creates large spurious
+model changes in directions of the eigenvectors with the smallest
+singular values \citep[e.g ][]{dr_Aster05a}. Unfortunately, there is
+no obvious way to overcome this issue when using coda waves alone
+since the constraints are based on separation. Fortunately however,
+combining coda waves with measurements of travel times alleviates
+this problem and facilitate the removal of a local coordinate system
 altogether.
 
-Despite these observations about the error structure however, we gain confidence in the
-optimisation procedure due to its stability for different starting locations and
-because of the small average coordinate errors of 2.0\,m and 2.8\,m
-for examples 1 and 2, respectively.
+Despite our observations about the error structure however, we gain
+confidence in the optimisation procedure due to its stability for
+different starting locations and because of the small average
+coordinate errors of 2.0\,m and 2.8\,m for examples 1 and 2,
+respectively.
 
@@
 
-A set of earthquakes and their corresponding coda wave estimates of separation can be thought of as
-a network. In this network the earthquakes are nodes and the constraints are branches or links
-which join them together. Synthetic examples 1 and 2 use 100\% direct linkage between event pairs. That is, there is a constraint
-between each earthquake and all other events. In reality, we might expect that the separation between some
-pairs will not be constrained by CWI data due to poor signal to noise ratio in the coda for common stations.
-Obviously, the less stations that record an event the more likely it is that links
-between it and other events will be broken.
-In such cases the probabilistic distance constraint between a pair of
-events may only exist indirectly through multiple pairs. In this section we
-consider the impact of reduced linkage between event pairs. In example 3, we repeat example 2
-using 90\%, 80\%, ..., 10\% of the links. As with the above examples, we undertake the
+A set of earthquakes and their corresponding coda wave estimates of
+separation form a network. In this network the earthquakes are nodes
+and the constraints are branches or links which join the nodes
+together. Synthetic examples 1 and 2 use 100\% direct linkage
+between event pairs. That is, there is a constraint between each
+earthquake and all other events. In reality, we might expect that
+the separation between some pairs will not be constrained by CWI
+data due to poor signal to noise ratio in the coda for common
+stations. Obviously, the less stations that record an event the more
+likely it is that links between it and other events will be broken.
+In such cases the probabilistic distance constraint between a pair
+of events may only exist indirectly through multiple pairs. In this
+section we consider the impact of reduced linkage between event
+pairs. In example 3, we repeat example 2 using 90\%, 80\%, ..., 10\%
+of the links. As with the above examples, we undertake the
 optimisation with 25 randomly chosen starting locations.
@@
 
-In Figs. \ref{fig:optimisationresults-2Dsynth}(a) and (b) we examine the performance of the optimisation statistically. In particular,
-we plot the maximum $\Delta_{max}$ and mean $\Delta_\mu$ of the coordinate difference as a function of increasing linkage.
-We show the statistics for the `best' optimisation solution (black) and for the solution space
-when all 25 optimisations are considered (grey). In this case the best solution is determined
-by the set of event locations which lead to the smallest value of $L$.
-We observe similar errors in the best solution for all cases when at least 30\% of the
-branches are used. The errors increase drastically when only 10\% or 20\% of the constraints are included.
-Interestingly, this breakdown around 20\% to 30\% coincides with the point where the average number of branches
-required to link each pair reaches 2 (see Fig.\ref{fig:optimisationresults-2Dsynth}(c)). Since the average number of branches can be computed
-in advance it can be used as an indication of the potential stability of the inversion prior
-to optimisation. An earlier breakdown is observed when all 25 solutions
-are considered collectively. For example, the
-maximum coordinate error $\Delta_{max}$ is significantly higher than that for the best solution for all
-cases with 60\% of the constraints or less. This observation suggests that
-the optimisation is susceptible to the presence of local minima and that a range of starting points
-should be considered.
+In Figs. \ref{fig:optimisationresults-2Dsynth}(a) and (b) we examine
+the performance of the optimisation statistically. In particular, we
+plot the maximum $\Delta_{max}$ and mean $\Delta_\mu$ of the
+coordinate difference as a function of increasing linkage. We show
+the statistics for the `best' optimisation solution (black) and for
+the solution space when all 25 optimisations are considered (grey).
+In this case the best solution is determined by the set of event
+locations which lead to the smallest value of $L$. We observe
+similar errors in the best solution for all cases when at least 30\%
+of the branches are used. The errors increase drastically when only
+10\% or 20\% of the constraints are included. Interestingly, this
+breakdown around 20\% to 30\% coincides with the point where the
+average number of branches required to link each pair reaches 2 (see
+Fig.\ref{fig:optimisationresults-2Dsynth}(c)). Since the average
+number of branches can be computed in advance it can be used as an
+indication of the potential stability of the inversion prior to
+optimisation. An earlier breakdown is observed when all 25 solutions
+are considered collectively. For example, the maximum coordinate
+error $\Delta_{max}$ is significantly higher than that for the best
+solution for all cases with 60\% of the constraints or less. This
+observation confirms that the optimisation is susceptible to the
+presence of local minima and that a range of starting points should
+be considered.
 
@@
 
-As in the 2D example we observe a consistency of the optimisation procedure when the number of direct links used
-is high. That is, when 70\% of the direct constraints are considered all optimisation results (grey) are consistent with
-the best solution (black). Furthermore, the best solution appears to constrain the event locations down to 30\%
-of the direct links. There is however, one notable difference between the 3D and 2D results.
-In 2D the final iteration was typically close to the actual solution
-when the optimisation chain failed to converge after 1200 iterations. Contrastingly,
-in 3D the optimisation appears to converge to the correct solution or fail completely, leading to a set locations which
-in no way resemble the actual solution. This is depicted in Fig. \ref{fig:optimisationresults-3Dsynth}
-by the absence of the grey and black lines below 60\% and 30\% of the constraints, respectively.
-The reason for this difference may be due to the increased number of degrees
-of freedom in 3D requiring a greater number of iterations to converge. Nevertheless, the accurate convergence of the best
-solution for cases with 30\% or more of the links is encouraging for the potential
-of coda wave optimisation to constrain earthquake location more generally.
+As in the 2D example we observe a consistency of the optimisation
+procedure when the number of direct links used is high. That is,
+when 70\% of the direct constraints are considered all optimisation
+results (grey) are consistent with the best solution (black). The
+best solution constrains the event locations down to 30\% of the
+direct links.
+
+There is one notable difference between the 3D and 2D results. In 2D
+the final iteration was typically close to the actual solution when
+the optimisation chain failed to converge after 1200 iterations.
+Contrastingly, in 3D the optimisation appears to converge to the
+correct solution or fail completely, leading to a set locations
+which in no way resemble the actual solution. This is depicted in
+Fig. \ref{fig:optimisationresults-3Dsynth} by the absence of the
+grey and black lines below 60\% and 30\% of the constraints,
+respectively. The reason for this difference may be due to the
+increased number of degrees of freedom in 3D requiring a greater
+number of iterations to converge. Nevertheless, the accurate
+convergence of the best solution for cases with 30\% linkage or
+higher is encouraging for the potential of coda wave optimisation to
+constrain earthquake location more generally.
 
@@
 
-In summary, the synthetic examples demonstrate the ability of coda wave data to constrain event location
-using optimisation. The optimisation error is influenced by the
-noise on CWI estimates with greater $\bar{\sigma}_N$ leading to larger
-errors in the solutions. When 70\% or more of the direct branches are used the
-optimiser is stable with no observable difference in the solution for 25 randomly chosen starting
-locations. As the direct linkage reduces to 50\% the optimisation becomes less stable and the best solution
-from 25 random starting locations is required to find the optimal solution. Finally, as the number of links decrease
-below 30\% the best solution also fails to converge to a useful result.
+In summary, the synthetic examples demonstrate the ability of coda
+wave data to constrain relative event location using optimisation.
+The optimisation error is influenced by the noise on CWI estimates
+with greater $\bar{\sigma}_N$ leading to larger errors in the
+solutions. When 70\% or more of the direct branches are used the
+optimiser is stable with no observable difference in the solution
+for 25 randomly chosen starting locations. As the direct linkage
+reduces to 50\% the optimisation becomes less stable and the best
+solution from 25 random starting locations is required to find the
+optimal solution. Finally, as the number of links decrease below
+30\% the best solution also fails to converge to a useful result.
 
@@
 
-In this section we consider real
-earthquakes and undertake a complete coda wave analysis beginning with waveform selection, filtering, pairwise application
-of CWI and optimisation.
-\begin{itemize}
-\item Introduce the Calaveras Fault and provide a brief background of why it is chosen here (Figure \ref{fig:-eqopti-California-Calaveras})
-\item Discuss Catalogue Locations - hypoDD locations and CWI locations
-(Figure \ref{fig-69Calaverasevents_eg1})
-\begin{itemize}
-\item mention difference between hypoDD inversions when 68 or
-308 earthquakes considered but don't show figure (i.e. difference in coordinates for
-the two solutions is roughly 2\,m)
-\item provide details on CWI application - waveform selection, filtering etc.
-\end{itemize}
-\item Discuss comparison between CWI and catalogue locations - first order performance of CWI and clustering
-\item Discuss comparison between CWI and hypoDD locations - second order result and streaks.
-\end{itemize}
+In this section we relocate 68 earthquakes from the Calaveras Fault,
+California. The 68 earthquakes are selected from the 308 earthquake
+Calaveras example released with the open source Double Difference
+algorithm or hypoDD \citep{dr_Waldhauser00a,dr_Waldhauser01a}. These
+events are chosen for three reasons. Firstly, they are recorded by a
+large number of stations (figure
+\ref{fig:-eqopti-California-Calaveras}) and therefore lend
+themselves to accurate travel time location. Secondly, they are
+distributed over a range of distances between near zero and hundreds
+meters making them ideal for application of CWI. Finally, Calaveras
+earthquakes have been well researched with several studies having
+relocated events in the region \citep{dr_Waldhauser01a,
+dr_Schaff02a, dr_Waldhauser08a}. The relocations in this paper are
+sorted into four examples summarised in table \ref{tab:examples}.
 
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Elevation in California showing location
-of the 308 event Calaveras cluster (black star) and 805 seismic stations (red triangles).}
-\label{fig:-eqopti-California-Calaveras}
+\noindent\includegraphics[width =
+20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
+\caption{Elevation in California showing location of the 308 event
+Calaveras cluster (black star) and 805 seismic stations (red
+triangles).} \label{fig:-eqopti-California-Calaveras}
 \end{figure}
+
+\begin{table}
+\caption{Experiment locations performed for 68 earthquakes on teh
+Calaveras Fault} \label{tab:examples}
+\begin{tabular}{ll}
+\hline
+Example 1 & comparison of CWI, catalogue and hypoDD \\
+ & locations. \\
+Example 2 & exploration of station dependance for CWI and \\
+ & hypoDD. \\
+Example 3 & combined use of CWI and travel time data \\
+& with all and a reduced number of stations. \\
+Example 4 & combined use of CWI and travel time data \\
+ & when travel times constrain only 50\% of the events. \\
+ \hline
+\end{tabular}
+\end{table}
+
+\subsection{Example 1 - comparison of CWI, catalogue and hypoDD locations}
+
+Figure \ref{fig-69Calaverasevents_eg1} illustrates three sets of
+locations for the Calaveras earthquakes. The first column shows the
+original catalogue locations for all 308 earthquakes when each event
+is located individually using all available travel time arrivals and
+a regional velocity model. The 68 earthquakes of interest in this
+study are0 differentiated in black. Catalogue locations suggest that
+the 68 earthquakes of interest are distributed spatially throughout
+all events.
 
@@
 \includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-308 events (column 2) and CWI example 1 (column 3).
-Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
+\caption{Comparison of earthquake hypocenters using three different
+methods: catalogue location (column 1), hypoDD with all 308 events
+(column 2) and CWI example 1 (column 3). Note that in the case of
+the CWI locations we consider only the 68 earthquakes in red, the
 blue events are shown for the purpose of orientation only.}
@@
 
-\subsection{Dependance on the number of stations}
-
-\begin{itemize}
-\item Explain issues associated with poor station coverage - superimpose
-the three SWSZ (i.e. Australian) stations onto  Figure
-\ref{fig:-eqopti-California-Calaveras}
-\item Show setup for consideration of fewer stations (Table
-\ref{tab:Calaveras-stationremoval}
-and Figure \ref{fig:-eqopti-Calaveras-substations})
-\item Show the results (Figures \ref{fig-68Calaveras_CWIxyloc-statremove}
-to \ref{fig-68Calaveras_hypoDDyzloc-statremove} and Figure \ref{fig-statremoval_summarystats})
-\item Discuss the better performance of CWI with fewer stations
-\item Question/Discuss why hypoDD continues to suggest streaks with 2 or 3 stations - there must be regularization
-\end{itemize}
+Now, we turn our attention to the coda waves to see if we can locate
+the events using CWI. Available waveforms for the 68 earthquakes are
+downloaded from the Northern California Earthquake Data Center
+(NCEDC) and visually inspected. Unsuitable waveforms are removed
+using the conditions summarised in table 5 of
+\citep{dr_Robinson11a}. The remaining waveforms are filtered between
+1 and 5\,Hz and aligned  to $P$ arrivals at 0\,s. CWI estimates are
+obtained from 5\,s wide non-overlapping time windows between $2.5
+\leq t \leq 20$\,s and used to create probabilistic constraints on
+event separation. We introduce the local coordinate system of
+section \ref{sec:theory} and find the relative locations using the
+CWI data and Polak-Ribiere optimisation.
+
+The CWI locations for the 68 events are illustrated in column two of
+figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (grey)
+are shown for the remaining 240 earthquakes and are included to ease
+comparison. The third column of figure
+\ref{fig-69Calaverasevents_eg1} illustrates the locations given by
+hypoDD with Singular Value Decomposition (SVD) when absolute arrival
+times and cross correlation computed time differences for the 68
+earthquakes are considered collectively.
+
+Note that by using coda waves alone we can not obtain actual
+locations. For the sake of comparison, we arbitrary choose a
+`master' event and translate our locations to align with the hypoDD
+location for the same event. We return to this issue of relative
+versus actual location in Example 3 by introducing a combined travel
+time and coda wave inversion.
+
+The spatial distribution of the CWI locations is clearly tighter
+than the catalogue locations of column 1. That is, CWI provides an
+independent indication of clustering for the 68 events and to first
+order, similar locations to those from hypoDD (column 3).
+Interestingly, we observe a smaller second order difference between
+the CWI and hypoDD based locations. In particular, the lineation is
+less clear in the CWI locations (column 2) than that suggested by
+the hypoDD (column 3). Our results suggest that the coda are less
+supportive of the presence of streaks although a complete
+understanding of these differences is left for future work. Our
+attention now is devoted towards understanding how both techniques
+perform with fewer stations (Example 2) and exploring how the two
+techniques may be combined (Examples 3 and 4).
+
+\subsection{Example 2 - Dependance on the number of stations}
+
+Accurate location of the Calaveras events is possible using arrival
+phases because of the excellent recording situation in California
+with many stations and strong azimuthal coverage (see figure
+\ref{fig:-eqopti-California-Calaveras}). In contrast, a small number
+of stations and poor azimuthal coverage are common limitations when
+trying to understand intraplate seismicity. For example, there are
+only 3 network seismic stations in the South West Seismic Zone of
+Western Australia, a region similar in size to that hosting 805
+stations in figure \ref{fig:-eqopti-California-Calaveras}.
+
+We explore the impact of poorer recording situations in Example 2 by
+re-locating the 68 Calaveras events  using hypoDD and coda waves
+with a reduced number of stations. We begin with 10 stations and
+repeat the process removing one at a time until a single station
+remains. The 10 stations considered are shown in figure
+\ref{fig:-eqopti-Calaveras-substations} and the order of removal
+explained in table \ref{tab:Calaveras-stationremoval}.
 
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-\caption{Location of the 10 stations (red triangles) used to relocate the Calaveras events.
-Stations are removed one at a time according to the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated (see Figures \ref{fig-68Calaveras_CWIxyloc-statremove} to \ref{fig-68Calaveras_hypoDDyzloc-statremove}).
-The 304 Calaveras events are indicated with black circles.}
+\noindent\includegraphics[width =
+20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
+\caption{Location of the 10 stations (triangles) used to relocate
+the Calaveras events in Example 2. Stations are removed one at a
+time according to the order in Table
+\ref{tab:Calaveras-stationremoval} and the events relocated. The
+events are indicated with black circles.}
 \label{fig:-eqopti-Calaveras-substations}
@@
 \begin{table}
-\caption{Stations considered when exploring the effect of reduced station coverage.}
-\label{tab:Calaveras-stationremoval}
+\caption{Stations considered when exploring the imnpact of reduced
+station coverage.} \label{tab:Calaveras-stationremoval}
 \begin{tabular}{|r|l|}
@@
 
+The CWI locations are illustrated in figure
+\ref{fig-CWIreducesstats} for the inversions with 7, 5, 4, 3, 2 and
+1 station. We observe a high level of consistency between these 6
+inversions and the locations shown in figure
+\ref{fig-69Calaverasevents_eg1} (column 2) when all stations are
+considered. That is, the coda wave approach is self-consistent
+regardless of the number of stations available, reinforcing our
+hypothesis that coda waves can constrain location in poor recording
+situations.
+
 \begin{figure*}
 \includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{....}
-\label{fig-CWIreducesstats}
+\caption{....} \label{fig-CWIreducesstats}
 \end{figure*}
+
+Figure \ref{fig-HYPODDreducesstats} illustrates the hypoDD inversion
+results for 7, 5 and 4 stations. The travel time problem is
+ill-posed for fewer than 4 stations so it is not possible to apply
+hypoDD with SVD for 3 or fewer stations.  The hypoDD locations are
+not self-consistent as the number of stations is reduced. We observe
+a general increase in scatter and a higher number of stray events
+outside the cluster when less stations are used with hypoDD. Even
+with 7 stations the linear streak of figure
+\ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
 
@@
 %%=========================================================================
+
+As the number of stations are reduced both the CWI and hypoDD
+techniques are not able to re-locate all events. To use the coda
+waves we need at least one pairwise separation constraint to be
+formed from the available stations. This means that for every event
+there must be at least one station that records it and at least one
+other earthquake sufficiently well to apply CWI. Fortunately, we can
+make an assessment of this prior to starting the inversion. The top
+row of figure \ref{fig-statremoval_summarystats} demonstrates that
+when 5 or more stations are used we can constrain the location of
+all 68 earthquakes. When less than 5 stations are used the coda
+waves constrain a decreasing number of events until at 1 station it
+is only possible to locate 55 events.
 
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
-\caption{Statistics on coordinate differences for reduced station inversions. Differences
-are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-locations for all 308 events. The top subplot illustrates the number of constrainable
-events in the CWI and hypoDD inversions as a function of the stations considered.}
+\noindent\includegraphics[width =
+20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Statistics on
+coordinate differences for reduced station inversions. Differences
+are computed between the inversion results (CWI and hypoDD) and the
+complete hypoDD locations for all 308 events. The top subplot
+illustrates the number of constrainable events in the CWI and hypoDD
+inversions as a function of the stations considered.}
 \label{fig-statremoval_summarystats}
@@
 
-\section{Combining travel time and CWI constraints}
-\label{sec:CalaverasLoc-CWIandTT}
-\begin{itemize}
-\item Pose the problem
-\item Introduce the idea of a travel time based separation PDF with mean event locations from hypoDD outputs and
-some measure of uncertainty (we will consider three levels of uncertainty as in paper1).
-\item Explain how to combine the CWI based posterior with these new travel time based separation PDFs
-\item Show the derivatives of the travel time based separation PDF
-\item Undertake the combined inversion show/discuss findings (Figure \ref{fig-68Calaverasevents_ttandcoda1} )
-\end{itemize}
+The hypoDD program also struggles to locate all events as the number
+of stations is reduced. In the case of hypoDD an event can be
+identified as unconstrainable in one of two stages. Firstly, the
+data are analysed to ensure that there exists travel time
+differences for each event and at least one other earthquake. This
+is analogous to the situation for the coda wave technique. The
+hypoDD program also has a secondary identification phase in which
+events that can not be located sufficiently are rejected during the
+inversion. This process is presumably related to the iterative
+removal of outliers described by \citet{dr_Waldhauser00a}. The top
+row of figure \ref{fig-statremoval_summarystats} shows that the
+number of events re-located by hypoDD fluctuates between 63 and 28
+earthquakes for 10 to 4 stations and it demonstrates that the number
+of events located by hypoDD is less than the number located by CWI
+in all cases.
+
+The remaining rows of figure \ref{fig-statremoval_summarystats}
+illustrate a statistical comparison of the CWI and hypoDD reduced
+station locations to those using hypoDD with all available data. For
+the CWI inversions the mean and maximum coordinate difference is
+consistent regardless of the number of stations considered. In
+contrast, the statistics for the hypoDD inversions fluctuate between
+... and .... for the mean coordinate error and ... and ...  for the
+maximum confirming that the hypoDD inversion procedure is less
+stable than CWI with fewer stations.
+
+\section{Theory for Combining travel time and CWI constraints}
+
+In Examples 1 and 2 we compare the location of the Calaveras
+earthquakes using coda wave and arrival time based constraints
+independently. Since the arrival time (direct or difference) and
+coda wave data
+ come from different sections of the waveform they provide independent constraints on the locations.
+ In this section we devise a location algorithm which incorporates
+ both CWI and travel time data.
+
+We do not propose a new technique for earthquake location using
+travel time differences. Rather, we exploit the information created
+by hypoDD with SVD to define a probability density (or posterior)
+function
+\begin{equation}
+\label{eq-multi-var-Gauss-tt} P(\mathbf{e}_p|\Delta_{TT}) =
+\frac{1}{(2\pi)^{\frac{3}{2}}\sqrt{|\Sigma|}} \exp
+\left({-\frac{1}{2}\left([\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T
+\Sigma^{-1} [\mathbf{e}_p-\mu_{\mathbf{e}_p}]\right)} \right),
+\end{equation}
+where
+\begin{equation}
+\mathbf{e}_p = (x_p,y_p,z_p)^T
+\end{equation}
+is the location of event $p$,
+\begin{equation}
+\mu_{\mathbf{e}_p} = (\mu_{x_p}, \mu_{y_p},\mu_{z_p})^T
+\end{equation}
+is the most likely location as determined using the travel time
+data, and
+\begin{equation}
+\label{eq:Sigma-expression}
+\Sigma = \left( \begin{array}{ccc} \sigma_{x_p}^2 & 0 & 0\\
+0 &  \sigma_{y_p}^2 & 0 \\
+0 & 0 & \sigma_{z_p}^2  \end{array} \right)
+\end{equation}
+is the covariance matrix. In this paper we define the mean location
+$\mu_{\mathbf{e}_p}$ and covariance matrix by hypoDD optimum
+solution and its uncertainties. It is important to note that hypoDD
+must be used with SVD to obtain useful estimates of $\sigma_{x_p}$,
+$\sigma_{y_p}$ and $\sigma_{z_p}$ (\textbf{ADD REF}).
+
+We pose the location problem using the negative log likelihood
+\begin{equation}
+\label{eq-Lstar-tt-cwi} L(\mathbf{e}_1, \mathbf{e}_2, ...,
+\mathbf{e}_1, \mathbf{e}_n) = - \sum_{i=1}^n
+ln\left[P(\mathbf{e}_i|\Delta_{TT})\right] - \sum_{i=1}^{n-1}
+\sum_{j=i+1}^n
+ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right],
+\end{equation}
+where $(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n)$ is the joint
+location,
+\begin{equation}
+\label{eq-ttcomponent} \sum_{i=1}^n
+ln\left[P(\mathbf{e}_i|\Delta_{TT})\right]
+\end{equation}
+incorporates the travel time constraints and
+\begin{equation}
+\label{eq-codacomponent} \sum_{i=1}^{n-1} \sum_{j=i+1}^n
+ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right]
+\end{equation}
+ the coda waves.
+
+We must differentiate $L$ to use the Polak-Ribiere conjugate
+gradient technique of \citet{dr_Press87a}. The derivative of
+$L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n)$ with respect to
+$x_p$ is given by
+\begin{equation}
+\frac{\partial L}{\partial x_p} =  - \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p} \\
+- \sum_{i=p+1}^{N} \frac{ \partial \ln
+\left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
+x_p} - \sum_{j=1}^{p-1} \frac{ \partial \ln
+\left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
+x_p}
+\end{equation}
+where $\sum_{i=p+1}^{N} \frac{ \partial \ln
+\left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
+x_p}$ and $\sum_{j=1}^{p-1} \frac{ \partial \ln
+\left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
+x_p}$ are defined in Appendix \ref{sec-Appendix-derivatives_ofL} and
+\begin{equation}
+\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p}
+= -\frac{1}{2}\left([1,0,0]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [1,0,0] \right).
+\end{equation}
+Similarly, for the derivatives with respect to $y_p$ and $z_p$ we
+have
+\begin{equation}
+\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial y_p}
+= -\frac{1}{2} \left( [0,1,0]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,1,0] \right)
+\end{equation}
+and
+\begin{equation}
+\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial z_p}
+= -\frac{1}{2} \left( [0,0,1]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,0,1] \right).
+\end{equation}
+
+Aggregating the travel time and coda wave data offers two
+advantages. Firstly, it combines independent constraints on the
+event locations offering further confidence in the resulting
+solution. Secondly, the travel time constraints in the form of
+equation \ref{eq-ttcomponent} resolve the inherent non-uniqueness
+associated with translation, rotation and reflection around a global
+coordinate system. This means that it is no longer necessary to use
+a local coordinate system and we can solve directly for location
+with respect to a global reference. Collectively, these advantages
+improve the behavior of the Polak-Ribiere optimisation leading to
+faster and more stable convergence. Consequently, we no longer have
+to consider multiple randomly chosen starting locations.
+
+\subsection{Example 3 - Combining travel time and CWI constraints}
+\label{sec:CalaverasLoc-CWIandTT} Figure
+\ref{fig-68Calaverasevents_ttandcoda1} illustrates the earthquake
+locations obtained when we combine the travel time and coda wave
+data using all data (left) and 5 stations (right). The linear
+features observed in the original hypoDD inversions (see figure
+\ref{fig-69Calaverasevents_eg1}) is evident in both cases. However,
+the coda waves introduce a scatter around these streaks. That is,
+the locations in figure \ref{fig-68Calaverasevents_ttandcoda1}
+result from a trade-off between hypoDD's desire to place the events
+on linear features and the coda waves voracity to push them away
+from streaks. When all stations are used the hypoDD constraints are
+strong and little off-streak scatter is introduced. As we reduce
+hypoDD's leverage by decreasing the number of stations to 5, we
+observe an increase in off-streak scatter resulting from the
+enhanced influence of the coda.
 
@@
 %\end{figure*}
+
+% This is the version using hypoDD with SVD
+\begin{figure*}
+\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
+\caption{Combined HypoDD (SVD) and CWI: all stations and 5
+stations.} \label{fig-68Calaverasevents_ttandcoda1}
+\end{figure*}
+
 %%=========================================================================
 
-\subsection{Combining CWI and travel times when the travel times constrain a limited number of events}
-
-\begin{itemize}
-\item Explain the idea of a temporary deployment of stations i.e. for aftershocks
-\item Discuss Omori formula and the $M_s$7.8 Hokkaido-Nansei-Oki earthquake
-\citep[Figure \ref{fig:Omorifigure},]{dr_Utsu95a}
-\item Show/Discuss results (Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1})
-\end{itemize}
+\subsection{Example 4 - Combining CWI and travel times when the travel times constrain a limited number of events}
+
+In intraplate regions such as Australia it is common to deploy
+temporary seismometers to monitor aftershocks for significant events
+\citep{dr_Bowman90a, dr_Leonard02a}). Traditionally, these
+deployments are used to locate aftershocks to an accuracy of the
+temporary array, whereas events occurring outside the deployment
+period can only be located to the accuracy of the network. Using our
+combined inversion it is possible to re-locate all events by
+employing the detailed travel time data when the temporary network
+is in-situ and using coda waves from network stations when the
+deployment is absent.
+
+The Omori formula
+\begin{equation}
+label{eq:original_omori}
+ n(t) = K(t+C)^{-p}
+\end{equation}
+can be used to estimate the aftershock frequency per unit time
+interval $n(t)$ at time $t$ (\textbf{ADD REF}). \citet{dr_Utsu95a}
+converted equation \ref{eq:original_omori} to a cumulated number of
+events
+\begin{equation}
+N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}.
+\end{equation}
+
+The empirically derived constants, $K$, $C$ and $p$ vary between
+tectonic settings. For example, using recorded aftershocks with
+$M\ge3.2$ of the  Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of
+12 July 1993, \citet{dr_Utsu95a} obtains maximum likelihood
+estimates for $K$, $p$ and $c$ of 906.5, 1.256 and 1.433,
+respectively.  With these empirically derived values an array
+deployed within 4 days and left for 150 days will record roughly one
+half of the aftershocks occurring within the first 1000 days. That
+is,
+\begin{equation}
+\frac{N(150+4)-N(4)}{N(1000)} = \frac{2257-934}{2626} \approx 0.5.
+\end{equation}
+This idea is illustrated figure \ref{fig:Omorifigure} which shows
+the best fitting Omori Formula separated into segments before
+(dashed), during (solid) and after (dashed) the temporary
+deployment.
 
@@
 \noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-\caption{Cumulative number of aftershocks for the Hokkaido-Nansei-Oki, Japan
-$M_s=7.8$ earthquake of 12 July 1993 according to the best fitting modified Omori Formula
-\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost dashed signify aftershocks occurring before, during and
-after the deployment of a temporary array installed 7 days after the main shock and left for
-65 days.}
-\label{fig:Omorifigure}
+\caption{Cumulative number of aftershocks for the
+Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
+according to the best fitting modified Omori Formula
+\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost
+dashed signify aftershocks occurring before, during and after the
+deployment of a temporary array installed 4 days after the main
+shock and left for 150 days. A temporary deployment of this kind
+will record roughly 50\% of the aftershocks in the 1000 days
+following the mainshock. } \label{fig:Omorifigure}
 \end{figure}
+
+With this idea of a temporary deployment in mind we have another
+attempt at relocating the Calaveras earthquakes. This time however,
+we consider the travel time constraints on half (34) of the
+earthquakes and incorporate coda wave data from a single stations
+for all 68 earthquakes. The combined inversion is shown in column 1
+of figure \ref{fig-68Calaverasevents_ttsubsetandcoda1}. The
+inversion result is similar to the combined inversion when all
+travel time data is incorporated (see figure
+\ref{fig-68Calaverasevents_ttandcoda1}). The slight increase in
+scatter observed here can be explained by the events with no travel
+time constraints and the tendency of the coda to push events away
+from streaks.
+
+Remarkably, the combined coda wave and travel time inversion locates
+all 68 earthquakes to an accuracy similar to the inversions with all
+data. In contrast when travel time data is used alone it is only
+possible to locate the 34 events recorded by the pseudo temporary
+deployment. The ability of coda waves to link events during and
+outside the deployment period is likely their strongest asset. This
+ability of  coda waves to constrain the location of events recorded
+by a single station creates new opportunities for understanding
+earthquakes in regions with limited station coverage.
 
@@
 \begin{figure*}
-\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Combined HypoDD (SVD) and CWI: all stations and 5 stations.}
-\label{fig-69Calaverasevents_eg1}
+\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
+\caption{Mimicking the deployment of a temporary network by ignoring
+data from all but station CCO for 50\% (or 34) of the events using
+by combining CWI and TT (left) and using TT only (right). Only by
+combining the data is it possible to locate all 68 events.
+Furthermore, combining the data leads to a solution more consistent
+with figure ..... } \label{fig-68Calaverasevents_ttsubsetandcoda1}
 \end{figure*}
@@
 
+?????A number of studies have reported similar streaks on the
+Calaveras and other fault systems in California
+\citep{dr_Rubin99a,dr_Waldhauser99a, dr_Waldhauser02a, dr_Schaff02a,
+dr_Waldhauser04a}. \citet{dr_Rubinstein07a} argue that such streaks
+represent the boundary between creeping and locked sections of the
+faults. Earthquakes of interest for  our study align along one of
+these streaks. ???comment on circular versus linear error????
+
 \begin{acknowledgments}
-(Text here)
+Geoscience Australia, the Research School of Earth Sciences at The
+Australian National University, and the Center for Wave Phenomena at
+the Colorado School of Mines, are acknowledged for supporting this
+research. The paper is published with permission of the CEO
+Geoscience Australia. Work was conducted as part of an Australian
+Research Council Discovery Project (DP0665111). We thank the
+Northern California Earthquake Data Center (NCEDC) for providing the
+Calaveras data and the Northern California Seismic Network (NCSN),
+U.S. Geological Survey, Menlo Park and Berkeley Seismological
+Laboratory, University of California, Berkeley for contributing it
+to the NCEDC. We also acknowledge Felix Waldhauser and William
+Ellsworth, the authors of the openly available Double Difference
+location algorithm, hypoDD. This paper has benefited significantly
+from reviews by ......... at Geoscience Australia.
 \end{acknowledgments}
 
-\bibliography{../../refs/drrefs}
+\bibliography{../refs/drrefs}
 
@@
 \end{equation}
-\citep{dr_Robinson10b}. The parameters $\mu_1$ and $\sigma_1$ used in
-eq. (\ref{eq:Adefn}) are defined by the expresions
+\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
+in eq. (\ref{eq:Adefn}) are defined by the expresions
 \begin{equation}

### 2012-07-17 paper2/diags/build_OmoriFigure.m

@@ -2,8 +2,8 @@ function [] = build_OmoriFigure()
 
 % The purpose of this function is to build the Omori figure...
 
-tstart = 7;
-tdays = 65;
+tstart = 4;
+tdays = 150;
 tend = tstart+tdays; 
 ttotal = 1000;
 
@@ -22,7 +22,7 @@ N2 = Cumm_Omori(t2);
 hold on
 plot(t2,N2,'k','linewidth',4)
 
-t3 = [tend:100];
+t3 = [tend:200];
 N3 = Cumm_Omori(t3);
 plot(t3,N3,'k--','linewidth',4)
 

### 2012-07-17 paper2/diags/synth2Dmulti/plot_outcomes.m
imported from thesis subversion dir - a few minor changes to get it working - you need to use this to build the statistical figure for the 2D synthetic examples - use wrap_plot_outcomes

@@ -1,0 +1,125 @@
+function [inversion_results,fh] = plot_outcomes(dirname)
+currentdir = pwd;
+cd(dirname)
+
+opttype = 'fortran'; % 'fortran' or 'matlab'
+load(['randsearch_',opttype,'.mat'])
+[sorted_x2, ind]=sort(xend(2,:));
+
+[nevnts, nrand] = size(xend);
+
+inversion_results.otherstuff.E = E;
+
+% Have a quick look at the solution space
+fh.allsolutions = figure;
+colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'};
+colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'};
+
+% Plot the joiner lines between actual location and optimisation solns
+for i = 1:nevnts
+    for j = 1:nrand
+        plot([xend(i,j) E(i,1)], [yend(i,j) E(i,2)],'Color','k')
+        hold on
+    end
+end
+% Plot the optimisation solutions
+for i = 1:nevnts
+    plot(xend(i,:), yend(i,:),'ro','markersize',7)
+    hold on
+end
+% Plot the actual solutions
+for i = 1:nevnts
+    plot(E(i,1),E(i,2), 'bo', 'markersize',7)
+    hold on
+end
+plot([ 0 0], get(gca,'ylim'),'k')
+plot(get(gca,'xlim'),[0 0],'k')
+
+
+
+% figure
+% colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
+% colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
+% ind = find(f<-127.38);
+% for i = 1:nevnts
+%     plot(E(i,1), E(i,2), 'bo','markersize',10)
+%     hold on
+%     %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
+%     for j = 1:length(ind)
+%         plot(xend(i,ind(j)),yend(i,ind(j)), 'ro','markersize',10)
+%         hold on
+%         plot([xend(i,ind(j)) E(i,1)], [yend(i,ind(j)) E(i,2)],'Color',[0.7 0.7 0.7]),'linewidth',2,'markersize',10
+%     end
+% end
+% set(gca,'xlim',[-70,70], 'ylim',[-70,70], 'fontsize',18)
[…]

### 2012-07-17 paper2/diags/synth2Dmulti/run_script.m

@@ -1,0 +1,83 @@
+% This script sets up the runs and loops through all of the directrories
+
+%========================================
+% Setup parameters:
+opttype = 'fortran'; %use 'fortran' for speed or 'matlab' for small dimensional problems if needed
+fdom = 2.5;  % dominant frequency for synthetic data
+vs = 3300;  % shear wave velocity
+nrand = 30;  % number of random start locations
+nE = 50;   % nE number of events 
+npar = nE*2-2-1; % npar the number of parameters
+dirlist = { 'const_010perc'; 'const_020perc'; 'const_030perc'; ...
+            'const_040perc'; 'const_050perc'; ...
+            'const_060perc'; 'const_070perc'; 'const_080perc'; ...
+            'const_090perc'; 'const_100perc'};
+        
+%========================================
+% Generate the events 
+tic
+rand('state',0)
+E =  50 + (-50- 50).*rand(nE,2);
+E(1,:) = [0 0];  % fix first event at the centre
+E(2,1) = abs(E(2,1)); E(2,2) = 0; % fix the second event to be on the positive x-axis
+
+%========================================
+% Generate the constraints
+[nE, mE] = size(E);
+count = 1;
+for i = 1:nE-1
+    for j = i+1:nE
+        delta_tnorm(count) = sqrt( (E(i,1)- E(j,1))^2 +  (E(i,2)- E(j,2))^2)*fdom/vs;
+        [ynew_mu(count), ynew_sigma(count)] = make_synthetic_muN(delta_tnorm(count));
+        CWI_stat_master(count,:) = [i j 0.1 0.02 0.1 ynew_mu(count) 2*ynew_sigma(count) fdom vs];
+        count = count+1;
+        % col3 = mean
+        % col4 = std
+        % col5 = median
+        % col6 = mu_N for non-zero Gaussian by fitting
+        % col7 = sigma_N for non-zero Gaussian by fitting
+        % col8 = fdom
+    end
+end
+events_oi = 1:nE;
+save CWI_stat_master.mat CWI_stat_master events_oi  %save the master copy to avoid regeneration
+
+nconst = length(CWI_stat_master(:,1));
+clear CWI_stat
+%========================================
+% Now loop over the directories and run simulations
+currentdir = pwd;
+ndir = length(dirlist);
+for i = 1:ndir
+    disp(['===== Doing directory ', num2str(i),' of ', num2str(ndir),': ', dirlist{i}])
+    cd([currentdir,filesep,dirlist{i}])  % move to the run directory
[…]

### 2012-07-17 paper2/diags/synth2Dmulti/wrap_plot_outcomes.m

@@ -1,0 +1,233 @@
+% This script wraps the plotting function plot_outcomes.m 
+% assembles all of the data in a convenient format and then 
+% draws some plots analysing the simulations
+
+
+%if strcmp(filesep,'/')
+%    error('ERROR: you must run this on the Windows notebook to get the Latex figure labels')
+%end
+
+dirlist = { 'const_010perc'; 'const_020perc'; 'const_030perc'; ...
+            'const_040perc'; 'const_050perc'; ...
+            'const_060perc'; 'const_070perc'; 'const_080perc'; ...
+            'const_090perc'; 'const_100perc'};
+
+maxvals_all = zeros(1,length(dirlist));        
+meanvals_all = zeros(1,length(dirlist));
+stdvals_all = zeros(1,length(dirlist));
+minvals_all = zeros(1,length(dirlist));
+maxvals_best = zeros(1,length(dirlist));        
+meanvals_best = zeros(1,length(dirlist));
+stdvals_best = zeros(1,length(dirlist));
+minvals_best = zeros(1,length(dirlist));
+for i = 1:length(dirlist)
+    [res.(dirlist{i}),fh] = plot_outcomes(dirlist{i});
+    maxvals_all(i) = res.(dirlist{i}).allsol.maxval;
+    meanvals_all(i) = res.(dirlist{i}).allsol.meanval;
+    stdvals_all(i) = res.(dirlist{i}).allsol.stdval;
+    minvals_all(i) = res.(dirlist{i}).allsol.minval;
+    maxvals_best(i) = res.(dirlist{i}).bestsol.maxval;
+    meanvals_best(i) = res.(dirlist{i}).bestsol.meanval;
+    stdvals_best(i) = res.(dirlist{i}).bestsol.stdval;
+    minvals_best(i) = res.(dirlist{i}).bestsol.minval;
+    ticklabelstr{i} = [num2str(str2num(dirlist{i}(7:9))),'%'];
+    figure(fh.allsolutions)
+    switchval = dirlist{i};
+    switch switchval
+        case {'const_040perc'; 'const_050perc'; 'const_060perc'; ...
+              'const_070perc'; 'const_080perc'; 'const_090perc'; 'const_100perc'}
[…]

### 2012-07-17 paper2/diags/synth3Dmulti/plot_outcomes.m
imported from thesis subversion dir - a few minor changes to get it working - you need to use this to build the statistical figure for the 3D synthetic examples - use wrap_plot_outcomes

@@ -1,0 +1,91 @@
+function [inversion_results,fh] = plot_outcomes(dirname)
+currentdir = pwd;
+cd(dirname)
+
+opttype = 'fortran'; % 'fortran' or 'matlab'
+load(['randsearch_',opttype,'.mat'])
+[sorted_x2, ind]=sort(xend(2,:));
+
+[nevnts, nrand] = size(xend);
+
+inversion_results.otherstuff.E = E;
+
+% Have a quick look at the solution space
+%fh.allsolutions = figure;
+fh = [];
+colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'};
+colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'};
+
+%% Plot the joiner lines between actual location and optimisation solns
+%for i = 1:nevnts
+%    for j = 1:nrand
+%        plot([xend(i,j) E(i,1)], [yend(i,j) E(i,2)],'Color','k')
+%        hold on
+%    end
+%end
+% Plot the optimisation solutions
+%for i = 1:nevnts
+%    plot(xend(i,:), yend(i,:),'ro','markersize',7)
+%    hold on
+%end
+% Plot the actual solutions
+%for i = 1:nevnts
+%    plot(E(i,1),E(i,2), 'bo', 'markersize',7)
+%    hold on
+%end
+%plot([ 0 0], get(gca,'ylim'),'k')
+%plot(get(gca,'xlim'),[0 0],'k')
+
+[nevnts, nrand] = size(xend);
+
+
+% Do analysis of all solutions
+ExMat = repmat(E(2:end,1), 1,nrand);  % Note we are omiting the 0 values
+EyMat = repmat(E(3:end,2), 1,nrand);
+EzMat = repmat(E(3:end,3), 1,nrand);
+deltaxMat = ExMat - xend(2:end,:); 
+deltayMat = EyMat - yend(3:end,:);
+deltazMat = EzMat - zend(3:end,:);
+deltax = deltaxMat(:);
+deltay = deltayMat(:);
+deltaz = deltazMat(:);
+delta_coord = [deltax; deltay; deltaz];
+inversion_results.allsol.nrand = nrand;
+inversion_results.allsol.fminval = f;
+inversion_results.allsol.minval = min(abs(delta_coord));
+inversion_results.allsol.maxval = max(abs(delta_coord));
+inversion_results.allsol.meanval = mean(abs(delta_coord));
[…]

### 2012-07-17 paper2/diags/synth3Dmulti/run_script.m

@@ -1,0 +1,100 @@
+% This script sets up the runs and loops through all of the directrories
+
+%========================================
+% Setup parameters:
+opttype = 'fortran'; %use 'fortran' for speed or 'matlab' for small dimensional problems if needed
+fdom = 2.5;  % dominant frequency for synthetic data
+vs = 3300;  % shear wave velocity
+nrand = 30;  % number of random start locations
+nE = 50;   % nE number of events 
+npar = nE*3-3-2-1;
+dirlist = { 'const_010perc'; 'const_020perc'; 'const_030perc'; ...
+            'const_040perc'; 'const_050perc'; ...
+            'const_060perc'; 'const_070perc'; 'const_080perc'; ...
+            'const_090perc'; 'const_100perc'};
+        
+dirlist = {'const_100perc'};
+%dirlist = { 'const_050perc'; 'const_070perc'};
+%========================================
+% Generate the events 
+tic
+rand('state',0)
+E =  50 + (-50- 50).*rand(nE,3);
+E(1,:) = [0 0 0];  % fix first event at the centre
+E(2,1) = abs(E(2,1)); E(2,2) = 0; E(2,3) = 0;% fix the second event to be on the positive x-axis
+E(3,2) = abs(E(3,2)); E(3,3) = 0; 
+E(4,3) = abs(E(4,3)); %120
+%E(5,3) = -120;
+
+%========================================
+% Generate the constraints
+[nE, mE] = size(E);
+count = 1;
+for i = 1:nE-1
+    for j = i+1:nE
+        delta_tnorm(count) = sqrt( (E(i,1)- E(j,1))^2 +  (E(i,2)- E(j,2))^2 + (E(i,3)- E(j,3))^2)*fdom/vs;
+        [ynew_mu(count), ynew_sigma(count)] = make_synthetic_muN(delta_tnorm(count));
+        CWI_stat_master(count,:) = [i j 0.1 0.02 0.1 ynew_mu(count) ynew_sigma(count) fdom vs];
+        count = count+1;
+        % col3 = mean
+        % col4 = std
+        % col5 = median
+        % col6 = mu_N for non-zero Gaussian by fitting
+        % col7 = sigma_N for non-zero Gaussian by fitting
+        % col8 = fdom
+    end
+end
+events_oi = 1:nE;
+save CWI_stat_master.mat CWI_stat_master events_oi  %save the master copy to avoid regeneration
+
+nconst = length(CWI_stat_master(:,1));
+clear CWI_stat
[…]

### 2012-07-17 paper2/diags/synth3Dmulti/wrap_plot_outcomes.m

@@ -1,0 +1,198 @@
+% This script wraps the plotting function plot_outcomes.m 
+% assembles all of the data in a convenient format and then 
+% draws some plots analysing the simulations
+
+
+%if strcmp(filesep,'/')
+%    error('ERROR: you must run this on the Windows notebook to get the Latex figure labels')
+%end
+
+dirlist = { 'const_010perc'; 'const_020perc'; 'const_030perc'; ...
+            'const_040perc'; 'const_050perc'; ...
+            'const_060perc'; 'const_070perc'; 'const_080perc'; ...
+            'const_090perc'; 'const_100perc'};
+
+maxvals_all = zeros(1,length(dirlist));        
+meanvals_all = zeros(1,length(dirlist));
+stdvals_all = zeros(1,length(dirlist));
+minvals_all = zeros(1,length(dirlist));
+maxvals_best = zeros(1,length(dirlist));        
+meanvals_best = zeros(1,length(dirlist));
+stdvals_best = zeros(1,length(dirlist));
+minvals_best = zeros(1,length(dirlist));
+for i = 1:length(dirlist)
+    [res.(dirlist{i}),fh] = plot_outcomes(dirlist{i});
+    maxvals_all(i) = res.(dirlist{i}).allsol.maxval;
+    meanvals_all(i) = res.(dirlist{i}).allsol.meanval;
+    stdvals_all(i) = res.(dirlist{i}).allsol.stdval;
+    minvals_all(i) = res.(dirlist{i}).allsol.minval;
+    maxvals_best(i) = res.(dirlist{i}).bestsol.maxval;
+    meanvals_best(i) = res.(dirlist{i}).bestsol.meanval;
+    stdvals_best(i) = res.(dirlist{i}).bestsol.stdval;
+    minvals_best(i) = res.(dirlist{i}).bestsol.minval;
+    ticklabelstr{i} = [num2str(str2num(dirlist{i}(7:9))),'%'];
+    %figure(fh.allsolutions)
+    %set(gca,'xlim',[-150,150],'ylim',[-150,150])
+    %set(gca,'xtick',[-100,0 100],'ytick',[-100,0 100])
+    %set(gca,'xminortick','on','yminortick','on')
+    %plot([ 0 0], get(gca,'ylim'),'k')
[…]

### 2012-07-17 paper2/diags/build_OmoriFigure.m
minor changes to improve figure

@@ -22,7 +22,8 @@ N2 = Cumm_Omori(t2);
 hold on
 plot(t2,N2,'k','linewidth',4)
 
-t3 = [tend:200];
+tend2 = 1000;
+t3 = [tend:tend2];
 N3 = Cumm_Omori(t3);
 plot(t3,N3,'k--','linewidth',4)
 
@@ -30,6 +31,8 @@ fsize = 16;
 set(gca,'fontsize',fsize)
 xlabel('time (days)','fontsize',fsize)
 ylabel('Cummulative number of aftershocks','fontsize',fsize)
+
+set(gca,'xlim',[-25, tend2],'xtick',[0:100:tend2])
 
 print -depsc OmoriFigure.eps
 

### 2012-07-17 events/matlab/Lstar.m
added matlab events toolkit - copied from my thesis subversion directory

@@ -1,0 +1,330 @@
+function [f,grad] = Lstar(x)
+% This function takes a bunch of locations and returns the value of L* and 
+% its gradient at x (the location of N events with some minor
+% modification - see below). 
+%
+% INPUTS: 
+% x         [double - vector] A column vector containing the coordinates 
+%           for the events of interest. Note that if there are N events
+%           then length(x) = N-5 and has form 
+%             x = [x2, x3,y3,z3,x4,y4,z4,...,xN,yN,zN]'
+%           Note that x1 = y1 = z1 = 0 sets the first event to be the
+%           origin and y2 = z2 =0 sets the second event to be on the
+%           arbitrarily oriented x-axis. The two contstraints remove 
+%           non-uniqueness associated with translation and rotation 
+%           of the event set, respectively. 
+%
+% OUTPUTS:
+% f         [scalar] value of L* at x
+% grad      [vector] this is the gradient of L* at x
+% EXTRAS        **  Note that this function will search for a file called
+%                   CWI_stat in the local directory and load it. This file 
+%                   must contain a matrix with same name CWI_stat with 8 
+%                   columns as given by 
+%                       col1 = eventid1
+%                       col2 = eventid2
+%                       col3 = mean
+%                       col4 = std
+%                       col5 = median
+%                       col6 = mu_N for non-zero Gaussian by fitting
+%                       col7 = sigma_N for non-zero Gaussian by fitting
+%                       col8 = fdom
[…]

### 2012-07-17 events/matlab/Lstar_2D.m

@@ -1,0 +1,310 @@
+function [f,grad] = Lstar_2D(x)
+% This function takes a bunch of locations and returns the value of L* and 
+% its gradient at x (the location of N events with some minor
+% modification - see below). 
+%
+% INPUTS: 
+% x         [double - vector] A column vector containing the coordinates 
+%           for the events of interest. Note that if there are N events
+%           then length(x) = N-5 and has form 
+%             x = [x2, x3,y3,x4,y4,...,xN,yN]'
+%           Note that x1 = y1 = 0 sets the first event to be the
+%           origin and y2 =0 sets the second event to be on the
+%           arbitrarily oriented x-axis. The two contstraints remove 
+%           non-uniqueness associated with translation and rotation 
+%           of the event set, respectively. 
+%
+% OUTPUTS:
+% f         [scalar] value of L* at x
+% grad      [vector] this is the gradient of L* at x
+% EXTRAS        **  Note that this function will search for a file called
+%                   CWI_stat in the local directory and load it. This file 
+%                   must contain a matrix with same name CWI_stat with 8 
+%                   columns as given by 
+%                       col1 = eventid1
+%                       col2 = eventid2
+%                       col3 = mean
+%                       col4 = std
+%                       col5 = median
+%                       col6 = mu_N for non-zero Gaussian by fitting
+%                       col7 = sigma_N for non-zero Gaussian by fitting
+%                       col8 = fdom
+%               **  Note that the order of the events in CWI_stat is very
[…]

### 2012-07-17 events/matlab/Smooth2D.m

@@ -1,0 +1,92 @@
+function A = smooth2D(B)
+% Smooth2D smooths a matrix with a 3 x 3 running window. 
+%
+% David Robinson
+% APRIL 2003
+
+% Orientation as perceived by program
+% Note that 5 represents the point of interest
+% 1   4   7
+% 2   5   8
+% 3   6   9
+
+
+[n,m] = size(B);
+A = zeros(n,m);
+
+% All points on top row
+
+
+% All central points
+A(2:n-1,2:m-1)= ...
+    B(1:n-2,1:m-2) + ...       % 1   i.e. one shift up and one shift to the left    
+    B(2:n-1,1:m-2) + ...       % 2   i.e. one shift to the left
+    B(3:n,1:m-2)   + ...       % 3   i.e. one shift down and one shift to the left  
+    B(1:n-2,2:m-1) + ...       % 4   i.e. one shift up
+    B(2:n-1,2:m-1) + ...       % 5   i.e. central position     
+    B(3:n,2:m-1)   + ...       % 6   i.e. one shift down
+    B(1:n-2,3:m)   + ...       % 7   i.e. one shift up and one shift to the right
+    B(2:n-1,3:m)   + ...       % 8   i.e. one shift to the right
+    B(3:n,3:m);                % 9   i.e. one shift down and one shift to the right
+    
+ % Points in top centre
+ A(1,2:m-1)= ...
+    B(1,1:m-2) + ...           % 1   i.e. one shift up (take copy of actual) and one shift to the left    
+    B(1,1:m-2) + ...           % 2   i.e. one shift to the left
+    B(2,1:m-2) + ...           % 3   i.e. one shift down and one shift to the left  
+    B(1,2:m-1) + ...           % 4   i.e. one shift up (take copy of actual)
+    B(1,2:m-1) + ...           % 5   i.e. central position     
+    B(2,2:m-1) + ...           % 6   i.e. one shift down
+    B(1,3:m)   + ...           % 7   i.e. one shift up (take copy of actual) and one shift to the right
+    B(1,3:m)   + ...           % 8   i.e. one shift to the right
+    B(2,3:m);                  % 9   i.e. one shift down and one shift to the right
+
+% Points in Bottom centre
+A(n,2:m-1)= ...
+    B(n-1,1:m-2) + ...         % 1   i.e. one shift up and one shift to the left    
+    B(n,1:m-2) + ...           % 2   i.e. one shift to the left
[…]

### 2012-07-17 events/matlab/align_waveforms.m

@@ -1,0 +1,147 @@
+function [time1,wave1,time2,wave2,details] = align_waveforms(intime1,inwave1,intime2,inwave2,alignval1,alignval2,qa)
+% To align two waveforms
+% Note that the waves are truncated to the same length as well.
+%
+%INPUTS:
+% intime1   [double - vector] time values for wave 1
+% inwave1   [double - vector] wave 1
+% intime2   [double - vector] time values for wave 2
+% inwave2   [double - vector] wave 2
+% aignval1  [double - scalar] time value in time1 for which to align the vector
+%           around i.e. tp, ts or some other critical point.
+% aignval2  [double - scalar] time value in time2 for which to align the vector
+%           around i.e. tp, ts or some other critical point.
+% qa        [OPTIONAL]
+%               'v'  => verbose comments
+%
+% OUTPUTS:
+% time1   [double - vector] aligned time values for wave 1 (starts at 0 and truncated)
+% wave1   [double - vector] aligned wave 1 (truncated as needed)
+% time2   [double - vector] aligned time values for wave 2 (starts at 0 and truncated)
+% wave2   [double - vector] aligned wave 2 (truncated as needed) 
+% details [structure]  contains information about the alignment
+
+% make sure the intime1 and intime2 are row vectors (find_closest bombs if
+% they are column vectors)
+
+%% First we must make sure the waves cover roughly the same time bounds. If
+% they are vastly different then the following code may not work. 
+mintime = max([min(intime1),min(intime2)]);
+maxtime = min([max(intime1), max(intime2)]);
+% intime1 = intime1(intime1>=mintime & intime1<=maxtime);
+% inwave1 = inwave1(intime1>=mintime & intime1<=maxtime);
+% intime2 = intime2(intime2>=mintime & intime2<=maxtime);
+% inwave2 = inwave2(intime2>=mintime & intime2<=maxtime);
+ind1 = find(intime1>=mintime & intime1<=maxtime);
+intime1 = intime1(ind1);
+inwave1 = inwave1(ind1);
+ind2 = find(intime2>=mintime & intime2<=maxtime);
+intime2 = intime2(ind2);
+inwave2 = inwave2(ind2);
+
+intime1 = intime1(:);
+intime2 = intime2(:);
+[details.ind1,details.closest1,details.mind1] = find_closest(intime1,alignval1,'euclidean');
+[details.ind2,details.closest2,details.mind2] = find_closest(intime2,alignval2,'euclidean');
[…]

### 2012-07-17 events/matlab/analyse_CWIest_pdftype.m

@@ -1,0 +1,128 @@
+function [fitted_par,fh] = analyse_CWIest_pdftype(data,col, normtype,Hcut,Lcut,outputdir,outputfileprefix,nbins,qa_switch)
+
+% INPUTS: 
+% data    [structure or string]
+%              if data = structure => use data as it is
+%              if data = string => load data from file given by string
+% col     [integer = 2,3,4] column to use from CWI separation output
+%               2 => Taylo series approximation
+%               3 => auto-correlation method (unperturbved wave)
+%               4 => auto-correlation method (unperturbved wave)
+% normtype [integer = 0,1]
+%               0 => do not normalise separation
+%               1 => normalise separation by wavelength
+% Hcut      [vector] lower bound for Butterworth bandpass used on data.
+%           Loops through all values.
+% Lcut      [vector] upper bound for Butterworth bandpass used on data. 
+% outputdir         [string] full path to director in which to save plots 
+%                   or './' 
+% outputfileprefix  [string] prefix to be used with filename of saved plots
+% nbins     [scalar] number of bins to be used when drawing the histograms
+% qa_switch [scalar]
+%               1=> print figure
+%               0=> do not print figure (note figure created and then
+%               closed. 
+%
+% OUTPUTS
+% fitted_par    [structure] stores the fitted parameters in the following
+%               form:
+%                   fitted_par.for1to5Hz(i,1) => mean for known_sep(i)
+%                   fitted_par.for1to5Hz(i,2) => std for known_sep(i)
+%                   fitted_par.for1to5Hz(i,2) => amplitude scaling for plotting for known_sep(i)
+%   ** printed figures saved to file
+% 
+% USEAGE
+% analyse_CWIest_pdftype('errorbar_data_col3_normtype1.mat',3,1,[1 2 3 4],[2 3 4 5],'./','pdf_hist_')
+
+
+if isstruct(data)
+    errorbar_data = data;
+elseif ischar(data)
+    load(data)
+end
+
+if length(Hcut) ~=length(Lcut)
[…]

### 2012-07-17 events/matlab/analyse_data_extras.m

@@ -1,0 +1,171 @@
+
+function [data, hf] = analyse_data_extras(medinp, atype,plot_struct,startval,diag,known_sep)
+
+%INPUTS:
+% medinp    [structure] multi-tiered structure containing all of the data for
+%           the medium of interest i.e. separation vectors for all event
+%           pairs at each station. Structure tiers are best explained by 
+%           the following example for the medium exp001: 
+%               exp001 = 
+%                       xcorrStruc: [1x1 struct]
+%                       sepStruc: [1x1 struct]
+%               exp001.sepStruc =
+%                       receiver000468_receiver000469: [1x1 struct]
+%                       receiver000468_receiver000470: [1x1 struct]
+%                       receiver000468_receiver000471: [1x1 struct]
+%                       receiver000468_receiver000472: [1x1 struct]
+%                       receiver000468_receiver000473: [1x1 struct]
+%                       receiver000468_receiver000474: [1x1 struct]
+%                       receiver000468_receiver000475: [1x1 struct]
+%                       receiver000468_receiver000476: [1x1 struct]
+%                       receiver000468_receiver000477: [1x1 struct]
+%                       receiver000468_receiver000478: [1x1 struct]
+%                       receiver000468_receiver000479: [1x1 struct]
+%                       receiver000468_receiver000480: [1x1 struct]
+%                       receiver000468_receiver000481: [1x1 struct]
+%                       receiver000468_receiver000482: [1x1 struct]
+%                       receiver000468_receiver000483: [1x1 struct]
+%               exp001.sepStruc.receiver000468_receiver000469
+%                       station1: [22x4 double]
+%                       station2: [22x4 double]
+%                       station3: [22x4 double]
+%                       station4: [22x4 double]
+%                       station5: [22x4 double]
+%                       station6: [22x4 double]
+%                       station7: [22x4 double]
+%                       station8: [22x4 double]
+%                       station9: [22x4 double]
+%                       station10: [22x4 double]
+%                       station11: [22x4 double]
+% atype         [scalar - switch]
+%                   1 => do analysis with separation estimates sepStruc
+%                   2 => do analysis with maximum cross correlations xcorrStruc
+% plot_struct   [structure with plotting options] - all are optional
[…]

### 2012-07-17 events/matlab/assembleinput4_analyse_CWIest_pdftype.m

@@ -1,0 +1,32 @@
+function [assembled_data] = assembleinput4_analyse_CWIest_pdftype(datain, knownsep, Hcut, Lcut)
+% The purpose of this function is to assemble data for use with analyse_CWIest_pdftype
+%
+% INPUTS: 
+% datain        [matrix] 1 column for each value in knownsep. Rows contain the
+%               CWI separation estimates of interest
+% knownsep      [vector]  contains all of the known separations
+% Hcut          [vector] lower bound for Butterworth bandpass used on data.
+%               Loops through all values.
+% Lcut          [vector] upper bound for Butterworth bandpass used on data. 
+%
+%
+% OUTPUTS: 
+% assembled_data [structure] data input for analyse_CWIest_pdftype
+%
+% Note that this can only be used for 1 frequency band at a time. Any
+% organisation of 
+
+% David Robinson
+
+[n m] = size(datain.((['for_',num2str(Hcut(1)),'to', num2str(Lcut(1)),'Hz']))); 
+for j = 1:length(Hcut)
+    assembled_data.known_sep_perfreq.(['for_',num2str(Hcut(j)),'to', num2str(Lcut(j)),'Hz']) = ...
+        knownsep.(['for_',num2str(Hcut(j)),'to', num2str(Lcut(j)),'Hz']); 
+    for i = 1:m
+        ind = ~isnan(datain.(['for_',num2str(Hcut(j)),'to', num2str(Lcut(j)),'Hz'])(:,i));
+         assembled_data.agg_data.(['for_',num2str(Hcut(j)),'to', num2str(Lcut(j)),'Hz']).(['knownsep',num2str(i)]) = ...
+             datain.(['for_',num2str(Hcut(j)),'to', num2str(Lcut(j)),'Hz'])(ind,i);
+    end
+end
+
+    

### 2012-07-17 events/matlab/build_likelihood4_CWIN.m

@@ -1,0 +1,57 @@
+function [P_CWIN_deltat] = build_likelihood4_CWIN(delta_t,delta_cwi,mu_1,sigma_1,mu_N,sigma_N)
+% Builds the likelihood function: P(delta_CWIN|delta_t,I)
+%
+% INPUTS: 
+% delta_t   [vector 1xn] n values at which to evaluate P(delta_CWIN|delta_t,I)
+% delta_CWI [vector 1xm] m values at which to consider non-noisy CWI
+%           values. Note that we integrate ocver these. 
+% mu_1      [vector 1xn] mean estimate of PDF (bounded Gaussian with delta>0) 
+%           for the CWI estimates defined for each value in delta_t. 
+% sigma_1   [vector 1xn] standard deviation estimate of PDF (bounded Gaussian
+%           with delta>0) for the CWI estimates defined for each value in delta_t. 
+% mu_N      [scalar] noisy data value (i.e. delta_CWIN). Note that
+%           typically this is given by the sample mean of all the noisy CWI
+%           estimates that we have (Hence the terminology mu_N) 
+% sigma_N   [scalar] standard deviation of noisy data (i.e. delta_CWIN). Note that
+%           typically this is given by the sample standard deviation of all the 
+%           noisy CWI estimates that we have (Hence the terminology mu_N) 
+%
+% David Robinson
+% 7 March 2008
+
+% Make sure delta_cwi is a column vector
+delta_cwi = delta_cwi(:);
+
+
+
+
+%for i = 1:length(delta_t)   % loop over all of the delta_t
+    % compute A
+    [theoretical_likelihood.Y,Phi_mu1_sigma1_0] = ...
+        folded_normal_pdf(delta_t,mu_1,sigma_1);
+    A = 1./((1-Phi_mu1_sigma1_0).*sigma_1*sqrt(2*pi)); 
+    
+    % Get everything into a large matrix size 
+    %       number of rows = length(delta_cwi)
+    %       number of columns = length(mu_1)
+    MU_1 = repmat(mu_1, length(delta_cwi), 1);
+    SIGMA_1 = repmat(sigma_1, length(delta_cwi), 1);
+    DELTA_cwi = repmat(delta_cwi,1,length(mu_1));
+    
+    % compute B
[…]

### 2012-07-17 events/matlab/compute_energy.m

@@ -1,0 +1,11 @@
+function [energy] = compute_energy(event,time)
+
+%Inputs: 
+% event     [vector 1Xn] seismogram
+% time      [vector 1Xn] time
+%
+% OUTPUTS:
+% energy    [scalar] = int(dt x energy.^2, time(1),time(end))
+
+%error('BE CAREFUL - I Think you should normalise by time(end)-time(1)')
+energy = trapz(time,event.^2);

### 2012-07-17 events/matlab/create_movie.m

@@ -1,0 +1,139 @@
+% load all of the data files and create the movie
+
+pgrids = {'pgrid00030' 'pgrid00060' 'pgrid00090' 'pgrid00120' ...
+'pgrid00150' 'pgrid00180' 'pgrid00210' 'pgrid00240' 'pgrid00270' 'pgrid00300' 'pgrid00330' ...
+'pgrid00360' 'pgrid00390' 'pgrid00420' 'pgrid00450' 'pgrid00480' 'pgrid00510'...
+'pgrid00540' 'pgrid00570' 'pgrid00600' 'pgrid00630' 'pgrid00660' 'pgrid00690'...
+'pgrid00720' 'pgrid00750' 'pgrid00780' 'pgrid00810' 'pgrid00840' 'pgrid00870'...
+'pgrid00900' 'pgrid00930' 'pgrid00960' 'pgrid00990' 'pgrid01020' 'pgrid01050'...
+ 'pgrid01080' 'pgrid01110' 'pgrid01140' 'pgrid01170'  'pgrid01200' 'pgrid01230'...
+'pgrid01260'  'pgrid01290' 'pgrid01320' 'pgrid01350' 'pgrid01380' 'pgrid01410'...
+'pgrid01440' 'pgrid01470' 'pgrid01500' 'pgrid01530' 'pgrid01560' 'pgrid01590' 'pgrid01620'...
+'pgrid01650' 'pgrid01680' 'pgrid01710' 'pgrid01740' 'pgrid01770'  'pgrid01800'...
+ 'pgrid01830' 'pgrid01860' 'pgrid01890' 'pgrid01920' 'pgrid01950' 'pgrid01980' 'pgrid02010' ...
+'pgrid02040' 'pgrid02070' 'pgrid02100' 'pgrid02130' 'pgrid02160' 'pgrid02190'...
+'pgrid02220' 'pgrid02250'  'pgrid02280' 'pgrid02310' 'pgrid02340' 'pgrid02370'...
+'pgrid02400' 'pgrid02430' 'pgrid02460' 'pgrid02490' 'pgrid02520' 'pgrid02550' ...
+'pgrid02580' 'pgrid02610' 'pgrid02640' 'pgrid02670' 'pgrid02700' 'pgrid02730' ...
+'pgrid02760' 'pgrid02790' 'pgrid02820' 'pgrid02850' 'pgrid02880' 'pgrid02910'...
[…]

### 2012-07-17 events/matlab/do_flips4inversion.m

@@ -1,0 +1,48 @@
+function [Hypo_loc_out] = do_flips4inversion(Hypo_loc_in)
+% 
+% This routine flips the local coordinates for Hypo_loc_in events to ensure that
+% that x2>0, y3>0 and z4>0 (i.e. we try to solve the inversion in this
+% space)
+%
+% INPUTS:
+% Hypo_loc_in   [double nEx3]
+%               Events in a local coordinate system
+%                 Hypo_loc_in=  [0      0       0;
+%                                x2     0       0;      x2 = +/-
+%                                x3     y3      0;      y3 = +/-
+%                                x4     y4      z4;     z4 = +/-
+%                                x5     y5      z5; 
+%                                ...    ...     ...;
+%                                xnE    ynE     znE];
+%
+% Hypo_loc_out  [double nEx3]
+%               Events in a local coordinate system with x2>0, y3>0 and
+%               z4>0
+%                 Hypo_loc_in=  [0      0       0;
+%                                x2     0       0;      x2 >0
+%                                x3     y3      0;      y3 >0
+%                                x4     y4      z4;     z4 >0
+%                                x5     y5      z5; 
+%                                ...    ...     ...;
+%                                xnE    ynE     znE];
+%
+%
+% David Robinson 
+% 4 August 2008
+
+Hypo_loc_out = Hypo_loc_in;
+
+% Flip according to x2
+if Hypo_loc_out(2,1) <0
+    Hypo_loc_out(:,1) = -Hypo_loc_out(:,1);
+end
+
+% Flip according to y3
+if Hypo_loc_out(3,2) <0
+    Hypo_loc_out(:,2) = -Hypo_loc_out(:,2);
+end
+                    
+% Flip according to z4
+if Hypo_loc_out(4,3) <0
+    Hypo_loc_out(:,3) = -Hypo_loc_out(:,3);
+end

### 2012-07-17 events/matlab/eqdist.m

@@ -1,0 +1,19 @@
+function distance = eqdist(lat1,lon1,depth1,lat2,lon2,depth2)
+% computes the euclidean distance between two earthquakes
+%
+% INPUTS:
+% lat1      latitude of earthquake 1 (degrees)
+% lon1      longitude of earthquake 1 (degrees)
+% depth1    depth of earthquake 1 from ellipsoid (meters)
+%               0 =>    surface of ellipsoid
+%               +ve =>  below ellipsoid (most common)
+%               -ve =>  above elipsoid   
+% lat2      latitude of earthquake 2 (degrees)
+% lon2      longitude of earthquake 2 (degrees)
+% depth2    depth of earthquake 2 from ellipsoid 
+%
+% OUTPUTS
+% distance  euclidean distance (meters)
+[x1,y1,z1] = llh2xyz(lat1,lon1,-depth1);
+[x2,y2,z2] = llh2xyz(lat2,lon2,-depth2);
+distance = sqrt((x1-x2)^2+(y1-y2)^2+(z1-z2)^2);

### 2012-07-17 events/matlab/filter_waveform.m

@@ -1,0 +1,115 @@
+function [waveout_p, waveout_u,extras] = filter_waveform(wavein_u, time_u,wavein_p, time_p,Lcut,Hcut,diag_switch )
+% INPUTS:
+% wave_in = wave to be filtered
+% time = time vector for wave_in
+% diag_switch   [scalar]
+%                   1 => draw plots
+%                   0 => do not draw plots (compute values only)
+%
+% Outputs:
+% waveout_p     [vector mx1]: the perturbed wave after filtering (note time data not
+%               included: - this must be re-built from sample_rate
+% waveout_u     [vector mx1]: the un-perturbed or reference wave after filtering 
+%               (note time data not included: - this must be re-built from
+%               sample_rate)
+% extras        [structure] contains optional extra outputs
+%                 **** For the initial (input) waves
+%                   extras.init.u.fdom = dominant frequency of unperturbed wave
+%                   extras.init.u.power = power spectra [frequency,power] of unperturbed
+%                   extras.init.p.fdom = dominant frequency of perturbed wave
+%                   extras.init.p.power = power spectra [frequency,power] of perturbed
+%                 **** For the end (after filtering) waves
+%                   extras.end.u.fdom = dominant frequency of unperturbed wave
+%                   extras.end.u.power = power spectra [frequency,power] of unperturbed
+%                   extras.end.p.fdom = dominant frequency of perturbed wave
+%                   extras.end.p.power = power spectra [frequency,power] of perturbed
+
+sample_rate = 1/(time_u(2)-time_u(1));
+
+    % Now we need to mean shift the waveform so it is around 0
+    waveout_u = wavein_u - median(wavein_u);
+    waveout_p = wavein_p - median(wavein_p);
+    [hf_loc_init, omega2_init, genplots_init] = generate_plots(wavein_u, time_u, wavein_p, time_p, ...
+            'original waveforms (step 1)', [0,2],[-2500/200,2500/200], 0);
+    extras.init = genplots_init;
+    if diag_switch ~=1
+        close(hf_loc_init)
+    end
+%     
+    %Now we should taper it to zero at the end
+    if length(wavein_p) > 1000
+        extras.taperlength = 201;
+    else
[…]

### 2012-07-17 events/matlab/grab2Calaveras_waveforms.m

@@ -1,0 +1,153 @@
+function [waves] = grab2Calaveras_waveforms(eventid1,eventid2,station,channel,fbounds, qa_switch)
+% Get's two waveforms from the Calaveras data set and returns them based on
+% properties defined by wavetype
+% INPUTS: 
+% eventid1      [str] eventid for firts event
+% eventid2      [str] eventid for second event
+% station       [str] desired station
+% channel       [str] desired channel
+% fbounds       [double 1x2] bounds for the bandpass filter [Hcut,Lcut]
+% qa_switch     [integer] diagnostic switch
+%                   1 => create the plot
+%                   0 => do not do any plotting 
+%
+% OUTPUTS:
+
+%%setup
+Hcut = fbounds(1);
+Lcut = fbounds(2);
+
+
+%% get the filenames
+wave_store = '/export/storage/davidr/play/HYPODD_examples/Calaveras/';
+supportdir = '/export/storage/davidr/play/HYPODD_examples/example2';
+wavedir1 = [wave_store,eventid1,filesep];
+wavedir2 = [wave_store,eventid2,filesep];
+[filename1] = LOC_findthewaveform(wavedir1,station,channel);
+[filename2] = LOC_findthewaveform(wavedir2,station,channel);
+
+%% Get the pahse data - needed for the alignments
+[A, B, C, D, E, F, G, H, I , J, K, L, M, N, O] = textread([supportdir,'/Calaveras.pha'],'%s%f%f%s%f%f%f%f%f%f%f%f%f%f%f');
+ind2phasepicks = strmatch('#',A);
+
+ind2phasepicks = [ind2phasepicks;length(A)];
+for g = 1:length(ind2phasepicks)-1
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).year = B(ind2phasepicks(g));
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).month = C(ind2phasepicks(g));
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).day = str2double(D(ind2phasepicks(g)));
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).hour = E(ind2phasepicks(g));
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).minute = F(ind2phasepicks(g));
+    phasedata.(['event', num2str(O(ind2phasepicks(g)))]).second = G(ind2phasepicks(g));
+    for h = ind2phasepicks(g)+1:ind2phasepicks(g+1)-1
[…]

### 2012-07-17 events/matlab/iseven.m

@@ -1,0 +1,24 @@
+function ans = iseven(number)
+% tells whether a number is even 
+%
+% INPUTS:
+% number    [scalar - double] number to be tested
+%
+% OUTPUTS:
+% ans       [scalar - ] 
+%               1 => number is even
+%               0 => number is odd
+%               -1 => number is neither odd or even
+
+tmp = number/2;
+tmp2 = floor(tmp);
+diff = tmp-tmp2;
+
+if diff == 0 % number is even
+    ans = 1;
+elseif diff == 0.5  % number is odd
+    ans = 0;
+else
+    ans = -1;
+end
+

### 2012-07-17 events/matlab/lsplane.m

@@ -1,0 +1,61 @@
+function [x0, a, d, normd] = lsplane(X)
+% ---------------------------------------------------------------------
+% LSPLANE.M Least-squares plane (orthogonal distance
+% regression).
+%
+% Version 1.0
+% Last amended I M Smith 27 May 2002.
+% Created I M Smith 08 Mar 2002
+% ---------------------------------------------------------------------
+% Input
+% X Array [x y z] where x = vector of x-coordinates,
+% y = vector of y-coordinates and z = vector of
+% z-coordinates.
+% Dimension: m x 3.
+%
+% Output
+% x0 Centroid of the data = point on the best-fit plane.
+% Dimension: 3 x 1.
+%
+% a Direction cosines of the normal to the best-fit
+% plane.
+% Dimension: 3 x 1.
+%
+% <Optional...
+% d Residuals.
+% Dimension: m x 1.
+%
+% normd Norm of residual errors.
+% Dimension: 1 x 1.
+% ...>
+%
+% [x0, a <, d, normd >] = lsplane(X)
+% ---------------------------------------------------------------------
+
+% check number of data points
+m = size(X, 1);
+if m < 3
+error('At least 3 data points required: ' )
+end
+%
+% calculate centroid
+x0 = mean(X)';
+%
+% form matrix A of translated points
+A = [(X(:, 1) - x0(1)) (X(:, 2) - x0(2)) (X(:, 3) - x0(3))];
+%
+% calculate the SVD of A
+[U, S, V] = svd(A, 0);
+%
+% find the smallest singular value in S and extract from V the
+% corresponding right singular vector
+[s, i] = min(diag(S));
+a = V(:, i);
+%
+% calculate residual distances, if required
+if nargout > 2
+d = U(:, i)*s;
+normd = norm(d);
+end
+% ---------------------------------------------------------------------
+% End of LSPLANE.M. 

### 2012-07-17 events/matlab/make_circle.m

@@ -1,0 +1,14 @@
+function [circ_plus,circ_minus] = make_circle(xval, cent,r)
+% This function returns the top (circ_plus) and bottom (circ_minus) halves
+% of a circle with radius r and center cent.
+%
+% David Robinson
+% 13 August 2008
+
+circ_plus = cent(2) + sqrt(r^2-(xval-cent(1)).^2);
+circ_minus = cent(2) - sqrt(r^2-(xval-cent(1)).^2);
+
+
+
+
+

### 2012-07-17 events/matlab/make_fancyplot4simpleEG_2D.m

@@ -1,0 +1,59 @@
+function [fig_handle,a1,a2] = make_fancyplot4simpleEG_2D(grid_x2, grid_y2, PDF_2D,profile, caxis_lims,user_colormap,fancyplot_zlims)
+% Does the fancy plot for a 2D PDF of earthquake location. 
+% Example Useage: 
+%    make_fancyplot4simpleEG_2D(grid_x2_1, grid_y2_1, PDF_2D_EG1,profile_EG1, caxis_lims,tmp2)
+
+fig_handle = figure;
+a1 = subplot(3,1,[1:2]);
+ind = find(grid_x2>=0);
+sh_1 = surface(grid_x2(ind),grid_y2,PDF_2D(:,ind))
+hold on
+zdata_tmp = get(sh_1,'zdata');
+l1 = plot3(zeros(size(profile(:,1)))-0.005,profile(:,1),zdata_tmp(:,1)+0.001,'k','linewidth',1)
+%meshc(grid_x2_1,grid_y2_1,PDF_2D_EG1)
+%xlabel('x')
+%ylabel('y')
+shading interp
+caxis(caxis_lims)
+colormap(user_colormap)
+%axis equal
+set(a1,'view', [-46 18])
+set(a1,'zlim', fancyplot_zlims)
+set(gca,'xlim', [min(grid_x2), max(grid_x2)], 'ylim', [min(grid_y2), max(grid_y2)])
+grid on
+
+fsize = 16;
+h1 = ylabel('$\widetilde{y}$','interpreter','latex','fontsize',fsize)
+yposy = get(h1,'position')
+set(h1,'position', [yposy(1)+0.1,yposy(2)+0.5,yposy(3)])
+h2 = xlabel('$\widetilde{x}$','Interpreter','LaTex','fontsize',fsize)
+xposy = get(h2,'position')
+set(h2,'position', [xposy(1)+0.1+0.4,xposy(2)+0.1,xposy(3)])
+%zlabel('$P(E_2|E_1,\widetilde{\delta}_{CWIN})$','Interpreter','LaTex','fontsize',14)
+set(gca,'fontsize',fsize)
+
+a2 = subplot(3,1,3);
+pcolor(grid_x2,grid_y2,PDF_2D)
+shading interp
+caxis(caxis_lims)
+axis equal
+hold on
+plot([-1.2 1.2], [1.2 -1.2],'k--','linewidth',2)
+
[…]

### 2012-07-17 events/matlab/make_foldederrorbar_sigma.m

@@ -1,0 +1,32 @@
+function ydata = make_foldederrorbar_sigma(x, xdata)
+% Defines the shape of the errorbar sigma function 
+% Used by fit_errorbars
+%
+% Inputs
+% x     [vector 4x1] defines the parameters of the function
+% xdata [vector nx1] defines the values at which the fitting function is
+%       evaluated
+% 
+% David Robinson
+% 5 Feb 2008
+
+% orig
+% ydata = x(1).*  (x(2)*xdata.^x(4)+x(3).*xdata)./ ...
+%                 (x(2)*xdata.^x(4)+x(3).*xdata + 1);
+
+
+%ydata = 0.02 + x(1).*  (x(2)*xdata.^x(4)+x(3).*xdata.^x(5))./ ...
+%                 (x(2)*xdata.^x(4)+x(3).*xdata+x(6));
+
+% This was the latest try at making them different
+           ydata =  0.017 + ...%x(5).*xdata + ... %0.0167+...
+               x(1).*  (x(2)*xdata.^x(4)+x(3).*xdata.^x(5))./ ...
+               (x(2)*xdata.^x(4)+x(3).*xdata.^x(5) + 1);
+            
+
+           
+%        ydata = abs(x(1).*  (x(2)*xdata.^x(4)+x(3).*xdata)./ ...
+%                 (x(2)*xdata.^x(4)+x(3).*xdata + 1));     
+%             
+            
+         %   ydata = x(1)+x(2)*exp(-x(3)*xdata);

### 2012-07-17 events/matlab/nzday2monthday.m

@@ -1,0 +1,42 @@
+function [month day] = nzday2monthday(nzday, year);
+% converts nzday (day from start of the year) to month and day
+
+leapyears = 1800:4:2016;
+
+if (year>max(leapyears) | year <min(leapyears))
+    error('year input must be between 1800 and 2016')
+end
+    
+dayspermonth = [    31, ... %Jan  
+                    28, ... %Feb
+                    31, ... %Mar
+                    30, ... %Apr
+                    31, ... %May
+                    30, ... %Jun
+                    31, ... %Jul
+                    31, ... %Aug
+                    30, ... % Sept
+                    31, ... % Oct
+                    30, ... % Nov
+                    31];    %Dec
+ind =find(year==leapyears);
+if ~isempty(ind)
+    dayspermonth(2) = 29; 
+end
+
+incsum = cumsum(dayspermonth);
+
+if nzday<=31
+    month = 1;
+    day = nzday;
+elseif nzday>incsum(11)
+    month = 12; 
+    day = nzday-incsum(11);
+else
+    indhigher = find(incsum>=nzday);
+    month = indhigher(1);
+    day = nzday-incsum(indhigher(1)-1);
+end
+    
+
+

### 2012-07-17 events/matlab/plot_3delastic.m

@@ -1,0 +1,157 @@
+function [meanR, meanS, omega2] = plot_3delastic(fname_u, fname_p, sample_rate)
+
+% fname_u   [string] full path file name to the wave from the the unperturbed
+%           source
+% fname_p   [string] full path file name to the wave from the perturbed
+%           source. Must be recorded on the same instrument as fname_u
+% sample_rate   [float] sample rate of instrument. 
+
+if nargin==0
+    fname_u = '/export/storage/davidr/play/truns/run0053/station204.txt';
+    fname_p = '/export/storage/davidr/play/truns/run0055/station204.txt';  %plot_par.trans2 = 0.6
+    sample_rate = 1/0.0017;
+end
+
+fid = fopen(fname_u)
+event1 = fscanf(fid,'%i %e %e %e', [4 Inf]);
+event1 = event1';
+fclose(fid)
+% event1(:,1) = event1(:,1)*dt;
+wave_u_full = event1(:,2);
+
+fid = fopen(fname_p)
+event2 = fscanf(fid,'%i %e %e %e', [4 Inf]);
+event2 = event2';
+fclose(fid)
+% event1(:,1) = event1(:,1)*dt;
+wave_p_full = event2(:,2);
+
+
+src_type = 3 %(=2 => double couple source separation in a 3D elastic medium)
+
+plot_par.trans1 = 0;    % horizontal translation of event1(:,1) [time]
+plot_par.trans2 = 0;% 0.006;         % horizontal translation of event2(:,1) [time]
+plot_par.start_arrivwin = 0.5;
+plot_par.end_arrivwin = 1;
+plot_par.start_codawin = 2.2;
+plot_par.end_codawin = 2.7;
+plot_par.parrival = 0.6;
+plot_par.event1name = 'RUN0^o';
+plot_par.event2name = 'RUN5^o';
+plot_par.save = 1;
+%plot_par.u_name = 'receiver100001.txt';
+%plot_par.p_name = 'receiver100002.txt';
+plot_par.twindow = 0.5;
+plot_par.lbnd4nenergy = 0.02;
+plot_par.ubnd4nenergy = 0.14;
+
+
+
+
+timevector_u = 0:1/sample_rate: (length(wave_u_full)-1)*(1/sample_rate);
+timevector_p = 0:1/sample_rate: (length(wave_p_full)-1)*(1/sample_rate);
+
+% % Now we need to mean shift both waveforms so that they are around 0
+% wave_u_full = wave_u_full - median(wave_u_full);
[…]

### 2012-07-17 events/matlab/plot_grm_section.m

@@ -1,0 +1,41 @@
+function [grm_lims,hc] = plot_grm_section(fname,xcut,zcut,deltas,caxis_lims)
+
+% function to plot a grm cross section (works with 2D only). 
+% INPUTS:
+% fname         [string] full path filename to media of interest
+% xcut          [vector 2x1]  i.e. [lower_xlim, upper_xlim] for cut
+% zcut          [vector 2x1]  i.e. [lower_zlim, upper_zlim] for cut
+% deltas        [vector 3x1] [deltax, deltay, deltaz] in meters
+% caxis_lims    [vector 2x1] lower and upper limits for caxis re-scale of
+%               images. Note that scale is automatic if caxis_lims = [];
+
+%grm_full = load(fname);
+
+%grm = grm_full(zcut(1):zcut(2),xcut(1):xcut(2));
+
+grm = dlmread(fname, '', [zcut(1),xcut(1),zcut(2),xcut(2)]);
+[n m] = size(grm);
+
+x = 0:deltas(1):(m-1)*deltas(1);
+z = 0:deltas(3):(n-1)*deltas(3);
+
+figure
+h = pcolor(x/1000,z/1000,grm/1000);
+set(gca,'fontsize',26)
+shading interp
+if ~isempty(caxis_lims)
+    caxis([caxis_lims(1), caxis_lims(2)]);
+end
+hc = colorbar
+set(hc, 'fontsize',26)
+disp('   ')
+
+grm_lims(1) = min(grm(:));
+grm_lims(2) = max(grm(:));
+
+
+
+
+
+
+

### 2012-07-17 events/matlab/plot_waves.m

@@ -1,0 +1,194 @@
+function [] = plot_waves(fname_u, fname_p, sample_rate)
+
+% fname_u   [string] full path file name to the wave from the the unperturbed
+%           source
+% fname_p   [string] full path file name to the wave from the perturbed
+%           source. Must be recorded on the same instrument as fname_u
+% sample_rate   [float] sample rate of instrument. 
+
+if nargin==0
+    %fname_u = '/export/storage/davidr/play/flinders/2004/117/FR01.HHZ.2004:117:22:22:19';
+    %fname_p = '/export/storage/davidr/play/flinders/2004/127/FR01.HHZ.2004:127:01:12:45';  %plot_par.trans2 = 0.6
+    fname_u = '/export/storage/davidr/play/flinders/2004/220/FR01.HHZ.2004:220:11:31:19';
+    fname_p = '/export/storage/davidr/play/flinders/2004/131/FR01.HHZ.2004:131:01:44:42';  %plot_par.trans2 = 0.6
+ 
+    sample_rate = 200
+end
+
+
+wave_u_full = load(fname_u);
+wave_p_full = load(fname_p);
+
+
+
+
+%Now setup the plotting structure for PLOT_SEIS_XCORR
+plot_par.trans1 = 0.05;    % horizontal translation of event1(:,1) [time]
+plot_par.trans2 =  0%0.585;% 0.006;         % horizontal translation of event2(:,1) [time]
+plot_par.start_arrivwin = 29.7;
+plot_par.end_arrivwin = 32.7;
+plot_par.start_codawin = 40;
+plot_par.end_codawin = 43;
+plot_par.event1name = 'event1';
+plot_par.event2name = 'event2';
+
+timevector_u = 0:1/sample_rate: (length(wave_u_full)-1)*(1/sample_rate);
+timevector_p = 0:1/sample_rate: (length(wave_p_full)-1)*(1/sample_rate);
+
+figure
+subplot(2,1,1)
+h1 = plot(timevector_u, wave_u_full, 'b');
+xlabel('time(sec)')
+title('Event 1')
+subplot(2,1,2)
+h2 = plot(timevector_p, wave_p_full, 'r' );
+xlabel('time(sec)')
+title('Event 1')
+
+
[…]

### 2012-07-17 events/matlab/running_means5.m

@@ -1,0 +1,26 @@
+function y = running_means5(x)
+%
+% Robinson, D., Dhu, T. and Schneider, J. 
+% "SUA: A Computer Program to Compute Regolith Site-response and Estimate Uncertainty for
+% Probabilistic Seismic Hazard Analyses".
+% Computers and Geosciences
+%
+% y = RunningMeans5(x)
+%
+% RunningMeans5 computes the the five point running mean of x 
+% i.e. it smooths x. 
+%
+% Inputs:
+% x         Vector to be smoothed
+%
+% Outputs
+% y         Smoothed Vector
+%
+%                                           David Robinson
+%                                           Last Updated: 15/07/02
+
+x = x(:);
+
+len = length(x);
+x_n2=x(1:len-4);  x_n1=x(2:len-3);  x_p2=x(5:len);  x_p1=x(4:len-1);
+y = [x(1); (x(1)+x(2)+x(3))/3; (x_n2+x_n1+x(3:len-2)+x_p1+x_p2)/5; (x(len-2)+x(len-1)+x(len))/3;  x(len)];

### 2012-07-17 events/matlab/tot_fracvar.m

@@ -1,0 +1,5 @@
+function eps = tot_fracvar(a,mean_medium);
+meana = mean(a(:));
+eps = sqrt(mean(a(:).^2)/mean_medium^2);
+
+

### 2012-07-17 paper2/diags/synth2Dmulti/wrap_plot_outcomes.m
fixed the figure to the correct size and colour for the paper

@@ -84,40 +84,42 @@ for i = 1:length(dirlist)
     print('-depsc',['soln_space_2Dsynth50eq_bestsoln',dirlist{i},'.eps'])
 end
 
+
 fsize = 12
 % Now let's do the plotting
 fh.maxvals = figure;
-subplot(4,1,1)
-h1 = plot(maxvals_all,'b','linewidth',2);
+sh(1) = subplot(3,1,1)
+h2 = plot(maxvals_best,'color','k','linewidth',2) %  best
 hold on
-h2 = plot(maxvals_best,'r','linewidth',1)
-legend([h1,h2], {'all', 'best'})
+h1 = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+%legend([h1,h2], {'all', 'best'})
 set(gca,'xtick',1:10,'ytick',[0 50 100 150])
-set(gca,'xticklabel',ticklabelstr)
+set(gca,'xticklabel',{}) %ticklabelstr)
 set(gca,'fontsize',fsize)
-set(gca,'ylim',[0 150],'xlim',[1 10])
+set(gca,'ylim',[0 150],'xlim',[1 10],'units','centimeters')
 ylabel('$\Delta_{max}$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 %xlabel('Number of constraints','fontsize',fsize)
 
-subplot(4,1,2)
-h1 = plot(meanvals_all,'b','linewidth',2);
+sh(2) = subplot(3,1,2)
+h2 = plot(meanvals_best,'color','k','linewidth',2) % best
 hold on
-h2 = plot(meanvals_best,'r','linewidth',1)
+h1 = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+hold on
 set(gca,'xtick',1:10,'ytick',[0 20 40])
-set(gca,'xticklabel',ticklabelstr)
+set(gca,'xticklabel',{})%ticklabelstr)
 set(gca,'fontsize',fsize)
-set(gca,'ylim',[0 40],'xlim',[1 10])
+set(gca,'ylim',[0 40],'xlim',[1 10],'units','centimeters')
 ylabel('$\Delta_\mu$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 
-subplot(4,1,3)
-h1 = plot(stdvals_all,'b','linewidth',2);
-hold on
-h2 = plot(stdvals_best,'r','linewidth',1)
[…]

### 2012-07-17 paper2/diags/synth3Dmulti/wrap_plot_outcomes.m
updated so that figure is the correct size and color for the paper

@@ -72,46 +72,61 @@ ind_best = find(maxvals_best>150);
 maxvals_best(ind_best) = NaN;
 
 fh.maxvals = figure;
-subplot(3,1,1)
-h1 = plot(maxvals_all,'b','linewidth',2);
+
+sh(1) = subplot(3,1,1)
+h2 = plot(maxvals_best,'color','k','linewidth',2) %  best
 hold on
-h2 = plot(maxvals_best,'r','linewidth',1)
-legend([h1,h2], {'all', 'best'})
+h1 = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+%legend([h1,h2], {'all', 'best'})
 set(gca,'xlim',[1 10])
 set(gca,'xtick',1:10,'ytick',[0 50 100 150])
-set(gca,'xticklabel',ticklabelstr)
+set(gca,'xticklabel',{})%ticklabelstr)
 set(gca,'fontsize',fsize)
-set(gca,'ylim',[0 150],'xlim',[1 10])
+set(gca,'ylim',[0 150],'xlim',[1 10],'units','centimeters')
 ylabel('$\Delta_{max}$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 %xlabel('Number of constraints','fontsize',fsize)
 
-subplot(3,1,2)
 meanvals_all(ind_all) = NaN;
 meanvals_best(ind_best) = NaN;
-h1 = plot(meanvals_all,'b','linewidth',2);
+sh(2) = subplot(3,1,2)
+h2 = plot(meanvals_best,'color','k','linewidth',2) % best
 hold on
-h2 = plot(meanvals_best,'r','linewidth',1)
+h1 = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
 set(gca,'xlim',[1 10])
 set(gca,'xtick',1:10,'ytick',[0 20 40])
+ticklabelstr = {' ','20%',' ','40%',' ','60%',' ','80%',' ','100%'};
 set(gca,'xticklabel',ticklabelstr)
 set(gca,'fontsize',fsize)
-set(gca,'ylim',[0 40],'xlim',[1 10])
+set(gca,'ylim',[0 40],'xlim',[1 10],'units','centimeters')
 ylabel('$\Delta_\mu$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 
-subplot(3,1,3)
-stdvals_all(ind_all) = NaN;
-stdvals_best(ind_best) = NaN;
[…]

### 2012-07-17 paper2/paper2.tex
minor changes - improved typsetting of equations in Section 4 and fixed some figures so that they fit in a column
some minor changes

@@
 %\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\noindent\includegraphics[width = 20pc]{diags/ressummary_2Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
-and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
+\noindent\includegraphics[width = 20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (grey)
+and best (black) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
 $\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
@@
 %\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\noindent\includegraphics[width = 20pc]{diags/ressummary_3Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
-and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
+\noindent\includegraphics[width = 20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (grey)
+and best (black) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
 $\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
@@
 \begin{equation}
-\label{eq-multi-var-Gauss-tt} P(\mathbf{e}_p|\Delta_{TT}) =
-\frac{1}{(2\pi)^{\frac{3}{2}}\sqrt{|\Sigma|}} \exp
+\label{eq-multi-var-Gauss-tt} 
+\begin{array}{l}
+P(\mathbf{e}_p|\Delta_{TT}) 
+\frac{1}{(2\pi)^{\frac{3}{2}}\sqrt{|\Sigma|}} \\
+\hspace{5em} \times \exp
 \left({-\frac{1}{2}\left([\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T
 \Sigma^{-1} [\mathbf{e}_p-\mu_{\mathbf{e}_p}]\right)} \right),
+\end{array}
 \end{equation}
@@
 \begin{equation}
-\label{eq-Lstar-tt-cwi} L(\mathbf{e}_1, \mathbf{e}_2, ...,
+\label{eq-Lstar-tt-cwi}
+\begin{array}{l}
+ L(\mathbf{e}_1, \mathbf{e}_2, ...,
 \mathbf{e}_1, \mathbf{e}_n) = - \sum_{i=1}^n
-ln\left[P(\mathbf{e}_i|\Delta_{TT})\right] - \sum_{i=1}^{n-1}
+ln\left[P(\mathbf{e}_i|\Delta_{TT})\right] \\
+\hspace{6em}  - \sum_{i=1}^{n-1}
 \sum_{j=i+1}^n
 ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right],
+\end{array}
 \end{equation}
@@
 \begin{equation}
-\frac{\partial L}{\partial x_p} =  - \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p} \\
+\begin{array}{l}
+\frac{\partial L}{\partial x_p} =  - \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p}
 - \sum_{i=p+1}^{N} \frac{ \partial \ln
 \left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
-x_p} - \sum_{j=1}^{p-1} \frac{ \partial \ln
+x_p} \\
+\hspace{5em} - \sum_{j=1}^{p-1} \frac{ \partial \ln
 \left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
 x_p}
-\end{equation}
-where $\sum_{i=p+1}^{N} \frac{ \partial \ln
+\end{array}
+\end{equation}
+where 
+\begin{equation}
+\sum_{i=p+1}^{N} \frac{ \partial \ln
 \left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
-x_p}$ and $\sum_{j=1}^{p-1} \frac{ \partial \ln
+x_p} 
+\end{equation}
+and 
+\begin{equation}
+\sum_{j=1}^{p-1} \frac{ \partial \ln
 \left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
-x_p}$ are defined in Appendix \ref{sec-Appendix-derivatives_ofL} and
-\begin{equation}
+x_p} 
+\end{equation}
+are defined in Appendix \ref{sec-Appendix-derivatives_ofL} and
+\begin{equation}
+\begin{array}{l}
 \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p}
-= -\frac{1}{2}\left([1,0,0]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [1,0,0] \right).
+= -\frac{1}{2}[1,0,0]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
+\hspace{9em} -\frac{1}{2}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [1,0,0].
+\end{array}
 \end{equation}
@@
 \begin{equation}
+\begin{array}{l}
 \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial y_p}
-= -\frac{1}{2} \left( [0,1,0]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,1,0] \right)
+= -\frac{1}{2} [0,1,0]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
+\hspace{9em} -\frac{1}{2}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,1,0] 
+\end{array}
 \end{equation}
@@
 \begin{equation}
+\begin{array}{l}
 \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial z_p}
-= -\frac{1}{2} \left( [0,0,1]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] +
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,0,1] \right).
+= -\frac{1}{2} [0,0,1]^T \Sigma^{-1}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
+\hspace{9em} -\frac{1}{2}
+[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,0,1].
+\end{array}
 \end{equation}
@@
 % This is the version using hypoDD with SVD
-\begin{figure*}
+\begin{figure}
 \includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
@@
 stations.} \label{fig-68Calaverasevents_ttandcoda1}
-\end{figure*}
+\end{figure}
 
@@
 \begin{equation}
-label{eq:original_omori}
+\label{eq:original_omori}
  n(t) = K(t+C)^{-p}
@@
 % This is the version using hypoDD with SVD
-\begin{figure*}
+\begin{figure}
 \includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
@@
 with figure ..... } \label{fig-68Calaverasevents_ttsubsetandcoda1}
-\end{figure*}
+\end{figure}
 %%=========================================================================

### 2012-07-18 paper2/paper2.tex
another round of changes - We now have a complete draft

@@
 
-\date{Received 2010 Month Day; in original form 2010 Month Day}
+\date{Received 2012 Month Day; in original form 2012 Month Day}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \volume{200}
-\pubyear{2010}
+\pubyear{2012}
 
@@
 \begin{summary}
-(Type abstract here)
+ Coda wave interferometry (CWI) is an emerging tool for constraining 
+earthquake source properties from the intereference pattern of coda waves between nearby
+events. A new earthquake location algorithm is derived which relies on CWI based probabilistic estimates 
+of earthquake separation. The algorithm can be used with CWI estimates alone or in tandem with travel time
+data. Synthetic examples in 2D and 3D and real earthquakes on the 
+Calaveras Fault, California are used to demonstrate the usefulness of the CWI technique in locating 
+poorly recorded earthquakes. It is demonstrated that CWI: (a) outperforms traditional earthquake location 
+techniques when the number of stations is small; (b) is self-consistent across a broad range of station
+situations; and (c) can be used with a single station to locate earthquakes.
+
 \end{summary}
 
-\begin{keywords}
- Probability distributions; Earthquake source observations; Seismicity and tectonics; Wave scattering and diffraction
-\end{keywords}
+%\begin{keywords}
+% Probability distributions; Earthquake source observations; 
+%Seismicity and tectonics; Wave scattering and diffraction
+%\end{keywords}
 
@@
 
-Earthquake location is important for many applications. It assists
-our understanding of seismic activity by indicating regions of
-relatively higher seismicity such as lithospheric plate boundaries
-\citep[e.g., ][]{dr_Sykes67a, dr_Isacks68a, dr_Stein02a} or local
-active source zones \citep[e.g., ][]{dr_Gutenberg44a,
-dr_Giardini03a}. Earthquake locations are required for  magnitude
-determination \citep[e.g., ][]{dr_Richter35a, dr_Gutenberg45a},
-computing moment tensors \citep[e.g., ][]{dr_Sipkin02a} and
-seismological studies of the Earth's interior \citep[e.g.,
-][]{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a, dr_Kennett04a}. They
-are needed to understand strong motion and seismic attenuation
-\citep[e.g., ][]{dr_Toro97a, dr_Campbell03a}
- and model earthquake hazard or risk
-\citep[e.g., ][]{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
+Earthquake location is important for many applications. Locations 
+are required for:  magnitude
+determination \citep{dr_Richter35a, dr_Gutenberg45a};
+computing moment tensors \citep{dr_Sipkin02a};
+seismological studies of the Earth's interior 
+\citep{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a, dr_Kennett04a};
+understanding strong motion and seismic attenuation
+\citep{dr_Toro97a, dr_Campbell03a}
+ and modeling earthquake hazard or risk
+\citep{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
 
@@
 from microseismicity requires greater detail than determining
-whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning
-purposes. This paper focuses on reducing the uncertainty on the
-locations of a cluster of events when they are recorded by a small
+whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning.
+ This paper focuses on reducing location uncertainty for 
+a cluster of events when they are recorded by a small
 number of stations.
@@
 Without such phases the uncertainty is higher.}
-  These locations are created using global seismic networks.
 \citet{dr_Bondar04a} demonstrate that at the local scale, absolute
@@
 structure, relative location techniques compute locations directly
-from travel time differences between two waveforms \citep[e.g.,
-][]{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
+from travel time differences between two waveforms 
+\citep{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
 so, they remove errors associated with velocity variations outside
@@
 15 to 75\,m in local settings with good station coverage
-\citep[e.g., ][]{dr_Ito85a, dr_Got94a,
+\citep{dr_Ito85a, dr_Got94a,
 dr_Waldhauser99a,dr_Waldhauser08a}. Here, `good coverage' implies
@@
 diverse range of problems including: location of active fault planes
-\citep[e.g., ][]{dr_Deichmann92a, dr_Got94a, dr_Waldhauser99a,
+\citep{dr_Deichmann92a, dr_Got94a, dr_Waldhauser99a,
 dr_Waldhauser02a, dr_Shearer05a}; studying rupture mechanics
-\citep[e.g., ][]{dr_Rubin99a, dr_Rubin02a}; interpreting magma
-movement in volcanoes \citep[e.g., ][]{dr_Fremont87a}; and
-monitoring pumping induced seismicity \citep[e.g., ][]{dr_Lees98a,
-dr_Ake05a}. \citet{dr_Poupinet84a}, \citet{dr_Bokelmann00a} and
-\citet{dr_Rubin02b} apply relative location techniques to identify
-earthquake doublets, events that have near identical locations.
+\citep{dr_Rubin99a, dr_Rubin02a}; interpreting magma
+movement in volcanoes \citep{dr_Fremont87a}; and
+monitoring pumping induced seismicity \citep{dr_Lees98a,
+dr_Ake05a}.
 
@@
 station \citep{dr_Robinson07b}. This makes CWI particularly interesting
-for regions where station density is low such as intraplate areas.
+for regions where station density is low such as intraplate settings. In this 
+paper we demonstrate how CWI separation estimates can be used to constrain 
+location with data from a single station. 
 Our technique can be used on coda waves alone or in combination with
-travel times. We demonstrate that the use of coda waves improves
-the location of a cluster of events when the recording situation
-is poor and we show that it is possible to obtain accurate relative locations with as
-little as one station.
+travel times.
 
@@
 \end{equation}
-Similarly, we note that earthquake locations are independent and the
+Similarly, the earthquake locations are independent and the
 joint prior becomes
@@
 \end{equation}
-for three events. A detailed understanding of the location of a single event (e.g. $\mathbf{e}_2$) is obtained by computing the
+for three events.
+
+A detailed understanding of the location of a single event (e.g. $\mathbf{e}_2$) is obtained by computing the
 marginal
@@
 
-By following the same argument we get the posterior function
+Following the same argument we get the posterior function
 \begin{equation}
@@
 a local coordinate system. We choose a local coordinate system
-which removes ambiguity associated with transformations of the coordinate system,
-such as translations and rotations, that do not change the distance between events.
+which removes ambiguity associated with transformations of the coordinate system.
 In defining this coordinate system we fix the first event at the origin,
@@
 system when using coda waves alone because the CWI technique constrains only event separation
-between earthquakes. The inclusion of travel times in Sec. \ref{sec:CalaverasLoc-CWIandTT}
+between earthquakes. The inclusion of travel times in Section \ref{sec:CalaverasLoc-CWIandTT}
 allows us to move to a global reference system.
@@
 
-\subsection{Synthetic experiments}
+\section{Synthetic experiments}
 \label{sec:benchmarking}
@@
 
-\subsection{2D synthetic experiments}
-
-Actual locations are created by
+\subsection{Examples 1 and 2 - 2D synthetic experiments}
+
+We design a 2D synthetic experiment (Example 1) by
 randomly selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq \hat{x} \leq 50$ and $-50 \leq \hat{y} \leq 50$.
@@
 does not lead to the correct solution due to the addition of noise
-$\bar{\sigma}_N=0.02$ on the hypothetical CWI data. The average
+($\bar{\sigma}_N=0.02$) on the hypothetical CWI data. The average
 coordinate error is 2.0\,m which is small compared to the noise of
@@
 earthquake 2 on the positive $\hat{x}$-axis and earthquake 3 has
-$\hat{y}>0$. As the number of events increases the strength of this
-constraint on later events becomes weaker allowing small rotations
+$\hat{y}>0$. As the number of events increase the strength of these
+constraints on later events weakens allowing small rotations
 of events with respect to each other. That is, even though the
 rotational freedom of the cluster is in principal removed by the
-constraints imposed on the events (see eqs. \ref{eq:coord-const1} to
-\ref {eq:coord-const4}) we observe that in practice the presence of
+constraints imposed on the events (see equations (\ref{eq:coord-const1}) to
+(\ref{eq:coord-const4})) we observe that in practice the presence of
 noise allows the rotational non-uniqueness to reappear. This is
@@
 model changes in directions of the eigenvectors with the smallest
-singular values \citep[e.g ][]{dr_Aster05a}. Unfortunately, there is
+singular values \citep{dr_Aster05a}. Unfortunately, there is
 no obvious way to overcome this issue when using coda waves alone
@@
 
-\subsubsection{The impact of reduced linkage}
+\subsection{Example 3 - The impact of reduced linkage}
 
@@
 
-In Figs. \ref{fig:optimisationresults-2Dsynth}(a) and (b) we examine
-the performance of the optimisation statistically. In particular, we
-plot the maximum $\Delta_{max}$ and mean $\Delta_\mu$ of the
+Figure \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrates 
+the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of the
 coordinate difference as a function of increasing linkage. We show
@@
 In this case the best solution is determined by the set of event
-locations which lead to the smallest value of $L$. We observe
-similar errors in the best solution for all cases when at least 30\%
-of the branches are used. The errors increase drastically when only
+locations which lead to the smallest value of $L$. The
+error in the best solution is consistent when 30\%
+or more of the branches are used. The errors increase when only
 10\% or 20\% of the constraints are included. Interestingly, this
@@
 average number of branches required to link each pair reaches 2 (see
-Fig.\ref{fig:optimisationresults-2Dsynth}(c)). Since the average
+Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the average
 number of branches can be computed in advance it can be used as an
-indication of the potential stability of the inversion prior to
+indication of the inversion stability prior to
 optimisation. An earlier breakdown is observed when all 25 solutions
 are considered collectively. For example, the maximum coordinate
-error $\Delta_{max}$ is significantly higher than that for the best
-solution for all cases with 60\% of the constraints or less. This
-observation confirms that the optimisation is susceptible to the
-presence of local minima and that a range of starting points should
+error $\Delta_{max}$ exceeds that for the best
+solution for linkage $\leq$60\% confirming that the optimisation is susceptible to
+local minima and that a range of starting points should
 be considered.
 
-Interestingly, we note that some of the optimisations chains
-fail to converge after 1200 iterations when the linkage is 60\% or lower and all
-fail when then linkage is 20\% or lower. Despite their failure to converge however, many of the
-solutions remain relatively close to the actual solutions. The derivatives used in the conjugate gradient method
+Some optimisations 
+fail to converge after 1200 iterations when the linkage is 60\% or lower. All optimisations
+fail when then linkage is 20\% or lower. Despite their failure to converge however, the locations
+at final iteration are close to the actual solution. The derivatives used in the conjugate gradient method
 depend on events connected by CWI measurements. Consequently,
 earthquakes that are only connected via other events do not `communicate' with each other
-directly. To some extent, this should be taken care of during the iterative process where location information
+directly. To some extent, this should be adressed during the iterative process where location information
 can spread to events which have no direct links. However, the
-lack of connection through the gradient could prevent convergence in extreme cases, or more likely
+lack of direct connection through the gradient could prevent convergence in extreme cases, or more likely
 slow the procedure down. This could explain why some
@@
 
-\subsubsection{3D synthetic examples with reduced linkage}
-
-In this section we expand the optimisation routine to 3D and repeat example 3 of the 2D case.
-We randomly pick a set of actual event locations for 50 earthquakes with
+\subsection{Example 4 - 3D synthetic examples with reduced linkage}
+
+In Example 4 we expand the optimisation routine to 3D by randomly picking
+ a set of actual event locations for 50 earthquakes with
 $-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case we assume a local velocity
@@
  waveform data filtered between 1 and 5$\,$Hz.
-The hypothetical CWI mean is created using eq. \ref{eq:hypothetical-CWI-mean-optichapt}
+The hypothetical CWI mean is created using equation (\ref{eq:hypothetical-CWI-mean-optichapt})
 which ensures consistency between the sample mean of hypothetical separation estimates and CWI
@@
 optimisation 25 times using randomly chosen starting locations. The results are
-summarised in Fig. \ref{fig:optimisationresults-3Dsynth}.
+summarised in Figure \ref{fig:optimisationresults-3Dsynth}.
 
@@
 
-As in the 2D example we observe a consistency of the optimisation
-procedure when the number of direct links used is high. That is,
-when 70\% of the direct constraints are considered all optimisation
+When 70\% of the direct constraints are considered all optimisation
 results (grey) are consistent with the best solution (black). The
@@
 the final iteration was typically close to the actual solution when
-the optimisation chain failed to converge after 1200 iterations.
+the optimisation failed to converge.
 Contrastingly, in 3D the optimisation appears to converge to the
@@
 which in no way resemble the actual solution. This is depicted in
-Fig. \ref{fig:optimisationresults-3Dsynth} by the absence of the
+Figure \ref{fig:optimisationresults-3Dsynth} by the absence of the
 grey and black lines below 60\% and 30\% of the constraints,
@@
 higher is encouraging for the potential of coda wave optimisation to
-constrain earthquake location more generally.
-
-\subsubsection{Summary of findings}
+constrain earthquake location.
+
+\subsubsection{Summary of synthetic experiments}
 
@@
 solution from 25 random starting locations is required to find the
-optimal solution. Finally, as the number of links decrease below
-30\% the best solution also fails to converge to a useful result.
+optimal solution. As the number of links decrease below
+30\% the best solution fails to converge.
 
@@
 events are chosen for three reasons. Firstly, they are recorded by a
-large number of stations (figure
+large number of stations (Fig.
 \ref{fig:-eqopti-California-Calaveras}) and therefore lend
 themselves to accurate travel time location. Secondly, they are
-distributed over a range of distances between near zero and hundreds
+distributed over distances from near zero to hundreds
 meters making them ideal for application of CWI. Finally, Calaveras
@@
 \hline
-Example 1 & comparison of CWI, catalogue and hypoDD \\
+Example 5 & comparison of CWI, catalogue and hypoDD \\
  & locations. \\
-Example 2 & exploration of station dependance for CWI and \\
+Example 6 & exploration of station dependance for CWI and \\
  & hypoDD. \\
-Example 3 & combined use of CWI and travel time data \\
+Example 7 & combined use of CWI and travel time data \\
 & with all and a reduced number of stations. \\
-Example 4 & combined use of CWI and travel time data \\
+Example 8 & combined use of CWI and travel time data \\
  & when travel times constrain only 50\% of the events. \\
@@
 
-\subsection{Example 1 - comparison of CWI, catalogue and hypoDD locations}
+\subsection{Example 5 - comparison of CWI, catalogue and hypoDD locations}
 
@@
 locations for the Calaveras earthquakes. The first column shows the
-original catalogue locations for all 308 earthquakes when each event
+original catalogue locations for all 308 earthquakes. That is, each event
 is located individually using all available travel time arrivals and
 a regional velocity model. The 68 earthquakes of interest in this
-study are0 differentiated in black. Catalogue locations suggest that
+study are differentiated in black. Catalogue locations suggest that
 the 68 earthquakes of interest are distributed spatially throughout
@@
 
-Now, we turn our attention to the coda waves to see if we can locate
-the events using CWI. Available waveforms for the 68 earthquakes are
-downloaded from the Northern California Earthquake Data Center
-(NCEDC) and visually inspected. Unsuitable waveforms are removed
-using the conditions summarised in table 5 of
-\citep{dr_Robinson11a}. The remaining waveforms are filtered between
+To apply CWI we download available waveforms 
+from the Northern California Earthquake Data Center
+(NCEDC). Unsuitable waveforms are removed
+using the conditions summarised in Table 5 of
+\citet{dr_Robinson11a}. Remaining waveforms are filtered between
 1 and 5\,Hz and aligned  to $P$ arrivals at 0\,s. CWI estimates are
@@
 event separation. We introduce the local coordinate system of
-section \ref{sec:theory} and find the relative locations using the
-CWI data and Polak-Ribiere optimisation.
-
-The CWI locations for the 68 events are illustrated in column two of
-figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (grey)
+Section \ref{sec:theory} and find the optimum relative locations using 
+Polak-Ribiere optimisation.
+
+CWI locations for the 68 events are illustrated in column two of
+Figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (grey)
 are shown for the remaining 240 earthquakes and are included to ease
-comparison. The third column of figure
+comparison. The third column of Figure
 \ref{fig-69Calaverasevents_eg1} illustrates the locations given by
-hypoDD with Singular Value Decomposition (SVD) when absolute arrival
-times and cross correlation computed time differences for the 68
-earthquakes are considered collectively.
-
-Note that by using coda waves alone we can not obtain actual
-locations. For the sake of comparison, we arbitrary choose a
-`master' event and translate our locations to align with the hypoDD
+hypoDD with Singular Value Decomposition (SVD), absolute arrival
+times and cross correlation computed time differences.
+
+Global locations can not be found by CWI alone. 
+For the sake of comparison, we arbitrary choose a
+`master' event and translate our relative locations to align with the hypoDD
 location for the same event. We return to this issue of relative
-versus actual location in Example 3 by introducing a combined travel
+versus actual location in Example 7 by introducing a combined travel
 time and coda wave inversion.
@@
 independent indication of clustering for the 68 events and to first
-order, similar locations to those from hypoDD (column 3).
-Interestingly, we observe a smaller second order difference between
+order, similar locations to those from hypoDD (column 3). Figure 
+\ref{fig-69Calaverasevents_eg1}
+illustrates a small second order difference between
 the CWI and hypoDD based locations. In particular, the lineation is
-less clear in the CWI locations (column 2) than that suggested by
-the hypoDD (column 3). Our results suggest that the coda are less
+less clear in the CWI locations (column 2) than that given by
+hypoDD (column 3). Our results suggest that the coda are less
 supportive of the presence of streaks although a complete
@@
 attention now is devoted towards understanding how both techniques
-perform with fewer stations (Example 2) and exploring how the two
-techniques may be combined (Examples 3 and 4).
-
-\subsection{Example 2 - Dependance on the number of stations}
+perform with fewer stations (Example 6) and exploring how CWI and 
+travel times can be combined (Examples 7 and 8).
+
+\subsection{Example 6 - Dependance on the number of stations}
 
@@
 of stations and poor azimuthal coverage are common limitations when
-trying to understand intraplate seismicity. For example, there are
+trying to locate intraplate clusters. For example, there are
 only 3 network seismic stations in the South West Seismic Zone of
 Western Australia, a region similar in size to that hosting 805
-stations in figure \ref{fig:-eqopti-California-Calaveras}.
-
-We explore the impact of poorer recording situations in Example 2 by
+stations in Figure \ref{fig:-eqopti-California-Calaveras}.
+
+We explore the impact of poorer recording situations in Example 6 by
 re-locating the 68 Calaveras events  using hypoDD and coda waves
@@
 repeat the process removing one at a time until a single station
-remains. The 10 stations considered are shown in figure
+remains. The 10 stations considered are shown in Figure
 \ref{fig:-eqopti-Calaveras-substations} and the order of removal
-explained in table \ref{tab:Calaveras-stationremoval}.
+explained in Table \ref{tab:Calaveras-stationremoval}.
 
@@
 
-The CWI locations are illustrated in figure
+CWI locations are illustrated in Figure
 \ref{fig-CWIreducesstats} for the inversions with 7, 5, 4, 3, 2 and
 1 station. We observe a high level of consistency between these 6
-inversions and the locations shown in figure
+inversions and the locations shown in Figure
 \ref{fig-69Calaverasevents_eg1} (column 2) when all stations are
@@
 outside the cluster when less stations are used with hypoDD. Even
-with 7 stations the linear streak of figure
+with 7 stations the linear streak of Figure
 \ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
@@
 make an assessment of this prior to starting the inversion. The top
-row of figure \ref{fig-statremoval_summarystats} demonstrates that
-when 5 or more stations are used we can constrain the location of
+row of Figure \ref{fig-statremoval_summarystats} demonstrates that
+when 5 or more stations are used CWI can constrain the location of
 all 68 earthquakes. When less than 5 stations are used the coda
@@
 removal of outliers described by \citet{dr_Waldhauser00a}. The top
-row of figure \ref{fig-statremoval_summarystats} shows that the
+row of Figure \ref{fig-statremoval_summarystats} shows that the
 number of events re-located by hypoDD fluctuates between 63 and 28
@@
 
-The remaining rows of figure \ref{fig-statremoval_summarystats}
+The remaining rows of Figure \ref{fig-statremoval_summarystats}
 illustrate a statistical comparison of the CWI and hypoDD reduced
@@
 \section{Theory for Combining travel time and CWI constraints}
-
-In Examples 1 and 2 we compare the location of the Calaveras
+\label{sec:CalaverasLoc-CWIandTT}
+In Examples 5 and 6 we compare the location of the Calaveras
 earthquakes using coda wave and arrival time based constraints
@@
 is the covariance matrix. In this paper we define the mean location
-$\mu_{\mathbf{e}_p}$ and covariance matrix by hypoDD optimum
+$\mu_{\mathbf{e}_p}$ and covariance matrix by the hypoDD optimum
 solution and its uncertainties. It is important to note that hypoDD
@@
 solution. Secondly, the travel time constraints in the form of
-equation \ref{eq-ttcomponent} resolve the inherent non-uniqueness
+equation (\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
 associated with translation, rotation and reflection around a global
@@
 
-\subsection{Example 3 - Combining travel time and CWI constraints}
-\label{sec:CalaverasLoc-CWIandTT} Figure
+\subsection{Example 7 - Combining travel time and CWI constraints}
+ Figure
 \ref{fig-68Calaverasevents_ttandcoda1} illustrates the earthquake
@@
 
-The Omori formula
-\begin{equation}
-\label{eq:original_omori}
- n(t) = K(t+C)^{-p}
-\end{equation}
-can be used to estimate the aftershock frequency per unit time
-interval $n(t)$ at time $t$ (\textbf{ADD REF}). \citet{dr_Utsu95a}
-converted equation \ref{eq:original_omori} to a cumulated number of
-events
-\begin{equation}
-N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}.
-\end{equation}
-
+An estimate of the cummulative number of aftershocks $N(t)$ after 
+$t$ days is given by the modified Omori formula
+\begin{equation}
+N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}
+\end{equation}
+\citep{dr_Utsu95a}.
 The empirically derived constants, $K$, $C$ and $p$ vary between
@@
 $M\ge3.2$ of the  Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of
-12 July 1993, \citet{dr_Utsu95a} obtains maximum likelihood
+12 July 1993, \citet{dr_Utsu95a} obtained maximum likelihood
 estimates for $K$, $p$ and $c$ of 906.5, 1.256 and 1.433,
@@
 \end{equation}
-This idea is illustrated figure \ref{fig:Omorifigure} which shows
+This idea is illustrated in Figure \ref{fig:Omorifigure} which shows
 the best fitting Omori Formula separated into segments before
-(dashed), during (solid) and after (dashed) the temporary
+(dashed), during (solid) and after (dashed) the pseudo temporary
 deployment.
@@
 With this idea of a temporary deployment in mind we have another
-attempt at relocating the Calaveras earthquakes. This time however,
+attempt at relocating the Calaveras earthquakes. In Example 8
 we consider the travel time constraints on half (34) of the
@@
 for all 68 earthquakes. The combined inversion is shown in column 1
-of figure \ref{fig-68Calaverasevents_ttsubsetandcoda1}. The
+of Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1}. The
 inversion result is similar to the combined inversion when all
-travel time data is incorporated (see figure
+travel time data is incorporated (see Fig.
 \ref{fig-68Calaverasevents_ttandcoda1}). The slight increase in
@@
 possible to locate the 34 events recorded by the pseudo temporary
-deployment. The ability of coda waves to link events during and
-outside the deployment period is likely their strongest asset. This
+deployment. This
 ability of  coda waves to constrain the location of events recorded
@@
 
-\section{Conclusions}
-\begin{itemize}
-\item Emphasise strengths of the CWI relocation (i.e. with small number of stations,
-linking temporary deployments with catalogue locations)
-\item Discuss potential applications e.g. intraplate/downhole/tunnel monitoring etc.
-\end{itemize}
-
-?????A number of studies have reported similar streaks on the
-Calaveras and other fault systems in California
-\citep{dr_Rubin99a,dr_Waldhauser99a, dr_Waldhauser02a, dr_Schaff02a,
-dr_Waldhauser04a}. \citet{dr_Rubinstein07a} argue that such streaks
-represent the boundary between creeping and locked sections of the
-faults. Earthquakes of interest for  our study align along one of
-these streaks. ???comment on circular versus linear error????
+\section{Discussion and Conclusions}
+
+Coda wave interferometry is an emerging technique for constraining 
+earthquake location. The technique relies on the interference between coda waves
+of closely located events and is hence most useful
+for studying earthquake clusters and/or aftershock sequences. 
+Coda wave constraints are independent of travel times
+and can be used in isolation or combination with early onset body waves. The strength of coda
+is that it is possible to constrain earthquake location from a single station, 
+an outcome demonstrated most clearly by Figures .......
+
+Coda wave interferometry offers a new technique for understanding earthquakes in intraplate areas 
+with sparse networks and poor azimuthal coverage.
+In particular, the ability to combine coda wave constraints with travel times makes it possible
+to link well constrained events from 
+a temporary deployment with those recorded outside
+the deployment period. All that is required to achieve this is at 
+least one network station which has recorded
+sufficient events from both periods therefore opening new avenues
+for imaging intraplate fault structures and 
+improving our understanding of intraplate seismicity and earthquake hazard.
+
+Another potential application of CWI is in the area of hydraulic fracturing 
+such as hot rock geothermal projects and/or
+petroleum reservoir engineering. Monitoring pumping induced micro earthquakes is a key step in understanding
+the migration of fluids in such reservoirs. There is a trade-off in the ability of surface deployed networks
+to locate events which are small and/or deep. As we begin to push reservoir projects to deeper depths
+downhole seismic monitoring is likely to play increasingly important roles. 
+CWI creates new possibilities to monitor 
+pumping induced micro earthquakes from fewer boreholes and
+hence dramatically reduce the costs of reservoir monitoring at large depths. It may also be possible
+to utilise coda for understanding hazard in tunneled mining operations where the 
+location of deep tunnels prohibits
+azimuthal coverage of induced events.
 

### 2012-07-20 paper2/paper2.tex
The version sent to Malcolm for comment

@@
 %\documentclass[extra,mreferee]{gji}
+%\documentclass[extra, onecolumn, doublespacing]{gji}
 \documentclass[extra]{gji}
@@
 $^3$ Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines, Golden CO \emph{80401-1887}, USA \\
-$^4$ Earthquakes and the Environment Program, NORSAR,Kjeller, Norway}
+$^4$ ..................}
 
@@
  Coda wave interferometry (CWI) is an emerging tool for constraining
-earthquake source properties from the intereference pattern of coda waves between nearby
-events. A new earthquake location algorithm is derived which relies on CWI based probabilistic estimates 
-of earthquake separation. The algorithm can be used with CWI estimates alone or in tandem with travel time
-data. Synthetic examples in 2D and 3D and real earthquakes on the 
-Calaveras Fault, California are used to demonstrate the usefulness of the CWI technique in locating 
-poorly recorded earthquakes. It is demonstrated that CWI: (a) outperforms traditional earthquake location 
-techniques when the number of stations is small; (b) is self-consistent across a broad range of station
-situations; and (c) can be used with a single station to locate earthquakes.
+earthquake source properties from the intereference pattern of coda
+waves between nearby events. A new earthquake location algorithm is
+derived which relies on CWI based probabilistic estimates of
+earthquake separation. The algorithm can be used with CWI estimates
+alone or in tandem with travel time data. Synthetic examples in 2D
+and 3D and real earthquakes on the Calaveras Fault, California are
+used to demonstrate the potential of CWI for locating poorly
+recorded earthquakes. It is demonstrated that CWI: (a) outperforms
+traditional earthquake location techniques when the number of
+stations is small; (b) is self-consistent across a broad range of
+station situations; and (c) can be used with a single station to
+locate earthquakes.
 
@@
 
-We design a 2D synthetic experiment (Example 1) by
-randomly selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq \hat{x} \leq 50$ and $-50 \leq \hat{y} \leq 50$.
-These are indicated with triangles in Fig. \ref{fig-2D50eq-relocation_eg1}.
+We design a 2D synthetic experiment (Example 1) by randomly
+selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
+\hat{x} \leq 50$ and $-50 \leq \hat{y} \leq 50$. These are indicated
+with triangles in Figure \ref{fig-2D50eq-relocation_eg1}.
  We assume a local velocity of $v=3300\,$ms$^{-1}$ between all
@@
 optimisation procedure on the hypothetical CWI data yields the
-circles in Fig. \ref{fig-2D50eq-relocation_eg1}. The optimisation
+circles in Figure \ref{fig-2D50eq-relocation_eg1}. The optimisation
 does not lead to the correct solution due to the addition of noise
@@
 \includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-\caption{Example 3 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise
-$\bar{\sigma}_N= 2 \sigma_{1to5Hz}(\delta_t)$.
+\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N= 2
+\sigma_{1to5Hz}(\delta_t)$.
  Actual and optimisation event locations
@@
 synthetic acoustic experiment with filtering between 1 and 5\,Hz
-\citep[see Fig4(b) of ][]{dr_Robinson11a}. Repeating the
-optimisation leads to the circles in Fig.
+\citep[see Fig. 4(b) of ][]{dr_Robinson11a}. Repeating the
+optimisation leads to the circles in Figure
 \ref{fig-2D50eq-relocation_eg3} which have an average coordinate
@@
 
-We can draw three observations from the error structure in Figs.
+We can draw three observations from the error structure in Figures
 \ref{fig-2D50eq-relocation_eg1} and \ref{fig-2D50eq-relocation_eg3}.
-Firstly, the location errors depicted by grey bars increase between
+Firstly, the location errors depicted by gray bars increase between
 examples 1 and 2 with the introduction of larger noise. Secondly,
@@
 %\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\noindent\includegraphics[width = 20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (grey)
-and best (black) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
-$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
-The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
+\noindent\includegraphics[width =
+20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+\caption{Example 3 - Statistical measures of error in the
+optimisation solutions for the 2D synthetic cases when all (gray)
+and best (black) results are considered. The statistics
+$\Delta_{max}$ and $\Delta_\mu$  are the maximum and mean coordinate
+error, respectively. The bottom subplot shows the average minimum
+number of branches required to link the 2450 pairs.}
  \label{fig:optimisationresults-2Dsynth}
@@
 Figure \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrates
-the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of the
-coordinate difference as a function of increasing linkage. We show
-the statistics for the `best' optimisation solution (black) and for
-the solution space when all 25 optimisations are considered (grey).
-In this case the best solution is determined by the set of event
-locations which lead to the smallest value of $L$. The
-error in the best solution is consistent when 30\%
-or more of the branches are used. The errors increase when only
-10\% or 20\% of the constraints are included. Interestingly, this
-breakdown around 20\% to 30\% coincides with the point where the
-average number of branches required to link each pair reaches 2 (see
-Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the average
-number of branches can be computed in advance it can be used as an
-indication of the inversion stability prior to
-optimisation. An earlier breakdown is observed when all 25 solutions
-are considered collectively. For example, the maximum coordinate
-error $\Delta_{max}$ exceeds that for the best
-solution for linkage $\leq$60\% confirming that the optimisation is susceptible to
-local minima and that a range of starting points should
-be considered.
+the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
+the coordinate difference as a function of increasing linkage. We
+show the statistics for the `best' optimisation solution (black) and
+for the solution space when all 25 optimisations are considered
+(gray). In this case the best solution is determined by the set of
+event locations which lead to the smallest value of $L$. The error
+in the best solution is consistent when 30\% or more of the branches
+are used. The errors increase when only 10\% or 20\% of the
+constraints are included. Interestingly, this breakdown around 20\%
+to 30\% coincides with the point where the average number of
+branches required to link each pair reaches 2 (see
+Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the
+average number of branches can be computed in advance it can be used
+as an indication of the inversion stability prior to optimisation.
+An earlier breakdown is observed when all 25 solutions are
+considered collectively. For example, the maximum coordinate error
+$\Delta_{max}$ exceeds that for the best solution for linkage
+$\leq$60\% confirming that the optimisation is susceptible to local
+minima and that a range of starting points should be considered.
 
@@
 %\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\noindent\includegraphics[width = 20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (grey)
-and best (black) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
-$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
-The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
-when all or best optimisation result(s) are considered, respectively.}
+\noindent\includegraphics[width =
+20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+\caption{Example 4 - Statistical measures of error in the
+optimisation solutions for the 3D synthetic cases when all (gray)
+and best (black) results are considered. The statistics
+$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
+error, respectively. The absence of the gray and black lines below
+60\% and 30\% indicates a breakdown in the solutions when all or
+best optimisation result(s) are considered, respectively.}
 \label{fig:optimisationresults-3Dsynth}
@@
 When 70\% of the direct constraints are considered all optimisation
-results (grey) are consistent with the best solution (black). The
+results (gray) are consistent with the best solution (black). The
 best solution constrains the event locations down to 30\% of the
@@
 the final iteration was typically close to the actual solution when
-the optimisation failed to converge.
-Contrastingly, in 3D the optimisation appears to converge to the
-correct solution or fail completely, leading to a set locations
-which in no way resemble the actual solution. This is depicted in
-Figure \ref{fig:optimisationresults-3Dsynth} by the absence of the
-grey and black lines below 60\% and 30\% of the constraints,
-respectively. The reason for this difference may be due to the
-increased number of degrees of freedom in 3D requiring a greater
-number of iterations to converge. Nevertheless, the accurate
-convergence of the best solution for cases with 30\% linkage or
-higher is encouraging for the potential of coda wave optimisation to
-constrain earthquake location.
+the optimisation failed to converge. Contrastingly, in 3D the
+optimisation appears to converge to the correct solution or fail
+completely, leading to a set locations which in no way resemble the
+actual solution. This is depicted in Figure
+\ref{fig:optimisationresults-3Dsynth} by the absence of the gray and
+black lines below 60\% and 30\% of the constraints, respectively.
+The reason for this difference may be due to the increased number of
+degrees of freedom in 3D requiring a greater number of iterations to
+converge. Nevertheless, the accurate convergence of the best
+solution for cases with 30\% linkage or higher is encouraging for
+the potential of coda wave optimisation to constrain earthquake
+location.
 
@@
 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Elevation in California showing location of the 308 event
-Calaveras cluster (black star) and 805 seismic stations (red
-triangles).} \label{fig:-eqopti-California-Calaveras}
+\caption{Elevation in California showing location of the Calaveras
+cluster (white star) and 805 seismic stations (black triangles).}
+\label{fig:-eqopti-California-Calaveras}
 \end{figure}
@@
 \begin{table}
-\caption{Experiment locations performed for 68 earthquakes on teh
-Calaveras Fault} \label{tab:examples}
+\caption{Location examples for the 68 Calaveras earthquakes.}
+\label{tab:examples}
 \begin{tabular}{ll}
@@
 \includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\caption{Comparison of earthquake hypocenters using three different
-methods: catalogue location (column 1), hypoDD with all 308 events
-(column 2) and CWI example 1 (column 3). Note that in the case of
-the CWI locations we consider only the 68 earthquakes in red, the
-blue events are shown for the purpose of orientation only.}
+\caption{Example 5 - Comparison of earthquake locations using three
+different methods: catalogue location (column 1), CWI (column 2) and
+hypoDD (column 3). Note that in the case of the hypoDD and CWI
+inversions we consider only the 68 earthquakes in black, the gray
+events are shown for the purpose of orientation only.}
 \label{fig-69Calaverasevents_eg1}
@@
 CWI locations for the 68 events are illustrated in column two of
-Figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (grey)
+Figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (gray)
 are shown for the remaining 240 earthquakes and are included to ease
@@
 phases because of the excellent recording situation in California
-with many stations and strong azimuthal coverage (see figure
+with many stations and strong azimuthal coverage (see Fig.
 \ref{fig:-eqopti-California-Calaveras}). In contrast, a small number
 of stations and poor azimuthal coverage are common limitations when
-trying to locate intraplate clusters. For example, there are
-only 3 network seismic stations in the South West Seismic Zone of
-Western Australia, a region similar in size to that hosting 805
-stations in Figure \ref{fig:-eqopti-California-Calaveras}.
+trying to locate intraplate clusters. For example, there are only 3
+network seismic stations in the South West Seismic Zone of Western
+Australia, a region similar in size to that hosting 805 stations in
+Figure \ref{fig:-eqopti-California-Calaveras}.
 
@@
 \caption{Location of the 10 stations (triangles) used to relocate
-the Calaveras events in Example 2. Stations are removed one at a
-time according to the order in Table
+the Calaveras events in Example 6 to 8. Stations are removed one at
+a time according to the order in Table
 \ref{tab:Calaveras-stationremoval} and the events relocated. The
@@
 \includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{....} \label{fig-CWIreducesstats}
+\caption{Example 6 - CWI locations with reduced stations.}
+\label{fig-CWIreducesstats}
 \end{figure*}
@@
 \includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\caption{HypoDD (SVD) with reduced stations.}
+\caption{Example 6 - HypoDD (SVD) locations with reduced stations.}
 \label{fig-HYPODDreducesstats}
@@
 \noindent\includegraphics[width =
-20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Statistics on
-coordinate differences for reduced station inversions. Differences
-are computed between the inversion results (CWI and hypoDD) and the
-complete hypoDD locations for all 308 events. The top subplot
-illustrates the number of constrainable events in the CWI and hypoDD
-inversions as a function of the stations considered.}
+20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
+Statistics on coordinate differences for reduced station inversions.
+Differences are computed between the inversion results (CWI and
+hypoDD) and the complete hypoDD locations for all 308 events. The
+top subplot illustrates the number of constrainable events in the
+CWI and hypoDD inversions as a function of the stations considered.}
 \label{fig-statremoval_summarystats}
@@
 consistent regardless of the number of stations considered. In
-contrast, the statistics for the hypoDD inversions fluctuate between
-... and .... for the mean coordinate error and ... and ...  for the
-maximum confirming that the hypoDD inversion procedure is less
+contrast, the hypoDD mean and maximum coordinate error fluctuate
+above those for CWI confirming that the hypoDD inversion is less
 stable than CWI with fewer stations.
@@
 data using all data (left) and 5 stations (right). The linear
-features observed in the original hypoDD inversions (see figure
+features observed in the original hypoDD inversions (see Fig.
 \ref{fig-69Calaverasevents_eg1}) is evident in both cases. However,
@@
 \includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Combined HypoDD (SVD) and CWI: all stations and 5
-stations.} \label{fig-68Calaverasevents_ttandcoda1}
+\caption{Example 7 - Combined HypoDD (SVD) and CWI locations using
+data form all stations (left) and 5 stations (right).}
+\label{fig-68Calaverasevents_ttandcoda1}
 \end{figure}
@@
 \begin{equation}
+\label{eq:CumOmori}
  N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}
@@
 the best fitting Omori Formula separated into segments before
-(dashed), during (solid) and after (dashed) the pseudo temporary
+(gray), during (black) and after (gray) the pseudo temporary
 deployment.
@@
 Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-according to the best fitting modified Omori Formula
-\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost
-dashed signify aftershocks occurring before, during and after the
-deployment of a temporary array installed 4 days after the main
-shock and left for 150 days. A temporary deployment of this kind
-will record roughly 50\% of the aftershocks in the 1000 days
-following the mainshock. } \label{fig:Omorifigure}
+using equation \ref{eq:CumOmori}. The leftmost gray, middle black
+and rightmost gray lines signify aftershocks occurring before,
+during and after the deployment of a pseudo temporary array
+installed 4 days after the main shock and left for 150 days. A
+temporary deployment of this kind will record roughly 50\% of the
+aftershocks in the 1000 days following the mainshock. }
+\label{fig:Omorifigure}
 \end{figure}
@@
 \includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
-\caption{Mimicking the deployment of a temporary network by ignoring
-data from all but station CCO for 50\% (or 34) of the events using
-by combining CWI and TT (left) and using TT only (right). Only by
-combining the data is it possible to locate all 68 events.
+\caption{Example 8 - Mimicking the deployment of a temporary network
+by ignoring data from all but station CCO for 50\% (or 34) of the
+events. Locations are shown for the combined CWI and travel time
+inversion (left) and the inversion with travel times only (right)
+Only by combining the data is it possible to locate all 68 events.
 Furthermore, combining the data leads to a solution more consistent
-with figure ..... } \label{fig-68Calaverasevents_ttsubsetandcoda1}
+with Figure \ref{fig-69Calaverasevents_eg1}. }
+\label{fig-68Calaverasevents_ttsubsetandcoda1}
 \end{figure}
@@
 Coda wave interferometry is an emerging technique for constraining
-earthquake location. The technique relies on the interference between coda waves
-of closely located events and is hence most useful
-for studying earthquake clusters and/or aftershock sequences. 
-Coda wave constraints are independent of travel times
-and can be used in isolation or combination with early onset body waves. The strength of coda
-is that it is possible to constrain earthquake location from a single station, 
-an outcome demonstrated most clearly by Figures .......
-
-Coda wave interferometry offers a new technique for understanding earthquakes in intraplate areas 
-with sparse networks and poor azimuthal coverage.
-In particular, the ability to combine coda wave constraints with travel times makes it possible
-to link well constrained events from 
-a temporary deployment with those recorded outside
-the deployment period. All that is required to achieve this is at 
-least one network station which has recorded
-sufficient events from both periods therefore opening new avenues
-for imaging intraplate fault structures and 
-improving our understanding of intraplate seismicity and earthquake hazard.
-
-Another potential application of CWI is in the area of hydraulic fracturing 
-such as hot rock geothermal projects and/or
-petroleum reservoir engineering. Monitoring pumping induced micro earthquakes is a key step in understanding
-the migration of fluids in such reservoirs. There is a trade-off in the ability of surface deployed networks
-to locate events which are small and/or deep. As we begin to push reservoir projects to deeper depths
-downhole seismic monitoring is likely to play increasingly important roles. 
-CWI creates new possibilities to monitor 
-pumping induced micro earthquakes from fewer boreholes and
-hence dramatically reduce the costs of reservoir monitoring at large depths. It may also be possible
-to utilise coda for understanding hazard in tunneled mining operations where the 
-location of deep tunnels prohibits
-azimuthal coverage of induced events.
+earthquake location. The technique relies on the interference
+between coda waves of closely located events and is hence useful for
+studying earthquake clusters and/or aftershock sequences. Coda wave
+constraints are independent of travel times and can be used in
+isolation or combination with early onset body waves. The strength
+of coda is that it is possible to constrain earthquake location from
+a single station, an outcome demonstrated most clearly by Figures
+Figures \ref{fig-CWIreducesstats} and
+\ref{fig-68Calaverasevents_ttsubsetandcoda1}
+
+Coda wave interferometry offers a new technique for understanding
+earthquakes in intraplate areas with sparse networks and poor
+azimuthal coverage. In particular, the ability to combine coda wave
+constraints with travel times makes it possible to link well
+constrained events from a temporary deployment with those recorded
+outside the deployment period. All that is required to achieve this
+is at least one network station which has recorded sufficient events
+from both periods. CWI facilitates the location of poorly recorded
+events to an accuracy approaching those recorded during the
+temporary deployment and therefore opens new avenues for imaging
+intraplate fault structures and improved our understanding of
+intraplate seismicity and earthquake hazard.
+
+Another potential application of CWI is in the area of hydraulic
+fracturing such as hot rock geothermal projects and/or petroleum
+reservoir engineering. Monitoring pumping induced micro earthquakes
+is a key step in understanding the migration of fluids in such
+reservoirs. There is a trade-off in the ability of surface deployed
+networks to locate events which are small and/or deep. Downhole
+seismic monitoring is likely to play increasingly important roles in
+deep reservoir projects. CWI creates new possibilities to monitor
+pumping induced micro earthquakes from fewer boreholes and hence
+dramatically reduce the costs of reservoir monitoring at large
+depths. It may also be possible to utilize coda for understanding
+hazard in tunneled mining operations where the location of deep
+tunnels prohibits azimuthal coverage of induced events.
 
@@
 
-The noisy likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-used in eq. (\ref{eq:-bayesian-noisyform}) is given by
+The noisy likelihood
+$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ used in equation
+(\ref{eq:-bayesian-noisyform}) is given by
 \begin{equation}
@@
 \citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
-in eq. (\ref{eq:Adefn}) are defined by the expresions
+in equation (\ref{eq:Adefn}) are defined by the expressions
 \begin{equation}
@@
 \end{equation}
-with coefficients $a_1$ to $a_5$ and $c$ defined in Table \ref{tab-const4-mu1-sigma1}.
-The parameters $\bar{\mu}_N$ and $\bar{\sigma}_N$ used in
-eq. (\ref{eq:Cdefn}) are obtained by finding the values which minimise the
-difference in a least squares sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
-computed from the waveforms and the
-positively bounded Gaussian density function
+with coefficients $a_1$ to $a_5$ and $c$ defined in Table
+\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
+$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
+finding the values which minimize the difference in a least squares
+sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
+computed from the waveforms and the positively bounded Gaussian
+density function
 \begin{equation}
@@
 \begin{table}
-\caption{Coefficients for eqs. (\ref{eq:mu1}) and (\ref{eq:sigma1}).}
-\label{tab-const4-mu1-sigma1}
+\caption{Coefficients for equations. (\ref{eq:mu1}) and
+(\ref{eq:sigma1}).} \label{tab-const4-mu1-sigma1}
 \begin{tabular}{|c|c|}
@@
 \end{equation}
-are required by the Polak-Ribiere algorithm. These are used to guide the optimisation procedure
-towards the values of $(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$ which
-minimise $L$.
-
-The equations for the derivatives are convoluted so we
-build them gradually. We start with an expression for $\delta_t$, the wavelength normalised separation between two events
-$\mathbf{e}_p= (\hat{x}_p,\hat{y}_p,\hat{z}_p)$ and $\mathbf{e}_q = (\hat{x}_q,\hat{y}_q,\hat{z}_q)$
+are required by the Polak-Ribiere algorithm. These are used to guide
+the optimization procedure towards the values of
+$(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$ which minimize $L$.
+
+The equations for the derivatives are convoluted so we build them
+gradually. We start with an expression for $\delta_t$, the
+wavelength normalized separation between two events $\mathbf{e}_p=
+(\hat{x}_p,\hat{y}_p,\hat{z}_p)$ and $\mathbf{e}_q =
+(\hat{x}_q,\hat{y}_q,\hat{z}_q)$
 \begin{equation}
@@
 \end{equation}
-where differentiating eq. (\ref{eq:mu1}) gives
+where differentiating equation (\ref{eq:mu1}) gives
 \begin{equation}
@@
 %\end{equation}
-for a uniform prior. The change of sign in the middle (i.e. to addition) accounts for the change in
-order of the events under the conditional. Its inclusion here assumes the correct use of
-$\partial \widetilde{\delta}_t / \partial \hat{x}_p$
-or
-$\partial \widetilde{\delta}_t / \partial \hat{x}_q$
-when evaluating the left and right hand terms of the summation. The derivatives shown in this section
-appear complicated but are in practice trivial to compute numerically.
-Confidence in their accuracy is enhanced in the following sections by demonstrating that
-the optimisation procedure converges to the correct solution for a number of synthetic problems
+for a uniform prior. The change of sign in the middle (i.e. to
+addition) accounts for the change in order of the events under the
+conditional. Its inclusion here assumes the correct use of $\partial
+\widetilde{\delta}_t / \partial \hat{x}_p$ or $\partial
+\widetilde{\delta}_t / \partial \hat{x}_q$ when evaluating the left
+and right hand terms of the summation. The derivatives shown in this
+section appear complicated but are in practice trivial to compute
+numerically. Confidence in their accuracy is enhanced in the
+following sections by demonstrating that the optimization procedure
+converges to the correct solution for a number of synthetic problems
 in 2 and 3 dimensions.

### 2012-07-20 paper2/diags/build_OmoriFigure.m

@@ -15,25 +15,27 @@ prop_recorded = (Nend-Nstart)/Ntotal
 
 t1 = [0:tstart];
 N1 = Cumm_Omori(t1);
-plot(t1,N1,'k--','linewidth',4)
+plot(t1,N1,'linewidth',2,'color',[0.7,0.7,0.7])
 
 t2 = [tstart:tend];
 N2 = Cumm_Omori(t2);
 hold on
-plot(t2,N2,'k','linewidth',4)
+plot(t2,N2,'k','linewidth',2)
 
 tend2 = 1000;
 t3 = [tend:tend2];
 N3 = Cumm_Omori(t3);
-plot(t3,N3,'k--','linewidth',4)
+plot(t3,N3,'linewidth',2,'color',[0.7,0.7,0.7])
 
 fsize = 16;
-set(gca,'fontsize',fsize)
-xlabel('time (days)','fontsize',fsize)
-ylabel('Cummulative number of aftershocks','fontsize',fsize)
+%set(gca,'fontsize',fsize)
+xlabel('t (days)')%,'fontsize',fsize)
+%ylabel('Cummulative number of aftershocks','fontsize',fsize)
 
-set(gca,'xlim',[-25, tend2],'xtick',[0:100:tend2])
+ylabel('N(t)')
+set(gca,'xlim',[-25, tend2],'xtick',[0:200:tend2])
 
+set(gca,'units','centimeters','position',[4.6,1.5,7.5,6])
 print -depsc OmoriFigure.eps
 
 function [N] = Cumm_Omori(t)

### 2012-07-24 paper3/paper3.tex
Creating a git version of paper3 to start working on

--- 2011-12-06 paper2/paper2_jgr.tex
@@
 
-\documentclass[draft,jgrga]{agutex}
+%\documentclass[draft,grl]{agutex}
+\documentclass[grl]{agutex}
 \bibliographystyle{agufull08}
-%\usepackage{rotating}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %  (comment out this line for draft format):
-  \usepackage[dvips]{graphicx}
+\usepackage{graphicx}
+\usepackage{multirow}  % DR Needed to setup figure 1 - must comment out for final version..
 %
@@
 % Shorter version of title entered in capital letters:
-\titlerunninghead{EARTHQUAKE LOCATION USING CODA WAVES}
+\titlerunninghead{LOCATING POORLY RECORDED EARTHQUAKES USING CODA WAVES}
 
@@
 
-\authoraddr{J. Hauser,
-NORSAR, Postboks 53, Instituttveien 25, N-2027 Kjeller, Norge}
+\authoraddr{P. Cummins,
+Research School of Earth Sciences, Australian National University, Canberra, ACT, 0200, Australia.
+ (phil.cummins@anu.edu.au) and
+Risk Research Group, Geoscience Australia, GPO Box 378, Canberra, ACT, 2601, Australia.
+ (phil.cummins@ga.gov.au)}
+
+\authoraddr{J. Dawson,
+Earth Monitoring Group,Geoscience Australia, GPO Box 378, Canberra, ACT, 2601, Australia.
+ (john.dawson@ga.gov.au)}
 
@@
 
-\title{Relocating a cluster of earthquakes using coda waves from a single station}
+\title{Accurate relative location using coda waves of a poorly recorded cluster of earthquakes near Kalannie, Western Australia}
 %
@@
 M. SAMBRIDGE,  \altaffilmark{1}
-R. SNIEDER \altaffilmark{3}
-and J. HAUSER \altaffilmark{1,} \altaffilmark{4}}
+R. SNIEDER, \altaffilmark{3}
+P. CUMMINS \altaffilmark{1,} \altaffilmark{2}
+AND J. DAWSON \altaffilmark{4}}
 %E. Mosley-Thompson, \altaffilmark{2} R. Williams, \altaffilmark{3}
@@
 
-\altaffiltext{4}{Earthquakes and the Environment Program, NORSAR}
+\altaffiltext{4}{Earth Monitoring Group, Geoscience Australia}
 
@@
 \begin{itemize}
-\item Brief discussion of existing earthquake location techniques - first arrivals - need for good station coverage etc.
-\item Non-technical overview of CWI (\citealp{dr_Snieder05a}; \citealp{dr_Snieder06a})
-\item Comment how CWI pairwise separation does not require azimuthal station coverage \citep{dr_Robinson07b}
-\item Mention probabilistic version for CWI based separation (ref \textbf{paper1})
+\item South West Seismic Zone (SWSZ) - one of Australia's most active source zones
+\item Poor station coverage makes accurate location difficult
+\item Kalannie earthquake cluster (figure \ref{fig:-Kalannie-map}(a))
+\item \citet{dr_Dawson08a} composite mechanism (ref table \ref{tab-Dawson-Kalannie-results})
+\item Validity of composite mechanism assumes overlapping rupture on the same fault - we demonstrate that
+assumption holds despite the poor station coverage
 \end{itemize}
 
-\section{Theory}
+\section{Methodology}
 \begin{itemize}
-\item Key CWI formulae from \citet{dr_Snieder05a},
-\citet{dr_Snieder06a} and \textbf{paper1}
-\item Formulation of the misfit function $L$ (i.e. extract from Thesis Chapter 5)
-\item Discuss minimization of $L$ using Polak-Ribiere conjugate gradient method
-\item Derivation of Derivatives
+\item Compute Kalannie event sizes (Table \ref{tab:Kalannie-eventsizes}) and comment on location
+accuracy required to demonstrate that events are overlapping
+\item Relative location with a few stations - use the coda
+\item CWI separation (\citealp{dr_Snieder05a}; \citealp{dr_Snieder06a})
+\item Possible to get separation estimate with a single station (e.g. \citealp{dr_Robinson07b})
+\item \textbf{ref Paper1} - formulates CWI probabilistically for a pair of events - must comment on wavelength normalisation
+\item \textbf{ref Paper2} - formulation of the joint posterior, misfit function $L$ and minimization by optimisation.
+\item Problem with optimisation approach is that it gives a single solution only and can get trapped in
+local minima. We use Markov-Chain Monte-Carlo (MCMC) here which allows a complete assessment of uncertainty.
+This is only possible because of the small number of events considered.
+\item \textbf{Malcolm and Roel - there is potentially a large number of equations to show here. I propose that we keep
+the number of equations as small as possible and refer readers to the other papers and the thesis for details. Any
+thoughts?}
 \end{itemize}
 
-\section{Benchmarking}
-\begin{itemize}
-\item Introduce 2D synthetic studies (relocating 50 earthquakes) and show results for cases with
-two different uncertainty levels (Figures \ref{fig-2D50eq-relocation_eg1} and
-\ref{fig-2D50eq-relocation_eg3})
-\item Explain CWI constraints in terms of a network of points
-\item Repeat the relocations with reduced pairwise linkage and show results
-(Figure \ref{fig:optimisationresults-2Dsynth})
-\item Discuss process of repeating optimisation with 25 randomly chosen starting locations
- and compare results to the best optimisation chain - i.e. stability of the inversion.
-\item \textbf{Malcolm and Roel - at this stage I am not planning to include detailed pictures of the 2D
-inversions and discuss rotational error structure. I don't think it is needed in this paper but I welcome your thoughts}
-\item Repeat the experiment in 3D and show results
-(Figure \ref{fig:optimisationresults-3Dsynth})
-\item Discuss differences between the 2D and 3D versions -i.e. failed convergence (in 3D) versus slow convergence (in 2D)
-\end{itemize}
-
-\section{Relocating Earthquakes on the Calaveras Fault}
-\begin{itemize}
-\item Introduce the Calaveras Fault and provide a brief background of why it is chosen here (Figure \ref{fig:-eqopti-California-Calaveras})
-\item Discuss Catalogue Locations - hypoDD locations and CWI locations
-(Figure \ref{fig-69Calaverasevents_eg1})
-\begin{itemize}
-\item mention difference between hypoDD inversions when 68 or
-308 earthquakes considered but don't show figure (i.e. difference in coordinates for
-the two solutions is roughly 2\,m)
-\item provide details on CWI application - waveform selection, filtering etc.
-\end{itemize}
-\item Discuss comparison between CWI and catalogue locations - first order performance of CWI and clustering
-\item Discuss comparison between CWI and hypoDD locations - second order result and streaks.
-\end{itemize}
-
-\section{Dependance on the number of stations}
+\section{Results}
 
 \begin{itemize}
-\item Explain issues associated with poor station coverage - superimpose
-the three SWSZ (i.e. Australian) stations onto  Figure
-\ref{fig:-eqopti-California-Calaveras}
-\item Show setup for consideration of fewer stations (Table
-\ref{tab:Calaveras-stationremoval}
-and Figure \ref{fig:-eqopti-Calaveras-substations})
-\item Show the results (Figures \ref{fig-68Calaveras_CWIxyloc-statremove}
-to \ref{fig-68Calaveras_hypoDDyzloc-statremove} and Figure \ref{fig-statremoval_summarystats})
-\item Discuss the better performance of CWI with fewer stations
-\item Question/Discuss why hypoDD continues to suggest streaks with 2 or 3 stations - there must be regularization
-\end{itemize}
-
-\section{Combining travel time and CWI constraints}
-
-\begin{itemize}
-\item Pose the problem
-\item Introduce the idea of a travel time based separation PDF with mean event locations from hypoDD outputs and
-some measure of uncertainty (we will consider three levels of uncertainty as in paper1).
-\item Explain how to combine the CWI based posterior with these new travel time based separation PDFs
-\item Show the derivatives of the travel time based separation PDF
-\item Undertake the combined inversion show/discuss findings (Figure \ref{fig-68Calaverasevents_ttandcoda1} )
-\end{itemize}
-
-\section{Combining CWI and travel times when the travel times constrain a limited number of events}
-
-\begin{itemize}
-\item Explain the idea of a temporary deployment of stations i.e. for aftershocks
-\item Discuss Omori formula and the $M_s$7.8 Hokkaido-Nansei-Oki earthquake
-(Figure \ref{fig:Omorifigure}; \citealp{dr_Utsu95a})
-\item Show/Discuss results (Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1})
+\item Discuss waveforms, first arrival similarity and filtering between 1 and 2\,Hz (Figure \ref{fig:-Kalannie-map}(b))
+\item We only have access to data from 3 stations MORW, BLDU and KLBR (Figure \ref{fig:-Kalannie-map}(a))
+\item Application of CWI on event pairs (Figure \ref{fig:-Kalannie-map}(b))
+\item Computation of CWI based pairwise separation posteriors (Figure \ref{fig:Kalannie-CWI-Posteriors})
+\item Compare MCMC results (Expected Value and standard error) to optimisation solution (Table \ref{tab:Kalannie-InversionRes})
+\item MCMC in more detail: 1D marginals, covariance and correlation (Figure \ref{fig:Kalannie-CWI-NAB-1Dmarginals})
+\item MCMC in more detail: example 2D marginal (Figure \ref{fig:Kalannie-2Dmarginals_param23}).
+Shows that events 1 and 2 are close but not co-located.
+\item Discuss the separation estimates which incorporate CWI from all pairs (e.g. Table \ref{tab:-KalannieRes-separations})
 \end{itemize}
@@
 \begin{itemize}
-\item Emphasise strengths of the CWI relocation (i.e. with small number of stations,
-linking temporary deployments with catalogue locations)
-\item Discuss potential applications e.g. intraplate/downhole/tunnel monitoring etc.
+\item The power of CWI when limited stations available
+\item Advantage of the MCMC inversion approach (i.e. detailed picture of uncertainty). Disadvantage that it
+is computationally expensive (ref \textbf{Paper2} for optimisation approach with more events).
+\item Demonstration that the events are close but not co-located. Consistent with hypothesis that the
+four ruptures overlap on the same fault.
 \end{itemize}
@@
 
+% Put the figures here....
+
 %% ------------------------------------------------------------------------ %%
@@
 % copy in the contents of your .bbl file here.
+
 \bibliography{../../refs/drrefs}
@@
 
-% DR ... \end{thebibliography}
+% DR ...\end{thebibliography}
 
@@
 %%% End the article here:
-% Put the figures here....
 \clearpage
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise $\bar{\sigma}_N=0.02$.
-Actual and optimisation event locations
-are shown in blue and red circles, respectively.}
-\label{fig-2D50eq-relocation_eg1}
+\begin{tabular}{ll}
+(a) & (b) \\
+\multirow{15}{*}{\includegraphics[width = 16pc]{../../thesis_version2/diags/eq_location_simple/KalannieMap/KalannieMap1.eps}} &
+\multirow{15}{*}{\includegraphics[width = 20pc]{diags/waves_and_CWIest.eps}} \\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{tabular}
+\caption{(a) Map of the South West Seismic Zone (SWSZ) illustrating the location of the Kalannie earthquake cluster,
+the \cite{dr_Dawson08a} composite focal mechanism for the Kalannie events,
+large historical events (focal mechanisms), observed seismicity between 1998 to 2007 (circles) and
+Quaternary fault scarps (black lines) identified by \citet{dr_Clark09a}. The three available recording stations
+MORW (162\,km), BLDU (67\,km) and KLBR (169\,km) are depicted with red triangles. Figure courtesy of
+\citet{dr_Dawson08a} with minor modifications. (b) Example waveforms and CWI separation estimates
+for the Kalannie events. The top row illustrates waveforms at station MORW for Event 1 normalised to maximum
+amplitude and filtered between 1 and 2\,Hz for the three channels N,Z,E. Relative P, S and surface wave arrivals are also
+indicated at 0, 19 and 27\,s, respectively. Middle row demonstrates similarity of first arrivals at station MORW for Events 1 and 2 in
+the three channels. The bottom row shows the CWI separation estimates at MORW
+as a function of sliding time window with width 5\,s for event pair 1 and 2. The three traces
+represent different channels and the vertical black lines
+enclose the region between $t=$5\,s and $t_{surf}$ that we consider for the remaining analysis.}
+\label{fig:-Kalannie-map}
 \end{figure}
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-\caption{Example 3 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise
-$\bar{\sigma}_N= 2 \sigma_{1to5Hz}(\delta_t)$.
- Actual and optimisation event locations
-are shown in blue and red circles, respectively.}
-\label{fig-2D50eq-relocation_eg3}
+\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_simple/Kalannie_figs/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
+\caption{Posterior functions $P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the Kalannie
+event pairs $i$ and $j$. A
+second $x$-axis is shown in separation units of meters for convenience.}
+\label{fig:Kalannie-CWI-Posteriors}
 \end{figure}
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
-and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
-$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
-The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
- \label{fig:optimisationresults-2Dsynth}
+\begin{tabular}{ll}
+(a) & (b) \\
+\multirow{3}{*}{\noindent\includegraphics[width = 25pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}} & \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
+&  \\
+ & \\
+ &
+ \\
+\\
+\\
+\\
+\\
+& (c) \\
+&  \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\end{tabular}
+\caption{(a) One dimensional marginals for each of the six unknown Kalannie earthquake coordinates.
+Labels $\hat{x}$, $\hat{y}$ and $\hat{z}$ refer to a local coordinate system with
+origin corresponding to the event 1 location. Subscripts indicate the event number. Missing
+parameters $\hat{y}_2$, $\hat{z}_2$ and $\hat{z}_3$ are set to 0 to remove rotational non-uniqueness without
+loss of generality. Grey shaded regions illustrate the probability of each coordinate
+being within 500\,m of the origin. The relative size of the shaded area
+indicates that all event coordinates are likely within 500\,m of event 1
+(see table \ref{tab:Kalannie-InversionRes} for actual areas). (b) Covariance and (c) correlation matrices
+for the Kalannie earthquake location coordinates.
+Different colours in the covariance matrix suggest different levels of resolvability between
+coordinates. The off-diagonal structure of the correlation matrix indicates
+a low level of trade-off between different coordinates.}
+\label{fig:Kalannie-CWI-NAB-1Dmarginals}
 \end{figure}
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
-and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
-$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
-The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
-when all or best optimisation result(s) are considered, respectively.}
-\label{fig:optimisationresults-3Dsynth}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Elevation in California showing location
-of the 308 event Calaveras cluster (black star) and 805 seismic stations (red triangles).}
-\label{fig:-eqopti-California-Calaveras}
-\end{figure}
-
-\begin{figure}
-\includegraphics{diags/CalaverasLoc1.eps}
-\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-308 events (column 2) and CWI example 1 (column 3).
-Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
-blue events are shown for the purpose of orientation only.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-\caption{Location of the 10 stations (red triangles) used to relocate the Calaveras events.
-Stations are removed one at a time according to the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated (see Figures \ref{fig-68Calaveras_CWIxyloc-statremove} to \ref{fig-68Calaveras_hypoDDyzloc-statremove}).
-The 304 Calaveras events are indicated with black circles.}
-\label{fig:-eqopti-Calaveras-substations}
-\end{figure}
-
-\begin{figure}
-\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{....}
-\label{fig-CWIreducesstats}
-\end{figure}
-
-\begin{figure}
-\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
-\caption{....}
-\label{fig-HYPODDreducesstats}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
-\caption{Statistics on coordinate differences for reduced station inversions. Differences
-are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-locations for all 308 events. The top subplot illustrates the number of constrainable
-events in the CWI and hypoDD inversions as a function of the stations considered.}
-\label{fig-statremoval_summarystats}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics{diags/CalaverasLoc5.eps}
-\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
-levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
-(after \citealp{dr_Waldhauser08a}), Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
-column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m (after \citealp{dr_Shearer97a}). }
-\label{fig-68Calaverasevents_ttandcoda1}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-\caption{Cumulative number of aftershocks for the Hokkaido-Nansei-Oki, Japan
-$M_s=7.8$ earthquake of 12 July 1993 according to the best fitting modified Omori Formula
-\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost dashed signify aftershocks occurring before, during and
-after the deployment of a temporary array installed 7 days after the main shock and left for
-65 days.}
-\label{fig:Omorifigure}
-\end{figure}
-
-\begin{figure}
-\noindent\includegraphics{diags/CalaverasLoc6.eps}
-\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
-22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
-are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
-relocation only (i.e. no CWI) using ........}
-\label{fig-68Calaverasevents_ttsubsetandcoda1}
+\noindent\includegraphics[width=20pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
+\caption{Marginal $P(\mathbf{e}_3) = P(\hat{x}_3,\hat{y}_3)$  for the location of event 3 normalised to unit volume.
+We observe a clear maximum
+near ($\hat{x}_3=290$\,m, $\hat{y}_3=300$\,m) and a local minimum near the origin. The black lines
+enclose the 68\% confidence region. This figure suggests that events 3 and 1 (at origin) are close to one another but
+not co-located and is consistent with the inversion results from the optimiser (magenta circle) and
+MCMC (green circle).}
+\label{fig:Kalannie-2Dmarginals_param23}
 \end{figure}
@@
 \clearpage
+
+\begin{table*}
+\caption[InSAR source parameters for composite Kalannie mechanism]
+{\cite{dr_Dawson08a} InSAR derived source parameters for a composite Kalannie mechanism with 1$\sigma$ uncertainties.
+These parameters represent the point source which best explains the observed deformation at the surface. }
+\label{tab-Dawson-Kalannie-results}
+\begin{tabular}{ccccccc}
+\hline
+Long. ($^o$) & Lat. ($^o$) & Depth (km) & Mag. ($M_w$) & Strike ($^o$) & Dip ($^o$) & Rake ($^o$) \\
+\hline
+117.1700 & -30.1484 & 1.15 & 4.39 & 231.1 & 51.9 & 132.6 \\
+$\pm$0.12\,km &  $\pm$0.10\,km & $\pm$0.08 & $\pm$0.06 & $\pm$12.1 & $\pm$6.2 & $\pm$11.1 \\
+\hline
+\end{tabular}
+\end{table*}
+
 \begin{table}
-\caption{Stations considered when exploring the effect of reduced station coverage.}
-\label{tab:Calaveras-stationremoval}
-\begin{tabular}{|r|l|}
+\caption[Kalannie earthquake magnitudes, seismic moments and dimensions]
+{Estimated seismic moment $M_o$, moment magnitude $M_w$ and rupture diameter $2a$ for the
+four Kalannie events using the local magnitude $M_L$ of the Geoscience Australia catalogue and conversion
+formula discussed in text. In the case of the composite event (comp) we use the $M_w$ of \citet{dr_Dawson08a} and reverse
+the calculations.}
+\label{tab:Kalannie-eventsizes}
+\begin{tabular}{c|ccccc}
 \hline
-Number of & Station Names\\
-Stations  & \\
+Event & Date     & $M_L$ & $M_o$           & $M_w$   &  $2a$\\
+      & (2005)   &       & ($10^{14}$\,Nm) &         &  (m)\\
 \hline
-10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
-9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
-8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
-7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
-6  & CCO, JCB, JST, CMH, HSP, JAL \\
-5  & CCO, JCB, JST, CMH, HSP \\
-4  & CCO, JCB, JST, CMH \\
-3  & CCO, JCB, JST \\
-2  & CCO, JCB \\
-1  & CCO \\
+1     &  21-Sept & 4     & $9.55$          & 3.9     & 694\\
+2     &  21-Sept & 3.7   & $4.29$          & 3.7     & 531\\
+3     &  22-Sept  & 4.1  & $12.47$         & 4       & 759\\
+4     &  22-Sept  & 3.9  & $7.31$          & 3.8     & 635\\
+comp  &  NA       & 4.6  & $48.4$          & 4.39    & 1192\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Inversion results for the Kalannie earthquake coordinates. The expected value $E[\bar{X}_i]$
+and $var(\bar{X}_i)$ (the standard error of $E[\bar{X}_i]$) come from the Markov-chain Monte-Carlo approach, whereas
+$\hat{x}_i^*$ result from the optimiser. The
+outputs of both inversion procedures are consistent within the bounds of the standard error.
+In the final column we show the probability of each event coordinate being within 500\,m of the origin $P_{500}$ (see grey
+shaded regions of figure \ref{fig:Kalannie-CWI-NAB-1Dmarginals})}
+\label{tab:Kalannie-InversionRes}
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|cc|c|c}
+\hline
+parameter & $E[\bar{X}_i]$ &  $var(\bar{X}_i)$  & $\hat{x}_i^*$ & $P_{500}$\\
+\hline
+$\hat{x}_2$ & 348 & 220 & 329 & 0.76 \\
+\hline
+$\hat{x}_3$ & 156 & 433 & 307 & 0.68\\
+$\hat{y}_3$ & 369 & 223 & 377 & 0.73\\
+\hline
+$\hat{x}_4$ & 102 & 402 & -124 & 0.76\\
+$\hat{y}_4$ & 58 & 390 & 235 & 0.79\\
+$\hat{z}_4$ & 315 & 224 & 201 & 0.81\\
+\hline
+\end{tabular}
+\renewcommand{\arraystretch}{1}
+\end{table}
+
+\begin{table}
+\caption{Separation estimates between Kalannie event pairs using
+the optimisation and Markov-chain Monte-Carlo (MCMC) inversion
+results. The separations are generally smaller
+than the anticipated rupture size of each event (see table \ref{tab:Kalannie-eventsizes}) suggesting that
+the events could rupture overlapping sections of the same fault. We have
+more confidence in these separations than the pairwise CWI estimates because they
+simultaneously incorporate all coda wave data.}
+\label{tab:-KalannieRes-separations}
+\begin{tabular}{c|cc}
+\hline
+Pair & Optimiser & MCMC \\
+\hline
+$\delta_{12}$ & 329 & 348 \\
+$\delta_{13}$ & 486 & 401 \\
+$\delta_{14}$ & 333 & 336 \\
+$\delta_{23}$ & 378 & 416 \\
+$\delta_{24}$ & 548 & 404 \\
+$\delta_{34}$ & 496 & 446 \\
 \hline

### 2012-07-24 paper3/diags/create_wave_and_cwifig.m

@@ -1,0 +1,419 @@
+%% IMPORTANT SWITCHES ================================
+clear all
+
+waveform_figmode = 0;   % 0=> waveform figures designed for portrait half page
+% 1=> waveform figures designed for landscape full page
+waveform_cliptime = 1;  % 0=> show entire waveforms in plots
+% 1=> clip waveforms to tp-tstart<=t<=tp-tstart+twidth
+waveform_rotate = 0;    % 0=> Use original waveforms N,E,Z
+% 1=> Use rotated waveforms T,R,Z
+
+tstart.MORW = 5;
+twidth.MORW = 75;
+tstart.BLDU = 5;
+twidth.BLDU = 40;
+tstart.KLBR = 5;
+twidth.KLBR = 75;
+
+tsurface.MORW = 27;
+tsurface.BLDU = 11;
+tsurface.KLBR = 30;
+
+tshear.MORW = 19;
+tshear.BLDU = 8;
+tshear.KLBR = 20;
+
+if waveform_rotate ==0
+    channel_list = {'N','E','Z'}
+elseif waveform_rotate ==1
+    channel_list = {'R','T','Z'}
+end
+
+
+%% MORW ==============================================
+Kal_CWI.Event1.MORW.(channel_list{1}).fname = '2005264224434.00.MORW.SHN';
+Kal_CWI.Event1.MORW.(channel_list{2}).fname = '2005264224442.85.MORW.SHE';
+Kal_CWI.Event1.MORW.(channel_list{3}).fname = '2005264224443.41.MORW.SHZ';
+
+
+Kal_CWI.Event2.MORW.(channel_list{2}).fname = '2005264225837.21.MORW.SHE';
+Kal_CWI.Event2.MORW.(channel_list{1}).fname = '2005264225846.30.MORW.SHN';
+Kal_CWI.Event2.MORW.Z.fname = '2005264225847.10.MORW.SHZ';
+
+Kal_CWI.Event3.MORW.(channel_list{1}).fname = '2005265035136.96.MORW.SHN';
+Kal_CWI.Event3.MORW.(channel_list{2}).fname = '2005265035147.80.MORW.SHE';
+Kal_CWI.Event3.MORW.Z.fname = '2005265035149.30.MORW.SHZ';
+
+Kal_CWI.Event4.MORW.(channel_list{1}).fname = '2005265183329.96.MORW.SHN';
[…]

### 2012-07-28 paper2/paper2.tex
the latest version of edits. Note this is just before giving it to Trevor and Clive for review. It represents minor changes to the review sent to MS from whom I have not yet received comments

@@
 %\documentclass[extra,mreferee]{gji}
-%\documentclass[extra, onecolumn, doublespacing]{gji}
-\documentclass[extra]{gji}
+\documentclass[extra, onecolumn, doublespacing]{gji}
+%\documentclass[extra]{gji}
 
@@
 \begin{summary}
- Coda wave interferometry (CWI) is an emerging tool for constraining
-earthquake source properties from the intereference pattern of coda
-waves between nearby events. A new earthquake location algorithm is
-derived which relies on CWI based probabilistic estimates of
-earthquake separation. The algorithm can be used with CWI estimates
-alone or in tandem with travel time data. Synthetic examples in 2D
-and 3D and real earthquakes on the Calaveras Fault, California are
-used to demonstrate the potential of CWI for locating poorly
-recorded earthquakes. It is demonstrated that CWI: (a) outperforms
+Coda waves arise from scattering to form the later arriving
+components of a seismogram. Coda wave interferometry is an emerging
+tool for constraining earthquake source properties from the
+intereference pattern of coda waves between nearby events. A new
+earthquake location algorithm is derived which relies on coda wave
+based probabilistic estimates of earthquake separation. The
+algorithm can be used with coda waves alone or in tandem with travel
+time data. Synthetic examples in 2D and 3D and real earthquakes on
+the Calaveras Fault, California are used to demonstrate the
+potential of coda waves for locating poorly recorded earthquakes. It
+is demonstrated that coda wave interferometry: (a) outperforms
 traditional earthquake location techniques when the number of
@@
 the velocity model used in computing travel times. Uncertainties in
-absolute location are typically of the order of several km because
-they are susceptible to uncertainty in the velocity structure along
-the entire path between the source and receiver. For example,
-\citet{dr_Shearer99a} states that location uncertainty in the ISC
-and PDE catalogues are generally around 25\,km horizontally and at
-least 25\,km in depth.\footnote{Here the depth uncertainties of
-25\,km assume the use of depth dependent phases such as $pP$.
-Without such phases the uncertainty is higher.}
-\citet{dr_Bondar04a} demonstrate that at the local scale, absolute
-locations are accurate to within 5\,km with a 95\% confidence level
-when local networks meet a number of station related criteria. Such
-errors are too large for many applications, particularly those
-focussed on imaging rupture surfaces from aftershock sequences.
+absolute location are typically of the order of several kilometers
+because they are susceptible to uncertainty in the velocity
+structure along the entire path between the source and receiver. For
+example, \citet{dr_Shearer99a} states that location uncertainty in
+the ISC and PDE catalogues are generally around 25\,km horizontally
+and at least 25\,km in depth.\footnote{Here the depth uncertainties
+of 25\,km assume the use of depth dependent phases such as $pP$.
+Without such phases the uncertainty is higher.} \citet{dr_Bondar04a}
+demonstrate that at the local scale, absolute locations are accurate
+to within 5\,km with a 95\% confidence level when local networks
+meet a number of station related criteria. Such errors are too large
+for many applications, particularly those focussed on imaging
+rupture surfaces from aftershock sequences.
 
@@
 15 to 75\,m in local settings with good station coverage
-\citep{dr_Ito85a, dr_Got94a,
-dr_Waldhauser99a,dr_Waldhauser08a}. Here, `good coverage' implies
-multiple stations distributed across a broad range of azimuthal
-directions. Relative location techniques have been applied to a
-diverse range of problems including: location of active fault planes
-\citep{dr_Deichmann92a, dr_Got94a, dr_Waldhauser99a,
-dr_Waldhauser02a, dr_Shearer05a}; studying rupture mechanics
-\citep{dr_Rubin99a, dr_Rubin02a}; interpreting magma
-movement in volcanoes \citep{dr_Fremont87a}; and
-monitoring pumping induced seismicity \citep{dr_Lees98a,
-dr_Ake05a}.
-
-In traditional approaches to absolute and relative location
-only early onset body waves, typically $P$ and/or $S$ waves, are used.
-The data utilised may be the direct arrival times; the travel time difference computed
-between direct arrivals of two waveforms; or the time differences
-inferred from time-lagged cross correlation of relatively small windows
-around the body wave arrivals.
+\citep{dr_Ito85a, dr_Got94a, dr_Waldhauser99a,dr_Waldhauser08a}.
+Here, `good coverage' implies multiple stations distributed across a
+broad range of azimuthal directions. Relative location techniques
+have been used to image active fault planes \citep{dr_Deichmann92a,
+dr_Got94a, dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a};
+studying rupture mechanics \citep{dr_Rubin99a, dr_Rubin02a};
+interpreting magma movement in volcanoes \citep{dr_Fremont87a}; and
+monitoring pumping induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
+
+In traditional approaches to absolute and relative location only
+early onset body waves, typically $P$ and/or $S$ waves, are used.
+The data utilised may be the direct arrival times; travel time
+difference computed between direct arrivals of two waveforms; or
+time differences inferred from time-lagged cross correlation of
+relatively small windows around the body wave arrivals.
  In all three cases, the majority of the
@@
 
-Coda refers to  later arriving waves in the seismogram that arise from
-scattering  \citep{dr_Aki69a,dr_Snieder99a,dr_Snieder06a}.
-Typically, the coda waves are ignored in most seismological
-applications due to the complexity involved in modeling their
-generation. In this
-paper we develop an approach for locating earthquakes using coda waves.
+Coda refers to  later arriving waves in the seismogram that arise
+from scattering  \citep{dr_Aki69a,dr_Snieder99a,dr_Snieder06a}. Coda
+waves are ignored in most seismological applications due to the
+complexity involved in modeling their generation. In this paper we
+develop an approach for locating earthquakes using coda waves.
 
@@
 \end{equation}
-where $\sigma_\tau$ is the standard deviation of the travel time perturbation
-between the coda waves of two earthquakes,
-and $\alpha$ and $\beta$ are the near source $P$ and $S$ wave velocities,
+where $\sigma_\tau$ is the standard deviation of the travel time
+perturbation between the coda waves of two earthquakes, and $\alpha$
+and $\beta$ are the near source $P$ and $S$ wave velocities,
 respectively. The function $g$ depends on the type of excitation
 (explosion, point force, double couple) and on the direction of
-source displacement relative to the point force or double
-couple. For example, for two double couple sources displaced in the
-fault plane,
+source displacement relative to the point force or double couple.
+For example, for two double couple sources displaced in the fault
+plane,
 \begin{equation}
@@
 \end{equation}
-\citep{dr_Snieder05a}.
-
-The $\sigma_\tau$ in eq. (\ref{eq:Theory-dcwi_g_sigmat}) is related
-to $R_{max}$, the maximum of the cross correlation between the coda
-of the two waveforms and hence can be computed directly from the
-recorded data. In this paper we use the autocorrelation approach of
-\citet{dr_Robinson11a} when relating these parameters and we apply a
-restricted time lag search when evaluating $R_{max}$. These
-extensions to the original technique of \citet{dr_Snieder05a}
+\citep{dr_Snieder05a}. In this paper we use equation
+\ref{eq:LitReview-g-3d-dc} which assumes that the source mechanism
+of both events are identical, an assumption likely to be true for
+events in the same fault plane. \cite{dr_Robinson07c} explore the
+impact of a change in mechanism.
+
+The $\sigma_\tau$ in equation (\ref{eq:Theory-dcwi_g_sigmat}) is
+related to $R_{max}$, the maximum of the cross correlation between
+the coda of the two waveforms and hence can be computed directly
+from the recorded data. In this paper we use the autocorrelation
+approach of \citet{dr_Robinson11a} when relating these parameters
+and we apply a restricted time lag search when evaluating $R_{max}$.
+These extensions to the original technique of \citet{dr_Snieder05a}
 increase the range of applicability of CWI by 50\%.
@@
 $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
-likelihood and prior functions, respectively. In eq.
+likelihood and prior functions, respectively. In equation
 (\ref{eq-Bayes-three-locations}) $\mathbf{d}$ represents
@@
 \mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-travel time differences. In this derivation and in Sec.
+travel time differences. In this derivation and in Section
 \ref{sec:benchmarking} we focus on the constraints imposed by coda
-waves, whereas in Sec. \ref{sec:CalaverasLoc-CWIandTT} we
+waves, whereas in Section \ref{sec:CalaverasLoc-CWIandTT} we
 demonstrate how CWI and travel time data can be combined.
@@
 \end{equation}
-Combining eqs. (\ref{eq:-joint-likelihood4three}) and (\ref{eq:-joint-prior4three})
-gives the joint posterior function
+Combining equations (\ref{eq:-joint-likelihood4three}) and
+(\ref{eq:-joint-prior4three}) gives the joint posterior function
 \begin{equation}
@@
 \end{equation}
-where the intergral is taken over all plausible locations for $\mathbf{e}_1$ and $\mathbf{e}_3$.
-Alternatively, we can compute the marginal for a single event coordinate
-by integrating the posterior over all events and remaining coordinates
-for the chosen earthquake. Evaluation of $c$ in eq. (\ref{eq-3eqposterior}) involves finding the value which
-normalises the posterior function to unit area over all plausible locations.
-In many applications the constant of
-proportionality $c$ is not important. For example, it is not required
-when seeking the combination of locations which maximise
+where the intergral is taken over all plausible locations for
+$\mathbf{e}_1$ and $\mathbf{e}_3$. Alternatively, we can compute the
+marginal for a single event coordinate by integrating the posterior
+over all events and remaining coordinates for the chosen earthquake.
+Evaluation of $c$ in equation (\ref{eq-3eqposterior}) involves
+finding the value which normalises the posterior function to unit
+area over all plausible locations. In many applications the constant
+of proportionality $c$ is not important. For example, it is not
+required when seeking the combination of locations which maximise
  the posterior function, nor in Bayesian sampling algorithms such as Markov-chain Monte-Carlo
@@
 \end{equation}
-for $n$ events. When evaluating eq. (\ref{posterior-n-events}) over a range of locations
-it is necessary to compute and multiply many numbers close to zero.
-This is because the PDFs tend to zero as
-the locations get less likely (i.e. near the boundaries of the plausible region).
-Such calculations are prone to truncation errors so we
-work with the negative logarithm
+for $n$ events. When evaluating equation (\ref{posterior-n-events})
+over a range of locations it is necessary to compute and multiply
+many numbers close to zero. This is because the PDFs tend to zero as
+the locations get less likely (i.e. near the boundaries of the
+plausible region). Such calculations are prone to truncation errors
+so we work with the negative logarithm
 \begin{equation}
@@
 
-In summary, the posterior $P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN})$ and its negative
-logarithm $L$ describe the joint probability of multiple event locations given the observed coda waves.
-The most likely set of locations is given by the minimum of $L$.   In this paper we use the Polak-Ribiere
-technique \citep{dr_Press87a} to optimise $L$. The Polak-Ribiere
-technique is a particular choice of conjugate gradient method. It uses the
-derivatives of $L$ to guide the optimisation procedure. We derive the derivatives in Appendix \ref{sec-Appendix-derivatives_ofL}.
+In summary, the posterior $P(\mathbf{e}_1,...,\mathbf{e}_n |
+\widetilde{\mathbf{\delta}}_{CWIN})$ and its negative logarithm $L$
+describe the joint probability of multiple event locations given the
+observed coda waves. The most likely set of locations is given by
+the minimum of $L$.   In this paper we use the Polak-Ribiere
+technique \citep{dr_Press87a}, a conjugate gradient method, to
+optimise $L$. It uses the derivatives of $L$ to guide the
+optimisation procedure. We derive the derivatives in Appendix
+\ref{sec-Appendix-derivatives_ofL}. Note that when optimizing
+equation \ref{eq:-negative-log} the values of $ln \left[ c \right]$
+and $ln \left[ P(e_i) \right]$ can be ignored because they are
+constant\footnote{$ln \left[ P(e_i) \right]$ is constant because we
+consider a uniform prior.}
 
@@
 We use synthetic examples in 2D and 3D with 50 earthquakes to test
-the performance of the optimisation routine.
+the performance of the optimisation routine. In these examples the
+synthetic earthquakes are located randomly and CWI data generated
+according to the event separation. It is not necessary to generate
+synthetic waveforms and compute CWI estimates directly because we
+are testing the performance of the optimisation routine only. The
+ability of CWI to estimate event sepration has been demonstrated
+already \citep{dr_Snieder05a, dr_Robinson11a, dr_Robinson07b}. We
+undertake a complete coda wave location experiment, including the
+calculation of CWI separation estimates, for recorded earthquakes on
+the Calaveras Fault, California, in Section
+\ref{sec:CalaverasLoc-CWIonly}.
 
@@
 
-We design a 2D synthetic experiment (Example 1) by randomly
+We design a 2D synthetic experiment (example 1) by randomly
 selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
-\hat{x} \leq 50$ and $-50 \leq \hat{y} \leq 50$. These are indicated
-with triangles in Figure \ref{fig-2D50eq-relocation_eg1}.
+\hat{x}, \hat{y} \leq 50$. These are indicated with triangles in
+Figure \ref{fig-2D50eq-relocation_eg1}.
  We assume a local velocity of $v=3300\,$ms$^{-1}$ between all
@@
 \end{equation}
-using eq. (\ref{eq:mu1}). This assumption ensures that the sample
-mean of hypothetical separation estimates is consistent with known
-CWI biases \citep{dr_Robinson11a}. In example 1 we use
+using equation (\ref{eq:mu1}). This assumption ensures that the
+sample mean of hypothetical separation estimates is consistent with
+known CWI biases \citep{dr_Robinson11a}. In example 1 we use
 $\bar{\sigma}_N=0.02$ between all event pairs. Application of our
@@
 is often larger than 0.02 and that it increases with event
-separation. Consequently, example 1 is overly simplistic because we
-fix $\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase
-the uncertainty and introduce a distance dependance into the
+separation. Consequently, example 1 is simplistic because we fix
+$\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase the
+uncertainty and introduce a distance dependance into the
 hypothetical $\bar{\sigma}_N$ by defining
@@
 
-We can draw three observations from the error structure in Figures
+Three observations can be drawn from the error structure in Figures
 \ref{fig-2D50eq-relocation_eg1} and \ref{fig-2D50eq-relocation_eg3}.
@@
 positioning with few satellites. Our third observation is that the
-location errors appear to be circular, despite our attempt to
-correct for rotational non-uniqueness with the local coordinate
-system.
+location errors aare circular, despite our attempt to correct for
+rotational non-uniqueness with the local coordinate system.
 
@@
 $\hat{y}>0$. As the number of events increase the strength of these
-constraints on later events weakens allowing small rotations
-of events with respect to each other. That is, even though the
+constraints on later events weakens allowing small rotations of
+events with respect to each other. That is, even though the
 rotational freedom of the cluster is in principal removed by the
-constraints imposed on the events (see equations (\ref{eq:coord-const1}) to
-(\ref{eq:coord-const4})) we observe that in practice the presence of
-noise allows the rotational non-uniqueness to reappear. This is
-because the `easiest' way data noise can propagate is into the
-direction which is least constrained by the data. The same phenomena
-is observed in linear inversion where noise creates large spurious
-model changes in directions of the eigenvectors with the smallest
-singular values \citep{dr_Aster05a}. Unfortunately, there is
-no obvious way to overcome this issue when using coda waves alone
-since the constraints are based on separation. Fortunately however,
-combining coda waves with measurements of travel times alleviates
-this problem and facilitate the removal of a local coordinate system
-altogether.
+constraints imposed on the events (see equations
+(\ref{eq:coord-const1}) to (\ref{eq:coord-const3})\footnote{equation
+\ref{eq:coord-const4} is needed in 3D only}) we observe that in
+practice the presence of noise allows the rotational non-uniqueness
+to reappear. This is because the `easiest' way data noise can
+propagate is into the direction which is least constrained by the
+data. The same phenomena is observed in linear inversion where noise
+creates large spurious model changes in directions of the
+eigenvectors with the smallest singular values \citep{dr_Aster05a}.
+Unfortunately, there is no obvious way to overcome this issue when
+using coda waves alone since the constraints are based on
+separation. Fortunately however, combining coda waves with
+measurements of travel times alleviates this problem and facilitate
+the removal of a local coordinate system altogether (see Section
+\ref{sec:CalaverasLoc-CWIandTT}.
 
@@
 
-Figure \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrates
+Figures \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrates
 the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
-the coordinate difference as a function of increasing linkage. We
-show the statistics for the `best' optimisation solution (black) and
-for the solution space when all 25 optimisations are considered
-(gray). In this case the best solution is determined by the set of
+the coordinate error as a function of increasing linkage. We show
+the statistics for the `best' optimisation solution (black) and for
+the solution space when all 25 optimisations are considered (gray).
+In the later case the best solution is determined by the set of
 event locations which lead to the smallest value of $L$. The error
@@
 average number of branches can be computed in advance it can be used
-as an indication of the inversion stability prior to optimisation.
-An earlier breakdown is observed when all 25 solutions are
-considered collectively. For example, the maximum coordinate error
+as an indication of the inversion stability prior to optimisation. A
+higher breakdown is observed when all 25 solutions are considered
+collectively. For example, the maximum coordinate error
 $\Delta_{max}$ exceeds that for the best solution for linkage
@@
 
-Some optimisations
-fail to converge after 1200 iterations when the linkage is 60\% or lower. All optimisations
-fail when then linkage is 20\% or lower. Despite their failure to converge however, the locations
-at final iteration are close to the actual solution. The derivatives used in the conjugate gradient method
-depend on events connected by CWI measurements. Consequently,
-earthquakes that are only connected via other events do not `communicate' with each other
-directly. To some extent, this should be adressed during the iterative process where location information
-can spread to events which have no direct links. However, the
-lack of direct connection through the gradient could prevent convergence in extreme cases, or more likely
-slow the procedure down. This could explain why some
+Some optimisations fail to converge after 1200 iterations when the
+linkage is 60\% or lower. All optimisations fail when then linkage
+is 20\% or lower. Despite their failure to converge, the locations
+at final iteration are close to the actual solution.
+
+The derivatives used in the conjugate gradient method depend on
+events connected by CWI measurements. Consequently, earthquakes that
+are only connected via other events do not `communicate' with each
+other directly. To some extent, this should be adressed during the
+iterative process where location information can spread to events
+which have no direct links. However, the lack of direct connection
+through the gradient could prevent convergence in extreme cases, or
+more likely slow the procedure down. This could explain why some
 examples do not converge after 1200 iterations.
-\citet{dr_VanDecar94a} show that gradient damping acts
-slowly through iterative least-squares, because
+\citet{dr_VanDecar94a} show that gradient damping acts slowly
+through iterative least-squares, because
  every cell in one iteration communicates only with its neighbours, and they demonstrate that this can be
@@
 There is one notable difference between the 3D and 2D results. In 2D
-the final iteration was typically close to the actual solution when
-the optimisation failed to converge. Contrastingly, in 3D the
+the final iteration was close to the actual solution when the
+optimisation failed to converge. Contrastingly, in 3D the
 optimisation appears to converge to the correct solution or fail
-completely, leading to a set locations which in no way resemble the
-actual solution. This is depicted in Figure
+completely, leading to a set of locations at final iteration which
+do not resemble the actual solution. This is depicted in Figure
 \ref{fig:optimisationresults-3Dsynth} by the absence of the gray and
@@
 Calaveras example released with the open source Double Difference
-algorithm or hypoDD \citep{dr_Waldhauser00a,dr_Waldhauser01a}. These
-events are chosen for three reasons. Firstly, they are recorded by a
-large number of stations (Fig.
-\ref{fig:-eqopti-California-Calaveras}) and therefore lend
-themselves to accurate travel time location. Secondly, they are
-distributed over distances from near zero to hundreds
+algorithm or hypoDD \citep{dr_Waldhauser00a, dr_Waldhauser01a}[See
+also Data and Resources Section]. These events are chosen for three
+reasons. Firstly, they are recorded by a large number of stations
+(Fig. \ref{fig:-eqopti-California-Calaveras}) and therefore lend
+themselves to accurate travel time location. This makes them ideal
+for assessing the performance of a new location technique. Secondly,
+they are distributed over distances from near zero to hundreds
 meters making them ideal for application of CWI. Finally, Calaveras
@@
 dr_Schaff02a, dr_Waldhauser08a}. The relocations in this paper are
-sorted into four examples summarised in table \ref{tab:examples}.
+sorted into four examples summarised in Table \ref{tab:examples}.
 
@@
 \hline
-Example 5 & comparison of CWI, catalogue and hypoDD \\
- & locations. \\
-Example 6 & exploration of station dependance for CWI and \\
- & hypoDD. \\
-Example 7 & combined use of CWI and travel time data \\
+Example 5 & Comparison of CWI, catalogue and hypoDD \\
+ & locations (using all available data). \\
+Example 6 & Exploration of station dependance for CWI and \\
+ & hypoDD (using a subset of data). \\
+Example 7 & Combined use of CWI and travel time data \\
 & with all and a reduced number of stations. \\
-Example 8 & combined use of CWI and travel time data \\
+Example 8 & Combined use of CWI and travel time data \\
  & when travel times constrain only 50\% of the events. \\
@@
 
-To apply CWI we download available waveforms
-from the Northern California Earthquake Data Center
-(NCEDC). Unsuitable waveforms are removed
-using the conditions summarised in Table 5 of
-\citet{dr_Robinson11a}. Remaining waveforms are filtered between
-1 and 5\,Hz and aligned  to $P$ arrivals at 0\,s. CWI estimates are
-obtained from 5\,s wide non-overlapping time windows between $2.5
-\leq t \leq 20$\,s and used to create probabilistic constraints on
-event separation. We introduce the local coordinate system of
-Section \ref{sec:theory} and find the optimum relative locations using
-Polak-Ribiere optimisation.
+To apply CWI we download available waveforms from the Northern
+California Earthquake Data Center (See Data and Resources Section).
+Unsuitable waveforms are removed using the conditions summarised in
+Table 5 of \citet{dr_Robinson11a}. Remaining waveforms are filtered
+between 1 and 5\,Hz and aligned  to $P$ arrivals at 0\,s. CWI
+estimates are obtained from 5\,s wide non-overlapping time windows
+between $2.5 \leq t \leq 20$\,s and used to create probabilistic
+constraints on event separation. We introduce the local coordinate
+system of Section \ref{sec:theory} and find the optimum relative
+locations using Polak-Ribiere optimisation.
 
@@
 hypoDD with Singular Value Decomposition (SVD), absolute arrival
-times and cross correlation computed time differences.
+times and cross correlation computed travel time differences.
 
@@
 independent indication of clustering for the 68 events and to first
-order, similar locations to those from hypoDD (column 3). Figure
-\ref{fig-69Calaverasevents_eg1}
-illustrates a small second order difference between
-the CWI and hypoDD based locations. In particular, the lineation is
-less clear in the CWI locations (column 2) than that given by
-hypoDD (column 3). Our results suggest that the coda are less
-supportive of the presence of streaks although a complete
-understanding of these differences is left for future work. Our
-attention now is devoted towards understanding how both techniques
-perform with fewer stations (Example 6) and exploring how CWI and
-travel times can be combined (Examples 7 and 8).
+order, similar locations to those from hypoDD (column 3). There is a
+small second order difference between the CWI and hypoDD based
+locations. In particular, the lineation is less clear in the CWI
+locations (column 2) than the hypoDD locations (column 3). Our
+results suggest that the coda are less supportive of the presence of
+streaks although a complete understanding of these differences is
+left for future work. Our attention now is devoted towards
+understanding how both techniques perform with fewer stations
+(Example 6) and exploring how CWI and travel times can be combined
+(Examples 7 and 8).
 
@@
 
-We explore the impact of poorer recording situations in Example 6 by
+We explore the impact of poorer recording situations in example 6 by
 re-locating the 68 Calaveras events  using hypoDD and coda waves
@@
 waves constrain a decreasing number of events until at 1 station it
-is only possible to locate 55 events.
+is only possible to locate 55 of the 68 events.
 
@@
 must be used with SVD to obtain useful estimates of $\sigma_{x_p}$,
-$\sigma_{y_p}$ and $\sigma_{z_p}$ (\textbf{ADD REF}).
+$\sigma_{y_p}$ and $\sigma_{z_p}$ because the errors reported by
+conjugate gradient methods (LSQR) are grossly underestimated in
+hypoDD \citep{dr_Waldhauser01a}.
 
@@
 
-Aggregating the travel time and coda wave data offers two
-advantages. Firstly, it combines independent constraints on the
-event locations offering further confidence in the resulting
-solution. Secondly, the travel time constraints in the form of
-equation (\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
+Combining the travel time and coda wave data offers two advantages.
+Firstly, it combines independent constraints on the event locations
+offering further confidence in the resulting solution. Secondly, the
+travel time constraints in the form of equation
+(\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
 associated with translation, rotation and reflection around a global
@@
 temporary seismometers to monitor aftershocks for significant events
-\citep{dr_Bowman90a, dr_Leonard02a}). Traditionally, these
+\citep{dr_Bowman90a, dr_Leonard02a}. Traditionally, these
 deployments are used to locate aftershocks to an accuracy of the
@@
 Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-using equation \ref{eq:CumOmori}. The leftmost gray, middle black
+using equation (\ref{eq:CumOmori}). The leftmost gray, middle black
 and rightmost gray lines signify aftershocks occurring before,
@@
 With this idea of a temporary deployment in mind we have another
-attempt at relocating the Calaveras earthquakes. In Example 8
-we consider the travel time constraints on half (34) of the
-earthquakes and incorporate coda wave data from a single stations
-for all 68 earthquakes. The combined inversion is shown in column 1
-of Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1}. The
-inversion result is similar to the combined inversion when all
-travel time data is incorporated (see Fig.
-\ref{fig-68Calaverasevents_ttandcoda1}). The slight increase in
-scatter observed here can be explained by the events with no travel
-time constraints and the tendency of the coda to push events away
-from streaks.
+attempt at relocating the Calaveras earthquakes. In Example 8 we
+consider the travel time constraints on half (34) of the earthquakes
+and incorporate coda wave data from a single station for all 68
+earthquakes. The combined inversion is shown in column 1 of Figure
+\ref{fig-68Calaverasevents_ttsubsetandcoda1}. The inversion result
+is similar to the combined inversion when all travel time data is
+incorporated (see Fig. \ref{fig-68Calaverasevents_ttandcoda1}). The
+slight increase in scatter observed here can be explained by the
+events with no travel time constraints and the tendency of the coda
+to push events away from streaks.
 
@@
 a single station, an outcome demonstrated most clearly by Figures
-Figures \ref{fig-CWIreducesstats} and
+\ref{fig-CWIreducesstats} and
 \ref{fig-68Calaverasevents_ttsubsetandcoda1}
@@
 
+\section{Data and Resources}
+We thank the Northern California Earthquake Data Center (NCEDC) for
+providing the Calaveras data and the Northern California Seismic
+Network (NCSN), U.S. Geological Survey, Menlo Park and Berkeley
+Seismological Laboratory, University of California, Berkeley for
+contributing it to the NCEDC. The waveforms can be downloaded from
+http://www.ncedc.org/ncedc/access.html. We also acknowledge Felix
+Waldhauser and William Ellsworth, the authors of the openly
+available Double Difference location algorithm, hypoDD which can be
+downloaded from http://www.ldeo.columbia.edu/~felixw/hypoDD.html.
+
 \begin{acknowledgments}
@@
 Geoscience Australia. Work was conducted as part of an Australian
-Research Council Discovery Project (DP0665111). We thank the
-Northern California Earthquake Data Center (NCEDC) for providing the
-Calaveras data and the Northern California Seismic Network (NCSN),
-U.S. Geological Survey, Menlo Park and Berkeley Seismological
-Laboratory, University of California, Berkeley for contributing it
-to the NCEDC. We also acknowledge Felix Waldhauser and William
-Ellsworth, the authors of the openly available Double Difference
-location algorithm, hypoDD. This paper has benefited significantly
-from reviews by ......... at Geoscience Australia.
+Research Council Discovery Project (DP0665111).  This paper has
+benefited significantly from reviews by ......... at Geoscience
+Australia.
 \end{acknowledgments}
@@
 section appear complicated but are in practice trivial to compute
-numerically. Confidence in their accuracy is enhanced in the
-following sections by demonstrating that the optimization procedure
-converges to the correct solution for a number of synthetic problems
-in 2 and 3 dimensions.
+numerically. Confidence in their accuracy is enhanced by
+demonstrating that the optimization procedure converges to the
+correct solution for a number of synthetic problems in 2 and 3
+dimensions.
 

### 2012-07-31 paper3/paper3.tex
fiddling with the Kalannie Map
now have it working from local copies of figures.aux

@@
 (a) & (b) \\
-\multirow{15}{*}{\includegraphics[width = 16pc]{../../thesis_version2/diags/eq_location_simple/KalannieMap/KalannieMap1.eps}} &
+\multirow{15}{*}{\includegraphics[width =
+16pc]{./diags/KalannieMap/KalannieMap1.eps}} &
 \multirow{15}{*}{\includegraphics[width = 20pc]{diags/waves_and_CWIest.eps}} \\
@@
 \begin{figure}
-\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_simple/Kalannie_figs/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
-\caption{Posterior functions $P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the Kalannie
-event pairs $i$ and $j$. A
-second $x$-axis is shown in separation units of meters for convenience.}
+\noindent\includegraphics[width=20pc]{./diags/CopiedFromThesis/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
+\caption{Posterior functions
+$P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the
+Kalannie event pairs $i$ and $j$. A second $x$-axis is shown in
+separation units of meters for convenience.}
 \label{fig:Kalannie-CWI-Posteriors}
@@
 (a) & (b) \\
-\multirow{3}{*}{\noindent\includegraphics[width = 25pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}} & \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
+\multirow{3}{*}{\noindent\includegraphics[width=25pc]{./diags/CopiedFromThesis/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}}
+ %{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}}
+& \multirow{2}{*}{\includegraphics[width=10pc]{./diags/CopiedFromThesis/Kalannie_covariance.eps}}\\
+%{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
 &  \\
@@
 & (c) \\
-&  \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
+&
+\multirow{2}{*}{\includegraphics[width=10pc]{./diags/CopiedFromThesis/Kalannie_correlation.eps}}
+%{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
 \\
@@
 \begin{figure}
-\noindent\includegraphics[width=20pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
+\noindent\includegraphics[width=20pc]{./diags/CopiedFromThesis/Kalannie_marginals2Dcont_param2_3.eps}
+%{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
 \caption{Marginal $P(\mathbf{e}_3) = P(\hat{x}_3,\hat{y}_3)$  for the location of event 3 normalised to unit volume.

### 2012-12-12 paper2/paper2.tex
commited most of Clive's comments

@@
 related to $R_{max}$, the maximum of the cross correlation between
-the coda of the two waveforms and hence can be computed directly
+the coda of the two waveforms, and hence can be computed directly
 from the recorded data. In this paper we use the autocorrelation
@@
 These extensions to the original technique of \citet{dr_Snieder05a}
-increase the range of applicability of CWI by 50\%.
+increase the range of applicability of CWI by 50\% (i.e. from 300 to
+450\,m separation for 1–5\,Hz filtered coda waves).
 
@@
 \end{equation}
-The logarithm improves numerical stability by replacing products with summations. The negative assists with
-optimisation, many algorithms for which are designed to minimise an objective function.
+The logarithm improves numerical stability by replacing products
+with summations. The negative facilitates the use of optimisation
+algorithms that are designed to minimise an objective function.
 
@@
 optimise $L$. It uses the derivatives of $L$ to guide the
-optimisation procedure. We derive the derivatives in Appendix
+optimization procedure. We derive the derivatives in Appendix
 \ref{sec-Appendix-derivatives_ofL}. Note that when optimizing
@@
 We use synthetic examples in 2D and 3D with 50 earthquakes to test
-the performance of the optimisation routine. In these examples the
+the performance of the optimization routine. In these examples the
 synthetic earthquakes are located randomly and CWI data generated
@@
 synthetic waveforms and compute CWI estimates directly because we
-are testing the performance of the optimisation routine only. The
-ability of CWI to estimate event sepration has been demonstrated
-already \citep{dr_Snieder05a, dr_Robinson11a, dr_Robinson07b}. We
+are testing the performance of the optimization routine only. The
+ability of CWI to estimate event separation has been demonstrated
+already \citep{dr_Snieder05a, dr_Robinson07b, dr_Robinson11a}. We
 undertake a complete coda wave location experiment, including the
@@
 selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
-\hat{x}, \hat{y} \leq 50$. These are indicated with triangles in
+\hat{x}, \hat{y} \leq 50$\,m. These are indicated with triangles in
 Figure \ref{fig-2D50eq-relocation_eg1}.
- We assume a local velocity of $v=3300\,$ms$^{-1}$ between all
+ We assume a local velocity of $v=3,300\,$ms$^{-1}$ between all
 event pairs and a dominant frequency of 2.5$\,$Hz to represent waveform data filtered between 1 and 5$\,$Hz.
@@
 $\bar{\sigma}_N=0.02$ between all event pairs. Application of our
-optimisation procedure on the hypothetical CWI data yields the
-circles in Figure \ref{fig-2D50eq-relocation_eg1}. The optimisation
+optimization procedure on the hypothetical CWI data yields the
+circles in Figure \ref{fig-2D50eq-relocation_eg1}. The optimization
 does not lead to the correct solution due to the addition of noise
@@
 using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
-optimisation event locations are shown in triangles and circles,
+optimization event locations are shown in triangles and circles,
 respectively.} \label{fig-2D50eq-relocation_eg1}
@@
 \sigma_{1to5Hz}(\delta_t)$.
- Actual and optimisation event locations
+ Actual and optimization event locations
 are shown in triangles and circles, respectively.}
@@
 \citep[see Fig. 4(b) of ][]{dr_Robinson11a}. Repeating the
-optimisation leads to the circles in Figure
+optimization leads to the circles in Figure
 \ref{fig-2D50eq-relocation_eg3} which have an average coordinate
@@
 
-Conjugate gradient based optimisation techniques are susceptible to
+Conjugate gradient based optimization techniques are susceptible to
 the presence of local minima. This is because they use the slope of
@@
 impact of local minima for our CWI location problem by beginning the
-optimisation from 25 randomly chosen starting positions. We observe
+optimization from 25 randomly chosen starting positions. We observe
 no differences in the solution for either example.
@@
 positioning with few satellites. Our third observation is that the
-location errors aare circular, despite our attempt to correct for
+location errors are circular, despite our attempt to correct for
 rotational non-uniqueness with the local coordinate system.
@@
 the removal of a local coordinate system altogether (see Section
-\ref{sec:CalaverasLoc-CWIandTT}.
+\ref{sec:CalaverasLoc-CWIandTT}).
 
 Despite our observations about the error structure however, we gain
-confidence in the optimisation procedure due to its stability for
+confidence in the optimization procedure due to its stability for
 different starting locations and because of the small average
@@
 
-A set of earthquakes and their corresponding coda wave estimates of
-separation form a network. In this network the earthquakes are nodes
-and the constraints are branches or links which join the nodes
-together. Synthetic examples 1 and 2 use 100\% direct linkage
-between event pairs. That is, there is a constraint between each
-earthquake and all other events. In reality, we might expect that
-the separation between some pairs will not be constrained by CWI
-data due to poor signal to noise ratio in the coda for common
-stations. Obviously, the less stations that record an event the more
-likely it is that links between it and other events will be broken.
-In such cases the probabilistic distance constraint between a pair
-of events may only exist indirectly through multiple pairs. In this
-section we consider the impact of reduced linkage between event
-pairs. In example 3, we repeat example 2 using 90\%, 80\%, ..., 10\%
-of the links. As with the above examples, we undertake the
-optimisation with 25 randomly chosen starting locations.
+Synthetic examples 1 and 2 use 100\% direct linkage between event
+pairs. That is, there is a constraint between each earthquake and
+all other events. In reality, we might expect that the separation
+between some pairs will not be constrained by CWI data due to poor
+signal to noise ratio in the coda for common stations. Obviously,
+the fewer stations that record an event the more likely it is that
+links between it and other events will be broken. In such cases the
+probabilistic distance constraint between a pair of events may only
+exist indirectly through multiple pairs. In this section we consider
+the impact of reduced linkage between event pairs. In example 3, we
+repeat example 2 using 90\%, 80\%, ..., 10\% of the links. As with
+the above examples, we undertake the optimization with 25 randomly
+chosen starting locations.
 
@@
 \caption{Example 3 - Statistical measures of error in the
-optimisation solutions for the 2D synthetic cases when all (gray)
+optimization solutions for the 2D synthetic cases when all (gray)
 and best (black) results are considered. The statistics
@@
 the coordinate error as a function of increasing linkage. We show
-the statistics for the `best' optimisation solution (black) and for
-the solution space when all 25 optimisations are considered (gray).
-In the later case the best solution is determined by the set of
+the statistics for the `best' optimization solution (black) and for
+the solution space when all 25 optimizations are considered (gray).
+In the latter case the best solution is determined by the set of
 event locations which lead to the smallest value of $L$. The error
@@
 average number of branches can be computed in advance it can be used
-as an indication of the inversion stability prior to optimisation. A
+as an indication of the inversion stability prior to optimization. A
 higher breakdown is observed when all 25 solutions are considered
@@
 $\Delta_{max}$ exceeds that for the best solution for linkage
-$\leq$60\% confirming that the optimisation is susceptible to local
+$\leq$60\% confirming that the optimization is susceptible to local
 minima and that a range of starting points should be considered.
 
-Some optimisations fail to converge after 1200 iterations when the
-linkage is 60\% or lower. All optimisations fail when then linkage
+Some optimizations fail to converge after 1200 iterations when the
+linkage is 60\% or lower. All optimizations fail when then linkage
 is 20\% or lower. Despite their failure to converge, the locations
@@
  every cell in one iteration communicates only with its neighbours, and they demonstrate that this can be
-fixed with preconditioning in some cases. Their findings suggest that it may be possible to improve
-the convergence (stability and/or speed) of the CWI optimisation by preconditioning.
+fixed with preconditioning in some cases. Their findings suggest
+that it may be possible to improve the convergence (stability and/or
+speed) of the CWI optimization by preconditioning.
 
@@
 
-In Example 4 we expand the optimisation routine to 3D by randomly picking
+In Example 4 we expand the optimization routine to 3D by randomly
+picking
  a set of actual event locations for 50 earthquakes with
@@
  waveform data filtered between 1 and 5$\,$Hz.
-The hypothetical CWI mean is created using equation (\ref{eq:hypothetical-CWI-mean-optichapt})
-which ensures consistency between the sample mean of hypothetical separation estimates and CWI
-biases. We use a standard deviation for the noisy CWI estimates
-of $\bar{\sigma}_N = \sigma_{1to5Hz}$ and perform the optimisation using 10\%,
-20\%, ..., 100\% of the direct links.
-In each case we repeat the
-optimisation 25 times using randomly chosen starting locations. The results are
-summarised in Figure \ref{fig:optimisationresults-3Dsynth}.
+The hypothetical CWI mean is created using equation
+(\ref{eq:hypothetical-CWI-mean-optichapt}) which ensures consistency
+between the sample mean of hypothetical separation estimates and CWI
+biases. We use a standard deviation for the noisy CWI estimates of
+$\bar{\sigma}_N = \sigma_{1to5Hz}$ and perform the optimization
+using 10\%, 20\%, ..., 100\% of the direct links. In each case we
+repeat the optimization 25 times using randomly chosen starting
+locations. The results are summarised in Figure
+\ref{fig:optimisationresults-3Dsynth}.
 
@@
 \caption{Example 4 - Statistical measures of error in the
-optimisation solutions for the 3D synthetic cases when all (gray)
+optimization solutions for the 3D synthetic cases when all (gray)
 and best (black) results are considered. The statistics
@@
 60\% and 30\% indicates a breakdown in the solutions when all or
-best optimisation result(s) are considered, respectively.}
+best optimization result(s) are considered, respectively.}
 \label{fig:optimisationresults-3Dsynth}
@@
 
-When 70\% of the direct constraints are considered all optimisation
+When 70\% of the direct constraints are considered all optimization
 results (gray) are consistent with the best solution (black). The
@@
 the final iteration was close to the actual solution when the
-optimisation failed to converge. Contrastingly, in 3D the
-optimisation appears to converge to the correct solution or fail
-completely, leading to a set of locations at final iteration which
-do not resemble the actual solution. This is depicted in Figure
+optimization failed to converge. Conversely, in 3D the optimization
+appears to converge to the correct solution or fail completely,
+leading to a set of locations at final iteration which do not
+resemble the actual solution. This is depicted in Figure
 \ref{fig:optimisationresults-3Dsynth} by the absence of the gray and
@@
 solution for cases with 30\% linkage or higher is encouraging for
-the potential of coda wave optimisation to constrain earthquake
+the potential of coda wave optimization to constrain earthquake
 location.
@@
 In summary, the synthetic examples demonstrate the ability of coda
-wave data to constrain relative event location using optimisation.
-The optimisation error is influenced by the noise on CWI estimates
+wave data to constrain relative event location using optimization.
+The optimization error is influenced by the noise on CWI estimates
 with greater $\bar{\sigma}_N$ leading to larger errors in the
@@
 for 25 randomly chosen starting locations. As the direct linkage
-reduces to 50\% the optimisation becomes less stable and the best
+reduces to 50\% the optimization becomes less stable and the best
 solution from 25 random starting locations is required to find the
-optimal solution. As the number of links decrease below
-30\% the best solution fails to converge.
+optimal solution. As the number of links decrease below 30\% the
+best solution fails to converge.
 
@@
 for assessing the performance of a new location technique. Secondly,
-they are distributed over distances from near zero to hundreds
+they are distributed with separations from near zero to hundreds
 meters making them ideal for application of CWI. Finally, Calaveras
@@
 \includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\caption{Example 5 - Comparison of earthquake locations using three
-different methods: catalogue location (column 1), CWI (column 2) and
-hypoDD (column 3). Note that in the case of the hypoDD and CWI
-inversions we consider only the 68 earthquakes in black, the gray
-events are shown for the purpose of orientation only.}
+\caption{Example 5 - Comparison of relative earthquake locations
+using three different methods: catalogue location (column 1), CWI
+(column 2) and hypoDD (column 3). Note that in the case of the
+hypoDD and CWI inversions we consider only the 68 earthquakes in
+black, the gray catalogue locations for the remaining 240 (308-68)
+earthquakes are shown for the purpose of orientation only.}
 \label{fig-69Calaverasevents_eg1}
@@
 system of Section \ref{sec:theory} and find the optimum relative
-locations using Polak-Ribiere optimisation.
+locations using Polak-Ribiere optimization.
 
@@
 
-Global locations can not be found by CWI alone.
-For the sake of comparison, we arbitrary choose a
-`master' event and translate our relative locations to align with the hypoDD
-location for the same event. We return to this issue of relative
-versus actual location in Example 7 by introducing a combined travel
-time and coda wave inversion.
+Global locations cannot be found by CWI alone. For the sake of
+comparison, we arbitrarily choose a `master' event and translate our
+relative locations to align with the hypoDD location for the same
+event. This arbitrary translation does not change the relative
+locations. We return to this issue of relative versus actual
+location in Example 7 by introducing a combined travel time and coda
+wave inversion.
 
@@
 of stations and poor azimuthal coverage are common limitations when
-trying to locate intraplate clusters. For example, there are only 3
-network seismic stations in the South West Seismic Zone of Western
-Australia, a region similar in size to that hosting 805 stations in
-Figure \ref{fig:-eqopti-California-Calaveras}.
+trying to locate intraplate clusters. For example, there are only
+four network seismic stations in the South West Seismic Zone of
+Western Australia, a region similar in size to that hosting 805
+stations in Figure \ref{fig:-eqopti-California-Calaveras}.
 
@@
 \begin{table}
-\caption{Stations considered when exploring the imnpact of reduced
+\caption{Stations considered when exploring the impact of reduced
 station coverage.} \label{tab:Calaveras-stationremoval}
@@
 \includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{Example 6 - CWI locations with reduced stations.}
+\caption{Example 6 - CWI relative locations with reduced stations.}
 \label{fig-CWIreducesstats}
@@
 Figure \ref{fig-HYPODDreducesstats} illustrates the hypoDD inversion
-results for 7, 5 and 4 stations. The travel time problem is
-ill-posed for fewer than 4 stations so it is not possible to apply
-hypoDD with SVD for 3 or fewer stations.  The hypoDD locations are
-not self-consistent as the number of stations is reduced. We observe
-a general increase in scatter and a higher number of stray events
-outside the cluster when less stations are used with hypoDD. Even
-with 7 stations the linear streak of Figure
-\ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
+results for seven, five and four stations. The travel time problem
+is ill-posed for fewer than four stations so it is not possible to
+apply hypoDD with SVD for three or fewer stations.  The hypoDD
+locations are not self-consistent as the number of stations is
+reduced. We observe a general increase in scatter and a higher
+number of stray events outside the cluster when less stations are
+used with hypoDD. Even with seven stations the linear geometry of
+Figure \ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
 
@@
 \includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\caption{Example 6 - HypoDD (SVD) locations with reduced stations.}
-\label{fig-HYPODDreducesstats}
+\caption{Example 6 - HypoDD (SVD) relative locations with reduced
+stations.} \label{fig-HYPODDreducesstats}
 \end{figure*}
@@
 row of Figure \ref{fig-statremoval_summarystats} demonstrates that
-when 5 or more stations are used CWI can constrain the location of
-all 68 earthquakes. When less than 5 stations are used the coda
-waves constrain a decreasing number of events until at 1 station it
-is only possible to locate 55 of the 68 events.
+when five or more stations are used, CWI can constrain the location
+of all 68 earthquakes. When less than five stations are used the
+coda waves constrain a decreasing number of events until at one
+station it is only possible to locate 55 of the 68 events.
 
@@
 hypoDD) and the complete hypoDD locations for all 308 events. The
-top subplot illustrates the number of constrainable events in the
-CWI and hypoDD inversions as a function of the stations considered.}
-\label{fig-statremoval_summarystats}
+top subplot illustrates the number of constrainable events,$nE$ in
+the CWI and hypoDD inversions as a function of the stations
+considered.} \label{fig-statremoval_summarystats}
 \end{figure}
@@
 with respect to a global reference. Collectively, these advantages
-improve the behavior of the Polak-Ribiere optimisation leading to
+improve the behavior of the Polak-Ribiere optimization leading to
 faster and more stable convergence. Consequently, we no longer have
@@
 locations obtained when we combine the travel time and coda wave
-data using all data (left) and 5 stations (right). The linear
+data using all data (left) and five stations (right). The linear
 features observed in the original hypoDD inversions (see Fig.
-\ref{fig-69Calaverasevents_eg1}) is evident in both cases. However,
+\ref{fig-69Calaverasevents_eg1}) are evident in both cases. However,
 the coda waves introduce a scatter around these streaks. That is,
@@
 strong and little off-streak scatter is introduced. As we reduce
-hypoDD's leverage by decreasing the number of stations to 5, we
+hypoDD's leverage by decreasing the number of stations to five, we
 observe an increase in off-streak scatter resulting from the
@@
 \includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Example 7 - Combined HypoDD (SVD) and CWI locations using
-data form all stations (left) and 5 stations (right).}
-\label{fig-68Calaverasevents_ttandcoda1}
+\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
+locations using data form all stations (left) and 5 stations
+(right).} \label{fig-68Calaverasevents_ttandcoda1}
 \end{figure}
@@
 
-\subsection{Example 4 - Combining CWI and travel times when the travel times constrain a limited number of events}
+\subsection{Example 8 - Combining CWI and travel times when the travel times constrain a limited number of events}
 
@@
 \citep{dr_Bowman90a, dr_Leonard02a}. Traditionally, these
-deployments are used to locate aftershocks to an accuracy of the
-temporary array, whereas events occurring outside the deployment
-period can only be located to the accuracy of the network. Using our
-combined inversion it is possible to re-locate all events by
-employing the detailed travel time data when the temporary network
-is in-situ and using coda waves from network stations when the
-deployment is absent.
+deployments facilitate a higher accuracy of location for events
+occuring during the deployment period. Using our combined inversion
+it is possible to re-locate all events by employing the detailed
+travel time data when the temporary network is in-situ and using
+coda waves from network stations when the deployment is absent. The
+hypothesis, to be tested in this section, is that conducting such a
+combined inversion will improve the location accuracy of events
+outside the deployment period.
 
@@
 by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Locations are shown for the combined CWI and travel time
-inversion (left) and the inversion with travel times only (right)
-Only by combining the data is it possible to locate all 68 events.
-Furthermore, combining the data leads to a solution more consistent
-with Figure \ref{fig-69Calaverasevents_eg1}. }
+events. Relative locations are shown for the combined CWI and travel
+time inversion (left) and the inversion with travel times only
+(right) Only by combining the data is it possible to locate all 68
+events. Furthermore, combining the data leads to a solution more
+consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
 \label{fig-68Calaverasevents_ttsubsetandcoda1}
@@
 \ref{fig-CWIreducesstats} and
-\ref{fig-68Calaverasevents_ttsubsetandcoda1}
+\ref{fig-68Calaverasevents_ttsubsetandcoda1}.
 

### 2012-12-12 paper2/paper2.tex
incorporated most of Malcolm's comments - left some for a second pass

@@
 The data utilised may be the direct arrival times; travel time
-difference computed between direct arrivals of two waveforms; or
+difference computed between picked arrivals of two waveforms; or
 time differences inferred from time-lagged cross correlation of
@@
 estimates $\widetilde{\delta}_{CWIN}$; $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-is the likelihood function representing the forward model between the
-desired separation $\widetilde{\delta}_t$ and the data $\widetilde{\delta}_{CWIN}$; and
-$P(\widetilde{\delta}_t)$ is the prior function accounting for all a-priori information.
+is the likelihood function (or forward model) giving the probability that the separation
+estimates $\widetilde{\delta}_{CWIN}$ would be observed if the true separation was $\widetilde{\delta}_t$; and
+$P(\widetilde{\delta}_t)$ is the prior PDF accounting for all a-priori information.
 The tilde above the separation parameters in eq. (\ref{eq:-bayesian-noisyform})
@@
 with respect to dominant wavelength $\lambda_{d}$. In this paper we
-consider a uniform prior which gives emphasis to the recorded data.
-The algorithm for computing the noisy likelihood
+consider a uniform prior over appropriate bounds which gives emphasis to the recorded data.
+The procedure for computing the noisy likelihood
 $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
@@
  individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-to describe the location of multiple events with maximum identifying
+to describe the location of multiple events whose maximum corresponding to
  the most probable combination of locations.
-More importantly however, the PDF will
+More importantly however, the PDF shall
 quantify location uncertainty and provide information
@@
 This can be done because
-knowledge of location translates to separation.\footnote{Note that the reverse
-can not be said. That is, knowledge of separation between a single event pair
-does not translate to location but rather places a non-unique constraint on
+knowledge of location translates to separation.\footnote{Note that the reverse is 
+not true. That is, knowledge of separation between a single event pair
+does not uniquely translate to location but rather places a non-unique constraint on
 location.}
@@
 \label{eq:-E2-marginal}
-P(\mathbf{e}_2) = \int \int P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1 d\mathbf{e}_3
+P(\mathbf{e}_2|\mathbf{\delta}_{CWIN}) = \int \int P(\mathbf{e}_1, \mathbf{e}_2,
+ \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1 d\mathbf{e}_3
 \end{equation}
@@
 over all events and remaining coordinates for the chosen earthquake.
-Evaluation of $c$ in equation (\ref{eq-3eqposterior}) involves
-finding the value which normalises the posterior function to unit
-area over all plausible locations. In many applications the constant
-of proportionality $c$ is not important. For example, it is not
+Evaluation of the normalizing constant $c$ in equation (\ref{eq-3eqposterior}) involves
+finding the integral of the posterior function
+over all plausible locations. In many applications the constant
+of proportionality $c$ can be ignored. For example, it is not
 required when seeking the combination of locations which maximise
  the posterior function, nor in Bayesian sampling algorithms such as Markov-chain Monte-Carlo
-techniques which require evaluation of a function proportional to the PDF.
-
-Following the same argument we get the posterior function
+techniques which only require evaluation of a function proportional to the PDF.
+
+Extending to $n$ events we get the posterior function
 \begin{equation}
@@
 P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^n P(\mathbf{e}_i) \\
-\hspace{4em} \displaystyle  \times \prod_{i=1}^{n-1} \prod_{j=i+1}^n P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
+\hspace{4em} \displaystyle  \times \prod_{i=1}^{n-1} \prod_{j=i+1}^n P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j).
 \end{array}
 \end{equation}
-for $n$ events. When evaluating equation (\ref{posterior-n-events})
+When evaluating equation (\ref{posterior-n-events})
 over a range of locations it is necessary to compute and multiply
@@
 plausible region). Such calculations are prone to truncation errors
-so we work with the negative logarithm
+and so we work with the negative logarithm
 \begin{equation}
@@
 technique \citep{dr_Press87a}, a conjugate gradient method, to
-optimise $L$. It uses the derivatives of $L$ to guide the
-optimization procedure. We derive the derivatives in Appendix
-\ref{sec-Appendix-derivatives_ofL}. Note that when optimizing
+optimize $L$. It uses the derivatives of $L$, derived in Appendix
+\ref{sec-Appendix-derivatives_ofL}, to guide the
+optimization procedure. Note that when optimizing
 equation \ref{eq:-negative-log} the values of $ln \left[ c \right]$
@@
 circles in Figure \ref{fig-2D50eq-relocation_eg1}. The optimization
-does not lead to the correct solution due to the addition of noise
+does not lead to the exact solution due to the addition of noise
 ($\bar{\sigma}_N=0.02$) on the hypothetical CWI data. The average
@@
 
-\subsection{Example 3 - The impact of reduced linkage}
+\subsection{Example 3 - The impact of incomplete event pairs in 2D}
 
@@
 
-\subsection{Example 4 - 3D synthetic examples with reduced linkage}
+\subsection{Example 4 - The impact of incomplete event pairs in 3D}
 
@@
 regardless of the number of stations available, reinforcing our
-hypothesis that coda waves can constrain location in poor recording
-situations.
+hypothesis that coda waves can constrain location in what would
+normally be regarded as a poor station network.
 
@@
 
-The hypoDD program also struggles to locate all events as the number
+The hypoDD algorithm also struggles to locate all events as the number
 of stations is reduced. In the case of hypoDD an event can be
@@
 Research Council Discovery Project (DP0665111).  This paper has
-benefited significantly from reviews by ......... at Geoscience
-Australia.
+benefited significantly from: reviews by Trevor Allen and Clive Collins 
+at Geoscience Australia as well; as well as comments and advice received from 
+Felix Waldhauser on the this and earlier research on the application of 
+CWI to earthquake location. 
 \end{acknowledgments}

### 2012-12-12 paper2/paper2.tex
incorporated most of Roel's comments - left a couple of the harder ones

@@
 \citep{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
-
 The accuracy required in earthquake location depends on the
@@
 interpreting magma movement in volcanoes \citep{dr_Fremont87a}; and
-monitoring pumping induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
+monitoring pumping-induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
 
@@
 develop an approach for locating earthquakes using coda waves.
-
 \citet{dr_Snieder05a} demonstrate that the coda of two earthquakes
@@
 perturbation between the coda waves of two earthquakes, and $\alpha$
-and $\beta$ are the near source $P$ and $S$ wave velocities,
+and $\beta$ are the near-source $P$ and $S$ wave velocities,
 respectively. The function $g$ depends on the type of excitation
@@
 The $\sigma_\tau$ in equation (\ref{eq:Theory-dcwi_g_sigmat}) is
-related to $R_{max}$, the maximum of the cross correlation between
-the coda of the two waveforms, and hence can be computed directly
-from the recorded data. In this paper we use the autocorrelation
-approach of \citet{dr_Robinson11a} when relating these parameters
+related to the maximum of the cross correlation between
+the coda of the two waveforms, $R_{max}$, and hence can be computed directly
+from the recorded data. The original formulation by \citet{dr_Sniedr05a}
+used a Taylor series expansion to relate $\sigma_\tau$ and $R_{max}$ by
+\begin{equation}
+\label{eq:Rmax-disp-orig} R_{max}^{(t,t_w)} = 1 - \frac{1}{2}
+\overline{\omega^2} \sigma_\tau^2,
+\end{equation} 
+In this paper we use the autocorrelation
+approach of \citet{dr_Robinson11a} to relate the parameters directly
 and we apply a restricted time lag search when evaluating $R_{max}$.
@@
 with respect to dominant wavelength $\lambda_{d}$. In this paper we
-consider a uniform prior over appropriate bounds which gives emphasis to the recorded data.
+consider a uniform prior over appropriate bounds to ensure that the 
+posterior function is dominated by the recorded data.
 The procedure for computing the noisy likelihood
@@
  individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-to describe the location of multiple events whose maximum corresponding to
+to describe the location of multiple events whose maximum corresponds to
  the most probable combination of locations.
@@
 on the degree to which individual events are constrained
- by the data.
-
-For convenience, we begin with three earthquakes having locations
+ by the data. For convenience, we begin with three earthquakes having locations
 $\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian
@@
 a local coordinate system. We choose a local coordinate system
-which removes ambiguity associated with transformations of the coordinate system.
+which removes ambiguity associated with transformations of the coordinate system. It is 
+necessary to do this because the distances between events are invariant for rotations
+and translations of the seismicity patterns and hence we know in advance that rotations 
+and translations can not be resolved from CWI alone.  
 In defining this coordinate system we fix the first event at the origin,
@@
 
-We design a 2D synthetic experiment (example 1) by randomly
+We design a 2D synthetic acoustic experiment (example 1) by randomly
 selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
@@
 Figure \ref{fig-2D50eq-relocation_eg1}.
- We assume a local velocity of $v=3,300\,$ms$^{-1}$ between all
+ We assume a local velocity of $\alpha=3,300\,$ms$^{-1}$ between all
 event pairs and a dominant frequency of 2.5$\,$Hz to represent waveform data filtered between 1 and 5$\,$Hz.
@@
 using all constraints with noise $\bar{\sigma}_N= 2
-\sigma_{1to5Hz}(\delta_t)$.
+\epsilon(\delta_t)$.
  Actual and optimization event locations
@@
 hypothetical $\bar{\sigma}_N$ by defining
-$\bar{\sigma}_N=\sigma_{1to5Hz}(\delta_t)$, where
-$\sigma_{1to5Hz}(\delta_t)$ is the half-width of the errorbars for a
+$\bar{\sigma}_N=\epsilon(\delta_t)$, where
+$\epsilon(\delta_t)$ is the half-width of the errorbars for a
 synthetic acoustic experiment with filtering between 1 and 5\,Hz
@@
 positioning with few satellites. Our third observation is that the
-location errors are circular, despite our attempt to correct for
+location errors form a pattern of circular rotation, despite our attempt to correct for
 rotational non-uniqueness with the local coordinate system.
@@
 eigenvectors with the smallest singular values \citep{dr_Aster05a}.
-Unfortunately, there is no obvious way to overcome this issue when
-using coda waves alone since the constraints are based on
-separation. Fortunately however, combining coda waves with
+ Fortunately however, combining coda waves with
 measurements of travel times alleviates this problem and facilitate
@@
 to 30\% coincides with the point where the average number of
-branches required to link each pair reaches 2 (see
+branches required to link each event pair reaches 2 (see
 Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the
@@
 minima and that a range of starting points should be considered.
-
 Some optimizations fail to converge after 1200 iterations when the
@@
 biases. We use a standard deviation for the noisy CWI estimates of
-$\bar{\sigma}_N = \sigma_{1to5Hz}$ and perform the optimization
+$\bar{\sigma}_N = \epsilon$ and perform the optimization
 using 10\%, 20\%, ..., 100\% of the direct links. In each case we
@@
 best solution constrains the event locations down to 30\% of the
-direct links.
-
-There is one notable difference between the 3D and 2D results. In 2D
+direct links. There is one notable difference between the 3D and 2D results. In 2D
 the final iteration was close to the actual solution when the
@@
 study are differentiated in black. Catalogue locations suggest that
-the 68 earthquakes of interest are distributed spatially throughout
-all events.
+the 68 earthquakes of interest are spatially widely distributed on the scale of
+ Figure \ref{fig-69Calaverasevents_eg1}.
 
@@
 locations (column 2) than the hypoDD locations (column 3). Our
-results suggest that the coda are less supportive of the presence of
+experience suggest that the coda are less supportive of the presence of
 streaks although a complete understanding of these differences is
@@
 make an assessment of this prior to starting the inversion. The top
-row of Figure \ref{fig-statremoval_summarystats} demonstrates that
+panel of Figure \ref{fig-statremoval_summarystats} demonstrates that
 when five or more stations are used, CWI can constrain the location
@@
 removal of outliers described by \citet{dr_Waldhauser00a}. The top
-row of Figure \ref{fig-statremoval_summarystats} shows that the
+panel of Figure \ref{fig-statremoval_summarystats} shows that the
 number of events re-located by hypoDD fluctuates between 63 and 28
@@
 
-The remaining rows of Figure \ref{fig-statremoval_summarystats}
+The remaining panels of Figure \ref{fig-statremoval_summarystats}
 illustrate a statistical comparison of the CWI and hypoDD reduced
@@
 P(\mathbf{e}_p|\Delta_{TT})
-\frac{1}{(2\pi)^{\frac{3}{2}}\sqrt{|\Sigma|}} \\
+\frac{1}{(2\pi)^{3/2}\sqrt{|\Sigma|}} \\
 \hspace{5em} \times \exp
@@
 (\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
-associated with translation, rotation and reflection around a global
+of the CWI inversion that is associated with translation, rotation and reflection around a global
 coordinate system. This means that it is no longer necessary to use
@@
 Another potential application of CWI is in the area of hydraulic
-fracturing such as hot rock geothermal projects and/or petroleum
-reservoir engineering. Monitoring pumping induced micro earthquakes
+fracturing such as hot rock geothermal projects and petroleum
+or tight gas extraction. Monitoring pumping induced micro earthquakes
 is a key step in understanding the migration of fluids in such

### 2012-12-12 paper2/paper2.tex
incorporated most of Juerg's comments + started a second pass of the other review comments. I need to complete the second pass of Trevor Allen's comments then update figures and decided whether to add the suggested references

@@
 
-\title{Relocating a cluster of earthquakes using a single station}
+\title{Relocating a Cluster of Earthquakes Using a Single Seismic Station}
 \author[D.J. Robinson, M. Sambridge, R. Snieder and J Hauser]
-  {David J. Robinson$^{1,2}$, Malcolm Sambridge$^{1}$, Roel Snieder$^{3}$, J\"urg Hauser$^{4}$ \\
+  {David J. Robinson$^{1,2}$, Malcolm Sambridge$^{1}$, Roel Snieder$^{3}$, Juerg Hauser$^{4}$ \\
   $^1$ Research School of Earth Sciences, Australian National
@@
 $^3$ Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines, Golden CO \emph{80401-1887}, USA \\
-$^4$ ..................}
+$^4$ CSIRO Earth Science and Resource Engineering, Dick Perry Av, Kensington WA \emph{6151} Australia}
 
@@
 
-Earthquake location is important for many applications. Locations
+Accurate earthquake location is important for many applications. Locations
 are required for:  magnitude
@@
 locations are influenced by source to station distances, the number
-of stations and their geometry, quality of signal and accuracy of
+of stations and their geometry, signal-to-noise, clarity of onsets and accuracy of
 the velocity model used in computing travel times. Uncertainties in
@@
 In traditional approaches to absolute and relative location only
-early onset body waves, typically $P$ and/or $S$ waves, are used.
+early onset body waves or crustal phases are used.
 The data utilised may be the direct arrival times; travel time
@@
 waves are ignored in most seismological applications due to the
-complexity involved in modeling their generation. In this paper we
+complexity involved in constraining complex hetergeneous velocity models 
+in real settings. In this paper we
 develop an approach for locating earthquakes using coda waves.
@@
 interference pattern between the coda waves. Unlike travel time
-techniques, CWI
+based location techniques, CWI
  does not require multiple stations or good azimuthal coverage.
@@
 Our technique can be used on coda waves alone or in combination with
-travel times.
+travel times. We begin by introducing the theory of CWI based earthquake location 
+(Section \ref{sec:theory}). This is followed by a demonstration of capability using 
+synthetic examples (Section \ref{sec:benchmarking}) and application to earthquakes 
+on the Calaveras fault, California using CWI alone (Section \ref{sec:CalaverasLoc-CWIonly}
+and CWI in combination with travel time constraints (Section \ref{sec:CalaverasLoc-CWIandTT}).
 
@@
 
-\citet{dr_Robinson11a} show that coda waves provide only
+\citet{dr_Robinson11a} show that CWI leads to
 probabilistic constraints on source separation and introduce a
@@
 posterior function is dominated by the recorded data.
-The procedure for computing the noisy likelihood
+The procedure for computing the likelihood
 $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
@@
 $P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3)$ where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the
+\mathbf{e}_3)$, where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the
 wavelength normalised separation estimates. Alternatively, if we use
@@
 are defined by coordinates $\hat{x}$, $\hat{y}$ and $\hat{z}$
-where the hat $\hat{.}$ indicates use of
+where the hat indicates use of
 a local coordinate system. We choose a local coordinate system
@@
 and translations can not be resolved from CWI alone.  
-In defining this coordinate system we fix the first event at the origin,
+In defining this coordinate system we fix the first event at the origin
 \begin{equation}
@@
 \end{equation}
-This coordinate system reduces translational (constraint \ref{eq:coord-const1})
-and rotational (constraints \ref{eq:coord-const2} to \ref{eq:coord-const4}) non-uniqueness
+This coordinate system reduces translational (equation \ref{eq:coord-const1})
+and rotational (equations \ref{eq:coord-const2} to \ref{eq:coord-const4}) non-uniqueness
 without loss of generality. It is necessary to work with a local coordinate
@@
 technique \citep{dr_Press87a}, a conjugate gradient method, to
-optimize $L$. It uses the derivatives of $L$, derived in Appendix
+minimize $L$. It uses the derivatives of $L$, derived in Appendix
 \ref{sec-Appendix-derivatives_ofL}, to guide the
@@
 practice the presence of noise allows the rotational non-uniqueness
-to reappear. This is because the `easiest' way data noise can
-propagate is into the direction which is least constrained by the
-data. The same phenomena is observed in linear inversion where noise
+to reappear. This is because errors align themselves in directions 
+least constrained by data. For the CWI technique this ammounts to rotations in 2D. 
+The same phenomena is observed in linear inversion where noise
 creates large spurious model changes in directions of the
@@
 the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
-the coordinate error as a function of increasing linkage. We show
+the coordinate error as a function of percentage of earthquake pairs 
+that are directly linked by a separation estimate. We show
 the statistics for the `best' optimization solution (black) and for
@@
 Some optimizations fail to converge after 1200 iterations when the
-linkage is 60\% or lower. All optimizations fail when then linkage
+linkage is 60\% or lower. All optimizations fail when the linkage
 is 20\% or lower. Despite their failure to converge, the locations
@@
 examples do not converge after 1200 iterations.
-\citet{dr_VanDecar94a} show that gradient damping acts slowly
+\citet{dr_VanDecar94a} show that derivative based regularization acts slowly
 through iterative least-squares, because
@@
 When 70\% of the direct constraints are considered all optimization
-results (gray) are consistent with the best solution (black). The
+results (gray) are consistent with the best solution obtained from 
+all 25 starting locations (black). The
 best solution constrains the event locations down to 30\% of the
@@
 solutions. When 70\% or more of the direct branches are used the
-optimiser is stable with no observable difference in the solution
+optimizer is stable with no observable difference in the solution
 for 25 randomly chosen starting locations. As the direct linkage
@@
 solution from 25 random starting locations is required to find the
-optimal solution. As the number of links decrease below 30\% the
-best solution fails to converge.
+optimal solution. All optimisations fail to converge as the number 
+of links decrease below 30\%.
 
@@
 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Elevation in California showing location of the Calaveras
+\caption{Map showing location of the Calaveras
 cluster (white star) and 805 seismic stations (black triangles).}
@@
 
-Global locations cannot be found by CWI alone. For the sake of
+Absolute locations cannot be found by CWI alone. For the sake of
 comparison, we arbitrarily choose a `master' event and translate our
@@
 event. This arbitrary translation does not change the relative
-locations. We return to this issue of relative versus actual
+locations. We return to this issue of relative versus absolute
 location in Example 7 by introducing a combined travel time and coda
@@
 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
-Statistics on coordinate differences for reduced station inversions.
-Differences are computed between the inversion results (CWI and
-hypoDD) and the complete hypoDD locations for all 308 events. The
-top subplot illustrates the number of constrainable events,$nE$ in
+Number of constrainable events,$nE$ in
 the CWI and hypoDD inversions as a function of the stations
-considered.} \label{fig-statremoval_summarystats}
+considered (top). Mean (middle) and maximum (bottom) of the difference
+computed between the reduced station inversion results (CWI and
+hypoDD) and the complete hypoDD locations for all 308 events. } \label{fig-statremoval_summarystats}
 \end{figure}
@@
 
-The hypoDD algorithm also struggles to locate all events as the number
+The hypoDD algorithm also fails to locate all events as the number
 of stations is reduced. In the case of hypoDD an event can be
 identified as unconstrainable in one of two stages. Firstly, the
-data are analysed to ensure that there exists travel time
+data are analyzed to ensure that there exists travel time
 differences for each event and at least one other earthquake. This
@@
 events that can not be located sufficiently are rejected during the
-inversion. This process is presumably related to the iterative
+inversion. This process is related to the iterative
 removal of outliers described by \citet{dr_Waldhauser00a}. The top
@@
 Another potential application of CWI is in the area of hydraulic
-fracturing such as hot rock geothermal projects and petroleum
-or tight gas extraction. Monitoring pumping induced micro earthquakes
+fracturing such as hot rock geothermal projects, petroleum reservoir engineering, 
+tight gas extraction, CO$_2$ geosequestration and/or underground brine injection. 
+Monitoring pumping-induced micro earthquakes
 is a key step in understanding the migration of fluids in such
@@
 benefited significantly from: reviews by Trevor Allen and Clive Collins 
-at Geoscience Australia as well; as well as comments and advice received from 
-Felix Waldhauser on the this and earlier research on the application of 
+at Geoscience Australia; as well as comments and advice received from 
+Felix Waldhauser on this and earlier research on the application of 
 CWI to earthquake location. 
@@
 \frac{\partial \sigma_1}{\partial \hat{x}_p} \int_{-\infty}^0 e^g ds}
-{\sigma_1^2 \sqrt{2 \pi}}
+{\sigma_1^2 \sqrt{2 \pi}},
 \end{equation}
@@
 \begin{equation}
-\frac{\partial B} {\partial \hat{x}_p} = e^h \frac{\partial h}{\partial \hat{x}_p}
+\frac{\partial B} {\partial \hat{x}_p} = e^h \frac{\partial h}{\partial \hat{x}_p},
 \end{equation}

### 2012-12-13 paper2/paper2.tex
another proof read by me - still need to update the figures and have a look at some of the references

@@
 locations are influenced by source to station distances, the number
-of stations and their geometry, signal-to-noise, clarity of onsets and accuracy of
-the velocity model used in computing travel times. Uncertainties in
-absolute location are typically of the order of several kilometers
-because they are susceptible to uncertainty in the velocity
-structure along the entire path between the source and receiver. For
-example, \citet{dr_Shearer99a} states that location uncertainty in
-the ISC and PDE catalogues are generally around 25\,km horizontally
-and at least 25\,km in depth.\footnote{Here the depth uncertainties
-of 25\,km assume the use of depth dependent phases such as $pP$.
-Without such phases the uncertainty is higher.} \citet{dr_Bondar04a}
-demonstrate that at the local scale, absolute locations are accurate
-to within 5\,km with a 95\% confidence level when local networks
-meet a number of station related criteria. Such errors are too large
-for many applications, particularly those focussed on imaging
-rupture surfaces from aftershock sequences.
+of stations and their geometry, signal-to-noise, clarity of onsets
+and accuracy of the velocity model used in computing travel times.
+Uncertainties in absolute location are typically of the order of
+several kilometers because they are susceptible to uncertainty in
+the velocity structure along the entire path between the source and
+receiver. For example, \citet{dr_Shearer99a} states that location
+uncertainty in the ISC (International Sesimological
+Centre\footnote{http://www.isc.ac.uk}) and PDE (National Earthquake
+Information
+Center\footnote{http://earthquake.usgs.gov/earthquakes/eqarchives/epic/})
+catalogues are generally around 25\,km horizontally and at least
+25\,km in depth.\footnote{Here the depth uncertainties of 25\,km
+assume the use of depth dependent phases such as $pP$. Without such
+phases the uncertainty is higher.} \citet{dr_Bondar04a} demonstrate
+that at the local scale, absolute locations are accurate to within
+5\,km with a 95\% confidence level when local networks meet a number
+of station related criteria. Such errors are too large for many
+applications, particularly those focussed on imaging rupture
+surfaces from aftershock sequences.
 
@@
 have been used to image active fault planes \citep{dr_Deichmann92a,
-dr_Got94a, dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a};
-studying rupture mechanics \citep{dr_Rubin99a, dr_Rubin02a};
-interpreting magma movement in volcanoes \citep{dr_Fremont87a}; and
-monitoring pumping-induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
+dr_Got94a, dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a}; study
+rupture mechanics \citep{dr_Rubin99a, dr_Rubin02a}; interpret magma
+movement in volcanoes \citep{dr_Fremont87a}; and monitor
+pumping-induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
 
 In traditional approaches to absolute and relative location only
-early onset body waves or crustal phases are used.
-The data utilised may be the direct arrival times; travel time
+early onset body waves, typically $P$ and/or $S$ waves,are used. The
+data utilised may be the direct arrival times; travel time
 difference computed between picked arrivals of two waveforms; or
@@
 The $\sigma_\tau$ in equation (\ref{eq:Theory-dcwi_g_sigmat}) is
-related to the maximum of the cross correlation between
-the coda of the two waveforms, $R_{max}$, and hence can be computed directly
-from the recorded data. The original formulation by \citet{dr_Sniedr05a}
-used a Taylor series expansion to relate $\sigma_\tau$ and $R_{max}$ by
+related to the maximum of the cross correlation between the coda of
+the two waveforms, $R_{max}$, and hence can be computed directly
+from the recorded data. The original formulation by
+\citet{dr_Snieder05a} used a second-order Taylor series expansion of
+the waveform autocorrelation function to relate $\sigma_\tau$ and
+$R_{max}$ by
 \begin{equation}
@@
 \end{equation}
-In this paper we use the autocorrelation
-approach of \citet{dr_Robinson11a} to relate the parameters directly
-and we apply a restricted time lag search when evaluating $R_{max}$.
-These extensions to the original technique of \citet{dr_Snieder05a}
+In this paper we use the autocorrelation approach of
+\citet{dr_Robinson11a} to relate the parameters directly and we
+apply a restricted time lag search when evaluating $R_{max}$. These
+extensions to the original technique of \citet{dr_Snieder05a}
 increase the range of applicability of CWI by 50\% (i.e. from 300 to
-450\,m separation for 1–5\,Hz filtered coda waves).
+450\,m separation for 1 to 5\,Hz filtered coda waves).
 
@@
 \end{equation}
-where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the posterior function
-indicating the probability of true separation $\widetilde{\delta}_t$ given the noisy CWI separation
-estimates $\widetilde{\delta}_{CWIN}$; $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-is the likelihood function (or forward model) giving the probability that the separation
-estimates $\widetilde{\delta}_{CWIN}$ would be observed if the true separation was $\widetilde{\delta}_t$; and
-$P(\widetilde{\delta}_t)$ is the prior PDF accounting for all a-priori information.
-The tilde above the separation parameters in eq. (\ref{eq:-bayesian-noisyform})
-indicates the use of a wavelength normalised separation parameter
+where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the
+posterior function indicating the probability of true separation
+$\widetilde{\delta}_t$ given the noisy CWI separation estimates
+$\widetilde{\delta}_{CWIN}$;
+$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is the
+likelihood function (or forward model) giving the probability that
+the separation estimates $\widetilde{\delta}_{CWIN}$ would be
+observed if the true separation was $\widetilde{\delta}_t$; and
+$P(\widetilde{\delta}_t)$ is the prior PDF accounting for all
+a-priori information. The tilde above the separation parameters in
+equation (\ref{eq:-bayesian-noisyform}) indicates the use of a
+wavelength normalised separation parameter
 \begin{equation}
@@
 \mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-travel time differences. In this derivation and in Section
-\ref{sec:benchmarking} we focus on the constraints imposed by coda
-waves, whereas in Section \ref{sec:CalaverasLoc-CWIandTT} we
-demonstrate how CWI and travel time data can be combined.
+travel time differences. In the following derivation and in Sections
+\ref{sec:benchmarking} and \ref{sec:CalaverasLoc-CWIonly} we focus
+on the constraints imposed by coda waves, whereas in Section
+\ref{sec:CalaverasLoc-CWIandTT} we demonstrate how CWI and travel
+time data can be combined.
 
@@
 \begin{equation}
-\label{eq:-joint-prior4three}
-P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) = P((\mathbf{e}_1) \times P(\mathbf{e}_2) \times P(\mathbf{e}_3).
+\label{eq:-joint-prior4three} P(\mathbf{e}_1, \mathbf{e}_2,
+\mathbf{e}_3) = P(\mathbf{e}_1) \times P(\mathbf{e}_2) \times
+P(\mathbf{e}_3).
 \end{equation}
@@
 P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^3 P(\mathbf{e}_i) \\
-\hspace{4em}  \times \displaystyle \prod_{i=1}^2 \prod_{j=i+1}^3 P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
+\hspace{4em}  \times \displaystyle \prod_{i=1}^2 \prod_{j=i+1}^3
+P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
 \end{array}
@@
 P(\mathbf{e}_2|\mathbf{\delta}_{CWIN}) = \int \int P(\mathbf{e}_1, \mathbf{e}_2,
- \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1 d\mathbf{e}_3
+ \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1
+ d\mathbf{e}_3,
 \end{equation}
@@
 The event locations $\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n$
-are defined by coordinates $\hat{x}$, $\hat{y}$ and $\hat{z}$
-where the hat indicates use of
-a local coordinate system. We choose a local coordinate system
-which removes ambiguity associated with transformations of the coordinate system. It is 
-necessary to do this because the distances between events are invariant for rotations
-and translations of the seismicity patterns and hence we know in advance that rotations 
-and translations can not be resolved from CWI alone.  
-In defining this coordinate system we fix the first event at the origin
+are defined by coordinates $\hat{x}$, $\hat{y}$ and $\hat{z}$ where
+the hat indicates use of a local coordinate system. We choose a
+local coordinate system which removes ambiguity associated with
+transformations of the coordinate system. It is necessary to do this
+because the distances between events are invariant for rotations,
+reflections and translations of the seismicity pattern and hence
+cannot be resolved from CWI alone. In defining this coordinate
+system we fix the first event at the origin
 \begin{equation}
@@
  We assume a local velocity of $\alpha=3,300\,$ms$^{-1}$ between all
-event pairs and a dominant frequency of 2.5$\,$Hz to represent waveform data filtered between 1 and 5$\,$Hz.
-The CWI data are defined by the positive bounded Gaussian with statistics
-$\bar{\mu}_N$ and $\bar{\sigma}_N$. A hypothetical CWI mean is created by setting
+event pairs and a dominant frequency of 2.5$\,$Hz to represent
+waveform data filtered between 1 and 5$\,$Hz. The CWI data are
+defined by the dominant wavelength normalized positive bounded
+Gaussian PDF with statistics $\bar{\mu}_N$ and $\bar{\sigma}_N$
+\citep{dr_Robinson11a}. A hypothetical CWI mean is created by
+setting
 \begin{equation}
@@
 observation is analogous to problems associated with poor azimuthal
-coverage in common triangulation problems such as individual
-earthquake location from limited travel time data, or GPS
-positioning with few satellites. Our third observation is that the
-location errors form a pattern of circular rotation, despite our attempt to correct for
+coverage in triangulation problems such as individual earthquake
+location from limited travel time data, or GPS positioning with few
+satellites. Our third observation is that the location errors form a
+pattern of circular rotation, despite our attempt to correct for
 rotational non-uniqueness with the local coordinate system.
@@
 the removal of a local coordinate system altogether (see Section
-\ref{sec:CalaverasLoc-CWIandTT}).
-
-Despite our observations about the error structure however, we gain
+\ref{sec:CalaverasLoc-CWIandTT}). On balance however, we gain
 confidence in the optimization procedure due to its stability for
@@
 the coordinate error as a function of percentage of earthquake pairs
-that are directly linked by a separation estimate. We show
-the statistics for the `best' optimization solution (black) and for
-the solution space when all 25 optimizations are considered (gray).
-In the latter case the best solution is determined by the set of
-event locations which lead to the smallest value of $L$. The error
-in the best solution is consistent when 30\% or more of the branches
-are used. The errors increase when only 10\% or 20\% of the
-constraints are included. Interestingly, this breakdown around 20\%
-to 30\% coincides with the point where the average number of
-branches required to link each event pair reaches 2 (see
+that are directly linked by a separation estimate. We show the
+statistics for the `best' optimization solution (black) and for the
+solution space when all 25 optimizations are considered (gray). In
+the former case the best solution is determined by the set of event
+locations which lead to the smallest value of $L$. The error in the
+best solution is consistent when 30\% or more of the branches are
+used. The errors increase when only 10\% or 20\% of the constraints
+are included. Interestingly, this breakdown around 20\% to 30\%
+coincides with the point where the average number of branches
+required to link an event pair reaches 2 (see
 Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the
@@
 Some optimizations fail to converge after 1200 iterations when the
-linkage is 60\% or lower. All optimizations fail when the linkage
-is 20\% or lower. Despite their failure to converge, the locations
-at final iteration are close to the actual solution.
+linkage is 60\% or lower. All optimizations fail when the linkage is
+20\% or lower. Despite their failure to converge, the locations at
+final iteration are close to the actual solution.
 
@@
  a set of actual event locations for 50 earthquakes with
-$-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case we assume a local velocity
-of $v=3300\,$ms$^{-1}$ between all event pairs and a dominant frequency of 2.5$\,$Hz to represent
+$-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case
+we assume a local velocity of $v=3,300\,$ms$^{-1}$ between all event
+pairs and a dominant frequency of 2.5$\,$Hz to represent
  waveform data filtered between 1 and 5$\,$Hz.
@@
 Calaveras example released with the open source Double Difference
-algorithm or hypoDD \citep{dr_Waldhauser00a, dr_Waldhauser01a}[See
-also Data and Resources Section]. These events are chosen for three
+algorithm or hypoDD \citep{dr_Waldhauser00a, dr_Waldhauser01a} [See
+also Data and Resources Section]. These events are chosen for four
 reasons. Firstly, they are recorded by a large number of stations
@@
 for assessing the performance of a new location technique. Secondly,
-they are distributed with separations from near zero to hundreds
-meters making them ideal for application of CWI. Finally, Calaveras
+they are distributed with separations from near zero to hundreds of
+meters making them ideal for application of CWI. Thirdly, Calaveras
 earthquakes have been well researched with several studies having
 relocated events in the region \citep{dr_Waldhauser01a,
-dr_Schaff02a, dr_Waldhauser08a}. The relocations in this paper are
-sorted into four examples summarised in Table \ref{tab:examples}.
+dr_Schaff02a, dr_Waldhauser08a}. Finally, the hypoDD locations for
+these 68 earthquakes align in a streak increasing the likelihood
+that they have near identical source mechanisms, a necessary
+assumption for the application of equation
+\ref{eq:LitReview-g-3d-dc}. The relocations in this paper are sorted
+into four examples as summarised in Table \ref{tab:examples}.
 
@@
 Unsuitable waveforms are removed using the conditions summarised in
-Table 5 of \citet{dr_Robinson11a}. Remaining waveforms are filtered
-between 1 and 5\,Hz and aligned  to $P$ arrivals at 0\,s. CWI
-estimates are obtained from 5\,s wide non-overlapping time windows
-between $2.5 \leq t \leq 20$\,s and used to create probabilistic
-constraints on event separation. We introduce the local coordinate
-system of Section \ref{sec:theory} and find the optimum relative
-locations using Polak-Ribiere optimization.
+Table \ref{tab:-conditions4unsuitablewaveform}. Remaining waveforms
+are filtered between 1 and 5\,Hz and aligned  to $P$ arrivals at
+0\,s. CWI estimates are obtained from 5\,s wide non-overlapping time
+windows between $2.5 \leq t \leq 20$\,s and used to create
+probabilistic constraints on event separation. We introduce the
+local coordinate system of Section \ref{sec:theory} and find the
+optimum relative locations using Polak-Ribiere optimization.
+
+\begin{table}
+\caption[Conditions for identifying unsuitable waveforms when
+applying CWI] {Conditions used to identify unsuitable waveforms
+before applying CWI \citep[Originally published as Table
+5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
+\begin{tabular}{|l|p{0.7\textwidth}|}
+\hline
+ & \textbf{condition} \\
+\hline
+1 & waveform is clearly corrupted \\
+2 & waveform indicates recording of more then one event \\
+3 & signal to noise ratio is obviously low \\
+4 & there is insufficient coda recorded after the \\
+ & first arrivals \\
+5 & there is insufficient recording before the arrivals \\
+ &  (needed for accurate noise energy estimate) \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-Absolute locations cannot be found by CWI alone. For the sake of
-comparison, we arbitrarily choose a `master' event and translate our
-relative locations to align with the hypoDD location for the same
-event. This arbitrary translation does not change the relative
-locations. We return to this issue of relative versus absolute
-location in Example 7 by introducing a combined travel time and coda
-wave inversion.
+Absolute locations cannot be found by CWI alone. This is because of
+the non-uniquesness associated with translation, rotation and
+reflection. For the sake of comparison, we arbitrarily choose a
+`master' event and translate our relative locations to align with
+the hypoDD location for the same event. This arbitrary translation
+does not change the relative locations. We return to this issue of
+relative versus absolute location in Example 7 by introducing a
+combined travel time and coda wave inversion.
 
@@
 
-CWI locations are illustrated in Figure
-\ref{fig-CWIreducesstats} for the inversions with 7, 5, 4, 3, 2 and
-1 station. We observe a high level of consistency between these 6
+CWI locations are illustrated in Figure \ref{fig-CWIreducesstats}
+for the inversions with seven, five, four, three, two and one
+station. We observe a high level of consistency between these 6
 inversions and the locations shown in Figure
@@
 coda waves constrain a decreasing number of events until at one
-station it is only possible to locate 55 of the 68 events.
+station it is only possible to locate 55 of the 68 events. The
+hypoDD algorithm also fails to locate all events as the number of
+stations is reduced. In the case of hypoDD an event can be
+identified as unconstrainable in one of two stages. Firstly, the
+data are analyzed to ensure that there exists travel time
+differences for each event and at least one other earthquake. This
+is analogous to the situation for the coda wave technique. The
+hypoDD program also has a secondary identification phase in which
+events that can not be located sufficiently are rejected during the
+inversion. This process is related to the iterative removal of
+outliers described by \citet{dr_Waldhauser00a}. The top panel of
+Figure \ref{fig-statremoval_summarystats} shows that the number of
+events re-located by hypoDD fluctuates between 63 and 28 earthquakes
+for ten to four stations and it demonstrates that the number of
+events located by hypoDD is less than or equal to the number located
+by CWI.
 
@@
 %%=========================================================================
-
-The hypoDD algorithm also fails to locate all events as the number
-of stations is reduced. In the case of hypoDD an event can be
-identified as unconstrainable in one of two stages. Firstly, the
-data are analyzed to ensure that there exists travel time
-differences for each event and at least one other earthquake. This
-is analogous to the situation for the coda wave technique. The
-hypoDD program also has a secondary identification phase in which
-events that can not be located sufficiently are rejected during the
-inversion. This process is related to the iterative
-removal of outliers described by \citet{dr_Waldhauser00a}. The top
-panel of Figure \ref{fig-statremoval_summarystats} shows that the
-number of events re-located by hypoDD fluctuates between 63 and 28
-earthquakes for 10 to 4 stations and it demonstrates that the number
-of events located by hypoDD is less than the number located by CWI
-in all cases.
 
@@
 temporary deployment and therefore opens new avenues for imaging
-intraplate fault structures and improved our understanding of
+intraplate fault structures and improving our understanding of
 intraplate seismicity and earthquake hazard.
@@
 
-\section{The noisy likelihood}
+\section{The likelihood}
 \label{sec-Appendix-noisylikelihood}
 
-The noisy likelihood
-$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ used in equation
-(\ref{eq:-bayesian-noisyform}) is given by
+The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
+used in equation (\ref{eq:-bayesian-noisyform}) is given by
 \begin{equation}

### 2012-12-14 paper2/paper2.tex
from SAGM day at GA

@@
 \caption{Example 3 - Statistical measures of error in the
-optimization solutions for the 2D synthetic cases when all (gray)
-and best (black) results are considered. The statistics
-$\Delta_{max}$ and $\Delta_\mu$  are the maximum and mean coordinate
-error, respectively. The bottom subplot shows the average minimum
-number of branches required to link the 2450 pairs.}
+ solutions for the 2D synthetic cases when all and best
+optimization results are considered. The statistics $\Delta_{max}$
+and $\Delta_\mu$  are the maximum and mean coordinate error,
+respectively. The bottom subplot shows the average minimum number of
+branches required to link the 2450 pairs.}
  \label{fig:optimisationresults-2Dsynth}
@@
 20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
-Number of constrainable events,$nE$ in
-the CWI and hypoDD inversions as a function of the stations
-considered (top). Mean (middle) and maximum (bottom) of the difference
-computed between the reduced station inversion results (CWI and
-hypoDD) and the complete hypoDD locations for all 308 events. } \label{fig-statremoval_summarystats}
+Number of constrainable events $nE$ in the CWI and hypoDD inversions
+as a function of the stations considered (top). Mean (middle) and
+maximum (bottom) of the difference computed between the reduced
+station inversion results (CWI and hypoDD) and the complete hypoDD
+locations for all 308 events. } \label{fig-statremoval_summarystats}
 \end{figure}

### 2012-12-14 paper2/diags/synth3Dmulti/wrap_plot_outcomes.m
more from AGM day

@@ -74,24 +74,27 @@ maxvals_best(ind_best) = NaN;
 fh.maxvals = figure;
 
 sh(1) = subplot(3,1,1)
-h2 = plot(maxvals_best,'color','k','linewidth',2) %  best
+h1b = plot(maxvals_best,'color','k','linewidth',2) %  best
 hold on
-h1 = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+h1g = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
 %legend([h1,h2], {'all', 'best'})
 set(gca,'xlim',[1 10])
 set(gca,'xtick',1:10,'ytick',[0 50 100 150])
 set(gca,'xticklabel',{})%ticklabelstr)
 set(gca,'fontsize',fsize)
 set(gca,'ylim',[0 150],'xlim',[1 10],'units','centimeters')
+lh = legend([h1b,h1g],{'best','all'},'Location','Northeast')
+set(lh,'fontsize',10)
+set(lh,'Box','off')
 ylabel('$\Delta_{max}$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 %xlabel('Number of constraints','fontsize',fsize)
 
 meanvals_all(ind_all) = NaN;
 meanvals_best(ind_best) = NaN;
 sh(2) = subplot(3,1,2)
-h2 = plot(meanvals_best,'color','k','linewidth',2) % best
+h2b = plot(meanvals_best,'color','k','linewidth',2) % best
 hold on
-h1 = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+h2g = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
 set(gca,'xlim',[1 10])
 set(gca,'xtick',1:10,'ytick',[0 20 40])
 ticklabelstr = {' ','20%',' ','40%',' ','60%',' ','80%',' ','100%'};
@@ -126,9 +129,15 @@ set(sh(2), 'position',[statxstart, statystart+statheight+statygap, statwidth, st
 set(sh(1), 'position',[statxstart, statystart+2*statheight+2*statygap, statwidth, statheight])
 
 
+%print -depsc ressummary_3Dsynth50eq.eps
+print -depsc ../../Figure4_bw.eps
 
-print -depsc ressummary_3Dsynth50eq.eps
-
+% Now lets make the colour version
+set(h1b,'color','b')
[…]

### 2012-12-14 paper2/diags/CalaverasMap/matlab/plot_map.m
more from AGM

@@ -7,7 +7,7 @@ figure_switch = 1;
 %   2 => also compute large figure with all stations (SLOW)
 %====================================
 
-fsize = 16;
+fsize = 10;
 
 
 % Load the earthquakes
@@ -36,8 +36,20 @@ set(gca,'fontsize',fsize)
 [s, alpha12, alpha21] = vincenty_inverse(37.35,-121.65,37.35,-121.53705)
 plot([-121.65 -121.53705],[37.35 37.35],'k','linewidth',2)
 text(mean([-121.65 -121.53705])-0.015,37.36,'10km','fontsize',fsize)
+arrow([-121.6169,37.3048],[-121.6563,37.2916],10)
+text(-121.61,37.3180,'Calaveras')
+text(-121.61,37.2964,'Events')
 
-print -depsc Calaveras_substationmap.eps
+
+statwidth = 7.5;
+statheight = 7.5;
+statxstart = 1.5%4.6;
+statystart = 1.5%1.95;
+set(gca,'units','centimeters')
+set(gca, 'position',[statxstart, statystart, statwidth, statheight])
+
+%print -depsc Calaveras_substationmap.eps
+print -depsc ../../../Figure7.eps
 
 if figure_switch ==2
     figure

### 2012-12-14 paper2/diags/build_OmoriFigure.m

@@ -15,17 +15,17 @@ prop_recorded = (Nend-Nstart)/Ntotal
 
 t1 = [0:tstart];
 N1 = Cumm_Omori(t1);
-plot(t1,N1,'linewidth',2,'color',[0.7,0.7,0.7])
+l1 = plot(t1,N1,'linewidth',2,'color',[0.7,0.7,0.7])
 
 t2 = [tstart:tend];
 N2 = Cumm_Omori(t2);
 hold on
-plot(t2,N2,'k','linewidth',2)
+l2 = plot(t2,N2,'k','linewidth',2)
 
 tend2 = 1000;
 t3 = [tend:tend2];
 N3 = Cumm_Omori(t3);
-plot(t3,N3,'linewidth',2,'color',[0.7,0.7,0.7])
+l3 = plot(t3,N3,'linewidth',2,'color',[0.7,0.7,0.7])
 
 fsize = 16;
 %set(gca,'fontsize',fsize)
@@ -36,7 +36,15 @@ ylabel('N(t)')
 set(gca,'xlim',[-25, tend2],'xtick',[0:200:tend2])
 
 set(gca,'units','centimeters','position',[4.6,1.5,7.5,6])
-print -depsc OmoriFigure.eps
+%print -depsc OmoriFigure.eps
+print -depsc ../Figure12_bw.eps
+
+% Now create the colour version
+set(l1,'color','r')
+set(l2,'color','b')
+set(l3,'color','r')
+print -depsc ../Figure12_c.eps
+
 
 function [N] = Cumm_Omori(t)
 % Assume the following values

### 2012-12-14 paper2/diags/plot_2Dsynth_example1.m
more from GA AGM day

@@ -1,5 +1,12 @@
-datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
-
+home_switch = 0; %1=> at home PC, 0=> at work PC
+if home_switch ==1
+    datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
+elseif home_switch ==0
+    datadir = 'C:\datafiles\sandpit_ANU\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
+end
+    
+    
+    
 if strcmp(filesep,'/')
     error('You must be on Windows to get the Latex Interpreter for these figures')
 end
@@ -31,22 +38,43 @@ figure
 colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
 colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
 ind = find(f<-127.38);
+h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',10);
+hold on
+
+count = 1
 for i = 1:nevnts
-    h1 = plot(E(i,1), E(i,2), 'ko', 'markerfacecolor','w','markersize',10);
-    hold on
+    %h1 = plot(E(i,1), E(i,2), 'ko', 'markerfacecolor','w','markersize',10);
     %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
     for j = 1:length(ind)
-        h2 = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
-        hold on
+        h2(count) = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
         plot([xend(i,ind(j)) E(i,1)], [yend(i,ind(j)) E(i,2)],'Color',[0.7 0.7 0.7],'linewidth',2,'markersize',10)
+        count = count+1;
     end
 end
-set(gca,'xlim',[-70,70], 'ylim',[-70,70], 'fontsize',18)
+set(gca,'xlim',[-70,70], 'ylim',[-70,70])
 xlabel('$\hat{x}$ (m)','Interpreter','Latex')
 ylabel('$\hat{y}$ (m)','Interpreter','Latex') 
[…]

### 2012-12-14 paper2/diags/plot_2Dsynth_example3.m

@@ -1,5 +1,10 @@
-datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
-
+home_switch = 0; %1=> at home PC, 0=> at work PC
+if home_switch ==1
+    datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
+elseif home_switch ==0
+    datadir = 'C:\datafiles\sandpit_ANU\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
+end
+    
 if strcmp(filesep,'/')
     error('You must be on Windows to get the Latex Interpreter for these figures')
 end
@@ -31,22 +36,40 @@ figure
 colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
 colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
 ind = find(f<-127.38);
+h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',10);
+hold on
+count = 1
 for i = 1:nevnts
-    h1 = plot(E(i,1), E(i,2), 'ko', 'markerfacecolor','w','markersize',10);
-    hold on
     %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
     for j = 1:length(ind)
-        h2 = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
+        h2(count) = plot(xend(i,ind(j)),yend(i,ind(j)), 'k^','markerfacecolor','w','markersize',10)
         hold on
         plot([xend(i,ind(j)) E(i,1)], [yend(i,ind(j)) E(i,2)],'Color',[0.7 0.7 0.7],'linewidth',2,'markersize',10)
+        count = count+1;
     end
 end
-set(gca,'xlim',[-70,70], 'ylim',[-70,70], 'fontsize',18)
+set(gca,'xlim',[-70,70], 'ylim',[-70,70])
 xlabel('$\hat{x}$ (m)','Interpreter','Latex')
 ylabel('$\hat{y}$ (m)','Interpreter','Latex') 
-legend([h2,h1],{'Actual Location','Optimisation Soln'},'Location','NorthWest') 
[…]

### 2012-12-14 paper2/diags/plot_calaveras_loc2.m

@@ -3,6 +3,20 @@
 % .... This version (i.e. plot_calaveras_loc2.m utilises hypoDD with
 % .... SVD ........
 
+ 
+homeswitch =0; %1=> on home computer - 0=> on work PC
+if homeswitch ==1
+    path2thesis = '../../../thesis_version2/';
+elseif homeswitch ==0
+    path2thesis = '../../../../invert/davidr/thesis_version2/';
+end
+
+if homeswitch ==1
+        thesisdiags = '../../../thesis_version2/';
+elseif homeswitch ==0
+        thesisdiags = '../../../../invert/davidr/thesis_version2/diags/eq_location_optimisation/';
+end
+
 %% Machine check - must be on notebook for best figure
 if strcmp(filesep,'/')
     error('ERROR: must be on notebook for best figure quality')
@@ -44,9 +58,9 @@ ay_start = 0.7;
 
 
 %% Load inputdata
-events_oi = load('../../../thesis_version2/diags/eq_location_optimisation/events_oi.txt');
 
-CatLoc = load('../../../thesis_version2/diags/eq_location_optimisation/Calaveras_cat_locations.txt'); 
+events_oi = load([path2thesis,'/diags/eq_location_optimisation/events_oi.txt']);
+CatLoc = load([path2thesis,'/diags/eq_location_optimisation/Calaveras_cat_locations.txt']); 
 [n m] = size(CatLoc); 
 CatLoc_68 = [];
 CatLoc_not68 = [];
@@ -69,7 +83,8 @@ end
 if strcmp(filesep,'/')
     dirname = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
 else
-    dirname = '../../../thesis_version2/diags/eq_location_optimisation/'
+    dirname = '../../../../invert/davidr/thesis_version2/diags/eq_location_optimisation/';
+    %dirname = '../../../thesis_version2/diags/eq_location_optimisation/'
     dirname_hypoDD_SVD = '..\..\..\concluding_papers\paper2\diags\runs2\Hypodd_SVD\HYPODD2\runs\orig_68eqonly\';
 end
 % Get the original best hypoDD locations (i.e. those where we used LSQR)
@@ -95,6 +110,8 @@ Locs_hypoDDbest.not68z = tmphypoDDnot68(:,7);
 if strcmp(filesep,'/')
[…]

### 2012-12-14 paper2/diags/synth2Dmulti/wrap_plot_outcomes.m

@@ -89,21 +89,24 @@ fsize = 12
 % Now let's do the plotting
 fh.maxvals = figure;
 sh(1) = subplot(3,1,1)
-h2 = plot(maxvals_best,'color','k','linewidth',2) %  best
+h1b = plot(maxvals_best,'color','k','linewidth',2) %  best
 hold on
-h1 = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+h1g = plot(maxvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
 %legend([h1,h2], {'all', 'best'})
 set(gca,'xtick',1:10,'ytick',[0 50 100 150])
 set(gca,'xticklabel',{}) %ticklabelstr)
 set(gca,'fontsize',fsize)
 set(gca,'ylim',[0 150],'xlim',[1 10],'units','centimeters')
+lh = legend([h1b,h1g],{'best','all'},'Location','Northeast')
+set(lh,'fontsize',10)
+set(lh,'Box','off')
 ylabel('$\Delta_{max}$\,(m)','fontsize',fsize,'Interpreter','LaTex')
 %xlabel('Number of constraints','fontsize',fsize)
 
 sh(2) = subplot(3,1,2)
-h2 = plot(meanvals_best,'color','k','linewidth',2) % best
+h2b = plot(meanvals_best,'color','k','linewidth',2) % best
 hold on
-h1 = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
+h2g = plot(meanvals_all,'color',[0.7,0.7,0.7],'linewidth',1); % all
 hold on
 set(gca,'xtick',1:10,'ytick',[0 20 40])
 set(gca,'xticklabel',{})%ticklabelstr)
@@ -219,7 +222,7 @@ end
 fsize = 12
 figure(fh.maxvals)
 sh(3) = subplot(3,1,3)
-h1 = plot(average_pathlength_vec,'k','linewidth',2);
+h3b = plot(average_pathlength_vec,'k','linewidth',2);
 set(gca,'xtick',1:10)
 %set(gca,'ytick',[0 50 100 150])
 ticklabelstr = {' ','20%',' ','40%',' ','60%',' ','80%',' ','100%'};
@@ -243,4 +246,13 @@ set(sh(2), 'position',[statxstart, statystart+statheight+statygap, statwidth, st
[…]

### 2012-12-17 paper2/diags/plot_2Dsynth_example1.m
more changes

@@ -2,10 +2,10 @@ home_switch = 0; %1=> at home PC, 0=> at work PC
 if home_switch ==1
     datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
 elseif home_switch ==0
-    datadir = 'C:\datafiles\sandpit_ANU\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
+    datadir = 'Y:\earthquake\sandpits\drobinson\invert\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_1\';
 end
     
-    
+msize = 6
     
 if strcmp(filesep,'/')
     error('You must be on Windows to get the Latex Interpreter for these figures')
@@ -22,9 +22,9 @@ figure
 colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'}
 colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'}
 for i = 1:nevnts
-    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',10);
+    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',msize);
     hold on
-    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',10);
+    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',msize);
     hold on
     plot([xend(i,:) E(i,1)], [yend(i,:) E(i,2)],'Color',[0.5 0.5 0.5],'linewidth',2)
 end
@@ -38,7 +38,7 @@ figure
 colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
 colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
 ind = find(f<-127.38);
-h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',10);
+h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',msize);
 hold on
 
 count = 1
@@ -46,8 +46,8 @@ for i = 1:nevnts
[…]

### 2012-12-17 paper2/diags/plot_2Dsynth_example3.m

@@ -2,9 +2,11 @@ home_switch = 0; %1=> at home PC, 0=> at work PC
 if home_switch ==1
     datadir = 'C:\datafiles\workstuff\sandpit\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
 elseif home_switch ==0
-    datadir = 'C:\datafiles\sandpit_ANU\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
+    datadir = 'Y:\earthquake\sandpits\drobinson\invert\davidr\thesis_version2\diags\eq_location_optimisation\example_2D_50eq_3\';
 end
-    
+
+msize = 6; 
+
 if strcmp(filesep,'/')
     error('You must be on Windows to get the Latex Interpreter for these figures')
 end
@@ -20,9 +22,9 @@ figure
 colorlookup = {'b.','r.','g.','c.','m.','y.','k.','bo','ro','go'}
 colorlookup2 = {'b^','r^','g^','c^','m^','y^','k^','bd','rd','gd'}
 for i = 1:nevnts
-    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',10);
+    h1 = plot(xend(i,:), yend(i,:),'ko','markerfacecolor','k', 'markersize',msize);
     hold on
-    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',10);
+    h2 = plot(E(i,1),E(i,2), 'k^', 'markerfacecolor','k','markersize',msize);
     hold on
     plot([xend(i,:) E(i,1)], [yend(i,:) E(i,2)],'Color',[0.5 0.5 0.5],'linewidth',2)
 end
@@ -36,15 +38,15 @@ figure
 colorlookup = {'b+','bo','b^','bV','bd','bs','b*','bp','b>','b<'}
 colorlookup2 = {'r+','ro','r^','rV','rd','rs','r*','rp','r>','r<'}
 ind = find(f<-127.38);
-h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',10);
+h1 = plot(E(:,1), E(:,2), 'ko', 'markerfacecolor','w','markersize',msize);
 hold on
 count = 1
 for i = 1:nevnts
     %plot(xend(i,ind(j)),-yend(i,ind(j)), colorlookup{i})
     for j = 1:length(ind)
[…]

### 2012-12-17 paper2/diags/plot_calaveras_loc2.m

@@ -81,9 +81,9 @@ end
 
 % Lets get the results we need for this figure
 if strcmp(filesep,'/')
-    dirname = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    dirname = [path2thesis,'/diags/eq_location_optimisation/'];
 else
-    dirname = '../../../../invert/davidr/thesis_version2/diags/eq_location_optimisation/';
+    dirname = [path2thesis,'/diags/eq_location_optimisation/'];
     %dirname = '../../../thesis_version2/diags/eq_location_optimisation/'
     dirname_hypoDD_SVD = '..\..\..\concluding_papers\paper2\diags\runs2\Hypodd_SVD\HYPODD2\runs\orig_68eqonly\';
 end
@@ -108,14 +108,12 @@ Locs_hypoDDbest.not68x = tmphypoDDnot68(:,5);
 Locs_hypoDDbest.not68y = tmphypoDDnot68(:,6);
 Locs_hypoDDbest.not68z = tmphypoDDnot68(:,7);
 if strcmp(filesep,'/')
-    dirname = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/example_69eq_calaveras3';
+    dirname = [path2thesis,'/diags/eq_location_optimisation/example_69eq_calaveras3'];
 else
-    
-    
-    dirname = '..\..\..\thesis_version2/diags/eq_location_optimisation/example_69eq_calaveras3';
+    dirname = [path2thesis,'/diags/eq_location_optimisation/example_69eq_calaveras3'];
 end
 %dirname = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/CalaverasMultiSim/CWI/stat10';
-[CWIstats_best,Locs_CWIbest,fh] = plot_outcomes_cwi(dirname,plot_struct);
+[CWIstats_best,Locs_CWIbest,fh] = plot_outcomes_cwi(dirname,plot_struct,path2thesis);
 for i = 1:length(fh)
     close(fh(i))
 end
@@ -277,7 +275,7 @@ for j = 1: length(statlist)
     else
[…]

### 2012-12-17 paper2/diags/synth3Dmulti/wrap_plot_outcomes.m

@@ -102,7 +102,7 @@ set(gca,'xticklabel',ticklabelstr)
 set(gca,'fontsize',fsize)
 set(gca,'ylim',[0 40],'xlim',[1 10],'units','centimeters')
 ylabel('$\Delta_\mu$\,(m)','fontsize',fsize,'Interpreter','LaTex')
-
+xlabel('Number of constraints','fontsize',fsize)
 % sh(3) = subplot(3,1,3)
 % stdvals_all(ind_all) = NaN;
 % stdvals_best(ind_best) = NaN;

### 2012-12-17 paper2/paper2.tex
more changes

@@
 $f_{dom}=2.5$\,Hz corresponds to roughly 25\,m.
-\begin{figure}
-\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
-optimization event locations are shown in triangles and circles,
-respectively.} \label{fig-2D50eq-relocation_eg1}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N= 2
-\epsilon(\delta_t)$.
- Actual and optimization event locations
-are shown in triangles and circles, respectively.}
-\label{fig-2D50eq-relocation_eg3}
-\end{figure}
+
 \citet{dr_Robinson11a} demonstrates that the noise on CWI estimates
@@
 chosen starting locations.
-
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\noindent\includegraphics[width =
-20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\caption{Example 3 - Statistical measures of error in the
- solutions for the 2D synthetic cases when all and best
-optimization results are considered. The statistics $\Delta_{max}$
-and $\Delta_\mu$  are the maximum and mean coordinate error,
-respectively. The bottom subplot shows the average minimum number of
-branches required to link the 2450 pairs.}
- \label{fig:optimisationresults-2Dsynth}
-\end{figure}
 
@@
 
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\noindent\includegraphics[width =
-20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\caption{Example 4 - Statistical measures of error in the
-optimization solutions for the 3D synthetic cases when all (gray)
-and best (black) results are considered. The statistics
-$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
-error, respectively. The absence of the gray and black lines below
-60\% and 30\% indicates a breakdown in the solutions when all or
-best optimization result(s) are considered, respectively.}
-\label{fig:optimisationresults-3Dsynth}
-\end{figure}
-
 When 70\% of the direct constraints are considered all optimization
@@
 
-\begin{figure}
-\noindent\includegraphics[width =
-20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Map showing location of the Calaveras
-cluster (white star) and 805 seismic stations (black triangles).}
-\label{fig:-eqopti-California-Calaveras}
-\end{figure}
-
-\begin{table}
-\caption{Location examples for the 68 Calaveras earthquakes.}
-\label{tab:examples}
-\begin{tabular}{ll}
-\hline
-Example 5 & Comparison of CWI, catalogue and hypoDD \\
- & locations (using all available data). \\
-Example 6 & Exploration of station dependance for CWI and \\
- & hypoDD (using a subset of data). \\
-Example 7 & Combined use of CWI and travel time data \\
-& with all and a reduced number of stations. \\
-Example 8 & Combined use of CWI and travel time data \\
- & when travel times constrain only 50\% of the events. \\
- \hline
-\end{tabular}
-\end{table}
-
 \subsection{Example 5 - comparison of CWI, catalogue and hypoDD locations}
@@
  Figure \ref{fig-69Calaverasevents_eg1}.
-
-%%=======================================================================================
-% This is the original figure using HypoDD with LSQR
-%\begin{figure*}
-%\includegraphics{diags/CalaverasLoc1.eps}
-%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-%308 events (column 2) and CWI example 1 (column 3).
-%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
-%blue events are shown for the purpose of orientation only.}
-%\label{fig-69Calaverasevents_eg1}
-%\end{figure*}
-
-% Now we have the SVD version
-\begin{figure*}
-\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\caption{Example 5 - Comparison of relative earthquake locations
-using three different methods: catalogue location (column 1), CWI
-(column 2) and hypoDD (column 3). Note that in the case of the
-hypoDD and CWI inversions we consider only the 68 earthquakes in
-black, the gray catalogue locations for the remaining 240 (308-68)
-earthquakes are shown for the purpose of orientation only.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure*}
-%%=======================================================================================
 
@@
 optimum relative locations using Polak-Ribiere optimization.
-
-\begin{table}
-\caption[Conditions for identifying unsuitable waveforms when
-applying CWI] {Conditions used to identify unsuitable waveforms
-before applying CWI \citep[Originally published as Table
-5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
-\begin{tabular}{|l|p{0.7\textwidth}|}
-\hline
- & \textbf{condition} \\
-\hline
-1 & waveform is clearly corrupted \\
-2 & waveform indicates recording of more then one event \\
-3 & signal to noise ratio is obviously low \\
-4 & there is insufficient coda recorded after the \\
- & first arrivals \\
-5 & there is insufficient recording before the arrivals \\
- &  (needed for accurate noise energy estimate) \\
-\hline
-\end{tabular}
-\end{table}
 
@@
 
-\begin{figure}
-\noindent\includegraphics[width =
-20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-\caption{Location of the 10 stations (triangles) used to relocate
-the Calaveras events in Example 6 to 8. Stations are removed one at
-a time according to the order in Table
-\ref{tab:Calaveras-stationremoval} and the events relocated. The
-events are indicated with black circles.}
-\label{fig:-eqopti-Calaveras-substations}
-\end{figure}
-
-\begin{table}
-\caption{Stations considered when exploring the impact of reduced
-station coverage.} \label{tab:Calaveras-stationremoval}
-\begin{tabular}{|r|l|}
-\hline
-Number of & Station Names\\
-Stations  & \\
-\hline
-10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
-9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
-8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
-7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
-6  & CCO, JCB, JST, CMH, HSP, JAL \\
-5  & CCO, JCB, JST, CMH, HSP \\
-4  & CCO, JCB, JST, CMH \\
-3  & CCO, JCB, JST \\
-2  & CCO, JCB \\
-1  & CCO \\
-\hline
-\end{tabular}
-\end{table}
-
 CWI locations are illustrated in Figure \ref{fig-CWIreducesstats}
@@
 
-\begin{figure*}
-\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{Example 6 - CWI relative locations with reduced stations.}
-\label{fig-CWIreducesstats}
-\end{figure*}
-
 Figure \ref{fig-HYPODDreducesstats} illustrates the hypoDD inversion
@@
 Figure \ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
-
-%%=========================================================================
-% this is the original version using hypoDD with LSQ
-%\begin{figure*}
-%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
-%\caption{....}
-%\label{fig-HYPODDreducesstats}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure*}
-\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\caption{Example 6 - HypoDD (SVD) relative locations with reduced
-stations.} \label{fig-HYPODDreducesstats}
-\end{figure*}
-%%=========================================================================
 
@@
 
-%%=========================================================================
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
-%\caption{Statistics on coordinate differences for reduced station inversions. Differences
-%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-%locations for all 308 events. The top subplot illustrates the number of constrainable
-%events in the CWI and hypoDD inversions as a function of the stations considered.}
-%\label{fig-statremoval_summarystats}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\noindent\includegraphics[width =
-20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
-Number of constrainable events $nE$ in the CWI and hypoDD inversions
-as a function of the stations considered (top). Mean (middle) and
-maximum (bottom) of the difference computed between the reduced
-station inversion results (CWI and hypoDD) and the complete hypoDD
-locations for all 308 events. } \label{fig-statremoval_summarystats}
-\end{figure}
-%%=========================================================================
-
 The remaining panels of Figure \ref{fig-statremoval_summarystats}
@@
 
-%%=========================================================================
-% This is the original version using hypoDD with LSQ
-% This is only makes sense for LSQR so we remove it from this manuscript
-%\begin{figure*}
-%\noindent\includegraphics{diags/CalaverasLoc5.eps}
-%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
-%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
-%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
-%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
-%\label{fig-68Calaverasevents_ttandcoda1}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
-locations using data form all stations (left) and 5 stations
-(right).} \label{fig-68Calaverasevents_ttandcoda1}
-\end{figure}
-
-%%=========================================================================
-
 \subsection{Example 8 - Combining CWI and travel times when the travel times constrain a limited number of events}
@@
 
-\begin{figure}
-\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-\caption{Cumulative number of aftershocks for the
-Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-using equation (\ref{eq:CumOmori}). The leftmost gray, middle black
-and rightmost gray lines signify aftershocks occurring before,
-during and after the deployment of a pseudo temporary array
-installed 4 days after the main shock and left for 150 days. A
-temporary deployment of this kind will record roughly 50\% of the
-aftershocks in the 1000 days following the mainshock. }
-\label{fig:Omorifigure}
-\end{figure}
-
 With this idea of a temporary deployment in mind we have another
@@
 earthquakes in regions with limited station coverage.
-
-%%=========================================================================
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics{diags/CalaverasLoc6.eps}
-%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
-%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
-%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
-%relocation only (i.e. no CWI) using ........}
-%\label{fig-68Calaverasevents_ttsubsetandcoda1}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
-\caption{Example 8 - Mimicking the deployment of a temporary network
-by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Relative locations are shown for the combined CWI and travel
-time inversion (left) and the inversion with travel times only
-(right) Only by combining the data is it possible to locate all 68
-events. Furthermore, combining the data leads to a solution more
-consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
-\label{fig-68Calaverasevents_ttsubsetandcoda1}
-\end{figure}
-%%=========================================================================
 
@@
 
+\clearpage
+
+%%=======================================================================================
+% Table 1
+
+\begin{table}
+\caption{Location examples for the 68 Calaveras earthquakes.}
+\label{tab:examples}
+\begin{tabular}{ll}
+\hline
+Example 5 & Comparison of CWI, catalogue and hypoDD \\
+ & locations (using all available data). \\
+Example 6 & Exploration of station dependance for CWI and \\
+ & hypoDD (using a subset of data). \\
+Example 7 & Combined use of CWI and travel time data \\
+& with all and a reduced number of stations. \\
+Example 8 & Combined use of CWI and travel time data \\
+ & when travel times constrain only 50\% of the events. \\
+ \hline
+\end{tabular}
+\end{table}
+
+%%=======================================================================================
+% Table 2
+
+\begin{table}
+\caption[Conditions for identifying unsuitable waveforms when
+applying CWI] {Conditions used to identify unsuitable waveforms
+before applying CWI \citep[Originally published as Table
+5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
+\begin{tabular}{|l|p{0.7\textwidth}|}
+\hline
+ & \textbf{condition} \\
+\hline
+1 & waveform is clearly corrupted \\
+2 & waveform indicates recording of more then one event \\
+3 & signal to noise ratio is obviously low \\
+4 & there is insufficient coda recorded after the \\
+ & first arrivals \\
+5 & there is insufficient recording before the arrivals \\
+ &  (needed for accurate noise energy estimate) \\
+\hline
+\end{tabular}
+\end{table}
+
+%%=======================================================================================
+% Table 3
+
+\begin{table}
+\caption{Stations considered when exploring the impact of reduced
+station coverage.} \label{tab:Calaveras-stationremoval}
+\begin{tabular}{|r|l|}
+\hline
+Number of & Station Names\\
+Stations  & \\
+\hline
+10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
+9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
+8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
+7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
+6  & CCO, JCB, JST, CMH, HSP, JAL \\
+5  & CCO, JCB, JST, CMH, HSP \\
+4  & CCO, JCB, JST, CMH \\
+3  & CCO, JCB, JST \\
+2  & CCO, JCB \\
+1  & CCO \\
+\hline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+%%=======================================================================================
+
+%Figure 1
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
+\includegraphics[width = 20pc]{Figure1_c.eps}
+\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
+optimization event locations are shown in triangles and circles,
+respectively.} \label{fig-2D50eq-relocation_eg1}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 2
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
+\includegraphics[width = 20pc]{Figure2_c.eps}
+\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N= 2
+\epsilon(\delta_t)$.
+ Actual and optimization event locations
+are shown in triangles and circles, respectively.}
+\label{fig-2D50eq-relocation_eg3}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 3
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+\noindent\includegraphics[width=20pc]{Figure3_c.eps}
+\caption{Example 3 - Statistical measures of error in the
+ solutions for the 2D synthetic cases when all and best
+optimization results are considered. The statistics $\Delta_{max}$
+and $\Delta_\mu$  are the maximum and mean coordinate error,
+respectively. The bottom subplot shows the average minimum number of
+branches required to link the 2450 pairs.}
+ \label{fig:optimisationresults-2Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 4
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+\noindent\includegraphics[width=20pc]{Figure4_c.eps}
+\caption{Example 4 - Statistical measures of error in the
+optimization solutions for the 3D synthetic cases when all (gray)
+and best (black) results are considered. The statistics
+$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
+error, respectively. The absence of the gray and black lines below
+60\% and 30\% indicates a breakdown in the solutions when all or
+best optimization result(s) are considered, respectively.}
+\label{fig:optimisationresults-3Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 5
+\begin{figure}
+\noindent\includegraphics[width =
+20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
+\caption{Map showing location of the Calaveras cluster (white star)
+and 805 seismic stations (black triangles).}
+\label{fig:-eqopti-California-Calaveras}
+\end{figure}
+
+%%=======================================================================================
+% Figure 6
+
+% This is the original figure using HypoDD with LSQR
+%\begin{figure*}
+%\includegraphics{diags/CalaverasLoc1.eps}
+%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
+%308 events (column 2) and CWI example 1 (column 3).
+%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
+%blue events are shown for the purpose of orientation only.}
+%\label{fig-69Calaverasevents_eg1}
+%\end{figure*}
+
+% Now we have the SVD version
+\begin{figure*}
+\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
+\caption{Example 5 - Comparison of relative earthquake locations
+using three different methods: catalogue location (column 1), CWI
+(column 2) and hypoDD (column 3). Note that in the case of the
+hypoDD and CWI inversions we consider only the 68 earthquakes in
+black, the gray catalogue locations for the remaining 240 (308-68)
+earthquakes are shown for the purpose of orientation only.}
+\label{fig-69Calaverasevents_eg1}
+\end{figure*}
+%%=======================================================================================
+
+% Figure 7
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
+\noindent\includegraphics[width=20pc]{Figure7.eps} \caption{Location
+of the 10 stations (triangles) used to relocate the Calaveras events
+in Example 6 to 8. Stations are removed one at a time according to
+the order in Table \ref{tab:Calaveras-stationremoval} and the events
+relocated. The events are indicated with black circles.}
+\label{fig:-eqopti-Calaveras-substations}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 8
+\begin{figure*}
+\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
+\caption{Example 6 - CWI relative locations with reduced stations.}
+\label{fig-CWIreducesstats}
+\end{figure*}
+
+%%=========================================================================
+% Figure 9
+
+% this is the original version using hypoDD with LSQ
+%\begin{figure*}
+%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
+%\caption{....}
+%\label{fig-HYPODDreducesstats}
+%\end{figure*}
+
+% This is the version using hypoDD with SVD
+\begin{figure*}
+\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
+\caption{Example 6 - HypoDD (SVD) relative locations with reduced
+stations.} \label{fig-HYPODDreducesstats}
+\end{figure*}
+%%=========================================================================
+
+%Figure 10
+
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
+%\caption{Statistics on coordinate differences for reduced station inversions. Differences
+%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
+%locations for all 308 events. The top subplot illustrates the number of constrainable
+%events in the CWI and hypoDD inversions as a function of the stations considered.}
+%\label{fig-statremoval_summarystats}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+\noindent\includegraphics[width =
+20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
+Number of constrainable events $nE$ in the CWI and hypoDD inversions
+as a function of the stations considered (top). Mean (middle) and
+maximum (bottom) of the difference computed between the reduced
+station inversion results (CWI and hypoDD) and the complete hypoDD
+locations for all 308 events. } \label{fig-statremoval_summarystats}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 11
+
+% This is the original version using hypoDD with LSQ
+% This is only makes sense for LSQR so we remove it from this manuscript
+%\begin{figure*}
+%\noindent\includegraphics{diags/CalaverasLoc5.eps}
+%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
+%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
+%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
+%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
+%\label{fig-68Calaverasevents_ttandcoda1}
+%\end{figure*}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
+\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
+locations using data form all stations (left) and 5 stations
+(right).} \label{fig-68Calaverasevents_ttandcoda1}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 12
+
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
+\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
+\caption{Cumulative number of aftershocks for the
+Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
+using equation (\ref{eq:CumOmori}). The leftmost gray, middle black
+and rightmost gray lines signify aftershocks occurring before,
+during and after the deployment of a pseudo temporary array
+installed 4 days after the main shock and left for 150 days. A
+temporary deployment of this kind will record roughly 50\% of the
+aftershocks in the 1000 days following the mainshock. }
+\label{fig:Omorifigure}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 13
+
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics{diags/CalaverasLoc6.eps}
+%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
+%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
+%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
+%relocation only (i.e. no CWI) using ........}
+%\label{fig-68Calaverasevents_ttsubsetandcoda1}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
+\caption{Example 8 - Mimicking the deployment of a temporary network
+by ignoring data from all but station CCO for 50\% (or 34) of the
+events. Relative locations are shown for the combined CWI and travel
+time inversion (left) and the inversion with travel times only
+(right) Only by combining the data is it possible to locate all 68
+events. Furthermore, combining the data leads to a solution more
+consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
+\label{fig-68Calaverasevents_ttsubsetandcoda1}
+\end{figure}
+%%=========================================================================
+
 \appendix
+\clearpage
 

### 2012-12-17 events/matlab/plot_outcomes_cwi.m
updated these files so that they accept a path to thesis directory as well

@@ -1,4 +1,4 @@
-function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct)
+function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct,path2thesis)
 % This function plots the CWI outcomes. It is typically called by 
 % batch_doplots. 
 %
@@ -6,6 +6,8 @@ function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct)
 % dirname       [char]  director where hypoDD outputs are stored. Note that 
 %               eps figures are saved here as well. 
 % plot_struct   [structure] settings for the figures. 
+% path2thesis   [string] path to where the thesis is stored on the macjhine
+%               being used
 % 
 % OUTPUTS: 
 % CWIstats      [structure] contains statistics of interest
@@ -53,9 +55,9 @@ msize = plot_struct.msize;
 
 
 if strcmp(filesep,'/') % i.e. in Linus
-    parentdir = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
 else
-    parentdir = 'c:/datafiles/workstuff/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
     %error('Not yet operation for the Windows machine')
 end
 

### 2012-12-17 events/matlab/plot_outcomes_cwi_cartesian.m

@@ -1,4 +1,4 @@
-function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct)
+function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct,path2thesis)
 % This function plots the CWI outcomes. It is typically called by 
 % batch_doplots. 
 %
@@ -6,6 +6,8 @@ function [CWIstats,Locs,fh] = plot_outcomes_cwi(dirname,plot_struct)
 % dirname       [char]  director where hypoDD outputs are stored. Note that 
 %               eps figures are saved here as well. 
 % plot_struct   [structure] settings for the figures. 
+% path2thesis   [string] path to where the thesis is stored on the macjhine
+%               being used
 %
 % OUTPUTS: 
 % CWIstats      [structure] contains statistics of interest
@@ -54,9 +56,9 @@ msize = plot_struct.msize;
 
 
 if strcmp(filesep,'/') % i.e. in Linus
-    parentdir = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
 else
-    parentdir = 'c:/datafiles/workstuff/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
     %error('Not yet operation for the Windows machine')
 end
 

### 2012-12-17 events/matlab/plot_outcomes_hypoDD.m

@@ -1,4 +1,4 @@
-function [hypoDDstats,Locs,fh] = plot_outcomes_hypoDD(dirname,plot_struct,colorchoice)
+function [hypoDDstats,Locs,fh] = plot_outcomes_hypoDD(dirname,plot_struct,colorchoice,path2thesis)
 % This function plots the hypoDD outcomes. It is typically called by 
 % batch_doplots. 
 %
@@ -6,6 +6,9 @@ function [hypoDDstats,Locs,fh] = plot_outcomes_hypoDD(dirname,plot_struct,colorc
 % dirname       [char]  director where hypoDD outputs are stored. Note that 
 %               eps figures are saved here as well. 
 % plot_struct   [structure] settings for the figures. 
+% colorchoice 
+% path2thesis   [string] path to where the thesis is stored on the macjhine
+%               being used
 %
 % OUTPUTS: 
 % hypoDDstats   [structure] contains statistics of interest
@@ -27,7 +30,7 @@ function [hypoDDstats,Locs,fh] = plot_outcomes_hypoDD(dirname,plot_struct,colorc
 % David Robinson
 % 9 December 2009
 
-if nargin ==2
+if nargin ==2 | isempty(colorchoice)
     colorchoice = 'c';
 end
 
@@ -68,9 +71,9 @@ fsize = plot_struct.fsize;
 msize = plot_struct.msize;
 
 if strcmp(filesep,'/') % i.e. in Linus
-    parentdir = '/export/storage/davidr/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
 else 
-    parentdir = 'c:/datafiles/workstuff/sandpit/davidr/thesis_version2/diags/eq_location_optimisation/';
+    parentdir = [path2thesis,'/diags/eq_location_optimisation/'];
 %    error('Not yet operation for the Windows machine')
 end
 

### 2012-12-21 paper2/paper2.tex
commiting final changes prior to paper submission

@@
 
-\clearpage
-
-%%=======================================================================================
-
-%Figure 1
-\begin{figure}
-%\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-\includegraphics[width = 20pc]{Figure1_c.eps}
-\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
-optimization event locations are shown in triangles and circles,
-respectively.} \label{fig-2D50eq-relocation_eg1}
-\end{figure}
-
-%%=======================================================================================
-
-%Figure 2
-\begin{figure}
-%\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-\includegraphics[width = 20pc]{Figure2_c.eps}
-\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N= 2
-\epsilon(\delta_t)$.
- Actual and optimization event locations
-are shown in triangles and circles, respectively.}
-\label{fig-2D50eq-relocation_eg3}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 3
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\noindent\includegraphics[width=20pc]{Figure3_c.eps}
-\caption{Example 3 - Statistical measures of error in the
- solutions for the 2D synthetic cases when all and best
-optimization results are considered. The statistics $\Delta_{max}$
-and $\Delta_\mu$  are the maximum and mean coordinate error,
-respectively. The bottom subplot shows the average minimum number of
-branches required to link the 2450 pairs.}
- \label{fig:optimisationresults-2Dsynth}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 4
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\noindent\includegraphics[width=20pc]{Figure4_c.eps}
-\caption{Example 4 - Statistical measures of error in the
-optimization solutions for the 3D synthetic cases when all (gray)
-and best (black) results are considered. The statistics
-$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
-error, respectively. The absence of the gray and black lines below
-60\% and 30\% indicates a breakdown in the solutions when all or
-best optimization result(s) are considered, respectively.}
-\label{fig:optimisationresults-3Dsynth}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 5
-\begin{figure}
-\noindent\includegraphics[width =
-20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\caption{Map showing location of the Calaveras cluster (white star)
-and 805 seismic stations (black triangles).}
-\label{fig:-eqopti-California-Calaveras}
-\end{figure}
-
-%%=======================================================================================
-% Figure 6
-
-% This is the original figure using HypoDD with LSQR
-%\begin{figure*}
-%\includegraphics{diags/CalaverasLoc1.eps}
-%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-%308 events (column 2) and CWI example 1 (column 3).
-%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
-%blue events are shown for the purpose of orientation only.}
-%\label{fig-69Calaverasevents_eg1}
-%\end{figure*}
-
-% Now we have the SVD version
-\begin{figure*}
-\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\caption{Example 5 - Comparison of relative earthquake locations
-using three different methods: catalogue location (column 1), CWI
-(column 2) and hypoDD (column 3). Note that in the case of the
-hypoDD and CWI inversions we consider only the 68 earthquakes in
-black, the gray catalogue locations for the remaining 240 (308-68)
-earthquakes are shown for the purpose of orientation only.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure*}
-%%=======================================================================================
-
-% Figure 7
-\begin{figure}
-%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-\noindent\includegraphics[width=20pc]{Figure7.eps} \caption{Location
-of the 10 stations (triangles) used to relocate the Calaveras events
-in Example 6 to 8. Stations are removed one at a time according to
-the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated. The events are indicated with black circles.}
-\label{fig:-eqopti-Calaveras-substations}
-\end{figure}
-
-%%=======================================================================================
-
-%Figure 8
-\begin{figure*}
-\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\caption{Example 6 - CWI relative locations with reduced stations.}
-\label{fig-CWIreducesstats}
-\end{figure*}
-
-%%=========================================================================
-% Figure 9
-
-% this is the original version using hypoDD with LSQ
-%\begin{figure*}
-%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
-%\caption{....}
-%\label{fig-HYPODDreducesstats}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure*}
-\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\caption{Example 6 - HypoDD (SVD) relative locations with reduced
-stations.} \label{fig-HYPODDreducesstats}
-\end{figure*}
-%%=========================================================================
-
-%Figure 10
-
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
-%\caption{Statistics on coordinate differences for reduced station inversions. Differences
-%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-%locations for all 308 events. The top subplot illustrates the number of constrainable
-%events in the CWI and hypoDD inversions as a function of the stations considered.}
-%\label{fig-statremoval_summarystats}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\noindent\includegraphics[width =
-20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps} \caption{Example 6 -
-Number of constrainable events $nE$ in the CWI and hypoDD inversions
-as a function of the stations considered (top). Mean (middle) and
-maximum (bottom) of the difference computed between the reduced
-station inversion results (CWI and hypoDD) and the complete hypoDD
-locations for all 308 events. } \label{fig-statremoval_summarystats}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 11
-
-% This is the original version using hypoDD with LSQ
-% This is only makes sense for LSQR so we remove it from this manuscript
-%\begin{figure*}
-%\noindent\includegraphics{diags/CalaverasLoc5.eps}
-%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
-%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
-%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
-%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
-%\label{fig-68Calaverasevents_ttandcoda1}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
-locations using data form all stations (left) and 5 stations
-(right).} \label{fig-68Calaverasevents_ttandcoda1}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 12
-
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
-\caption{Cumulative number of aftershocks for the
-Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-using equation (\ref{eq:CumOmori}). The leftmost gray, middle black
-and rightmost gray lines signify aftershocks occurring before,
-during and after the deployment of a pseudo temporary array
-installed 4 days after the main shock and left for 150 days. A
-temporary deployment of this kind will record roughly 50\% of the
-aftershocks in the 1000 days following the mainshock. }
-\label{fig:Omorifigure}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 13
-
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics{diags/CalaverasLoc6.eps}
-%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
-%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
-%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
-%relocation only (i.e. no CWI) using ........}
-%\label{fig-68Calaverasevents_ttsubsetandcoda1}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
-\caption{Example 8 - Mimicking the deployment of a temporary network
-by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Relative locations are shown for the combined CWI and travel
-time inversion (left) and the inversion with travel times only
-(right) Only by combining the data is it possible to locate all 68
-events. Furthermore, combining the data leads to a solution more
-consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
-\label{fig-68Calaverasevents_ttsubsetandcoda1}
-\end{figure}
-%%=========================================================================
-
-\appendix
-\clearpage
-
-\section{The likelihood}
-\label{sec-Appendix-noisylikelihood}
-
-The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-used in equation (\ref{eq:-bayesian-noisyform}) is given by
-\begin{equation}
-\begin{array}{l}
-\label{eq-likelihood-int}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
-A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
-\hspace{3em} \times \int_0^\infty
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
-d\widetilde{\delta}_{CWI}
-\end{array}
-\end{equation}
-where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
-of noise,
-\begin{equation}
-\label{eq:Adefn}
-A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
-\end{equation}
-\begin{equation}
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
-\end{equation}
-\begin{equation}
-\label{eq:Cdefn}
-C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
-\end{equation}
-\begin{equation}
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
-\end{equation}
-and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
-\begin{equation}
-\label{eq-cummulative-Gaussian}
-\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
-\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
-\end{equation}
-\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
-in equation (\ref{eq:Adefn}) are defined by the expressions
-\begin{equation}
-\label{eq:mu1}
-\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
-\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
-\end{equation}
-and
-\begin{equation}
-\label{eq:sigma1}
-\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
-a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
-\end{equation}
-with coefficients $a_1$ to $a_5$ and $c$ defined in Table
-\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
-$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
-finding the values which minimize the difference in a least squares
-sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
-computed from the waveforms and the positively bounded Gaussian
-density function
-\begin{equation}
-\label{eq-likelihood-noisydata-pdf-orig}
-\begin{array}{l}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
-\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
-e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
-\end{array}
-\end{equation}
-with $\widetilde{\delta}_{CWIN} \geq 0$.
-
 \begin{table}
@@
 \end{table}
+
+\clearpage
+
+%%=======================================================================================
+
+%Figure 1
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
+\includegraphics[width = 20pc]{Figure1_c.eps}
+\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
+optimization event locations are shown in triangles and circles,
+respectively.} \label{fig-2D50eq-relocation_eg1}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 2
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
+\includegraphics[width = 20pc]{Figure2_c.eps}
+\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N= 2
+\epsilon(\delta_t)$.
+ Actual and optimization event locations
+are shown in triangles and circles, respectively.}
+\label{fig-2D50eq-relocation_eg3}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 3
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+\noindent\includegraphics[width=20pc]{Figure3_c.eps}
+\caption{Example 3 - Statistical measures of error in the
+ solutions for the 2D synthetic cases when all and best
+optimization results are considered. The statistics $\Delta_{max}$
+and $\Delta_\mu$  are the maximum and mean coordinate error,
+respectively. The bottom subplot shows the average minimum number of
+branches required to link the 2450 pairs.}
+ \label{fig:optimisationresults-2Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 4
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+\noindent\includegraphics[width=20pc]{Figure4_c.eps}
+\caption{Example 4 - Statistical measures of error in the
+optimization solutions for the 3D synthetic cases when all (gray)
+and best (black) results are considered. The statistics
+$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
+error, respectively. The absence of the gray and black lines below
+60\% and 30\% indicates a breakdown in the solutions when all or
+best optimization result(s) are considered, respectively.}
+\label{fig:optimisationresults-3Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 5
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
+\noindent\includegraphics[width=20pc]{Figure5.eps} \caption{Map
+showing location of the Calaveras cluster (white star) and 805
+seismic stations (black triangles).}
+\label{fig:-eqopti-California-Calaveras}
+\end{figure}
+
+%%=======================================================================================
+% Figure 6
+
+% This is the original figure using HypoDD with LSQR
+%\begin{figure*}
+%\includegraphics{diags/CalaverasLoc1.eps}
+%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
+%308 events (column 2) and CWI example 1 (column 3).
+%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
+%blue events are shown for the purpose of orientation only.}
+%\label{fig-69Calaverasevents_eg1}
+%\end{figure*}
+
+% Now we have the SVD version
+\begin{figure*}
+%\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
+\includegraphics{Figure6_bw.eps}
+\caption{Example 5 - Comparison of relative earthquake locations
+using three different methods: catalogue location (column 1), CWI
+(column 2) and hypoDD (column 3). Note that in the case of the
+hypoDD and CWI inversions we consider only the 68 earthquakes in
+black, the gray catalogue locations for the remaining 240 (308-68)
+earthquakes are shown for the purpose of orientation only.}
+\label{fig-69Calaverasevents_eg1}
+\end{figure*}
+%%=======================================================================================
+
+% Figure 7
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
+\noindent\includegraphics[width=20pc]{Figure7.eps} \caption{Location
+of the 10 stations (triangles) used to relocate the Calaveras events
+in Example 6 to 8. Stations are removed one at a time according to
+the order in Table \ref{tab:Calaveras-stationremoval} and the events
+relocated. The events are indicated with black circles.}
+\label{fig:-eqopti-Calaveras-substations}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 8
+\begin{figure*}
+%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
+\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
+\caption{Example 6 - CWI relative locations with reduced stations.}
+\label{fig-CWIreducesstats}
+\end{figure*}
+
+%%=========================================================================
+% Figure 9
+
+% this is the original version using hypoDD with LSQ
+%\begin{figure*}
+%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
+%\caption{....}
+%\label{fig-HYPODDreducesstats}
+%\end{figure*}
+
+% This is the version using hypoDD with SVD
+\begin{figure*}
+%\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
+\includegraphics[height = 25pc]{Figure9_bw.eps}
+\caption{Example 6 - HypoDD (SVD) relative locations with reduced
+stations.} \label{fig-HYPODDreducesstats}
+\end{figure*}
+%%=========================================================================
+
+%Figure 10
+
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
+%\caption{Statistics on coordinate differences for reduced station inversions. Differences
+%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
+%locations for all 308 events. The top subplot illustrates the number of constrainable
+%events in the CWI and hypoDD inversions as a function of the stations considered.}
+%\label{fig-statremoval_summarystats}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
+\noindent\includegraphics[width=20pc]{Figure10_c.eps}
+\caption{Example 6 - Number of constrainable events $nE$ in the CWI
+and hypoDD inversions as a function of the stations considered
+(top). Mean (middle) and maximum (bottom) of the difference computed
+between the reduced station inversion results (CWI and hypoDD) and
+the complete hypoDD locations for all 308 events. }
+\label{fig-statremoval_summarystats}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 11
+
+% This is the original version using hypoDD with LSQ
+% This is only makes sense for LSQR so we remove it from this manuscript
+%\begin{figure*}
+%\noindent\includegraphics{diags/CalaverasLoc5.eps}
+%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
+%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
+%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
+%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
+%\label{fig-68Calaverasevents_ttandcoda1}
+%\end{figure*}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
+\includegraphics{Figure11_bw.eps}
+\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
+locations using data form all stations (left) and 5 stations
+(right).} \label{fig-68Calaverasevents_ttandcoda1}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 12
+
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
+\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
+\caption{Cumulative number of aftershocks for the
+Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
+using equation (\ref{eq:CumOmori}). The leftmost red, middle blue
+and rightmost red lines signify aftershocks occurring before, during
+and after the deployment of a pseudo temporary array installed 4
+days after the main shock and left for 150 days. A temporary
+deployment of this kind will record roughly 50\% of the aftershocks
+in the 1000 days following the mainshock. } \label{fig:Omorifigure}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 13
+
+% This is the original version using hypoDD with LSQ
+%\begin{figure}
+%\noindent\includegraphics{diags/CalaverasLoc6.eps}
+%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
+%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
+%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
+%relocation only (i.e. no CWI) using ........}
+%\label{fig-68Calaverasevents_ttsubsetandcoda1}
+%\end{figure}
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
+\includegraphics{Figure13_bw.eps}
+\caption{Example 8 - Mimicking the deployment of a temporary network
+by ignoring data from all but station CCO for 50\% (or 34) of the
+events. Relative locations are shown for the combined CWI and travel
+time inversion (left) and the inversion with travel times only
+(right). Only by combining the data is it possible to locate all 68
+events. Furthermore, combining the data leads to a solution more
+consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
+\label{fig-68Calaverasevents_ttsubsetandcoda1}
+\end{figure}
+%%=========================================================================
+
+\appendix
+\clearpage
+
+\section{The likelihood}
+\label{sec-Appendix-noisylikelihood}
+
+The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
+used in equation (\ref{eq:-bayesian-noisyform}) is given by
+\begin{equation}
+\begin{array}{l}
+\label{eq-likelihood-int}
+P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
+A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
+\hspace{3em} \times \int_0^\infty
+B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
+D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
+d\widetilde{\delta}_{CWI}
+\end{array}
+\end{equation}
+where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
+of noise,
+\begin{equation}
+\label{eq:Adefn}
+A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
+\end{equation}
+\begin{equation}
+B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
+\end{equation}
+\begin{equation}
+\label{eq:Cdefn}
+C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
+\end{equation}
+\begin{equation}
+D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
+\end{equation}
+and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
+\begin{equation}
+\label{eq-cummulative-Gaussian}
+\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
+\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
+\end{equation}
+\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
+in equation (\ref{eq:Adefn}) are defined by the expressions
+\begin{equation}
+\label{eq:mu1}
+\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
+\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
+\end{equation}
+and
+\begin{equation}
+\label{eq:sigma1}
+\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
+a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
+\end{equation}
+with coefficients $a_1$ to $a_5$ and $c$ defined in Table
+\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
+$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
+finding the values which minimize the difference in a least squares
+sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
+computed from the waveforms and the positively bounded Gaussian
+density function
+\begin{equation}
+\label{eq-likelihood-noisydata-pdf-orig}
+\begin{array}{l}
+P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
+\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
+e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
+\end{array}
+\end{equation}
+with $\widetilde{\delta}_{CWIN} \geq 0$.
 

### 2012-12-21 paper2/diags/plot_calaveras_loc2.m
commiting final changes prior to paper submission

@@ -85,8 +85,10 @@ if strcmp(filesep,'/')
 else
     dirname = [path2thesis,'/diags/eq_location_optimisation/'];
     %dirname = '../../../thesis_version2/diags/eq_location_optimisation/'
-    dirname_hypoDD_SVD = '..\..\..\concluding_papers\paper2\diags\runs2\Hypodd_SVD\HYPODD2\runs\orig_68eqonly\';
+    %dirname_hypoDD_SVD = '..\..\..\concluding_papers\paper2\diags\runs2\Hypodd_SVD\HYPODD2\runs\orig_68eqonly\';
+    dirname_hypoDD_SVD = '.\runs2\Hypodd_SVD\HYPODD2\runs\orig_68eqonly\';
 end
+
 % Get the original best hypoDD locations (i.e. those where we used LSQR)
 tmphypoDD68 = load([dirname,'hypoDD_loc68.txt']);
 Locs_hypoDDbest_LSQR.relocx = tmphypoDD68(:,5);
@@ -242,8 +244,8 @@ set(gca,'fontsize',plot_struct.fsize)
 set(gca,'units','centimeters')
 set(gca,'position',[ax_start+2*awidth+2*hgap, ay_start, awidth, aheight])
 
-print -depsc CalaverasLoc1_hypoDD_SVD.eps
-
+%print -depsc CalaverasLoc1_hypoDD_SVD.eps
+print -depsc ../Figure6_bw.eps
 
 %% Figure 2 - CWI Reduces Stations
 % NO NEED TO MAKE THIS AGAIN SINCE IT DOESN'T CHANGE
@@ -429,8 +431,8 @@ set(gcf,'units','centimeters')
 set(gcf,'position',[5, 5, 26, 12.5],'PaperOrientation','Portrait')
 set(gcf,'PaperPosition',[0.6345    6.3452   27   15.2284])
 
-print -depsc CalaverasLoc3_hypoDD_SVD.eps
-
+%print -depsc CalaverasLoc3_hypoDD_SVD.eps
+print -depsc ../Figure9_bw.eps
 
 
 %% Figure 4 - statistical comparison of CWI and Travel Times
@@ -491,30 +493,30 @@ end
 sh = [];
 figure
 sh(1) = subplot(3,1,1); 
-hCWI = plot(station_counts,CWIstats_nE,'color',c2,'linewidth',2);
+hCWI_s1 = plot(station_counts,CWIstats_nE,'color',c2,'linewidth',2);
 hold on
[…]

### 2013-01-02 paper2/paper2.tex
a number of modifications after firs feedback from BSSA editorial office

@@
 %\documentclass[extra,mreferee]{gji}
-\documentclass[extra, onecolumn, doublespacing]{gji}
+%\documentclass[extra, onecolumn, doublespacing]{gji}
 %\documentclass[extra]{gji}
-
-\bibliographystyle{gji}
+%\RequirePackage{lineno}
+\documentclass[12pt,double]{article}
+
+%\bibliographystyle{agufull08} % Uncomment when generating bibliography
 \usepackage{timet}
 \usepackage[dvips]{graphicx}
-
-\title{Relocating a Cluster of Earthquakes Using a Single Seismic Station}
-\author[D.J. Robinson, M. Sambridge, R. Snieder and J Hauser]
-  {David J. Robinson$^{1,2}$, Malcolm Sambridge$^{1}$, Roel Snieder$^{3}$, Juerg Hauser$^{4}$ \\
-  $^1$ Research School of Earth Sciences, Australian National
-    University, Canberra ACT \emph{0200}, Australia, E-mail: david.robinson@anu.edu.au \\
-$^2$  Risk Analysis Methods, Geoscience Australia, GPO Box \emph{383} Canberra ACT \emph{2601} Australia, E-mail: david.robinson@ga.gov.au\\
-$^3$ Center for Wave Phenomena and Department of Geophysics, Colorado School of Mines, Golden CO \emph{80401-1887}, USA \\
-$^4$ CSIRO Earth Science and Resource Engineering, Dick Perry Av, Kensington WA \emph{6151} Australia}
-
-\date{Received 2012 Month Day; in original form 2012 Month Day}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\volume{200}
-\pubyear{2012}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{rotating}
+\usepackage{natbib}
+\usepackage{lineno}
+%\usepackage{titlesec}
+\linenumbers
+
+\linespread{1.5}
+
+\newcommand{\mitbf}[1]{  
+  \hbox{\mathversion{bold}$#1$}}  
+  \newcommand{\rmn}[1] {{\mathrm #1}}  
+  \newcommand{\itl}[1] {{\mathit #1}}  
+  \newcommand{\bld}[1] {{\mathbf #1}}
+
+%\titleformat{\section}
+%{\bf}{\thesection}{1em}{\MakeUppercase{#1}}
+
+%\date{Received 2012 Month Day; in original form 2012 Month Day}
+%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+%\volume{200}
+%\pubyear{2012}
 
@@
 
+\begin{centering}
+\LARGE{\textbf{Relocating a Cluster of Earthquakes Using a Single Seismic Station}} \\  
+\end{centering}
+\vspace{3em}
+\begin{centering}
+David J. Robinson, Malcolm Sambridge, Roel Snieder, Juerg Hauser \\
+\end{centering}
+
+\vspace{7em}
+\begin{tabular}{lp{0.6\textwidth}}
+ & \\
+David Robinson: & Earth Monitoring and Hazard Group \\
+ &  Geoscience Australia \\
+ & GPO Box \emph{383} \\
+ & Canberra ACT \emph{2601} Australia \\
+ & E-mail: david.robinson@ga.gov.au\\
+\end{tabular}
+
+\clearpage
 \label{firstpage}
 
-\maketitle
-
-\begin{summary}
+%\maketitle
+
+\vspace{2em}
+\begin{centering}
+\section*{Abstract}
+\end{centering}
 Coda waves arise from scattering to form the later arriving
@@
 
-\end{summary}
-
 %\begin{keywords}
@@
 
-\section{Introduction}
+\vspace{2em}
+\begin{centering}
+\section*{Introduction} 
+\end{centering}
 
@@
 uncertainty in the ISC (International Sesimological
-Centre\footnote{http://www.isc.ac.uk}) and PDE (National Earthquake
+Centre) and PDE (National Earthquake
 Information
-Center\footnote{http://earthquake.usgs.gov/earthquakes/eqarchives/epic/})
+Center)
 catalogues are generally around 25\,km horizontally and at least
-25\,km in depth.\footnote{Here the depth uncertainties of 25\,km
+25\,km in depth (Here the depth uncertainties of 25\,km
 assume the use of depth dependent phases such as $pP$. Without such
-phases the uncertainty is higher.} \citet{dr_Bondar04a} demonstrate
+phases the uncertainty is higher). \citet{dr_Bondar04a} demonstrate
 that at the local scale, absolute locations are accurate to within
@@
 \citet{dr_Douglas67a} who developed the technique commonly known as
-joint hypocenter determination.\footnote{\citet{dr_Douglas67a}
+joint hypocenter determination (\citet{dr_Douglas67a}
 originally used the term joint epicentre determination. However, he
-was solving for hypocentre.} In principle, relative locations can be
+was solving for hypocentre). In principle, relative locations can be
 computed by differencing absolute locations. However,
@@
 Our technique can be used on coda waves alone or in combination with
-travel times. We begin by introducing the theory of CWI based earthquake location
-(Section \ref{sec:theory}). This is followed by a demonstration of capability using
-synthetic examples (Section \ref{sec:benchmarking}) and application to earthquakes
-on the Calaveras fault, California using CWI alone (Section \ref{sec:CalaverasLoc-CWIonly}
-and CWI in combination with travel time constraints (Section \ref{sec:CalaverasLoc-CWIandTT}).
-
-\section{Theory}
+travel times. We begin by introducing the theory of CWI based earthquake location. 
+This is followed by a demonstration of capability using
+synthetic examples and application to earthquakes
+on the Calaveras fault, California using CWI alone
+and CWI in combination with travel time constraints.
+
+\vspace{2em}
+\begin{centering}
+\section*{Theory}
+\end{centering}
 \label{sec:theory}
@@
 separation $\delta_{CWI}$ between two earthquakes
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:Theory-dcwi_g_sigmat}
 \delta_{CWI}^2 = g(\alpha,\beta)\sigma_\tau^2,
-\end{equation}
+\end{equation} \end{linenomath*}
 where $\sigma_\tau$ is the standard deviation of the travel time
@@
 plane,
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:LitReview-g-3d-dc}
@@
 \frac{\left(\frac{2}{\alpha^6}+\frac{3}{\beta^6}\right)}{\left(\frac{6}{\alpha^8}+\frac{7}{\beta^8}\right)},
-\end{equation}
+\end{equation} \end{linenomath*}
 whereas, for two point sources in a 2D acoustic medium
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:LitReview-g-2d-ps} g(\alpha,\beta) = 2 \alpha^2
-\end{equation}
+\end{equation} \end{linenomath*}
 \citep{dr_Snieder05a}. In this paper we use equation
@@
 $R_{max}$ by
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:Rmax-disp-orig} R_{max}^{(t,t_w)} = 1 - \frac{1}{2}
 \overline{\omega^2} \sigma_\tau^2,
-\end{equation}
+\end{equation} \end{linenomath*}
 In this paper we use the autocorrelation approach of
@@
 given the CWI data. Their approach is summarised by
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:-bayesian-noisyform}
@@
 \times P(\widetilde{\delta}_t)
-\end{equation}
+\end{equation} \end{linenomath*}
 where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the
@@
 wavelength normalised separation parameter
-\begin{equation}
+\begin{linenomath*} \begin{equation} 
 \label{eq-normalisation-eqn}
 \widetilde{\delta} = \frac{\delta}{\lambda_{d}},
-\end{equation}
+\end{equation} \end{linenomath*}
 which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$)
@@
 formulation we write
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-Bayes-three-locations}
@@
 \times P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3),
-\end{equation}
+\end{equation} \end{linenomath*}
 where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$,
@@
 \mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-travel time differences. In the following derivation and in Sections
-\ref{sec:benchmarking} and \ref{sec:CalaverasLoc-CWIonly} we focus
-on the constraints imposed by coda waves, whereas in Section
-\ref{sec:CalaverasLoc-CWIandTT} we demonstrate how CWI and travel
+travel time differences. In the following derivation and in 
+Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault we focus
+on the constraints imposed by coda waves, whereas in 
+Combining Travel Time and CWI Constraints we demonstrate how CWI and travel
 time data can be combined.
@@
 This can be done because
-knowledge of location translates to separation.\footnote{Note that the reverse is
+knowledge of location translates to separation.Note that the reverse is
 not true. That is, knowledge of separation between a single event pair
 does not uniquely translate to location but rather places a non-unique constraint on
-location.}
+location.
 Furthermore, since the pairwise functions are independent the joint
 likelihood becomes
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 Similarly, the earthquake locations are independent and the
 joint prior becomes
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:-joint-prior4three} P(\mathbf{e}_1, \mathbf{e}_2,
@@
 P(\mathbf{e}_3).
-\end{equation}
+\end{equation} \end{linenomath*}
 Combining equations (\ref{eq:-joint-likelihood4three}) and
 (\ref{eq:-joint-prior4three}) gives the joint posterior function
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-3eqposterior}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 for three events.
@@
 marginal
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:-E2-marginal}
@@
  d\mathbf{e}_3,
-\end{equation}
+\end{equation} \end{linenomath*}
 where the intergral is taken over all plausible locations for
@@
 Extending to $n$ events we get the posterior function
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 When evaluating equation (\ref{posterior-n-events})
@@
 and so we work with the negative logarithm
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:-negative-log-part1}
 L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n) = -ln\left[ P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN} )  \right]
-\end{equation}
+\end{equation} \end{linenomath*}
 or
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 The logarithm improves numerical stability by replacing products
@@
 system we fix the first event at the origin
-\begin{equation}
+\begin{linenomath*} \begin{equation} 
 \label{eq:coord-const1}
 \mathbf{e}_1 = (0,0,0),
-\end{equation}
+\end{equation} \end{linenomath*}
 the second event on the positive $\hat{x}$-axis
-\begin{equation}
+\begin{linenomath*} \begin{equation} 
 \label{eq:coord-const2}
 \mathbf{e}_2 = (\hat{x}_2, 0, 0), \hat{x}_2>0
-\end{equation}
+\end{equation} \end{linenomath*}
 the third on the $\hat{x}-\hat{y}$ plane
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:coord-const3}
 \mathbf{e}_3 = (\hat{x}_3,\hat{y}_3,0), \hat{y}_3>0
-\end{equation}
+\end{equation} \end{linenomath*}
 and the fourth to
-\begin{equation}
+\begin{linenomath*} \begin{equation} 
 \label{eq:coord-const4}
 \mathbf{e}_4 = (\hat{x}_4,\hat{y}_4,\hat{z}_4), \hat{z}_4>0.
-\end{equation}
+\end{equation} \end{linenomath*}
 This coordinate system reduces translational (equation \ref{eq:coord-const1})
@@
 system when using coda waves alone because the CWI technique constrains only event separation
-between earthquakes. The inclusion of travel times in Section \ref{sec:CalaverasLoc-CWIandTT}
+between earthquakes. The inclusion of travel times in Combining Travel Time and CWI Constraints
 allows us to move to a global reference system.
@@
 and $ln \left[ P(e_i) \right]$ can be ignored because they are
-constant\footnote{$ln \left[ P(e_i) \right]$ is constant because we
-consider a uniform prior.}
-
-\section{Synthetic experiments}
+constant ($ln \left[ P(e_i) \right]$ is constant because we
+consider a uniform prior).
+
+\vspace{2em}
+\begin{centering}
+\section*{Synthetic experiments}
+\end{centering}
+
 \label{sec:benchmarking}
@@
 undertake a complete coda wave location experiment, including the
-calculation of CWI separation estimates, for recorded earthquakes on
-the Calaveras Fault, California, in Section
-\ref{sec:CalaverasLoc-CWIonly}.
-
-\subsection{Examples 1 and 2 - 2D synthetic experiments}
+calculation of CWI separation estimates, for recorded earthquakes in 
+Relocating Earthquakes on the Calaveras 
+Fault and in Combining Travel Time and CWI Constraints.
+
+\vspace{1em}
+\subsection*{Examples 1 and 2 - 2D synthetic experiments}
 
@@
 setting
-\begin{equation}
+\begin{linenomath*} \begin{equation} 
 \label{eq:hypothetical-CWI-mean-optichapt}
 \bar{\mu}_N = \mu_1 \left( \widetilde{\delta}_t \right)
-\end{equation}
+\end{equation} \end{linenomath*}
 using equation (\ref{eq:mu1}). This assumption ensures that the
@@
 constraints imposed on the events (see equations
-(\ref{eq:coord-const1}) to (\ref{eq:coord-const3})\footnote{equation
-\ref{eq:coord-const4} is needed in 3D only}) we observe that in
+(\ref{eq:coord-const1}) to (\ref{eq:coord-const3} - equation
+\ref{eq:coord-const4} is needed in 3D only) we observe that in
 practice the presence of noise allows the rotational non-uniqueness
@@
 measurements of travel times alleviates this problem and facilitate
-the removal of a local coordinate system altogether (see Section
-\ref{sec:CalaverasLoc-CWIandTT}). On balance however, we gain
+the removal of a local coordinate system altogether (see Combining Travel Time and 
+CWI Constraints). On balance however, we gain
 confidence in the optimization procedure due to its stability for
@@
 
-\subsection{Example 3 - The impact of incomplete event pairs in 2D}
+\subsection*{Example 3 - The impact of incomplete event pairs in 2D}
 
@@
 
-\subsection{Example 4 - The impact of incomplete event pairs in 3D}
+\subsection*{Example 4 - The impact of incomplete event pairs in 3D}
 
@@
 
-\subsubsection{Summary of synthetic experiments}
+\subsection*{Summary of synthetic experiments}
 
@@
 
-\section{Relocating Earthquakes on the Calaveras Fault}
+\vspace{2em}
+\begin{centering}
+\section*{Relocating Earthquakes on the Calaveras Fault}
+\end{centering}
 \label{sec:CalaverasLoc-CWIonly}
@@
 algorithm or hypoDD \citep{dr_Waldhauser00a, dr_Waldhauser01a} [See
-also Data and Resources Section]. These events are chosen for four
+also Data and Resources]. These events are chosen for four
 reasons. Firstly, they are recorded by a large number of stations
@@
 
-\subsection{Example 5 - comparison of CWI, catalogue and hypoDD locations}
+\subsection*{Example 5 - comparison of CWI, catalogue and hypoDD locations}
 
@@
 To apply CWI we download available waveforms from the Northern
-California Earthquake Data Center (See Data and Resources Section).
+California Earthquake Data Center (See Data and Resources).
 Unsuitable waveforms are removed using the conditions summarised in
@@
 windows between $2.5 \leq t \leq 20$\,s and used to create
-probabilistic constraints on event separation. We introduce the
-local coordinate system of Section \ref{sec:theory} and find the
+probabilistic constraints on event separation. We utilize the
+local coordinate system introduced in Theory and find the
 optimum relative locations using Polak-Ribiere optimization.
@@
 
-\subsection{Example 6 - Dependance on the number of stations}
+\subsection*{Example 6 - Dependance on the number of stations}
 
@@
 
-\section{Theory for Combining travel time and CWI constraints}
+\vspace{2em}
+\begin{centering}
+\section*{Combining Travel Time and CWI Constraints}
+\end{centering}
 \label{sec:CalaverasLoc-CWIandTT}
@@
 function
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-multi-var-Gauss-tt}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 where
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \mathbf{e}_p = (x_p,y_p,z_p)^T
-\end{equation}
+\end{equation} \end{linenomath*}
 is the location of event $p$,
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \mu_{\mathbf{e}_p} = (\mu_{x_p}, \mu_{y_p},\mu_{z_p})^T
-\end{equation}
+\end{equation} \end{linenomath*}
 is the most likely location as determined using the travel time
 data, and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:Sigma-expression}
@@
 0 & 0 & \sigma_{z_p}^2  \end{array} \right)
-\end{equation}
+\end{equation} \end{linenomath*}
 is the covariance matrix. In this paper we define the mean location
@@
 We pose the location problem using the negative log likelihood
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-Lstar-tt-cwi}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 where $(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n)$ is the joint
 location,
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-ttcomponent} \sum_{i=1}^n
 ln\left[P(\mathbf{e}_i|\Delta_{TT})\right]
-\end{equation}
+\end{equation} \end{linenomath*}
 incorporates the travel time constraints and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-codacomponent} \sum_{i=1}^{n-1} \sum_{j=i+1}^n
 ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right]
-\end{equation}
+\end{equation} \end{linenomath*}
  the coda waves.
@@
 $x_p$ is given by
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 where
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \sum_{i=p+1}^{N} \frac{ \partial \ln
@@
 x_p}
-\end{equation}
+\end{equation} \end{linenomath*}
 and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \sum_{j=1}^{p-1} \frac{ \partial \ln
@@
 x_p}
-\end{equation}
+\end{equation} \end{linenomath*}
 are defined in Appendix \ref{sec-Appendix-derivatives_ofL} and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 Similarly, for the derivatives with respect to $y_p$ and $z_p$ we
 have
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 
@@
 
-\subsection{Example 7 - Combining travel time and CWI constraints}
+\vspace{1em}
+\subsection*{Example 7 - Combining travel time and CWI constraints}
 Figure
@@
 
-\subsection{Example 8 - Combining CWI and travel times when the travel times constrain a limited number of events}
+\subsection*{Example 8 - Combining CWI and travel times when the travel times constrain a limited number of events}
 
@@
 $t$ days is given by the modified Omori formula
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:CumOmori}
  N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}
-\end{equation}
+\end{equation} \end{linenomath*}
 \citep{dr_Utsu95a}.
@@
 is,
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{N(150+4)-N(4)}{N(1000)} = \frac{2257-934}{2626} \approx 0.5.
-\end{equation}
+\end{equation} \end{linenomath*}
 This idea is illustrated in Figure \ref{fig:Omorifigure} which shows
@@
 
-\section{Discussion and Conclusions}
+\vspace{2em}
+\begin{centering}
+\section*{Discussion and Conclusions}
+\end{centering}
 
@@
 
-\section{Data and Resources}
+\vspace{2em}
+\begin{centering}
+\section*{Data and Resources}
+\end{centering}
 We thank the Northern California Earthquake Data Center (NCEDC) for
@@
 contributing it to the NCEDC. The waveforms can be downloaded from
-http://www.ncedc.org/ncedc/access.html. We also acknowledge Felix
+http://www.ncedc.org/ncedc/access.html (last accessed August 2012). 
+We also acknowledge Felix
 Waldhauser and William Ellsworth, the authors of the openly
 available Double Difference location algorithm, hypoDD which can be
-downloaded from http://www.ldeo.columbia.edu/~felixw/hypoDD.html.
-
-\begin{acknowledgments}
+downloaded from http://www.ldeo.columbia.edu/~felixw/hypoDD.html
+(last accessed August 2012).
+The International Sesimological Centre can be found at 
+http://www.isc.ac.uk/ (last accessed December 2012).
+The National Earthquake
+Information
+Center catalogue can be accessed from \\
+http://earthquake.usgs.gov/earthquakes/eqarchives/epic/
+(last accessed December 2012).
+
+\vspace{2em}
+\begin{centering}
+\section*{Acknowledgments}
+\end{centering}
+
 Geoscience Australia, the Research School of Earth Sciences at The
@@
 CWI to earthquake location.
-\end{acknowledgments}
-
-\bibliography{../refs/drrefs}
+
+%=============================================
+% Bibliography
+\vspace{2em}
+%\bibliography{../refs/drrefs}  %Uncomment when generating bibliography
+
+\newcommand{\areps}{\textit{Ann.\ Rev.\ Earth Planet\ Sci.}}
+\newcommand{\bssa}{\textit{Bull.\ Seism.\ Soc.\ Am.}}
+\newcommand{\eos}{\textit{Eos Trans.\ AGU}} 
+\newcommand{\eps}{\textit{Earth~Planets~Space}}
+\newcommand{\epsl}{\textit{Earth~Planet.\ Sci.\ Lett.}}
+\newcommand{\gca}{\textit{Geochim.\ Cosmochim.\ Acta}}
+\newcommand{\geo}{\textit{Geology}}
+\newcommand{\geop}{\textit{Geophysics}}
+\newcommand{\gji}{\textit{Geophys.\ J.\ Int.}}
+\newcommand{\gjras}{\textit{Geophys.\ J.\ R.\ Astr.\ Soc.}}
+\newcommand{\grl}{\textit{Geophys.\ Res.\ Lett.}}
+\newcommand{\gsab}{\textit{Geol.\ Soc.\ Am.\ Bull.}}
+\newcommand{\gs}{\textit{Geophys.\ Surv.}}
+\newcommand{\jgr}{\textit{J.\ Geophys.\ Res.}}
+\newcommand{\jpo}{\textit{J.\ Phys.\ Oceanogr.}} 
+\newcommand{\jseis}{\textit{J.~Seismology}}
+\newcommand{\mnras}{\textit{Mon.\ Not.\ R.\ astr.\ Soc.}} 
+\newcommand{\pag}{\textit{Pure Appl.\ Geophys.}}
+\newcommand{\pepi}{\textit{Phys.\ Earth Planet.\ Inter.}}
+\newcommand{\rg}{\textit{Rev.\ Geophys.}}
+\newcommand{\tecto}{\textit{Tectonophysics}}
+\newcommand{\jpe}{\textit{J. Phys. Earth}}  % Added by DR
+\newcommand{\srl}{\textit{Seism. Res. Let.}}  % Added by DR
+
+\begin{thebibliography}{45}
+\providecommand{\natexlab}[1]{#1}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+
+\bibitem[{\textit{Ake et~al.}(2005)\textit{Ake, O'{C}onnell, and
+  Block}}]{dr_Ake05a}
+Ake, J., D.~O'{C}onnell, and L.~Block (2005), Deep-injection and closely
+  monitored induced seismicity at {P}aradox {V}alley, {C}olorado,
+  \bssa, \textit{95}(2),
+  664--683.
+
+\bibitem[{\textit{Aki}(1969)}]{dr_Aki69a}
+Aki, K. (1969), Analysis of the seismic coda of local earthquakes as scattered
+  waves, \jgr, \textit{74}(2), 615--631.
+
+\bibitem[{\textit{Aster et~al.}(2005)\textit{Aster, Borchers, and
+  Thurber}}]{dr_Aster05a}
+Aster, R.~C., B.~Borchers, and C.~H. Thurber (2005), \textit{Parameter
+  estimation and inverse problems}, \textit{International Geophysics Series},
+  vol.~90, Elsevier Academic Press, USA.
+
+\bibitem[{\textit{Bond\'ar et~al.}(2004)\textit{Bond\'ar, Myers, Engdahl, and
+  Bergman}}]{dr_Bondar04a}
+Bond\'ar, I., S.~C. Myers, E.~R. Engdahl, and E.~A. Bergman (2004), Epicentre
+  accuracy based on seismic network criteria, \gji, \textit{156}, 483--496.
+
+\bibitem[{\textit{Bowman et~al.}(1990)\textit{Bowman, Gibson, and
+  Jones}}]{dr_Bowman90a}
+Bowman, J.~R., G.~Gibson, and T.~Jones (1990), Aftershocks of the 1988
+  {J}anuary 22 {T}ennant {C}reek, {A}ustralia intraplate earthquakes: evidence
+  for a complex thrust-fault geometry, \gji, \textit{100}, 87--97.
+
+\bibitem[{\textit{Campbell}(2003)}]{dr_Campbell03a}
+Campbell, K.~W. (2003), Strong motion attenuation, in \textit{International
+  Handbook of Earthquake and Engineering Seismology}, vol.~B, edited by
+  W.~H.~K. Lee, H.~Kanamori, P.~C. Jennings, and C.~Kisslinger, chap.~60, pp.
+  1003--1012, Academic Press, London.
+
+\bibitem[{\textit{Curtis and Snieder}(2002)}]{dr_Curtis02a}
+Curtis, A., and R.~Snieder (2002), Probing the {E}arth's interior with seismic
+  tomography, in \textit{International Handbook of Earthquake Engineering
+  Seismology}, vol.~{A}, edited by W.~H. Lee, H.~Kanamori, P.~C. Jennings, and
+  C.~Kisslinger, chap.~52, pp. 861--874, Academic Press, London.
+
+\bibitem[{\textit{Deichmann and Garcia-{F}ernandez}(1992)}]{dr_Deichmann92a}
+Deichmann, N., and M.~Garcia-{F}ernandez (1992), Rupture geometry from
+  high-precision relative hypocentre locations of microearthquake clusters,
+  \gji, \textit{110}, 501--517.
+
+\bibitem[{\textit{Douglas}(1967)}]{dr_Douglas67a}
+Douglas, A. (1967), Joint epicentre determination, \textit{Nature},
+  \textit{215}, 47--48.
+
+\bibitem[{\textit{Frankel et~al.}(2000)\textit{Frankel, Mueller, Barnhard,
+  Leyendecker, Wesson, Harmsen, Klein, Perkins, Dickman, Hanson, and
+  Hopper}}]{dr_Frankel00a}
+Frankel, A.~D., C.~S. Mueller, T.~P. Barnhard, E.~V. Leyendecker, R.~L. Wesson,
+  S.~C. Harmsen, F.~W. Klein, D.~M. Perkins, N.~C. Dickman, S.~L. Hanson, and
+  M.~G. Hopper (2000), {USGS} {N}ational seismic hazard maps,
+  \textit{Earthquake Spectra}, \textit{16}(1), 1--19.
+
+\bibitem[{\textit{Fr\`emont and Malone}(1987)}]{dr_Fremont87a}
+Fr\`emont, M.-J., and S.~D. Malone (1987), High precision relative locations of
+  earthquakes at {M}ount {St.} {H}elens, \jgr, \textit{92}(B10), 10,223--10,236.
+
+\bibitem[{\textit{Got et~al.}(1994)\textit{Got, Fr\`echet, and
+  Klein}}]{dr_Got94a}
+Got, J.-L., J.~Fr\`echet, and F.~W. Klein (1994), Deep fault plane geometry
+  inferred from multiplet relative relocation beneath the south flank of
+  {K}ilauea, \jgr, \textit{99}(B8),
+  15,375--15,386.
+
+\bibitem[{\textit{Gutenberg}(1945)}]{dr_Gutenberg45a}
+Gutenberg, B. (1945), Amplitudes of surface waves and magnitudes of shallow
+  earthquakes, \bssa,
+  \textit{35}, 3--12.
+
+\bibitem[{\textit{Ito}(1985)}]{dr_Ito85a}
+Ito, A. (1985), High resolution relative hypocenters of similar earthquakes by
+  cross-spectral analysis method, \jpe,
+  \textit{33}, 279--294.
+
+\bibitem[{\textit{Kennett et~al.}(1995)\textit{Kennett, Engdahl, and
+  Buland}}]{dr_Kennett95a}
+Kennett, B. L.~N., E.~R. Engdahl, and R.~Buland (1995), Constraints on seismic
+  velocities in the {E}arth from traveltimes, \gji, \textit{122}, 108--124.
+
+\bibitem[{\textit{Kennett et~al.}(2004)\textit{Kennett, Fishwick, and
+  Heintz}}]{dr_Kennett04a}
+Kennett, B. L.~N., S.~Fishwick, and M.~Heintz (2004), Lithospheric structure in
+  the {A}ustralian region - a synthesis of surface wave and body wave studies,
+  \textit{Exploration Geophysics}, \textit{35}, 242--250.
+
+\bibitem[{\textit{Lees}(1998)}]{dr_Lees98a}
+Lees, J.~M. (1998), Multiplet analysis at {C}oso {G}eothermal, \bssa, \textit{88}(5), 1127--1143.
+
+\bibitem[{\textit{Leonard}(2002)}]{dr_Leonard02a}
+Leonard, M. (2002), The {B}urakin {WA} earthquake sequence {S}ept 2000 --
+  {J}une 2002, in \textit{Total Risk Management in the Privatised Era},
+  \textit{Australian Earthquake Engineering Society Conference}, vol. 10th,
+  edited by M.~Griffith, D.~Love, P.~Mc{B}ean, A.~Mc{D}ougall, and B.~Butler,
+  pp. 22(1)--22(5), AEES, University of Adelaide.
+
+\bibitem[{\textit{Nadeau and Mc{E}villy}(1997)}]{dr_Nadeau97a}
+Nadeau, R.~M., and T.~V. Mc{E}villy (1997), Seismological studies at
+  {P}arkfield {V}: {C}haracteristic microearthquake sequences as fault--zone
+  drilling targets, \bssa,
+  \textit{87}(6), 1463--1472.
+
+\bibitem[{\textit{Pavlis}(1992)}]{dr_Pavlis92a}
+Pavlis, G.~L. (1992), Appraising relative earthquake location errors,
+  \bssa, \textit{82}(2),
+  836--859.
+
+\bibitem[{\textit{Press et~al.}(1987)\textit{Press, Flannery, Teukolsky, and
+  Vetterling}}]{dr_Press87a}
+Press, W.~H., B.~P. Flannery, S.~A. Teukolsky, and W.~T. Vetterling (1987),
+  \textit{Numerical Recipes: The Art of Scientific Computing}, Cambridge
+  University Press, USA.
+
+\bibitem[{\textit{Richter}(1935)}]{dr_Richter35a}
+Richter, C.~F. (1935), An instrumental earthquake magnitude scale,
+  \bssa, \textit{25}(1),
+  1--32.
+
+\bibitem[{\textit{Robinson et~al.}(2006)\textit{Robinson, Dhu, and
+  Schneider}}]{dr_Robinson06b}
+Robinson, D., T.~Dhu, and J.~Schneider (2006), Practical probabilistic seismic
+  risk analysis: {A} demonstration of capability, \srl, \textit{77}(4), 452--458.
+
+\bibitem[{\textit{Robinson et~al.}(2007{\natexlab{a}})\textit{Robinson,
+  Sambridge, and Snieder}}]{dr_Robinson07b}
+Robinson, D.~J., M.~Sambridge, and R.~Snieder (2007{\natexlab{a}}), Constraints
+  on coda wave interferometry estimates of source separation: The 2.5d acoustic
+  case, \textit{Exploration Geophysics}, \textit{38}(3), 189--199.
+
+\bibitem[{\textit{Robinson et~al.}(2007{\natexlab{b}})\textit{Robinson,
+  Snieder, and Sambridge}}]{dr_Robinson07c}
+Robinson, D.~J., R.~Snieder, and M.~Sambridge (2007{\natexlab{b}}), Using coda
+  wave interferometry for estimating the variation in source mechanism between
+  double couple events, \jgr, \textit{112},
+  b12302, doi:10.1029/2007JB004925.
+
+\bibitem[{\textit{Robinson et~al.}(2011)\textit{Robinson, Sambridge, and
+  Snieder}}]{dr_Robinson11a}
+Robinson, D.~J., M.~Sambridge, and R.~Snieder (2011), A probabilistic approach
+  for estimating the separation between a pair of earthquakes directly from
+  their coda waves, \jgr, \textit{B04309},
+  1--17.
+
+\bibitem[{\textit{Rubin}(2002)}]{dr_Rubin02a}
+Rubin, A.~M. (2002), Aftershocks of microearthquakes as probes of the mechanics
+  of rupture, \jgr, \textit{107}(B7,2142),
+  10.1029/2001JB000,496.
+
+\bibitem[{\textit{Rubin et~al.}(1999)\textit{Rubin, Gillard, and
+  Got}}]{dr_Rubin99a}
+Rubin, A.~M., D.~Gillard, and J.-L. Got (1999), Streaks of microearthquakes
+  along creeping faults, \textit{Nature}, \textit{400}, 635--641.
+
+\bibitem[{\textit{Schaff et~al.}(2002)\textit{Schaff, Bokelmann, and
+  Beroza}}]{dr_Schaff02a}
+Schaff, D.~P., G.~H.~R. Bokelmann, and G.~C. Beroza (2002), High-resolution
+  image of {C}alaveras {F}ault seismicity, \jgr, \textit{107}(B9), 2186, doi:10.1029/2001JB000,633.
+
+\bibitem[{\textit{Shearer et~al.}(2005)\textit{Shearer, Hauksson, and
+  Lin}}]{dr_Shearer05a}
+Shearer, P., E.~Hauksson, and G.~Lin (2005), Southern {C}alifornia hypocenter
+  relocation with waveform cross-correlation, {P}art 2: {R}esults using
+  source-specific station terms and cluster analysis, \bssa, \textit{95}(3), 904--915.
+  doi:10.1785/0120040,168.
+
+\bibitem[{\textit{Shearer}(1999)}]{dr_Shearer99a}
+Shearer, P.~M. (1999), \textit{Introduction to Seismology}, Cambridge
+  University Press, USA, 260pp.
+
+\bibitem[{\textit{Sipkin}(2002)}]{dr_Sipkin02a}
+Sipkin, S.~A. (2002), {USGS} earthquake moment tensor catalog, in
+  \textit{International Handbook of Earthquake Engineering Seismology},
+  vol.~{A}, edited by W.~H. Lee, H.~Kanamori, P.~C. Jennings, and
+  C.~Kisslinger, chap.~50, pp. 823--825, Academic Press, London.
+
+\bibitem[{\textit{Snieder}(1999)}]{dr_Snieder99a}
+Snieder, R. (1999), Imaging and averaging in complex media, in \textit{Diffuse
+  waves in complex media}, \textit{NATO Science Series C}, vol. 531, edited by
+  J.~P. Fouque, pp. 405--454, Kluwer Academic Publishers.
+
+\bibitem[{\textit{Snieder}(2006)}]{dr_Snieder06a}
+Snieder, R. (2006), The theory of coda wave interferometry, \pag, 
+\textit{163}, 455--473.
+
+\bibitem[{\textit{Snieder and Vrijlandt}(2005)}]{dr_Snieder05a}
+Snieder, R., and M.~Vrijlandt (2005), Constraining the source separation with
+  coda wave interferometry: Theory and application to earthquake doublets in
+  the {H}ayward {F}ault, {C}alifornia, \jgr, \textit{110}(B04301), doi:10.1029/2004JB003317.
+
+\bibitem[{\textit{Spencer and Gubbins}(1980)}]{dr_Spencer80a}
+Spencer, C., and D.~Gubbins (1980), Travel-time inversion for simultaneous
+  earthquake location and velocity structure determination in laterally varying
+  media, \gjras,
+  \textit{63}, 95--116.
+
+\bibitem[{\textit{Stirling et~al.}(2002)\textit{Stirling, Mc{V}erry, and
+  Berrryman}}]{dr_Stirling02a}
+Stirling, M.~W., G.~H. Mc{V}erry, and K.~R. Berrryman (2002), A new seismic
+  hazard model for {N}ew {Z}ealand, \bssa, \textit{92}(5), 1878--1903.
+
+\bibitem[{\textit{Toro et~al.}(1997)\textit{Toro, Abrahamson, and
+  Schneider}}]{dr_Toro97a}
+Toro, G.~R., N.~A. Abrahamson, and J.~F. Schneider (1997), Model of strong
+  ground motions from earthquakes in {C}entral and {E}astern {N}orth {A}merica:
+  {B}est estimates and uncertainties, \srl,
+  \textit{68}(1), 41--57.
+
+\bibitem[{\textit{Utsu et~al.}(1995)\textit{Utsu, Ogata, and
+  Matsu'ura}}]{dr_Utsu95a}
+Utsu, T., Y.~Ogata, and R.~S. Matsu'ura (1995), The {C}entenary of the {O}mori
+  {F}ormula for a decay law of aftershock activity, \jpe, \textit{43}, 1--33.
+
+\bibitem[{\textit{Van{D}ecar and Snieder}(1994)}]{dr_VanDecar94a}
+Van{D}ecar, J.~C., and R.~Snieder (1994), Obtaining smooth solutions to large
+  linear inverse problems, \textit{Geophysics}, \textit{59}, 818--829.
+
+\bibitem[{\textit{Waldhauser}(2001)}]{dr_Waldhauser01a}
+Waldhauser, F. (2001), hypo{DD} -- a program to compute double-difference
+  hypocenter locations (hypo{DD} version 1.0 - 03/2001), \textit{Open file
+  report 01-113}, United States Geological Survey, Menlo Park, California.
+
+\bibitem[{\textit{Waldhauser and Ellsworth}(2000)}]{dr_Waldhauser00a}
+Waldhauser, F., and W.~L. Ellsworth (2000), A double--difference earthquake
+  location algorithm: method and application to the northern {H}ayward {F}ault,
+  {C}alifornia, \bssa,
+  \textit{90}(6), 1353--1368.
+
+\bibitem[{\textit{Waldhauser and Ellsworth}(2002)}]{dr_Waldhauser02a}
+Waldhauser, F., and W.~L. Ellsworth (2002), Fault structure and mechanics of
+  the {H}ayward {F}ault, {C}alifornia, from double--difference earthquake
+  locations, \jgr, \textit{107}(B3),
+  10.1029/2000JB000,084.
+
+\bibitem[{\textit{Waldhauser and Schaff}(2008)}]{dr_Waldhauser08a}
+Waldhauser, F., and D.~P. Schaff (2008), Large-scale relocation of two decades
+  of {N}orthern {C}alifornia seismicity using cross-correlation and
+  double-difference methods, \jgr,
+  \textit{133}, {B08311, doi10.1029/2007JB005479}.
+
+\bibitem[{\textit{Waldhauser et~al.}(1999)\textit{Waldhauser, Ellsworth, and
+  Cole}}]{dr_Waldhauser99a}
+Waldhauser, F., W.~L. Ellsworth, and A.~Cole (1999), Slip-parallel lineations
+  on the {N}orthern {H}ayward {F}ault, {C}alifornia, \grl, \textit{26}(23), 3525--3528.
+
+\end{thebibliography}
+
+\vspace{2em}
+\begin{centering}
+\section*{Authors' Affiliations, Adresses}
+\end{centering}
+
+\begin{tabular}{lp{0.6\textwidth}}
+ & \\
+David Robinson: & Earth Monitoring and Hazard Group \\
+ &  Geoscience Australia \\
+ & GPO Box \emph{383} \\
+ & Canberra ACT \emph{2601} Australia \\
+ & E-mail: david.robinson@ga.gov.au\\
+ & \\
+ & Also at: Research School of Earth Sciences \\
+ & Australian National University \\ 
+ & Canberra ACT \emph{0200}, Australia \\
+ & E-mail: david.robinson@anu.edu.au \\
+ & \\
+ Malcolm Sambridge: & Research School of Earth Sciences \\
+ & Australian National University \\ 
+ & Canberra ACT \emph{0200}, Australia \\
+  & \\
+Roel Snieder: & Center for Wave Phenomena and Department of Geophysics \\
+ & Colorado School of Mines \\
+ & Golden CO \emph{80401-1887}, USA \\
+ & \\
+Juerg Hauser: & CSIRO Earth Science and Resource Engineering \\
+ & Dick Perry Av \\
+ & Kensington WA \emph{6151} Australia
+\end{tabular}
 
@@
 
+%\begin{centering}
+%\section*{Tables}
+%\end{centering}
 %%=======================================================================================
@@
 
+\clearpage
+
+%\begin{centering}
+%\section*{Figure Captions}
+%\end{centering} 
+%%=======================================================================================
+
+%Figure 1
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
+%\includegraphics[width = 20pc]{Figure1_c.eps}
+\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
+optimization event locations are shown in triangles and circles,
+respectively.} \label{fig-2D50eq-relocation_eg1}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 2
+\begin{figure}
+%\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
+%\includegraphics[width = 20pc]{Figure2_c.eps}
+\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
+using all constraints with noise $\bar{\sigma}_N= 2
+\epsilon(\delta_t)$.
+ Actual and optimization event locations
+are shown in triangles and circles, respectively.}
+\label{fig-2D50eq-relocation_eg3}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 3
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{Figure3_c.eps}
+\caption{Example 3 - Statistical measures of error in the
+ solutions for the 2D synthetic cases when all and best
+optimization results are considered. The statistics $\Delta_{max}$
+and $\Delta_\mu$  are the maximum and mean coordinate error,
+respectively. The bottom subplot shows the average minimum number of
+branches required to link the 2450 pairs.}
+ \label{fig:optimisationresults-2Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 4
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
+%\noindent\includegraphics[width=20pc]{Figure4_c.eps}
+\caption{Example 4 - Statistical measures of error in the
+optimization solutions for the 3D synthetic cases when all (gray)
+and best (black) results are considered. The statistics
+$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
+error, respectively. The absence of the gray and black lines below
+60\% and 30\% indicates a breakdown in the solutions when all or
+best optimization result(s) are considered, respectively.}
+\label{fig:optimisationresults-3Dsynth}
+\end{figure}
+
+%%=======================================================================================
+
+% Figure 5
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
+%\noindent\includegraphics[width=20pc]{Figure5.eps} 
+\caption{Map
+showing location of the Calaveras cluster (white star) and 805
+seismic stations (black triangles).}
+\label{fig:-eqopti-California-Calaveras}
+\end{figure}
+
+%%=======================================================================================
+% Figure 6
+
+% Now we have the SVD version
+\begin{figure}
+%\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
+%\includegraphics{Figure6_bw.eps}
+\caption{Example 5 - Comparison of relative earthquake locations
+using three different methods: catalogue location (column 1), CWI
+(column 2) and hypoDD (column 3). Note that in the case of the
+hypoDD and CWI inversions we consider only the 68 earthquakes in
+black, the gray catalogue locations for the remaining 240 (308-68)
+earthquakes are shown for the purpose of orientation only.}
+\label{fig-69Calaverasevents_eg1}
+\end{figure}
+%%=======================================================================================
+
+% Figure 7
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
+%\noindent\includegraphics[width=20pc]{Figure7.eps} 
+\caption{Location
+of the 10 stations (triangles) used to relocate the Calaveras events
+in Example 6 to 8. Stations are removed one at a time according to
+the order in Table \ref{tab:Calaveras-stationremoval} and the events
+relocated. The events are indicated with black circles.}
+\label{fig:-eqopti-Calaveras-substations}
+\end{figure}
+
+%%=======================================================================================
+
+%Figure 8
+\begin{figure}
+%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
+%\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
+\caption{Example 6 - CWI relative locations with reduced stations. \hspace{20em}}
+\label{fig-CWIreducesstats}
+\end{figure}
+
+%%=========================================================================
+% Figure 9
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
+%\includegraphics[height = 25pc]{Figure9_bw.eps}
+\caption{Example 6 - HypoDD (SVD) relative locations with reduced
+stations. \hspace{20em} }
+\label{fig-HYPODDreducesstats}
+\end{figure}
+%%=========================================================================
+
+%Figure 10
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\noindent\includegraphics[width=20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
+%\noindent\includegraphics[width=20pc]{Figure10_c.eps}
+\caption{Example 6 - Number of constrainable events $nE$ in the CWI
+and hypoDD inversions as a function of the stations considered
+(top). Mean (middle) and maximum (bottom) of the difference computed
+between the reduced station inversion results (CWI and hypoDD) and
+the complete hypoDD locations for all 308 events. }
+\label{fig-statremoval_summarystats}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 11
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
+%\includegraphics{Figure11_bw.eps}
+\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
+locations using data form all stations (left) and 5 stations
+(right).} \label{fig-68Calaverasevents_ttandcoda1}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 12
+
+\begin{figure}
+%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
+%\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
+\caption{Cumulative number of aftershocks for the
+Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
+using equation (\ref{eq:CumOmori}). The leftmost red, middle blue
+and rightmost red lines signify aftershocks occurring before, during
+and after the deployment of a pseudo temporary array installed 4
+days after the main shock and left for 150 days. A temporary
+deployment of this kind will record roughly 50\% of the aftershocks
+in the 1000 days following the mainshock. } \label{fig:Omorifigure}
+\end{figure}
+
+%%=========================================================================
+
+% Figure 13
+
+% This is the version using hypoDD with SVD
+\begin{figure}
+%\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
+%\includegraphics{Figure13_bw.eps}
+\caption{Example 8 - Mimicking the deployment of a temporary network
+by ignoring data from all but station CCO for 50\% (or 34) of the
+events. Relative locations are shown for the combined CWI and travel
+time inversion (left) and the inversion with travel times only
+(right). Only by combining the data is it possible to locate all 68
+events. Furthermore, combining the data leads to a solution more
+consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
+\label{fig-68Calaverasevents_ttsubsetandcoda1}
+\end{figure}
+%%=========================================================================
+
+\clearpage
+%\begin{centering}
+%\section*{Figure Captions}
+%\end{centering} 
+%%=======================================================================================
+
+%Figure 1
+\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
+\textbf{Figure 1:}
+
+%%=======================================================================================
+
+%Figure 2
+\clearpage
+\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
+\textbf{Figure 2:}
+
+%%=======================================================================================
+
+% Figure 3
+\clearpage
+\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
+\textbf{Figure 3:}
+
+%%=======================================================================================
+
+% Figure 4
+\clearpage
+\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
+\textbf{Figure 4:}
+
+%%=======================================================================================
+
+% Figure 5
+\clearpage
+\noindent\includegraphics[width=20pc]{Figure5.eps} \\
+\textbf{Figure 5:}
+
+%%=======================================================================================
+% Figure 6
+\clearpage
+\includegraphics{Figure6_bw.eps} \\
+\textbf{Figure 6:}
+
+%%=======================================================================================
+
+% Figure 7
+\clearpage
+\noindent\includegraphics[width=20pc]{Figure7.eps} \\
+\textbf{Figure 7:}
+
+%%=======================================================================================
+
+%Figure 8
+\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
+%\noindent\includegraphics[width= 50pc]{Figure8_bw.eps} \\
+
+%%=========================================================================
+% Figure 9
+\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
+\textbf{Figure 9:}
+
+%%=========================================================================
+
+%Figure 10
+\clearpage
+\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
+\textbf{Figure 10:}
+
+%%=========================================================================
+
+% Figure 11
+\clearpage
+\includegraphics{Figure11_bw.eps} \\
+\textbf{Figure 11:}
+
+%%=========================================================================
+
+% Figure 12
+\clearpage
+\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
+\textbf{Figure 12:}
+
+%%=========================================================================
+
+% Figure 13
+\clearpage
+\includegraphics{Figure13_bw.eps} \\
+\textbf{Figure 13:}
+
+\appendix
+\clearpage
+
+\vspace{2em}
+\begin{centering}
+\section*{The Likelihood}
+\end{centering}
+
+\label{sec-Appendix-noisylikelihood}
+
+The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
+used in equation (\ref{eq:-bayesian-noisyform}) is given by
+\begin{linenomath*} \begin{equation}
+\begin{array}{l}
+\label{eq-likelihood-int}
+P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
+A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
+\hspace{3em} \times \int_0^\infty
+B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
+D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
+d\widetilde{\delta}_{CWI}
+\end{array}
+\end{equation} \end{linenomath*}
+where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
+of noise,
+\begin{linenomath*} \begin{equation}
+\label{eq:Adefn}
+A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
+\end{equation} \end{linenomath*}
+\begin{linenomath*} \begin{equation}
+B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
+\end{equation} \end{linenomath*}
+\begin{linenomath*} \begin{equation}
+\label{eq:Cdefn}
+C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
+\end{equation} \end{linenomath*}
+\begin{linenomath*} \begin{equation}
+D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
+\end{equation} \end{linenomath*}
+and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
+\begin{linenomath*} \begin{equation}
+\label{eq-cummulative-Gaussian}
+\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
+\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
+\end{equation} \end{linenomath*}
+\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
+in equation (\ref{eq:Adefn}) are defined by the expressions
+\begin{linenomath*} \begin{equation}
+\label{eq:mu1}
+\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
+\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
+\end{equation} \end{linenomath*}
+and
+\begin{linenomath*} \begin{equation}
+\label{eq:sigma1}
+\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
+a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
+\end{equation} \end{linenomath*}
+with coefficients $a_1$ to $a_5$ and $c$ defined in Table
+\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
+$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
+finding the values which minimize the difference in a least squares
+sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
+computed from the waveforms and the positively bounded Gaussian
+density function
+\begin{linenomath*} \begin{equation}
+\label{eq-likelihood-noisydata-pdf-orig}
+\begin{array}{l}
+P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
+\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
+e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
+\end{array}
+\end{equation} \end{linenomath*}
+with $\widetilde{\delta}_{CWIN} \geq 0$.
+
+%=======================================================
+% Appendix Table
+
 \begin{table}
-\caption{Coefficients for equations. (\ref{eq:mu1}) and
+\caption{Coefficients for equations (\ref{eq:mu1}) and
 (\ref{eq:sigma1}).} \label{tab-const4-mu1-sigma1}
@@
 
-\clearpage
-
-%%=======================================================================================
-
-%Figure 1
-\begin{figure}
-%\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-\includegraphics[width = 20pc]{Figure1_c.eps}
-\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
-optimization event locations are shown in triangles and circles,
-respectively.} \label{fig-2D50eq-relocation_eg1}
-\end{figure}
-
-%%=======================================================================================
-
-%Figure 2
-\begin{figure}
-%\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-\includegraphics[width = 20pc]{Figure2_c.eps}
-\caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
-using all constraints with noise $\bar{\sigma}_N= 2
-\epsilon(\delta_t)$.
- Actual and optimization event locations
-are shown in triangles and circles, respectively.}
-\label{fig-2D50eq-relocation_eg3}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 3
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-\noindent\includegraphics[width=20pc]{Figure3_c.eps}
-\caption{Example 3 - Statistical measures of error in the
- solutions for the 2D synthetic cases when all and best
-optimization results are considered. The statistics $\Delta_{max}$
-and $\Delta_\mu$  are the maximum and mean coordinate error,
-respectively. The bottom subplot shows the average minimum number of
-branches required to link the 2450 pairs.}
- \label{fig:optimisationresults-2Dsynth}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 4
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-\noindent\includegraphics[width=20pc]{Figure4_c.eps}
-\caption{Example 4 - Statistical measures of error in the
-optimization solutions for the 3D synthetic cases when all (gray)
-and best (black) results are considered. The statistics
-$\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
-error, respectively. The absence of the gray and black lines below
-60\% and 30\% indicates a breakdown in the solutions when all or
-best optimization result(s) are considered, respectively.}
-\label{fig:optimisationresults-3Dsynth}
-\end{figure}
-
-%%=======================================================================================
-
-% Figure 5
-\begin{figure}
-%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-\noindent\includegraphics[width=20pc]{Figure5.eps} \caption{Map
-showing location of the Calaveras cluster (white star) and 805
-seismic stations (black triangles).}
-\label{fig:-eqopti-California-Calaveras}
-\end{figure}
-
-%%=======================================================================================
-% Figure 6
-
-% This is the original figure using HypoDD with LSQR
-%\begin{figure*}
-%\includegraphics{diags/CalaverasLoc1.eps}
-%\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
-%308 events (column 2) and CWI example 1 (column 3).
-%Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
-%blue events are shown for the purpose of orientation only.}
-%\label{fig-69Calaverasevents_eg1}
-%\end{figure*}
-
-% Now we have the SVD version
-\begin{figure*}
-%\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-\includegraphics{Figure6_bw.eps}
-\caption{Example 5 - Comparison of relative earthquake locations
-using three different methods: catalogue location (column 1), CWI
-(column 2) and hypoDD (column 3). Note that in the case of the
-hypoDD and CWI inversions we consider only the 68 earthquakes in
-black, the gray catalogue locations for the remaining 240 (308-68)
-earthquakes are shown for the purpose of orientation only.}
-\label{fig-69Calaverasevents_eg1}
-\end{figure*}
-%%=======================================================================================
-
-% Figure 7
-\begin{figure}
-%\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-\noindent\includegraphics[width=20pc]{Figure7.eps} \caption{Location
-of the 10 stations (triangles) used to relocate the Calaveras events
-in Example 6 to 8. Stations are removed one at a time according to
-the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated. The events are indicated with black circles.}
-\label{fig:-eqopti-Calaveras-substations}
-\end{figure}
-
-%%=======================================================================================
-
-%Figure 8
-\begin{figure*}
-%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
-\caption{Example 6 - CWI relative locations with reduced stations.}
-\label{fig-CWIreducesstats}
-\end{figure*}
-
-%%=========================================================================
-% Figure 9
-
-% this is the original version using hypoDD with LSQ
-%\begin{figure*}
-%\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
-%\caption{....}
-%\label{fig-HYPODDreducesstats}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure*}
-%\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-\includegraphics[height = 25pc]{Figure9_bw.eps}
-\caption{Example 6 - HypoDD (SVD) relative locations with reduced
-stations.} \label{fig-HYPODDreducesstats}
-\end{figure*}
-%%=========================================================================
-
-%Figure 10
-
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
-%\caption{Statistics on coordinate differences for reduced station inversions. Differences
-%are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
-%locations for all 308 events. The top subplot illustrates the number of constrainable
-%events in the CWI and hypoDD inversions as a function of the stations considered.}
-%\label{fig-statremoval_summarystats}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-%\noindent\includegraphics[width=20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
-\noindent\includegraphics[width=20pc]{Figure10_c.eps}
-\caption{Example 6 - Number of constrainable events $nE$ in the CWI
-and hypoDD inversions as a function of the stations considered
-(top). Mean (middle) and maximum (bottom) of the difference computed
-between the reduced station inversion results (CWI and hypoDD) and
-the complete hypoDD locations for all 308 events. }
-\label{fig-statremoval_summarystats}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 11
-
-% This is the original version using hypoDD with LSQ
-% This is only makes sense for LSQR so we remove it from this manuscript
-%\begin{figure*}
-%\noindent\includegraphics{diags/CalaverasLoc5.eps}
-%\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
-%levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
-%\citep[after]{dr_Waldhauser08a}, Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
-%column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m \citep[after]{dr_Shearer97a}. }
-%\label{fig-68Calaverasevents_ttandcoda1}
-%\end{figure*}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-%\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-\includegraphics{Figure11_bw.eps}
-\caption{Example 7 - Combined HypoDD (SVD) and CWI relative
-locations using data form all stations (left) and 5 stations
-(right).} \label{fig-68Calaverasevents_ttandcoda1}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 12
-
-\begin{figure}
-%\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
-\caption{Cumulative number of aftershocks for the
-Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-using equation (\ref{eq:CumOmori}). The leftmost red, middle blue
-and rightmost red lines signify aftershocks occurring before, during
-and after the deployment of a pseudo temporary array installed 4
-days after the main shock and left for 150 days. A temporary
-deployment of this kind will record roughly 50\% of the aftershocks
-in the 1000 days following the mainshock. } \label{fig:Omorifigure}
-\end{figure}
-
-%%=========================================================================
-
-% Figure 13
-
-% This is the original version using hypoDD with LSQ
-%\begin{figure}
-%\noindent\includegraphics{diags/CalaverasLoc6.eps}
-%\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
-%22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
-%are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
-%relocation only (i.e. no CWI) using ........}
-%\label{fig-68Calaverasevents_ttsubsetandcoda1}
-%\end{figure}
-
-% This is the version using hypoDD with SVD
-\begin{figure}
-%\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
-\includegraphics{Figure13_bw.eps}
-\caption{Example 8 - Mimicking the deployment of a temporary network
-by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Relative locations are shown for the combined CWI and travel
-time inversion (left) and the inversion with travel times only
-(right). Only by combining the data is it possible to locate all 68
-events. Furthermore, combining the data leads to a solution more
-consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
-\label{fig-68Calaverasevents_ttsubsetandcoda1}
-\end{figure}
-%%=========================================================================
-
-\appendix
-\clearpage
-
-\section{The likelihood}
-\label{sec-Appendix-noisylikelihood}
-
-The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-used in equation (\ref{eq:-bayesian-noisyform}) is given by
-\begin{equation}
-\begin{array}{l}
-\label{eq-likelihood-int}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
-A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
-\hspace{3em} \times \int_0^\infty
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
-d\widetilde{\delta}_{CWI}
-\end{array}
-\end{equation}
-where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
-of noise,
-\begin{equation}
-\label{eq:Adefn}
-A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
-\end{equation}
-\begin{equation}
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
-\end{equation}
-\begin{equation}
-\label{eq:Cdefn}
-C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
-\end{equation}
-\begin{equation}
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
-\end{equation}
-and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
-\begin{equation}
-\label{eq-cummulative-Gaussian}
-\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
-\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
-\end{equation}
-\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
-in equation (\ref{eq:Adefn}) are defined by the expressions
-\begin{equation}
-\label{eq:mu1}
-\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
-\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
-\end{equation}
-and
-\begin{equation}
-\label{eq:sigma1}
-\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
-a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
-\end{equation}
-with coefficients $a_1$ to $a_5$ and $c$ defined in Table
-\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
-$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
-finding the values which minimize the difference in a least squares
-sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
-computed from the waveforms and the positively bounded Gaussian
-density function
-\begin{equation}
-\label{eq-likelihood-noisydata-pdf-orig}
-\begin{array}{l}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
-\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
-e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
-\end{array}
-\end{equation}
-with $\widetilde{\delta}_{CWIN} \geq 0$.
-
-\section{Derivatives}
+%=======================================================
+
+\vspace{2em}
+\begin{centering}
+\section*{Derivatives}
+\end{centering}
+
 \label{sec-Appendix-derivatives_ofL}
@@
 The derivatives of $L(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial L}{\partial \hat{x}_1},
@@
 \frac{\partial L}{\partial \hat{z}_N}
-\end{equation}
+\end{equation} \end{linenomath*}
 are required by the Polak-Ribiere algorithm. These are used to guide
@@
 (\hat{x}_q,\hat{y}_q,\hat{z}_q)$
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:deltat4chapt6deriv}
 \delta_t = \frac{f_{dom}}{v_s}\sqrt{(\hat{x}_p-\hat{x}_q)^2 + (\hat{y}_p-\hat{y}_q)^2 +  (\hat{z}_p-\hat{z}_q)^2},
-\end{equation}
+\end{equation} \end{linenomath*}
 where $f_{dom}$ is the dominant frequency of the waveforms and $v_s$ is the velocity between the events. Expression
 \ref{eq:deltat4chapt6deriv} has derivatives
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-partial-xyz1}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 For brevity we focus the following derivation in terms of $\hat{x}_p$. The remaining terms for $\mathbf{e}_p$
@@
 by following the same procedure. The derivatives for $\mathbf{e}_q$ can be attained by exploiting the symmetry
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq:ep2eq-deriv-symmetry}
 \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_q} = - \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}.
-\end{equation}
+\end{equation} \end{linenomath*}
 
 The chain rule gives
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial \mu_1}{\partial \hat{x}_p} = \frac{\partial \mu_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}
-\end{equation}
+\end{equation} \end{linenomath*}
 where differentiating equation (\ref{eq:mu1}) gives
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \label{eq-dmu1-by-dx1}
@@
 {\left(a_2 \widetilde{\delta}_t^{a_4} +a_3 \widetilde{\delta}_t^{a_5} +1 \right)^2}.
-\end{equation}
+\end{equation} \end{linenomath*}
 Similarly, we have
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial \sigma_1}{\partial \hat{x}_p} = \frac{\partial \sigma_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}
 {\partial \hat{x}_p}
-\end{equation}
+\end{equation} \end{linenomath*}
 where $\frac{\partial \sigma_1}{\partial \widetilde{\delta}_t}$ has the identical form as \ref{eq-dmu1-by-dx1} with different constants
@@
 The cumulative Gaussian distribution function \ref{eq-cummulative-Gaussian} is
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \Phi_{\mu_1,\sigma_1}(0) = \frac{1}{\sigma_1 \sqrt{2 \pi}}
 \int_{-\infty}^0 e^{  \frac{-(s-\mu_1)^2}{2\sigma_1^2}  } ds
-\end{equation}
+\end{equation} \end{linenomath*}
 which has derivative
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial \Phi_{\mu_1,\sigma_1}(0)}{\partial \hat{x}_p} =
@@
 {\sigma_1^2 \sqrt{2 \pi}},
-\end{equation}
+\end{equation} \end{linenomath*}
 where
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 g = \frac{-(s-\mu_1)^2}{2 \sigma_1^2}
-\end{equation}
+\end{equation} \end{linenomath*}
 and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial g}{\partial \hat{x}_p} = \frac{4 \sigma_1^2 (s-\mu_1) \frac{\partial \mu_1}{\partial \hat{x}_p}
@@
 {4 \sigma_1^4}.
-\end{equation}
+\end{equation} \end{linenomath*}
 
 Now, we have all the pieces to compute the derivatives of $A=A(\delta_t)$ and $B = B(\delta_t,\delta_{CWI})$ as follows
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial A} {\partial \hat{x}_p} =
@@
 {\left(1- \Phi_{\mu_1,\sigma_1}(0) \right)^2 \sigma_1^2 \sqrt{2 \pi}}
-\end{equation}
+\end{equation} \end{linenomath*}
 and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial B} {\partial \hat{x}_p} = e^h \frac{\partial h}{\partial \hat{x}_p},
-\end{equation}
+\end{equation} \end{linenomath*}
 where
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 h =  \frac{-(\delta_{CWI}-\mu_1)^2}{2 \sigma_1^2}
-\end{equation}
+\end{equation} \end{linenomath*}
 and
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{\partial h}{\partial \hat{x}_p} = \frac{
@@
 {4 \sigma_1^4}.
-\end{equation}
+\end{equation} \end{linenomath*}
 Finally, we can differentiate the likelihood for an individual event pair
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \begin{array}{l}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 and for the logarithm we have
-\begin{equation}
+\begin{linenomath*} \begin{equation}
 \frac{ \partial \ln \left[ P(\delta_{CWIN}|\delta_t) \right] } {\partial \hat{x}_p}
 = \frac{1}{P(\delta_{CWIN}|\delta_t)} \frac{\partial P(\delta_{CWIN}|\delta_t)}{\partial \hat{x}_p}.
-\end{equation}
+\end{equation} \end{linenomath*}
 
 Thus, it follows that the derivative of $L$ with respect to $\hat{x}_p$ is given by
-%\begin{equation}
+%\begin{linenomath*} \begin{equation}
 %\label{eq-derivative-Lstar-cwionly22}
@@
 %+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
-%\end{equation}
-\begin{equation}
+%\end{equation} \end{linenomath*}
+\begin{linenomath*} \begin{equation}   
 \label{eq-derivative-Lstar-cwionly}
@@
 \end{array}
-\end{equation}
+\end{equation} \end{linenomath*}
 %
@@
 %+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}}
-%\end{equation}
+%\end{equation} \end{linenomath*} 
 for a uniform prior. The change of sign in the middle (i.e. to

### 2013-01-04 paper2/paper2.tex
this is the version submitted after responding to the first set of comments from the Editorial office

@@
 %\bibliographystyle{agufull08} % Uncomment when generating bibliography
-\usepackage{timet}
+%\usepackage{timet}
 \usepackage[dvips]{graphicx}
@@
 Seismological Laboratory, University of California, Berkeley for
-contributing it to the NCEDC. The waveforms can be downloaded from
+contributing it to the NCEDC. The waveforms can be downloaded from \\
 http://www.ncedc.org/ncedc/access.html (last accessed August 2012). 
@@
 available Double Difference location algorithm, hypoDD which can be
-downloaded from http://www.ldeo.columbia.edu/~felixw/hypoDD.html
+downloaded from \\
+http://www.ldeo.columbia.edu/~felixw/hypoDD.html
 (last accessed August 2012).
-The International Sesimological Centre can be found at 
+The International Sesimological Centre can be found at \\
 http://www.isc.ac.uk/ (last accessed December 2012).
@@
 
-\clearpage
+%\clearpage
 %\begin{centering}
@@
 %Figure 1
-\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
-\textbf{Figure 1:}
+%\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
+%\textbf{Figure 1:}
 
@@
 %Figure 2
-\clearpage
-\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
-\textbf{Figure 2:}
+%\clearpage
+%\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
+%\textbf{Figure 2:}
 
@@
 % Figure 3
-\clearpage
-\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
-\textbf{Figure 3:}
+%\clearpage
+%\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
+%\textbf{Figure 3:}
 
@@
 % Figure 4
-\clearpage
-\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
-\textbf{Figure 4:}
+%\clearpage
+%\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
+%\textbf{Figure 4:}
 
@@
 % Figure 5
-\clearpage
-\noindent\includegraphics[width=20pc]{Figure5.eps} \\
-\textbf{Figure 5:}
+%\clearpage
+%\noindent\includegraphics[width=20pc]{Figure5.eps} \\
+%\textbf{Figure 5:}
 
@@
 % Figure 6
-\clearpage
-\includegraphics{Figure6_bw.eps} \\
-\textbf{Figure 6:}
+%\clearpage
+%\includegraphics{Figure6_bw.eps} \\
+%\textbf{Figure 6:}
 
@@
 % Figure 7
-\clearpage
-\noindent\includegraphics[width=20pc]{Figure7.eps} \\
-\textbf{Figure 7:}
+%\clearpage
+%\noindent\includegraphics[width=20pc]{Figure7.eps} \\
+%\textbf{Figure 7:}
 
@@
 %Figure 8
-\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
+%\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
 %\noindent\includegraphics[width= 50pc]{Figure8_bw.eps} \\
@@
 % Figure 9
-\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
-\textbf{Figure 9:}
+%\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
+%\textbf{Figure 9:}
 
@@
 %Figure 10
-\clearpage
-\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
-\textbf{Figure 10:}
+%\clearpage
+%\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
+%\textbf{Figure 10:}
 
@@
 % Figure 11
-\clearpage
-\includegraphics{Figure11_bw.eps} \\
-\textbf{Figure 11:}
+%\clearpage
+%\includegraphics{Figure11_bw.eps} \\
+%\textbf{Figure 11:}
 
@@
 % Figure 12
-\clearpage
-\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
-\textbf{Figure 12:}
+%\clearpage
+%\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
+%\textbf{Figure 12:}
 
@@
 % Figure 13
-\clearpage
-\includegraphics{Figure13_bw.eps} \\
-\textbf{Figure 13:}
+%\clearpage
+%\includegraphics{Figure13_bw.eps} \\
+%\textbf{Figure 13:}
 

### 2013-06-23 paper2/paper2.tex
finished incorporating review - needs one last check

@@
 \end{centering}
-Coda waves arise from scattering to form the later arriving
-components of a seismogram. Coda wave interferometry is an emerging
+Coda-waves arise from scattering to form the later arriving
+components of a seismogram. Coda-wave interferometry is an emerging
 tool for constraining earthquake source properties from the
-intereference pattern of coda waves between nearby events. A new
-earthquake location algorithm is derived which relies on coda wave
+intereference pattern of coda-waves between nearby events. A new
+earthquake location algorithm is derived which relies on coda-wave
 based probabilistic estimates of earthquake separation. The
-algorithm can be used with coda waves alone or in tandem with travel
+algorithm can be used with cod-waves alone or in tandem with arrival
 time data. Synthetic examples in 2D and 3D and real earthquakes on
 the Calaveras Fault, California are used to demonstrate the
-potential of coda waves for locating poorly recorded earthquakes. It
+potential of coda-waves for locating poorly recorded earthquakes. It
 is demonstrated that coda wave interferometry: (a) outperforms
@@
 locations are influenced by source to station distances, the number
-of stations and their geometry, signal-to-noise, clarity of onsets
-and accuracy of the velocity model used in computing travel times.
+of stations and their geometry, signal-to-noise ratio, clarity of onsets
+and accuracy of the velocity model used in computing arrival-times.
 Uncertainties in absolute location are typically of the order of
-several kilometers because they are susceptible to uncertainty in
+several kilometers, primarily because they are susceptible to uncertainty in
 the velocity structure along the entire path between the source and
 receiver. For example, \citet{dr_Shearer99a} states that location
-uncertainty in the ISC (International Sesimological
+uncertainties in the ISC (International Sesimological
 Centre) and PDE (National Earthquake
@@
 phases the uncertainty is higher). \citet{dr_Bondar04a} demonstrate
-that at the local scale, absolute locations are accurate to within
-5\,km with a 95\% confidence level when local networks meet a number
-of station related criteria. Such errors are too large for many
+that absolute locations are accurate to within
+5\,km with a 95\% confidence level when local networks meet the following 
+criteria:
+\begin{enumerate}
+\item there are 10 or more stations, all within 250 km, 
+\item an azimuthal gap of less than 110$^o$, 
+\item a secondary azimuthal gap of less than 160$^o$, and 
+\item at least one station within 30 km. 
+\end{enumerate}. Such errors are too large for many
 applications, particularly those focussed on imaging rupture
@@
 computed in this way. To reduce errors from unknown velocity
-structure, relative location techniques compute locations directly
-from travel time differences between two waveforms
-\citep{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
-so, they remove errors associated with velocity variations outside
+structure, relative location techniques typically compute locations directly
+from arrival-time differences computed by time-lag cross correlation of
+early-onset body waves 
+\citep{dr_Ito85a, dr_Got94a, dr_Slunga95a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
+so, remove errors associated with velocity variations outside
 the local region, because such variations influence all waveforms in
-the same manner \citep{dr_Shearer99a}.
+a similar manner \citep{dr_Shearer99a}.
 
@@
 early onset body waves, typically $P$ and/or $S$ waves,are used. The
-data utilised may be the direct arrival times; travel time
+data utilised may be the direct arrival times; arrival-time
 difference computed between picked arrivals of two waveforms; or
@@
 in real settings. In this paper we
-develop an approach for locating earthquakes using coda waves.
+develop an approach for locating earthquakes using coda-waves.
 \citet{dr_Snieder05a} demonstrate that the coda of two earthquakes
@@
 technique, known as coda wave interferometry (CWI), is based on the
-interference pattern between the coda waves. Unlike travel time
+interference pattern between the coda-waves. Unlike arrival-time
 based location techniques, CWI
@@
 location with data from a single station.
-Our technique can be used on coda waves alone or in combination with
-travel times. We begin by introducing the theory of CWI based earthquake location. 
+Our technique can be used on coda-waves alone or in combination with
+arrival-times. We begin by introducing the theory of CWI based earthquake location. 
 This is followed by a demonstration of capability using
@@
 on the Calaveras fault, California using CWI alone
-and CWI in combination with travel time constraints.
+and CWI in combination with arrival-time constraints.
 
@@
 \end{equation} \end{linenomath*}
-where $\sigma_\tau$ is the standard deviation of the travel time
-perturbation between the coda waves of two earthquakes, and $\alpha$
+where $\sigma_\tau$ is the standard deviation of the arrival-time
+perturbation between the coda-waves of two earthquakes, and $\alpha$
 and $\beta$ are the near-source $P$ and $S$ wave velocities,
@@
 \end{equation} \end{linenomath*}
-\citep{dr_Snieder05a}. In this paper we use equation
+\citep{dr_Snieder05a}. \citet{dr_Snieder05a} also show that for two 
+double couple sources that are not in the same fault plane
+\begin{linenomath*} \begin{equation}
+\label{eq:LitReview-fulDC-sep}
+\sigma_\tau^2 = 
+\frac{ \left(\frac{6}{\alpha^8}+\frac{7}{\beta^8} \right) \delta_{\| fault}^2 + 
+2 \left(\frac{1}{\alpha^8}+\frac{2}{\beta^8} \right) \delta_{\perp fault}^2 }
+{7 \left(\frac{2}{\alpha^8}+\frac{3}{\beta^8} \right)},
+\end{equation} \end{linenomath*}
+where $\delta_{\| fault}^2$ and $\delta_{\perp fault}^2$ are the separation parallel 
+and perpendicular to the fault, respectively. In this paper we use 
+equation \ref{eq:LitReview-g-2d-ps} for the 2D examples.
+For the 3D examples we use equation
 \ref{eq:LitReview-g-3d-dc} which assumes that the source mechanism
@@
 \end{equation} \end{linenomath*}
+where $\overline{\omega^2}$ is the square of the dominant angular frequency
+\begin{equation}
+\label{eq:square-of-domangfreq}
+\overline{\omega^2} =
+\frac{\int_{t-t_w}^{t+t_w}\dot{u}_i^2(t')dt'}{\int_{t-t_w}^{t+t_w}u_i^2(t')dt'},
+\end{equation}
+and $\dot{u}_i$ represents the time derivative of $u_i$.
 In this paper we use the autocorrelation approach of
@@
 increase the range of applicability of CWI by 50\% (i.e. from 300 to
-450\,m separation for 1 to 5\,Hz filtered coda waves).
+450\,m separation for 1 to 5\,Hz filtered coda-waves).
 
@@
 observed if the true separation was $\widetilde{\delta}_t$; and
-$P(\widetilde{\delta}_t)$ is the prior PDF accounting for all
-a-priori information. The tilde above the separation parameters in
+$P(\widetilde{\delta}_t)$ is the prior probability density function (PDF) accounting for all
+a-priori information. The use of $N$ in $\delta_{CWIN}$ depicts CWI separations that include noise. 
+The nomenclature is adopted here to remain consistent with \citet{dr_Robinson11a} who study 
+synthetically generated noise-free $\delta_{CWI}$ and relate them to noisy estimates $\delta_{CWIN}$
+The tilde above the separation parameters in
 equation (\ref{eq:-bayesian-noisyform}) indicates the use of a
@@
 
-We seek a probability density function (PDF) which links
+We seek a PDF which links
  individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
@@
  the most probable combination of locations.
-More importantly however, the PDF shall
+More importantly, however, the PDF shall
 quantify location uncertainty and provide information
@@
 observations that constrain the locations. They can be any
-combination of travel times, geodetic information  or CWI
-separations. For example, if coda waves are used we have
+combination of arrival-times, geodetic information  or CWI
+separations. For example, if coda-waves are used we have
 $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 |
@@
 wavelength normalised separation estimates. Alternatively, if we use
-CWI and travel time data we may write $P(\mathbf{e}_1, \mathbf{e}_2,
+CWI and arrival-time data we may write $P(\mathbf{e}_1, \mathbf{e}_2,
 \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN},
@@
 \mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-travel time differences. In the following derivation and in 
+arrival-time differences. In the following derivation and in 
 Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault we focus
-on the constraints imposed by coda waves, whereas in 
-Combining Travel Time and CWI Constraints we demonstrate how CWI and travel
-time data can be combined.
+on the constraints imposed by coda-waves, whereas in 
+Combining Arrival-Time and CWI Constraints we demonstrate how CWI and arrival-time data can be combined.
 
@@
 This can be done because
-knowledge of location translates to separation.Note that the reverse is
+knowledge of location translates to separation. Note, however, that the reverse is
 not true. That is, knowledge of separation between a single event pair
 does not uniquely translate to location but rather places a non-unique constraint on
-location.
-Furthermore, since the pairwise functions are independent the joint
-likelihood becomes
+location. In other words, knowing $|e1-e2|$ and $|e2-e3|$ does not mean that $|e1-e3|$ is 
+uniquely defined. Consequently, the likelihoods are weekly dependent, in that some 
+likelihood-pairs share common events, an occurrence that becomes relatively less frequent 
+as the number of events being located increases. 
+For the purpose of this work we ignore this week dependance and assume independence. Therefore, we have
 \begin{linenomath*} \begin{equation}
@@
 \label{eq:-joint-likelihood4three}
-P(\widetilde{\mathbf{\delta}}_{CWIN} | \mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) =
+P(\widetilde{\mathbf{\delta}}_{CWIN} | \mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) \approx
 P(\widetilde{\delta}_{CWIN,12} | \mathbf{e}_1, \mathbf{e}_2) \\
@@
 without loss of generality. It is necessary to work with a local coordinate
-system when using coda waves alone because the CWI technique constrains only event separation
-between earthquakes. The inclusion of travel times in Combining Travel Time and CWI Constraints
+system when using coda-waves alone because the CWI technique constrains only event separation
+between earthquakes. The inclusion of arrival-times in Combining Arrival-Time and CWI Constraints
 allows us to move to a global reference system.
@@
 describe the joint probability of multiple event locations given the
-observed coda waves. The most likely set of locations is given by
+observed coda-waves. The most likely set of locations is given by
 the minimum of $L$.   In this paper we use the Polak-Ribiere
@@
 Relocating Earthquakes on the Calaveras 
-Fault and in Combining Travel Time and CWI Constraints.
+Fault and in Combining Arrival-Time and CWI Constraints.
 
@@
 
-We design a 2D synthetic acoustic experiment (example 1) by randomly
+We design a 2D synthetic acoustic experiment (example 1) to test the 
+performance of our CWI based relative location algorithm by randomly
 selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
@@
 event pairs and a dominant frequency of 2.5$\,$Hz to represent
-waveform data filtered between 1 and 5$\,$Hz. The CWI data are
+waveform data filtered between 1 and 5$\,$Hz. The purpose of these
+examples is to synthetically test the location algorithm. 
+Hence, we do not need to synthetically generate waveforms and compute
+CWI separation estimates, Rather, we begin by synthetically generating 
+the CWI separation estimates directly. \citet{dr_Robinson11a} showed that
+the CWI data are
 defined by the dominant wavelength normalized positive bounded
-Gaussian PDF with statistics $\bar{\mu}_N$ and $\bar{\sigma}_N$
-\citep{dr_Robinson11a}. A hypothetical CWI mean is created by
+Gaussian PDF with statistics $\bar{\mu}_N$ and $\bar{\sigma}_N$. 
+A hypothetical CWI mean is created by
 setting
@@
 ($\bar{\sigma}_N=0.02$) on the hypothetical CWI data. The average
-coordinate error is 2.0\,m which is small compared to the noise of
+coordinate error is 2.0\,m  (average location error of $\approx$4\,m) 
+which is small compared to the noise of
 $\bar{\sigma}_N=0.02$ which for $v_s=3300$\,ms$^{-1}$ and
@@
 \ref{fig-2D50eq-relocation_eg3} which have an average coordinate
-error of 2.8\,m.
+error of 2.8\,m (average location error of $\approx$9\,m).
 
@@
 optimization from 25 randomly chosen starting positions. We observe
-no differences in the solution for either example.
+negligble difference in the solutions indicating that neither example 
+is susceptible to local minima.
 
@@
 coverage in triangulation problems such as individual earthquake
-location from limited travel time data, or GPS positioning with few
+location from limited arrival-time data, or GPS positioning with few
 satellites. Our third observation is that the location errors form a
@@
 events with respect to each other. That is, even though the
-rotational freedom of the cluster is in principal removed by the
+rotational freedom of the cluster is in principle removed by the
 constraints imposed on the events (see equations
@@
 least constrained by data. For the CWI technique this ammounts to rotations in 2D.
-The same phenomena is observed in linear inversion where noise
+The same phenomenon is observed in linear inversion where noise
 creates large spurious model changes in directions of the
 eigenvectors with the smallest singular values \citep{dr_Aster05a}.
- Fortunately however, combining coda waves with
-measurements of travel times alleviates this problem and facilitate
-the removal of a local coordinate system altogether (see Combining Travel Time and 
-CWI Constraints). On balance however, we gain
+ Fortunately, however, combining coda-waves with
+measurements of arrival-times alleviates this problem and facilitates
+the removal of a local coordinate system altogether (see Combining Arrival-Time and 
+CWI Constraints). On balance, however, we gain
 confidence in the optimization procedure due to its stability for
@@
 the impact of reduced linkage between event pairs. In example 3, we
-repeat example 2 using 90\%, 80\%, ..., 10\% of the links. As with
-the above examples, we undertake the optimization with 25 randomly
+repeat example 2 using 90\%, 80\%, ..., 10\% of the links. 
+That is, we randomly select 10\% of the event pairs and remove the 
+separation estimates between those pairs to create a data set with 90\% 
+linkage. Then, we randomly remove 20\% of the links and so on. 
+This is experiment is designed to mimic a realistic recording situation 
+where CWI estimates are not available for all event pairs due to station 
+problems, poor signal-to-noise ratio or any number of other reasons.
+As with the above examples, we undertake the optimization with 25 randomly
 chosen starting locations.
 
-Figures \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrates
+Figures \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrate
 the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
@@
 that are directly linked by a separation estimate. We show the
-statistics for the `best' optimization solution (black) and for the
-solution space when all 25 optimizations are considered (gray). In
+statistics for the `best' optimization solution (thick) and for the
+solution space when all 25 optimizations are considered (this). In
 the former case the best solution is determined by the set of event
@@
 linkage is 60\% or lower. All optimizations fail when the linkage is
-20\% or lower. Despite their failure to converge, the locations at
-final iteration are close to the actual solution.
+20\% or lower.
 
@@
 In Example 4 we expand the optimization routine to 3D by randomly
-picking
- a set of actual event locations for 50 earthquakes with
+picking a set of event locations for 50 earthquakes with
 $-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case
-we assume a local velocity of $v=3,300\,$ms$^{-1}$ between all event
+we assume a local velocity of $v=3300\,$ms$^{-1}$ between all event
 pairs and a dominant frequency of 2.5$\,$Hz to represent
@@
 biases. We use a standard deviation for the noisy CWI estimates of
-$\bar{\sigma}_N = \epsilon$ and perform the optimization
+$\bar{\sigma}_N = \epsilon(\delta_t)$ (where $\epsilon(\delta_t)$ is the same 
+as that used in Examples 2 and 3) and perform the optimization
 using 10\%, 20\%, ..., 100\% of the direct links. In each case we
@@
 When 70\% of the direct constraints are considered all optimization
-results (gray) are consistent with the best solution obtained from
-all 25 starting locations (black). The
+results (thin) are consistent with the best solution obtained from
+all 25 starting locations (thick). The
 best solution constrains the event locations down to 30\% of the
-direct links. There is one notable difference between the 3D and 2D results. In 2D
-the final iteration was close to the actual solution when the
-optimization failed to converge. Conversely, in 3D the optimization
-appears to converge to the correct solution or fail completely,
-leading to a set of locations at final iteration which do not
-resemble the actual solution. This is depicted in Figure
-\ref{fig:optimisationresults-3Dsynth} by the absence of the gray and
-black lines below 60\% and 30\% of the constraints, respectively.
-The reason for this difference may be due to the increased number of
-degrees of freedom in 3D requiring a greater number of iterations to
-converge. Nevertheless, the accurate convergence of the best
+direct links. This is depicted in Figure
+\ref{fig:optimisationresults-3Dsynth} by the absence of the this and
+thick lines below 60\% and 30\% of the constraints, respectively.
+The accurate convergence of the best
 solution for cases with 30\% linkage or higher is encouraging for
@@
 wave data to constrain relative event location using optimization.
-The optimization error is influenced by the noise on CWI estimates
+The optimization error is rotational in nature and 
+influenced by the noise on CWI estimates
 with greater $\bar{\sigma}_N$ leading to larger errors in the
@@
 (Fig. \ref{fig:-eqopti-California-Calaveras}) and therefore lend
-themselves to accurate travel time location. This makes them ideal
+themselves to accurate arrival-time location. This makes them ideal
 for assessing the performance of a new location technique. Secondly,
@@
 \ref{eq:LitReview-g-3d-dc}. The relocations in this paper are sorted
-into four examples as summarised in Table \ref{tab:examples}.
+into four examples as summarised in Table \ref{tab:examples}. Waveforms, 
+cross correlations and separation estimates for example Calaveras event pairs are 
+illustrated by \citet{dr_Robinson11a}.
 
@@
 original catalogue locations for all 308 earthquakes. That is, each event
-is located individually using all available travel time arrivals and
+is located individually using all available arrival-time data and
 a regional velocity model. The 68 earthquakes of interest in this
@@
 probabilistic constraints on event separation. We utilize the
-local coordinate system introduced in Theory and find the
+local coordinate system introduced in the Theory Section and find the
 optimum relative locations using Polak-Ribiere optimization.
+
+In this, and the following Calaveras examples, we allow the earthquakes to 
+move freely in all three directions during the inversion despite using the 
+in-fault separation estimates given by \ref{eq:LitReview-fulDC-sep}.
+We allow the events to move freely so that we can test the 
+performance of our algorithm without assuming a-priori 
+that the earthquakes are constrained on the same fault plane. 
+We approximate the true event separation using the in-fault separation 
+of equation \ref{eq:LitReview-fulDC-sep} so that we can focus on developing 
+a working algorithm and demonstrate capability 
+without dealing with the complexity of 
+in-fault ($\delta_{\| fault}$) and and out-of-fault 
+($\delta_{\perp fault}^2$) displacement. Considering 
+the more complicated formulation of equation \ref{eq:LitReview-fulDC-sep} is
+left for future work. Another potential focus for future work 
+involves refining our algorithm  
+to simultaneously resolve event location and representative fault plane 
+by restricting the events to align in a single (unknown a-priori) plane. 
+Such an algorithm would be useful for cases where the earthquakes are 
+believed to be in the same plane.
 
@@
 hypoDD with Singular Value Decomposition (SVD), absolute arrival
-times and cross correlation computed travel time differences.
+times and cross correlation computed arrival-time differences.
 
 Absolute locations cannot be found by CWI alone. This is because of
-the non-uniquesness associated with translation, rotation and
+the non-uniqueness associated with translation, rotation and
 reflection. For the sake of comparison, we arbitrarily choose a
 `master' event and translate our relative locations to align with
-the hypoDD location for the same event. This arbitrary translation
+the hypoDD location for that event. This arbitrary translation
 does not change the relative locations. We return to this issue of
 relative versus absolute location in Example 7 by introducing a
-combined travel time and coda wave inversion.
+combined arrival-time and coda-wave inversion.
 
@@
 locations (column 2) than the hypoDD locations (column 3). Our
-experience suggest that the coda are less supportive of the presence of
+experience suggests that the CWI locationsare less supportive of the presence of
 streaks although a complete understanding of these differences is
@@
 understanding how both techniques perform with fewer stations
-(Example 6) and exploring how CWI and travel times can be combined
+(Example 6) and exploring how CWI and arrival-times can be combined
 (Examples 7 and 8).
@@
 We explore the impact of poorer recording situations in example 6 by
-re-locating the 68 Calaveras events  using hypoDD and coda waves
+re-locating the 68 Calaveras events  using hypoDD and coda-waves
 with a reduced number of stations. We begin with 10 stations and
 repeat the process removing one at a time until a single station
-remains. The 10 stations considered are shown in Figure
-\ref{fig:-eqopti-Calaveras-substations} and the order of removal
-explained in Table \ref{tab:Calaveras-stationremoval}.
+remains. The 10 stations and there order of removal are shown in Figure
+\ref{fig:-eqopti-Calaveras-substations}.
 
@@
 \ref{fig-69Calaverasevents_eg1} (column 2) when all stations are
-considered. That is, the coda wave approach is self-consistent
+considered. That is, the coda-wave approach is self-consistent
 regardless of the number of stations available, reinforcing our
-hypothesis that coda waves can constrain location in what would
+claim that coda-waves can constrain location in what would
 normally be regarded as a poor station network.
@@
 Figure \ref{fig-HYPODDreducesstats} illustrates the hypoDD inversion
-results for seven, five and four stations. The travel time problem
+results for seven, five and four stations. The arrival-time problem
 is ill-posed for fewer than four stations so it is not possible to
 apply hypoDD with SVD for three or fewer stations.  The hypoDD
-locations are not self-consistent as the number of stations is
+locations are less self-consistent as the number of stations is
 reduced. We observe a general increase in scatter and a higher
@@
 
-As the number of stations are reduced both the CWI and hypoDD
-techniques are not able to re-locate all events. To use the coda
+As the number of stations is reduced neither the CWI nor hypoDD
+techniques are able to re-locate all events. To use the coda
 waves we need at least one pairwise separation constraint to be
@@
 of all 68 earthquakes. When less than five stations are used the
-coda waves constrain a decreasing number of events until at one
+coda-waves constrain a decreasing number of events until at one
 station it is only possible to locate 55 of the 68 events. The
@@
 identified as unconstrainable in one of two stages. Firstly, the
-data are analyzed to ensure that there exists travel time
+data are analyzed to ensure that there exist arrival-time
 differences for each event and at least one other earthquake. This
-is analogous to the situation for the coda wave technique. The
+is analogous to the situation for the coda-wave technique. The
 hypoDD program also has a secondary identification phase in which
-events that can not be located sufficiently are rejected during the
+events that can not be located sufficiently well are rejected during the
 inversion. This process is related to the iterative removal of
@@
 The remaining panels of Figure \ref{fig-statremoval_summarystats}
-illustrate a statistical comparison of the CWI and hypoDD reduced
-station locations to those using hypoDD with all available data. For
+illustrate a statistical comparison of the CWI and hypoDD locations 
+with a reduced number of stations to those using hypoDD with all available data. For
 the CWI inversions the mean and maximum coordinate difference is
@@
 \begin{centering}
-\section*{Combining Travel Time and CWI Constraints}
+\section*{Combining Arrival-Time and CWI Constraints}
 \end{centering}
@@
 In Examples 5 and 6 we compare the location of the Calaveras
-earthquakes using coda wave and arrival time based constraints
+earthquakes using coda-wave and arrival time based constraints
 independently. Since the arrival time (direct or difference) and
-coda wave data
+coda-wave data
  come from different sections of the waveform they provide independent constraints on the locations.
  In this section we devise a location algorithm which incorporates
- both CWI and travel time data.
+ both CWI and arrival-time data.
 
 We do not propose a new technique for earthquake location using
-travel time differences. Rather, we exploit the information created
+arrival-time differences. Rather, we exploit the information created
 by hypoDD with SVD to define a probability density (or posterior)
@@
 \end{equation} \end{linenomath*}
-is the most likely location as determined using the travel time
+is the most likely location as determined using the arrival-time
 data, and
@@
 \end{equation} \end{linenomath*}
-is the covariance matrix. In this paper we define the mean location
+is the covariance matrix. We define the mean location
 $\mu_{\mathbf{e}_p}$ and covariance matrix by the hypoDD optimum
@@
 \end{equation} \end{linenomath*}
-incorporates the travel time constraints and
+incorporates the arrival-time constraints and
 \begin{linenomath*} \begin{equation}
@@
 \end{equation} \end{linenomath*}
- the coda waves.
+ the coda-waves.
 
@@
 
-Combining the travel time and coda wave data offers two advantages.
+Combining the arrival-time and coda-wave data offers two advantages.
 Firstly, it combines independent constraints on the event locations
 offering further confidence in the resulting solution. Secondly, the
-travel time constraints in the form of equation
+arrival-time constraints in the form of equation
 (\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
@@
 \vspace{1em}
-\subsection*{Example 7 - Combining travel time and CWI constraints}
+\subsection*{Example 7 - Combining arrival-time and CWI constraints}
 Figure
 \ref{fig-68Calaverasevents_ttandcoda1} illustrates the earthquake
-locations obtained when we combine the travel time and coda wave
+locations obtained when we combine the arrival-time and coda-wave
 data using all data (left) and five stations (right). The linear
@@
 \ref{fig-69Calaverasevents_eg1}) are evident in both cases. However,
-the coda waves introduce a scatter around these streaks. That is,
+the coda-waves introduce a scatter around these streaks. That is,
 the locations in figure \ref{fig-68Calaverasevents_ttandcoda1}
 result from a trade-off between hypoDD's desire to place the events
-on linear features and the coda waves voracity to push them away
+on linear features and the coda-waves voracity to push them away
 from streaks. When all stations are used the hypoDD constraints are
@@
 
-\subsection*{Example 8 - Combining CWI and travel times when the travel times constrain a limited number of events}
+\subsection*{Example 8 - Combining CWI and arrival-times when the arrival-times constrain a limited number of events}
 
@@
 it is possible to re-locate all events by employing the detailed
-travel time data when the temporary network is in-situ and using
-coda waves from network stations when the deployment is absent. The
+arrival-time data when the temporary network is in-situ and using
+coda-waves from network stations when the deployment is absent. The
 hypothesis, to be tested in this section, is that conducting such a
@@
 An estimate of the cummulative number of aftershocks $N(t)$ after
-$t$ days is given by the modified Omori formula
+$t$ days can be modeled by the modified Omori formula
 \begin{linenomath*} \begin{equation}
@@
 \end{equation} \end{linenomath*}
-This idea is illustrated in Figure \ref{fig:Omorifigure} which shows
+This is illustrated in Figure \ref{fig:Omorifigure} which shows
 the best fitting Omori Formula separated into segments before
@@
 attempt at relocating the Calaveras earthquakes. In Example 8 we
-consider the travel time constraints on half (34) of the earthquakes
-and incorporate coda wave data from a single station for all 68
+consider the arrival-time constraints on half (34) of the earthquakes
+and incorporate coda-wave data from a single station for all 68
 earthquakes. The combined inversion is shown in column 1 of Figure
 \ref{fig-68Calaverasevents_ttsubsetandcoda1}. The inversion result
-is similar to the combined inversion when all travel time data is
+is similar to the combined inversion when all arrival-time data are
 incorporated (see Fig. \ref{fig-68Calaverasevents_ttandcoda1}). The
 slight increase in scatter observed here can be explained by the
-events with no travel time constraints and the tendency of the coda
+events with no arrival-time constraints and the tendency of the coda
 to push events away from streaks.
 
-Remarkably, the combined coda wave and travel time inversion locates
+Remarkably, the combined coda-wave and arrival-time inversion locates
 all 68 earthquakes to an accuracy similar to the inversions with all
-data. In contrast when travel time data is used alone it is only
+data. In contrast when arrival-time data are used alone it is only
 possible to locate the 34 events recorded by the pseudo temporary
 deployment. This
-ability of  coda waves to constrain the location of events recorded
+ability of  coda-waves to constrain the location of events recorded
 by a single station creates new opportunities for understanding
@@
 
-Coda wave interferometry is an emerging technique for constraining
+Coda-wave interferometry is an emerging technique for constraining
 earthquake location. The technique relies on the interference
-between coda waves of closely located events and is hence useful for
-studying earthquake clusters and/or aftershock sequences. Coda wave
-constraints are independent of travel times and can be used in
+between coda-waves of closely located events and is hence useful for
+studying earthquake clusters and/or aftershock sequences. Coda-wave
+constraints are independent of arrival-times and can be used in
 isolation or combination with early onset body waves. The strength
@@
 
-Coda wave interferometry offers a new technique for understanding
+Coda-wave interferometry offers a new technique for understanding
 earthquakes in intraplate areas with sparse networks and poor
-azimuthal coverage. In particular, the ability to combine coda wave
-constraints with travel times makes it possible to link well
+azimuthal coverage. In particular, the ability to combine coda-wave
+constraints with arrival-times makes it possible to link well
 constrained events from a temporary deployment with those recorded
@@
 intraplate fault structures and improving our understanding of
-intraplate seismicity and earthquake hazard.
+intraplate seismicity and earthquake hazard. Importantly, this analysis 
+can be conducted for and historical aftershock sequence or earthquake swarm
+recorded by a temporay deployment, Our technique is, in that sense, related
+to the retorspective sesimological observation technique of 
+\citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
+on newly installed sensors regardless of whether the event occure before, 
+during or after the physical installation of the sensor.
 
@@
 benefited significantly from: reviews by Trevor Allen and Clive Collins
-at Geoscience Australia; as well as comments and advice received from
+at Geoscience Australia, the BSSA editorial team, Andrew Curtis from 
+the School fo GeoSciences at the University of Edinburgh and an anonymous 
+reviewer. The authors have also benefited fro comments and advice received from
 Felix Waldhauser on this and earlier research on the application of
@@
 
+\bibitem[{\textit{Curtis et~al.}(2012)}]{dr_Curtis12a_EPSL}
+Curtis, A., Behr, Y., Entwistle, E., Galetti, E., Townend J. Bannister, S. (2012),
+The benefit of hindsight in observational science: {R}etrospective
+seismological observations, \epsl, \textit{345--348}, 212--220.
+
 \bibitem[{\textit{Deichmann and Garcia-{F}ernandez}(1992)}]{dr_Deichmann92a}
@@
   C.~Kisslinger, chap.~50, pp. 823--825, Academic Press, London.
+
+\bibitem[{\textit{Slunga et~al.}(1995)}]{dr_Slunga95a}
+Slunga, R., R{\"o}gnvaldsson, {S. Th.} and B{\"o}dvarsson, R. (1995),
+Absolute and relative locations of similar events with application to microearthquakes in southern {I}celand,
+\gji,\textit{123}(2),409--419.
 
@@
  & hypoDD (using a subset of data). \\
-Example 7 & Combined use of CWI and travel time data \\
+Example 7 & Combined use of CWI and arrival-time data \\
 & with all and a reduced number of stations. \\
-Example 8 & Combined use of CWI and travel time data \\
- & when travel times constrain only 50\% of the events. \\
+Example 8 & Combined use of CWI and arrival-time data \\
+ & when arrival-times constrain only 50\% of the events. \\
  \hline
@@
 
-%%=======================================================================================
-% Table 3
-
-\begin{table}
-\caption{Stations considered when exploring the impact of reduced
-station coverage.} \label{tab:Calaveras-stationremoval}
-\begin{tabular}{|r|l|}
-\hline
-Number of & Station Names\\
-Stations  & \\
-\hline
-10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
-9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
-8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
-7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
-6  & CCO, JCB, JST, CMH, HSP, JAL \\
-5  & CCO, JCB, JST, CMH, HSP \\
-4  & CCO, JCB, JST, CMH \\
-3  & CCO, JCB, JST \\
-2  & CCO, JCB \\
-1  & CCO \\
-\hline
-\end{tabular}
-\end{table}
-
 \clearpage
@@
 using all constraints with noise $\bar{\sigma}_N=0.02$. Actual and
-optimization event locations are shown in triangles and circles,
+optimization event locations are identified by triangles and circles,
 respectively.} \label{fig-2D50eq-relocation_eg1}
@@
  Actual and optimization event locations
-are shown in triangles and circles, respectively.}
+are identified by triangles and circles, respectively.}
 \label{fig-2D50eq-relocation_eg3}
@@
 \caption{Example 4 - Statistical measures of error in the
-optimization solutions for the 3D synthetic cases when all (gray)
-and best (black) results are considered. The statistics
+optimization solutions for the 3D synthetic cases when all
+and best results are considered. The statistics
 $\Delta_{max}$ and $\Delta_\mu$ are the maximum and mean coordinate
-error, respectively. The absence of the gray and black lines below
+error, respectively. The absence of the lines below
 60\% and 30\% indicates a breakdown in the solutions when all or
@@
 \caption{Map
-showing location of the Calaveras cluster (white star) and 805
-seismic stations (black triangles).}
+showing location of the Calaveras cluster (star) and 805
+seismic stations (triangles).}
 \label{fig:-eqopti-California-Calaveras}
@@
 black, the gray catalogue locations for the remaining 240 (308-68)
-earthquakes are shown for the purpose of orientation only.}
+earthquakes are shown for the purpose of orientation only. In this and subsequent
+similar figures (Figures \ref{{fig-CWIreducesstats}}, \ref{fig-HYPODDreducesstats},
+\ref{fig-68Calaverasevents_ttandcoda1} and \ref{fig-68Calaverasevents_ttsubsetandcoda1}) 
+$x$ is defined as positive towards the east, y is positive towards the north and z is 
+positive down.}
 \label{fig-69Calaverasevents_eg1}
@@
 of the 10 stations (triangles) used to relocate the Calaveras events
-in Example 6 to 8. Stations are removed one at a time according to
-the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated. The events are indicated with black circles.}
+in Examples 6 to 8. Stations are removed one at a time according to
+the order defined by the bracketed numbers. That is, JRR is the first station to 
+be removed, JHL is the second and so on. Events are indicated with circles.}
 \label{fig:-eqopti-Calaveras-substations}
@@
 %\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
-\caption{Example 6 - CWI relative locations with reduced stations. \hspace{20em}}
+\caption{Example 6 - CWI relative locations with reduced stations. 
+Axes as defined in Figure \ref{fig-69Calaverasevents_eg1}.
+\hspace{20em}}
 \label{fig-CWIreducesstats}
@@
 \caption{Example 6 - HypoDD (SVD) relative locations with reduced
-stations. \hspace{20em} }
+stations. Axes as defined in Figure \ref{fig-69Calaverasevents_eg1}. 
+\hspace{20em} }
 \label{fig-HYPODDreducesstats}
@@
 locations using data form all stations (left) and 5 stations
-(right).} \label{fig-68Calaverasevents_ttandcoda1}
+(right). Axes as defined in Figure \ref{fig-69Calaverasevents_eg1}.} 
+\label{fig-68Calaverasevents_ttandcoda1}
 \end{figure}
@@
 Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
-using equation (\ref{eq:CumOmori}). The leftmost red, middle blue
-and rightmost red lines signify aftershocks occurring before, during
+using equation (\ref{eq:CumOmori}). The leftmost, middle
+and rightmost lines signify aftershocks occurring before, during
 and after the deployment of a pseudo temporary array installed 4
@@
 by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Relative locations are shown for the combined CWI and travel
-time inversion (left) and the inversion with travel times only
+events. Relative locations are shown for the combined CWI and arrival
+time inversion (left) and the inversion with arrival times only
 (right). Only by combining the data is it possible to locate all 68
 events. Furthermore, combining the data leads to a solution more
-consistent with Figure \ref{fig-69Calaverasevents_eg1}. }
+consistent with Figure \ref{fig-69Calaverasevents_eg1}. Axes as defined 
+in Figure \ref{fig-69Calaverasevents_eg1}.}
 \label{fig-68Calaverasevents_ttsubsetandcoda1}
@@
 
+%\appendix
+\clearpage
+\begin{centering}
+\section*{Appendix}
+\end{centering}
+
+\vspace{2em}
+
 \appendix
-\clearpage
-
-\vspace{2em}
-\begin{centering}
-\section*{The Likelihood}
-\end{centering}
+\subsection*{The Likelihood}
+%\numberwithin{equation}{section}
+\setcounter{equation}{0}
+\renewcommand{\theequation}{A\arabic{equation}}
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
 
@@
 \vspace{2em}
-\begin{centering}
-\section*{Derivatives}
-\end{centering}
+%\begin{centering}
+\subsection*{Derivatives}
+%\end{centering}
 

### 2013-06-23 paper2/figures.tex
finished incorporating review - needs one last check

--- 2013-01-04 paper2/paper2.tex
@@
 \begin{centering}
-\LARGE{\textbf{Relocating a Cluster of Earthquakes Using a Single Seismic Station}} \\  
+\LARGE{\textbf{Figures For: Relocating a Cluster of Earthquakes Using a Single Seismic Station}} \\  
 \end{centering}
@@
 \end{centering}
-
-\vspace{7em}
-\begin{tabular}{lp{0.6\textwidth}}
- & \\
-David Robinson: & Earth Monitoring and Hazard Group \\
- &  Geoscience Australia \\
- & GPO Box \emph{383} \\
- & Canberra ACT \emph{2601} Australia \\
- & E-mail: david.robinson@ga.gov.au\\
-\end{tabular}
-
-\clearpage
-\label{firstpage}
-
-%\maketitle
-
-\vspace{2em}
-\begin{centering}
-\section*{Abstract}
-\end{centering}
-Coda waves arise from scattering to form the later arriving
-components of a seismogram. Coda wave interferometry is an emerging
-tool for constraining earthquake source properties from the
-intereference pattern of coda waves between nearby events. A new
-earthquake location algorithm is derived which relies on coda wave
-based probabilistic estimates of earthquake separation. The
-algorithm can be used with coda waves alone or in tandem with travel
-time data. Synthetic examples in 2D and 3D and real earthquakes on
-the Calaveras Fault, California are used to demonstrate the
-potential of coda waves for locating poorly recorded earthquakes. It
-is demonstrated that coda wave interferometry: (a) outperforms
-traditional earthquake location techniques when the number of
-stations is small; (b) is self-consistent across a broad range of
-station situations; and (c) can be used with a single station to
-locate earthquakes.
-
-%\begin{keywords}
-% Probability distributions; Earthquake source observations;
-%Seismicity and tectonics; Wave scattering and diffraction
-%\end{keywords}
-
-\vspace{2em}
-\begin{centering}
-\section*{Introduction} 
-\end{centering}
-
-Accurate earthquake location is important for many applications. Locations
-are required for:  magnitude
-determination \citep{dr_Richter35a, dr_Gutenberg45a};
-computing moment tensors \citep{dr_Sipkin02a};
-seismological studies of the Earth's interior
-\citep{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a, dr_Kennett04a};
-understanding strong motion and seismic attenuation
-\citep{dr_Toro97a, dr_Campbell03a}
- and modeling earthquake hazard or risk
-\citep{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
-The accuracy required in earthquake location depends on the
-application. For example, imaging the structure of a fracture system
-from microseismicity requires greater detail than determining
-whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning.
- This paper focuses on reducing location uncertainty for
-a cluster of events when they are recorded by a small
-number of stations.
-
-Absolute location describes the location of an earthquake with
-respect to a global reference such as latitude, longitude (or
-easting/northing) and depth. Uncertainties associated with absolute
-locations are influenced by source to station distances, the number
-of stations and their geometry, signal-to-noise, clarity of onsets
-and accuracy of the velocity model used in computing travel times.
-Uncertainties in absolute location are typically of the order of
-several kilometers because they are susceptible to uncertainty in
-the velocity structure along the entire path between the source and
-receiver. For example, \citet{dr_Shearer99a} states that location
-uncertainty in the ISC (International Sesimological
-Centre) and PDE (National Earthquake
-Information
-Center)
-catalogues are generally around 25\,km horizontally and at least
-25\,km in depth (Here the depth uncertainties of 25\,km
-assume the use of depth dependent phases such as $pP$. Without such
-phases the uncertainty is higher). \citet{dr_Bondar04a} demonstrate
-that at the local scale, absolute locations are accurate to within
-5\,km with a 95\% confidence level when local networks meet a number
-of station related criteria. Such errors are too large for many
-applications, particularly those focussed on imaging rupture
-surfaces from aftershock sequences.
-
-Relative earthquake location involves locating a group of
-earthquakes with respect to one another and was first introduced by
-\citet{dr_Douglas67a} who developed the technique commonly known as
-joint hypocenter determination (\citet{dr_Douglas67a}
-originally used the term joint epicentre determination. However, he
-was solving for hypocentre). In principle, relative locations can be
-computed by differencing absolute locations. However,
-\citet{dr_Pavlis92a} shows that inadequate knowledge of velocity
-structure leads to systematic biases when relative positions are
-computed in this way. To reduce errors from unknown velocity
-structure, relative location techniques compute locations directly
-from travel time differences between two waveforms
-\citep{dr_Ito85a, dr_Got94a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
-so, they remove errors associated with velocity variations outside
-the local region, because such variations influence all waveforms in
-the same manner \citep{dr_Shearer99a}.
-
-Reported location uncertainties from relative techniques are  around
-15 to 75\,m in local settings with good station coverage
-\citep{dr_Ito85a, dr_Got94a, dr_Waldhauser99a,dr_Waldhauser08a}.
-Here, `good coverage' implies multiple stations distributed across a
-broad range of azimuthal directions. Relative location techniques
-have been used to image active fault planes \citep{dr_Deichmann92a,
-dr_Got94a, dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a}; study
-rupture mechanics \citep{dr_Rubin99a, dr_Rubin02a}; interpret magma
-movement in volcanoes \citep{dr_Fremont87a}; and monitor
-pumping-induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
-
-In traditional approaches to absolute and relative location only
-early onset body waves, typically $P$ and/or $S$ waves,are used. The
-data utilised may be the direct arrival times; travel time
-difference computed between picked arrivals of two waveforms; or
-time differences inferred from time-lagged cross correlation of
-relatively small windows around the body wave arrivals.
- In all three cases, the majority of the
-waveform is discarded. Furthermore, obtaining high accuracy with these techniques
-requires multiple stations with good azimuthal coverage.
-In this paper we demonstrate that it is possible to
-significantly reduce location uncertainty when few stations are
-available by using more of the waveform.
-
-Coda refers to  later arriving waves in the seismogram that arise
-from scattering  \citep{dr_Aki69a,dr_Snieder99a,dr_Snieder06a}. Coda
-waves are ignored in most seismological applications due to the
-complexity involved in constraining complex hetergeneous velocity models
-in real settings. In this paper we
-develop an approach for locating earthquakes using coda waves.
-\citet{dr_Snieder05a} demonstrate that the coda of two earthquakes
-can be used to estimate the separation between them. Their
-technique, known as coda wave interferometry (CWI), is based on the
-interference pattern between the coda waves. Unlike travel time
-based location techniques, CWI
- does not require multiple stations or good azimuthal coverage.
-In fact, it is possible to obtain estimates of separation using a single
-station \citep{dr_Robinson07b}. This makes CWI particularly interesting
-for regions where station density is low such as intraplate settings. In this
-paper we demonstrate how CWI separation estimates can be used to constrain
-location with data from a single station.
-Our technique can be used on coda waves alone or in combination with
-travel times. We begin by introducing the theory of CWI based earthquake location. 
-This is followed by a demonstration of capability using
-synthetic examples and application to earthquakes
-on the Calaveras fault, California using CWI alone
-and CWI in combination with travel time constraints.
-
-\vspace{2em}
-\begin{centering}
-\section*{Theory}
-\end{centering}
-\label{sec:theory}
-
-\citet{dr_Snieder05a} introduce a CWI based estimator of source
-separation $\delta_{CWI}$ between two earthquakes
-\begin{linenomath*} \begin{equation}
-\label{eq:Theory-dcwi_g_sigmat}
-\delta_{CWI}^2 = g(\alpha,\beta)\sigma_\tau^2,
-\end{equation} \end{linenomath*}
-where $\sigma_\tau$ is the standard deviation of the travel time
-perturbation between the coda waves of two earthquakes, and $\alpha$
-and $\beta$ are the near-source $P$ and $S$ wave velocities,
-respectively. The function $g$ depends on the type of excitation
-(explosion, point force, double couple) and on the direction of
-source displacement relative to the point force or double couple.
-For example, for two double couple sources displaced in the fault
-plane,
-\begin{linenomath*} \begin{equation}
-\label{eq:LitReview-g-3d-dc}
-g(\alpha,\beta) = 7
-\frac{\left(\frac{2}{\alpha^6}+\frac{3}{\beta^6}\right)}{\left(\frac{6}{\alpha^8}+\frac{7}{\beta^8}\right)},
-\end{equation} \end{linenomath*}
-whereas, for two point sources in a 2D acoustic medium
-\begin{linenomath*} \begin{equation}
-\label{eq:LitReview-g-2d-ps} g(\alpha,\beta) = 2 \alpha^2
-\end{equation} \end{linenomath*}
-\citep{dr_Snieder05a}. In this paper we use equation
-\ref{eq:LitReview-g-3d-dc} which assumes that the source mechanism
-of both events are identical, an assumption likely to be true for
-events in the same fault plane. \cite{dr_Robinson07c} explore the
-impact of a change in mechanism.
-
-The $\sigma_\tau$ in equation (\ref{eq:Theory-dcwi_g_sigmat}) is
-related to the maximum of the cross correlation between the coda of
-the two waveforms, $R_{max}$, and hence can be computed directly
-from the recorded data. The original formulation by
-\citet{dr_Snieder05a} used a second-order Taylor series expansion of
-the waveform autocorrelation function to relate $\sigma_\tau$ and
-$R_{max}$ by
-\begin{linenomath*} \begin{equation}
-\label{eq:Rmax-disp-orig} R_{max}^{(t,t_w)} = 1 - \frac{1}{2}
-\overline{\omega^2} \sigma_\tau^2,
-\end{equation} \end{linenomath*}
-In this paper we use the autocorrelation approach of
-\citet{dr_Robinson11a} to relate the parameters directly and we
-apply a restricted time lag search when evaluating $R_{max}$. These
-extensions to the original technique of \citet{dr_Snieder05a}
-increase the range of applicability of CWI by 50\% (i.e. from 300 to
-450\,m separation for 1 to 5\,Hz filtered coda waves).
-
-\citet{dr_Robinson11a} show that CWI leads to
-probabilistic constraints on source separation and introduce a
-Bayesian approach for describing the probability of true separation
-given the CWI data. Their approach is summarised by
-\begin{linenomath*} \begin{equation}
-\label{eq:-bayesian-noisyform}
-P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN}) \propto P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)
-\times P(\widetilde{\delta}_t)
-\end{equation} \end{linenomath*}
-where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the
-posterior function indicating the probability of true separation
-$\widetilde{\delta}_t$ given the noisy CWI separation estimates
-$\widetilde{\delta}_{CWIN}$;
-$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is the
-likelihood function (or forward model) giving the probability that
-the separation estimates $\widetilde{\delta}_{CWIN}$ would be
-observed if the true separation was $\widetilde{\delta}_t$; and
-$P(\widetilde{\delta}_t)$ is the prior PDF accounting for all
-a-priori information. The tilde above the separation parameters in
-equation (\ref{eq:-bayesian-noisyform}) indicates the use of a
-wavelength normalised separation parameter
-\begin{linenomath*} \begin{equation} 
-\label{eq-normalisation-eqn}
-\widetilde{\delta} = \frac{\delta}{\lambda_{d}},
-\end{equation} \end{linenomath*}
-which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$)
-with respect to dominant wavelength $\lambda_{d}$. In this paper we
-consider a uniform prior over appropriate bounds to ensure that the
-posterior function is dominated by the recorded data.
-The procedure for computing the likelihood
-$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
-\citet{dr_Robinson11a} and summarised in Appendix
-\ref{sec-Appendix-noisylikelihood}. With these two pieces in place
-we can compute the posterior
-$P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ (or PDF) for the
-separation between any pair of events directly from their coda
-waves.
-
-We seek a probability density function (PDF) which links
- individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-to describe the location of multiple events whose maximum corresponds to
- the most probable combination of locations.
-More importantly however, the PDF shall
-quantify location uncertainty and provide information
-on the degree to which individual events are constrained
- by the data. For convenience, we begin with three earthquakes having locations
-$\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian
-formulation we write
-\begin{linenomath*} \begin{equation}
-\label{eq-Bayes-three-locations}
-P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3| \mathbf{d}) \propto P( \mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)
-\times P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3),
-\end{equation} \end{linenomath*}
-where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$,
-$P(\mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ and
-$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
-likelihood and prior functions, respectively. In equation
-(\ref{eq-Bayes-three-locations}) $\mathbf{d}$ represents
-observations that constrain the locations. They can be any
-combination of travel times, geodetic information  or CWI
-separations. For example, if coda waves are used we have
-$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 |
-\widetilde{\mitbf{\delta}}_{CWIN})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3)$, where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the
-wavelength normalised separation estimates. Alternatively, if we use
-CWI and travel time data we may write $P(\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN},
-\mathbf{\Delta}_{TT})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{\Delta}_{TT}|\mathbf{e}_1,
-\mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-travel time differences. In the following derivation and in 
-Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault we focus
-on the constraints imposed by coda waves, whereas in 
-Combining Travel Time and CWI Constraints we demonstrate how CWI and travel
-time data can be combined.
-
-For three earthquakes we have likelihoods;
-$P(\widetilde{\delta}_{CWIN,12}|\mathbf{e}_1, \mathbf{e}_2)$,
-$P(\widetilde{\delta}_{CWIN,13}|\mathbf{e}_1, \mathbf{e}_3)$
-and
-$P(\widetilde{\delta}_{CWIN,23}|\mathbf{e}_2, \mathbf{e}_3)$.
-In writing
-these likelihoods we have replaced the conditional term on separation
-$\widetilde{\delta}_t$ with the locations (e.g. $\mathbf{e}_1$ and $\mathbf{e}_2$).
-This can be done because
-knowledge of location translates to separation.Note that the reverse is
-not true. That is, knowledge of separation between a single event pair
-does not uniquely translate to location but rather places a non-unique constraint on
-location.
-Furthermore, since the pairwise functions are independent the joint
-likelihood becomes
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\label{eq:-joint-likelihood4three}
-P(\widetilde{\mathbf{\delta}}_{CWIN} | \mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) =
-P(\widetilde{\delta}_{CWIN,12} | \mathbf{e}_1, \mathbf{e}_2) \\
-\hspace{2em} \times P(\widetilde{\delta}_{CWIN,13} | \mathbf{e}_1, \mathbf{e}_3)
-\times  P(\widetilde{\delta}_{CWIN,23} | \mathbf{e}_2, \mathbf{e}_3).
-\end{array}
-\end{equation} \end{linenomath*}
-Similarly, the earthquake locations are independent and the
-joint prior becomes
-\begin{linenomath*} \begin{equation}
-\label{eq:-joint-prior4three} P(\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3) = P(\mathbf{e}_1) \times P(\mathbf{e}_2) \times
-P(\mathbf{e}_3).
-\end{equation} \end{linenomath*}
-Combining equations (\ref{eq:-joint-likelihood4three}) and
-(\ref{eq:-joint-prior4three}) gives the joint posterior function
-\begin{linenomath*} \begin{equation}
-\label{eq-3eqposterior}
-\begin{array}{l}
-P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^3 P(\mathbf{e}_i) \\
-\hspace{4em}  \times \displaystyle \prod_{i=1}^2 \prod_{j=i+1}^3
-P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
-\end{array}
-\end{equation} \end{linenomath*}
-for three events.
-
-A detailed understanding of the location of a single event (e.g. $\mathbf{e}_2$) is obtained by computing the
-marginal
-\begin{linenomath*} \begin{equation}
-\label{eq:-E2-marginal}
-P(\mathbf{e}_2|\mathbf{\delta}_{CWIN}) = \int \int P(\mathbf{e}_1, \mathbf{e}_2,
- \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1
- d\mathbf{e}_3,
-\end{equation} \end{linenomath*}
-where the intergral is taken over all plausible locations for
-$\mathbf{e}_1$ and $\mathbf{e}_3$. Alternatively, we can compute the
-marginal for a single event coordinate by integrating the posterior
-over all events and remaining coordinates for the chosen earthquake.
-Evaluation of the normalizing constant $c$ in equation (\ref{eq-3eqposterior}) involves
-finding the integral of the posterior function
-over all plausible locations. In many applications the constant
-of proportionality $c$ can be ignored. For example, it is not
-required when seeking the combination of locations which maximise
- the posterior function, nor in Bayesian sampling algorithms such as Markov-chain Monte-Carlo
-techniques which only require evaluation of a function proportional to the PDF.
 

### 2013-06-23 paper2/paper2_submitted.tex
finished incorporating review - needs one last check

--- 2013-01-04 paper2/paper2.tex
@@
 of the 10 stations (triangles) used to relocate the Calaveras events
-in Example 6 to 8. Stations are removed one at a time according to
+in Examples 6 to 8. Stations are removed one at a time according to
 the order in Table \ref{tab:Calaveras-stationremoval} and the events
-relocated. The events are indicated with black circles.}
+relocated. Events are indicated with circles.}
 \label{fig:-eqopti-Calaveras-substations}

### 2013-06-30 paper2/paper2.tex
re-read the paper and made another set of edits

@@
 based probabilistic estimates of earthquake separation. The
-algorithm can be used with cod-waves alone or in tandem with arrival
-time data. Synthetic examples in 2D and 3D and real earthquakes on
+algorithm can be used with cod-waves alone or in tandem with arrival-time 
+data. Synthetic examples in 2D and 3D and real earthquakes on
 the Calaveras Fault, California are used to demonstrate the
 potential of coda-waves for locating poorly recorded earthquakes. It
-is demonstrated that coda wave interferometry: (a) outperforms
+is demonstrated that coda-wave interferometry: (a) outperforms
 traditional earthquake location techniques when the number of
@@
 application. For example, imaging the structure of a fracture system
-from microseismicity requires greater detail than determining
+from microseismicity requires greater location accuracy than determining
 whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning.
@@
 \item at least one station within 30 km. 
-\end{enumerate}. Such errors are too large for many
+\end{enumerate}
+Such errors are too large for many
 applications, particularly those focussed on imaging rupture
@@
 early-onset body waves 
-\citep{dr_Ito85a, dr_Got94a, dr_Slunga95a, dr_Nadeau97a, dr_Waldhauser99a}. By doing
-so, remove errors associated with velocity variations outside
+\citep{dr_Ito85a, dr_Got94a, dr_Slunga95a, dr_Nadeau97a, dr_Waldhauser99a}. Doing
+so removes errors associated with velocity variations outside
 the local region, because such variations influence all waveforms in
@@
 In traditional approaches to absolute and relative location only
-early onset body waves, typically $P$ and/or $S$ waves,are used. The
-data utilised may be the direct arrival times; arrival-time
+early onset body waves, typically $P$ and/or $S$ waves, are used. The
+data utilised may be the direct arrival-times; arrival-time
 difference computed between picked arrivals of two waveforms; or
-time differences inferred from time-lagged cross correlation of
+arrival-time differences inferred from time-lagged cross correlation of
 relatively small windows around the body wave arrivals.
@@
 The nomenclature is adopted here to remain consistent with \citet{dr_Robinson11a} who study 
-synthetically generated noise-free $\delta_{CWI}$ and relate them to noisy estimates $\delta_{CWIN}$
+synthetically generated noise-free $\delta_{CWI}$ and relate them to noisy estimates $\delta_{CWIN}$.
 The tilde above the separation parameters in
@@
 $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
-\citet{dr_Robinson11a} and summarised in Appendix
+\citet{dr_Robinson11a} and summarised in Appendix (The Likelihood)
 \ref{sec-Appendix-noisylikelihood}. With these two pieces in place
@@
 $P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{\Delta}_{TT}|\mathbf{e}_1,
-\mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represent
-arrival-time differences. In the following derivation and in 
-Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault we focus
+\mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represents
+the arrival-time differences. In the following derivation and in 
+the Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault section we focus
 on the constraints imposed by coda-waves, whereas in 
@@
 as the number of events being located increases. 
-For the purpose of this work we ignore this week dependance and assume independence. Therefore, we have
+For the purpose of this work we ignore this week dependance 
+and assume independence
 \begin{linenomath*} \begin{equation}
@@
 system when using coda-waves alone because the CWI technique constrains only event separation
-between earthquakes. The inclusion of arrival-times in Combining Arrival-Time and CWI Constraints
+between earthquakes. The inclusion of arrival-times in the Combining Arrival-Time 
+and CWI Constraints section 
 allows us to move to a global reference system.
@@
 technique \citep{dr_Press87a}, a conjugate gradient method, to
-minimize $L$. It uses the derivatives of $L$, derived in Appendix
+minimize $L$. It uses the derivatives of $L$, derived in Appendix (Derivatives)
 \ref{sec-Appendix-derivatives_ofL}, to guide the
@@
 Figure \ref{fig-2D50eq-relocation_eg1}.
- We assume a local velocity of $\alpha=3,300\,$ms$^{-1}$ between all
+ We assume a local velocity of $\alpha=3300\,$ms$^{-1}$ between all
 event pairs and a dominant frequency of 2.5$\,$Hz to represent
@@
 ($\bar{\sigma}_N=0.02$) on the hypothetical CWI data. The average
-coordinate error is 2.0\,m  (average location error of $\approx$4\,m) 
+coordinate error is 2.0\,m  (average location error $\approx$4\,m) 
 which is small compared to the noise of
@@
 \ref{fig-2D50eq-relocation_eg3} which have an average coordinate
-error of 2.8\,m (average location error of $\approx$9\,m).
+error of 2.8\,m (average location error $\approx$9\,m).
 
@@
 observation is analogous to problems associated with poor azimuthal
-coverage in triangulation problems such as individual earthquake
+coverage in triangulation such as individual earthquake
 location from limited arrival-time data, or GPS positioning with few
@@
 linkage. Then, we randomly remove 20\% of the links and so on. 
-This is experiment is designed to mimic a realistic recording situation 
+This experiment is designed to mimic a realistic recording situation 
 where CWI estimates are not available for all event pairs due to station 
@@
 
-Figures \ref{fig:optimisationresults-2Dsynth}(a) and (b) illustrate
+Figure \ref{fig:optimisationresults-2Dsynth} illustrates
 the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
@@
 statistics for the `best' optimization solution (thick) and for the
-solution space when all 25 optimizations are considered (this). In
+solution space when all 25 optimizations are considered (thin). In
 the former case the best solution is determined by the set of event
@@
 average number of branches can be computed in advance it can be used
-as an indication of the inversion stability prior to optimization. A
+as an indication of inversion stability prior to optimization. A
 higher breakdown is observed when all 25 solutions are considered
@@
 direct links. This is depicted in Figure
-\ref{fig:optimisationresults-3Dsynth} by the absence of the this and
-thick lines below 60\% and 30\% of the constraints, respectively.
+\ref{fig:optimisationresults-3Dsynth} by the absence of the thin and
+thick lines below 60\% and 30\% linkage, respectively.
 The accurate convergence of the best
@@
 with greater $\bar{\sigma}_N$ leading to larger errors in the
-solutions. When 70\% or more of the direct branches are used the
+solutions. In 3D, when 70\% or more of the direct branches are used the
 optimizer is stable with no observable difference in the solution
@@
 cross correlations and separation estimates for example Calaveras event pairs are 
-illustrated by \citet{dr_Robinson11a}.
+illustrated by \citet{dr_Robinson11a} an are not repeated her for the sake of brevity.
 
@@
 0\,s. CWI estimates are obtained from 5\,s wide non-overlapping time
-windows between $2.5 \leq t \leq 20$\,s and used to create
+windows between $2.5 < t \leq 20$\,s and used to create
 probabilistic constraints on event separation. We utilize the
@@
 move freely in all three directions during the inversion despite using the 
-in-fault separation estimates given by \ref{eq:LitReview-fulDC-sep}.
+in-fault separation estimates given by equation \ref{eq:LitReview-g-3d-dc}.
 We allow the events to move freely so that we can test the 
@@
 We approximate the true event separation using the in-fault separation 
-of equation \ref{eq:LitReview-fulDC-sep} so that we can focus on developing 
+of equation \ref{eq:LitReview-g-3d-dc} so that we can focus on developing 
 a working algorithm and demonstrate capability 
 without dealing with the complexity of 
-in-fault ($\delta_{\| fault}$) and and out-of-fault 
+in-fault ($\delta_{\| fault}$) and out-of-fault 
 ($\delta_{\perp fault}^2$) displacement. Considering 
@@
 by restricting the events to align in a single (unknown a-priori) plane. 
-Such an algorithm would be useful for cases where the earthquakes are 
-believed to be in the same plane.
+That is, for cases where the earthquakes are 
+believed a-priori to be in the same plan.
 
@@
 locations (column 2) than the hypoDD locations (column 3). Our
-experience suggests that the CWI locationsare less supportive of the presence of
+experience suggests that the CWI locations are less supportive of the presence of
 streaks although a complete understanding of these differences is
@@
 formed from the available stations. This means that for every event
-there must be at least one station that records it and at least one
-other earthquake sufficiently well to apply CWI. Fortunately, we can
+there must be at least one station that records it, and at least one
+other earthquake, sufficiently well to apply CWI. Fortunately, we can
 make an assessment of this prior to starting the inversion. The top
@@
 improve the behavior of the Polak-Ribiere optimization leading to
-faster and more stable convergence. Consequently, we no longer have
+faster and more stable convergence. Consequently, we no longer need
 to consider multiple randomly chosen starting locations.
@@
 This is illustrated in Figure \ref{fig:Omorifigure} which shows
-the best fitting Omori Formula separated into segments before
-(gray), during (black) and after (gray) the pseudo temporary
+the best fitting Omori Formula separated into segments before, during 
+and after the pseudo temporary
 deployment.
@@
 intraplate seismicity and earthquake hazard. Importantly, this analysis 
-can be conducted for and historical aftershock sequence or earthquake swarm
+can be conducted for any historical aftershock sequence or earthquake swarm
 recorded by a temporay deployment, Our technique is, in that sense, related
@@
 \citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
-on newly installed sensors regardless of whether the event occure before, 
+on newly installed sensors regardless of whether the event occurs before, 
 during or after the physical installation of the sensor.
@@
 at Geoscience Australia, the BSSA editorial team, Andrew Curtis from 
-the School fo GeoSciences at the University of Edinburgh and an anonymous 
-reviewer. The authors have also benefited fro comments and advice received from
+the School of GeoSciences at the University of Edinburgh and an anonymous 
+reviewer. The authors have also benefited from comments and advice received from
 Felix Waldhauser on this and earlier research on the application of
@@
 earthquakes are shown for the purpose of orientation only. In this and subsequent
-similar figures (Figures \ref{{fig-CWIreducesstats}}, \ref{fig-HYPODDreducesstats},
+similar figures (Figures \ref{fig-CWIreducesstats}, \ref{fig-HYPODDreducesstats},
 \ref{fig-68Calaverasevents_ttandcoda1} and \ref{fig-68Calaverasevents_ttsubsetandcoda1}) 
@@
 \caption{Example 6 - Number of constrainable events $nE$ in the CWI
-and hypoDD inversions as a function of the stations considered
+and hypoDD inversions as a function of the number of stations considered
 (top). Mean (middle) and maximum (bottom) of the difference computed
@@
 %\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
-\caption{Cumulative number of aftershocks for the
+\caption{Modeled cumulative number of aftershocks for the
 Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of 12 July 1993
@@
 \caption{Example 8 - Mimicking the deployment of a temporary network
-by ignoring data from all but station CCO for 50\% (or 34) of the
-events. Relative locations are shown for the combined CWI and arrival
-time inversion (left) and the inversion with arrival times only
+by ignoring data from all but station CCO for 50\% (or 34) of the 68
+events. Relative locations are shown for the combined CWI and arrival-time 
+inversion (left) and the inversion with arrival-times only
 (right). Only by combining the data is it possible to locate all 68

### 2013-06-30 paper2/paper2_figures.tex
added a pdf of figures only

--- 2013-06-30 paper2/paper2.tex
@@
 
-\begin{centering}
-\LARGE{\textbf{Relocating a Cluster of Earthquakes Using a Single Seismic Station}} \\  
-\end{centering}
-\vspace{3em}
-\begin{centering}
-David J. Robinson, Malcolm Sambridge, Roel Snieder, Juerg Hauser \\
-\end{centering}
-
-\vspace{7em}
-\begin{tabular}{lp{0.6\textwidth}}
- & \\
-David Robinson: & Earth Monitoring and Hazard Group \\
- &  Geoscience Australia \\
- & GPO Box \emph{383} \\
- & Canberra ACT \emph{2601} Australia \\
- & E-mail: david.robinson@ga.gov.au\\
-\end{tabular}
-
-\clearpage
-\label{firstpage}
-
-%\maketitle
-
-\vspace{2em}
-\begin{centering}
-\section*{Abstract}
-\end{centering}
-Coda-waves arise from scattering to form the later arriving
-components of a seismogram. Coda-wave interferometry is an emerging
-tool for constraining earthquake source properties from the
-intereference pattern of coda-waves between nearby events. A new
-earthquake location algorithm is derived which relies on coda-wave
-based probabilistic estimates of earthquake separation. The
-algorithm can be used with cod-waves alone or in tandem with arrival-time 
-data. Synthetic examples in 2D and 3D and real earthquakes on
-the Calaveras Fault, California are used to demonstrate the
-potential of coda-waves for locating poorly recorded earthquakes. It
-is demonstrated that coda-wave interferometry: (a) outperforms
-traditional earthquake location techniques when the number of
-stations is small; (b) is self-consistent across a broad range of
-station situations; and (c) can be used with a single station to
-locate earthquakes.
-
-%\begin{keywords}
-% Probability distributions; Earthquake source observations;
-%Seismicity and tectonics; Wave scattering and diffraction
-%\end{keywords}
-
-\vspace{2em}
-\begin{centering}
-\section*{Introduction} 
-\end{centering}
-
-Accurate earthquake location is important for many applications. Locations
-are required for:  magnitude
-determination \citep{dr_Richter35a, dr_Gutenberg45a};
-computing moment tensors \citep{dr_Sipkin02a};
-seismological studies of the Earth's interior
-\citep{dr_Spencer80a, dr_Kennett95a, dr_Curtis02a, dr_Kennett04a};
-understanding strong motion and seismic attenuation
-\citep{dr_Toro97a, dr_Campbell03a}
- and modeling earthquake hazard or risk
-\citep{dr_Frankel00a, dr_Stirling02a, dr_Robinson06b}.
-The accuracy required in earthquake location depends on the
-application. For example, imaging the structure of a fracture system
-from microseismicity requires greater location accuracy than determining
-whether a $M_w=7.5$ earthquake occurs offshore for tsunami warning.
- This paper focuses on reducing location uncertainty for
-a cluster of events when they are recorded by a small
-number of stations.
-
-Absolute location describes the location of an earthquake with
-respect to a global reference such as latitude, longitude (or
-easting/northing) and depth. Uncertainties associated with absolute
-locations are influenced by source to station distances, the number
-of stations and their geometry, signal-to-noise ratio, clarity of onsets
-and accuracy of the velocity model used in computing arrival-times.
-Uncertainties in absolute location are typically of the order of
-several kilometers, primarily because they are susceptible to uncertainty in
-the velocity structure along the entire path between the source and
-receiver. For example, \citet{dr_Shearer99a} states that location
-uncertainties in the ISC (International Sesimological
-Centre) and PDE (National Earthquake
-Information
-Center)
-catalogues are generally around 25\,km horizontally and at least
-25\,km in depth (Here the depth uncertainties of 25\,km
-assume the use of depth dependent phases such as $pP$. Without such
-phases the uncertainty is higher). \citet{dr_Bondar04a} demonstrate
-that absolute locations are accurate to within
-5\,km with a 95\% confidence level when local networks meet the following 
-criteria:
-\begin{enumerate}
-\item there are 10 or more stations, all within 250 km, 
-\item an azimuthal gap of less than 110$^o$, 
-\item a secondary azimuthal gap of less than 160$^o$, and 
-\item at least one station within 30 km. 
-\end{enumerate}
-Such errors are too large for many
-applications, particularly those focussed on imaging rupture
-surfaces from aftershock sequences.
-
-Relative earthquake location involves locating a group of
-earthquakes with respect to one another and was first introduced by
-\citet{dr_Douglas67a} who developed the technique commonly known as
-joint hypocenter determination (\citet{dr_Douglas67a}
-originally used the term joint epicentre determination. However, he
-was solving for hypocentre). In principle, relative locations can be
-computed by differencing absolute locations. However,
-\citet{dr_Pavlis92a} shows that inadequate knowledge of velocity
-structure leads to systematic biases when relative positions are
-computed in this way. To reduce errors from unknown velocity
-structure, relative location techniques typically compute locations directly
-from arrival-time differences computed by time-lag cross correlation of
-early-onset body waves 
-\citep{dr_Ito85a, dr_Got94a, dr_Slunga95a, dr_Nadeau97a, dr_Waldhauser99a}. Doing
-so removes errors associated with velocity variations outside
-the local region, because such variations influence all waveforms in
-a similar manner \citep{dr_Shearer99a}.
-
-Reported location uncertainties from relative techniques are around
-15 to 75\,m in local settings with good station coverage
-\citep{dr_Ito85a, dr_Got94a, dr_Waldhauser99a,dr_Waldhauser08a}.
-Here, `good coverage' implies multiple stations distributed across a
-broad range of azimuthal directions. Relative location techniques
-have been used to image active fault planes \citep{dr_Deichmann92a,
-dr_Got94a, dr_Waldhauser99a, dr_Waldhauser02a, dr_Shearer05a}; study
-rupture mechanics \citep{dr_Rubin99a, dr_Rubin02a}; interpret magma
-movement in volcanoes \citep{dr_Fremont87a}; and monitor
-pumping-induced seismicity \citep{dr_Lees98a, dr_Ake05a}.
-
-In traditional approaches to absolute and relative location only
-early onset body waves, typically $P$ and/or $S$ waves, are used. The
-data utilised may be the direct arrival-times; arrival-time
-difference computed between picked arrivals of two waveforms; or
-arrival-time differences inferred from time-lagged cross correlation of
-relatively small windows around the body wave arrivals.
- In all three cases, the majority of the
-waveform is discarded. Furthermore, obtaining high accuracy with these techniques
-requires multiple stations with good azimuthal coverage.
-In this paper we demonstrate that it is possible to
-significantly reduce location uncertainty when few stations are
-available by using more of the waveform.
-
-Coda refers to  later arriving waves in the seismogram that arise
-from scattering  \citep{dr_Aki69a,dr_Snieder99a,dr_Snieder06a}. Coda
-waves are ignored in most seismological applications due to the
-complexity involved in constraining complex hetergeneous velocity models
-in real settings. In this paper we
-develop an approach for locating earthquakes using coda-waves.
-\citet{dr_Snieder05a} demonstrate that the coda of two earthquakes
-can be used to estimate the separation between them. Their
-technique, known as coda wave interferometry (CWI), is based on the
-interference pattern between the coda-waves. Unlike arrival-time
-based location techniques, CWI
- does not require multiple stations or good azimuthal coverage.
-In fact, it is possible to obtain estimates of separation using a single
-station \citep{dr_Robinson07b}. This makes CWI particularly interesting
-for regions where station density is low such as intraplate settings. In this
-paper we demonstrate how CWI separation estimates can be used to constrain
-location with data from a single station.
-Our technique can be used on coda-waves alone or in combination with
-arrival-times. We begin by introducing the theory of CWI based earthquake location. 
-This is followed by a demonstration of capability using
-synthetic examples and application to earthquakes
-on the Calaveras fault, California using CWI alone
-and CWI in combination with arrival-time constraints.
-
-\vspace{2em}
-\begin{centering}
-\section*{Theory}
-\end{centering}
-\label{sec:theory}
-
-\citet{dr_Snieder05a} introduce a CWI based estimator of source
-separation $\delta_{CWI}$ between two earthquakes
-\begin{linenomath*} \begin{equation}
-\label{eq:Theory-dcwi_g_sigmat}
-\delta_{CWI}^2 = g(\alpha,\beta)\sigma_\tau^2,
-\end{equation} \end{linenomath*}
-where $\sigma_\tau$ is the standard deviation of the arrival-time
-perturbation between the coda-waves of two earthquakes, and $\alpha$
-and $\beta$ are the near-source $P$ and $S$ wave velocities,
-respectively. The function $g$ depends on the type of excitation
-(explosion, point force, double couple) and on the direction of
-source displacement relative to the point force or double couple.
-For example, for two double couple sources displaced in the fault
-plane,
-\begin{linenomath*} \begin{equation}
-\label{eq:LitReview-g-3d-dc}
-g(\alpha,\beta) = 7
-\frac{\left(\frac{2}{\alpha^6}+\frac{3}{\beta^6}\right)}{\left(\frac{6}{\alpha^8}+\frac{7}{\beta^8}\right)},
-\end{equation} \end{linenomath*}
-whereas, for two point sources in a 2D acoustic medium
-\begin{linenomath*} \begin{equation}
-\label{eq:LitReview-g-2d-ps} g(\alpha,\beta) = 2 \alpha^2
-\end{equation} \end{linenomath*}
-\citep{dr_Snieder05a}. \citet{dr_Snieder05a} also show that for two 
-double couple sources that are not in the same fault plane
-\begin{linenomath*} \begin{equation}
-\label{eq:LitReview-fulDC-sep}
-\sigma_\tau^2 = 
-\frac{ \left(\frac{6}{\alpha^8}+\frac{7}{\beta^8} \right) \delta_{\| fault}^2 + 
-2 \left(\frac{1}{\alpha^8}+\frac{2}{\beta^8} \right) \delta_{\perp fault}^2 }
-{7 \left(\frac{2}{\alpha^8}+\frac{3}{\beta^8} \right)},
-\end{equation} \end{linenomath*}
-where $\delta_{\| fault}^2$ and $\delta_{\perp fault}^2$ are the separation parallel 
-and perpendicular to the fault, respectively. In this paper we use 
-equation \ref{eq:LitReview-g-2d-ps} for the 2D examples.
-For the 3D examples we use equation
-\ref{eq:LitReview-g-3d-dc} which assumes that the source mechanism
-of both events are identical, an assumption likely to be true for
-events in the same fault plane. \cite{dr_Robinson07c} explore the
-impact of a change in mechanism.
-
-The $\sigma_\tau$ in equation (\ref{eq:Theory-dcwi_g_sigmat}) is
-related to the maximum of the cross correlation between the coda of
-the two waveforms, $R_{max}$, and hence can be computed directly
-from the recorded data. The original formulation by
-\citet{dr_Snieder05a} used a second-order Taylor series expansion of
-the waveform autocorrelation function to relate $\sigma_\tau$ and
-$R_{max}$ by
-\begin{linenomath*} \begin{equation}
-\label{eq:Rmax-disp-orig} R_{max}^{(t,t_w)} = 1 - \frac{1}{2}
-\overline{\omega^2} \sigma_\tau^2,
-\end{equation} \end{linenomath*}
-where $\overline{\omega^2}$ is the square of the dominant angular frequency
-\begin{equation}
-\label{eq:square-of-domangfreq}
-\overline{\omega^2} =
-\frac{\int_{t-t_w}^{t+t_w}\dot{u}_i^2(t')dt'}{\int_{t-t_w}^{t+t_w}u_i^2(t')dt'},
-\end{equation}
-and $\dot{u}_i$ represents the time derivative of $u_i$.
-In this paper we use the autocorrelation approach of
-\citet{dr_Robinson11a} to relate the parameters directly and we
-apply a restricted time lag search when evaluating $R_{max}$. These
-extensions to the original technique of \citet{dr_Snieder05a}
-increase the range of applicability of CWI by 50\% (i.e. from 300 to
-450\,m separation for 1 to 5\,Hz filtered coda-waves).
-
-\citet{dr_Robinson11a} show that CWI leads to
-probabilistic constraints on source separation and introduce a
-Bayesian approach for describing the probability of true separation
-given the CWI data. Their approach is summarised by
-\begin{linenomath*} \begin{equation}
-\label{eq:-bayesian-noisyform}
-P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN}) \propto P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)
-\times P(\widetilde{\delta}_t)
-\end{equation} \end{linenomath*}
-where  $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ is the
-posterior function indicating the probability of true separation
-$\widetilde{\delta}_t$ given the noisy CWI separation estimates
-$\widetilde{\delta}_{CWIN}$;
-$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is the
-likelihood function (or forward model) giving the probability that
-the separation estimates $\widetilde{\delta}_{CWIN}$ would be
-observed if the true separation was $\widetilde{\delta}_t$; and
-$P(\widetilde{\delta}_t)$ is the prior probability density function (PDF) accounting for all
-a-priori information. The use of $N$ in $\delta_{CWIN}$ depicts CWI separations that include noise. 
-The nomenclature is adopted here to remain consistent with \citet{dr_Robinson11a} who study 
-synthetically generated noise-free $\delta_{CWI}$ and relate them to noisy estimates $\delta_{CWIN}$.
-The tilde above the separation parameters in
-equation (\ref{eq:-bayesian-noisyform}) indicates the use of a
-wavelength normalised separation parameter
-\begin{linenomath*} \begin{equation} 
-\label{eq-normalisation-eqn}
-\widetilde{\delta} = \frac{\delta}{\lambda_{d}},
-\end{equation} \end{linenomath*}
-which measures separation ($\delta$ = $\delta_{CWIN}$ or $\delta_t$)
-with respect to dominant wavelength $\lambda_{d}$. In this paper we
-consider a uniform prior over appropriate bounds to ensure that the
-posterior function is dominated by the recorded data.
-The procedure for computing the likelihood
-$P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$ is derived by
-\citet{dr_Robinson11a} and summarised in Appendix (The Likelihood)
-\ref{sec-Appendix-noisylikelihood}. With these two pieces in place
-we can compute the posterior
-$P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$ (or PDF) for the
-separation between any pair of events directly from their coda
-waves.
-
-We seek a PDF which links
- individual pairwise posteriors $P(\widetilde{\delta}_t|\widetilde{\delta}_{CWIN})$
-to describe the location of multiple events whose maximum corresponds to
- the most probable combination of locations.
-More importantly, however, the PDF shall
-quantify location uncertainty and provide information
-on the degree to which individual events are constrained
- by the data. For convenience, we begin with three earthquakes having locations
-$\mathbf{e}_1$, $\mathbf{e}_2$ and $\mathbf{e}_3$. Using a Bayesian
-formulation we write
-\begin{linenomath*} \begin{equation}
-\label{eq-Bayes-three-locations}
-P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3| \mathbf{d}) \propto P( \mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)
-\times P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3),
-\end{equation} \end{linenomath*}
-where $P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \mathbf{d})$,
-$P(\mathbf{d}|\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ and
-$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3)$ are the posterior,
-likelihood and prior functions, respectively. In equation
-(\ref{eq-Bayes-three-locations}) $\mathbf{d}$ represents
-observations that constrain the locations. They can be any
-combination of arrival-times, geodetic information  or CWI
-separations. For example, if coda-waves are used we have
-$P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 |
-\widetilde{\mitbf{\delta}}_{CWIN})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN}|\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3)$, where $\widetilde{\mitbf{\delta}}_{CWIN}$ are the
-wavelength normalised separation estimates. Alternatively, if we use
-CWI and arrival-time data we may write $P(\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN},
-\mathbf{\Delta}_{TT})$ and
-$P(\widetilde{\mitbf{\delta}}_{CWIN},\mathbf{\Delta}_{TT}|\mathbf{e}_1,
-\mathbf{e}_2, \mathbf{e}_3)$ where $\mathbf{\Delta}_{TT}$ represents
-the arrival-time differences. In the following derivation and in 
-the Synthetic Experiements and Relocating Earthquakes on the Calaveras Fault section we focus
-on the constraints imposed by coda-waves, whereas in 
-Combining Arrival-Time and CWI Constraints we demonstrate how CWI and arrival-time data can be combined.
-
-For three earthquakes we have likelihoods;
-$P(\widetilde{\delta}_{CWIN,12}|\mathbf{e}_1, \mathbf{e}_2)$,
-$P(\widetilde{\delta}_{CWIN,13}|\mathbf{e}_1, \mathbf{e}_3)$
-and
-$P(\widetilde{\delta}_{CWIN,23}|\mathbf{e}_2, \mathbf{e}_3)$.
-In writing
-these likelihoods we have replaced the conditional term on separation
-$\widetilde{\delta}_t$ with the locations (e.g. $\mathbf{e}_1$ and $\mathbf{e}_2$).
-This can be done because
-knowledge of location translates to separation. Note, however, that the reverse is
-not true. That is, knowledge of separation between a single event pair
-does not uniquely translate to location but rather places a non-unique constraint on
-location. In other words, knowing $|e1-e2|$ and $|e2-e3|$ does not mean that $|e1-e3|$ is 
-uniquely defined. Consequently, the likelihoods are weekly dependent, in that some 
-likelihood-pairs share common events, an occurrence that becomes relatively less frequent 
-as the number of events being located increases. 
-For the purpose of this work we ignore this week dependance 
-and assume independence
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\label{eq:-joint-likelihood4three}
-P(\widetilde{\mathbf{\delta}}_{CWIN} | \mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3) \approx
-P(\widetilde{\delta}_{CWIN,12} | \mathbf{e}_1, \mathbf{e}_2) \\
-\hspace{2em} \times P(\widetilde{\delta}_{CWIN,13} | \mathbf{e}_1, \mathbf{e}_3)
-\times  P(\widetilde{\delta}_{CWIN,23} | \mathbf{e}_2, \mathbf{e}_3).
-\end{array}
-\end{equation} \end{linenomath*}
-Similarly, the earthquake locations are independent and the
-joint prior becomes
-\begin{linenomath*} \begin{equation}
-\label{eq:-joint-prior4three} P(\mathbf{e}_1, \mathbf{e}_2,
-\mathbf{e}_3) = P(\mathbf{e}_1) \times P(\mathbf{e}_2) \times
-P(\mathbf{e}_3).
-\end{equation} \end{linenomath*}
-Combining equations (\ref{eq:-joint-likelihood4three}) and
-(\ref{eq:-joint-prior4three}) gives the joint posterior function
-\begin{linenomath*} \begin{equation}
-\label{eq-3eqposterior}
-\begin{array}{l}
-P(\mathbf{e}_1, \mathbf{e}_2, \mathbf{e}_3 | \widetilde{\mitbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^3 P(\mathbf{e}_i) \\
-\hspace{4em}  \times \displaystyle \prod_{i=1}^2 \prod_{j=i+1}^3
-P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)
-\end{array}
-\end{equation} \end{linenomath*}
-for three events.
-
-A detailed understanding of the location of a single event (e.g. $\mathbf{e}_2$) is obtained by computing the
-marginal
-\begin{linenomath*} \begin{equation}
-\label{eq:-E2-marginal}
-P(\mathbf{e}_2|\mathbf{\delta}_{CWIN}) = \int \int P(\mathbf{e}_1, \mathbf{e}_2,
- \mathbf{e}_3 | \widetilde{\mathbf{\delta}}_{CWIN}) d\mathbf{e}_1
- d\mathbf{e}_3,
-\end{equation} \end{linenomath*}
-where the intergral is taken over all plausible locations for
-$\mathbf{e}_1$ and $\mathbf{e}_3$. Alternatively, we can compute the
-marginal for a single event coordinate by integrating the posterior
-over all events and remaining coordinates for the chosen earthquake.
-Evaluation of the normalizing constant $c$ in equation (\ref{eq-3eqposterior}) involves
-finding the integral of the posterior function
-over all plausible locations. In many applications the constant
-of proportionality $c$ can be ignored. For example, it is not
-required when seeking the combination of locations which maximise
- the posterior function, nor in Bayesian sampling algorithms such as Markov-chain Monte-Carlo
-techniques which only require evaluation of a function proportional to the PDF.
-
-Extending to $n$ events we get the posterior function
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\label{posterior-n-events}
-P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN}) = c \displaystyle \prod_{i=1}^n P(\mathbf{e}_i) \\
-\hspace{4em} \displaystyle  \times \prod_{i=1}^{n-1} \prod_{j=i+1}^n P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j).
-\end{array}
-\end{equation} \end{linenomath*}
-When evaluating equation (\ref{posterior-n-events})
-over a range of locations it is necessary to compute and multiply
-many numbers close to zero. This is because the PDFs tend to zero as
-the locations get less likely (i.e. near the boundaries of the
-plausible region). Such calculations are prone to truncation errors
-and so we work with the negative logarithm
-\begin{linenomath*} \begin{equation}
-\label{eq:-negative-log-part1}
-L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n) = -ln\left[ P(\mathbf{e}_1,...,\mathbf{e}_n | \widetilde{\mathbf{\delta}}_{CWIN} )  \right]
-\end{equation} \end{linenomath*}
-or
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\label{eq:-negative-log}
-L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n) =
--ln\left[ c \right] - \displaystyle \sum_{i=1}^n ln\left[P(\mathbf{e}_i)\right] \\
-\hspace{3em} - \displaystyle \sum_{i=1}^{n-1} \sum_{j=i+1}^n ln\left[P(\widetilde{\delta}_{CWIN,ij}|\mathbf{e}_i,\mathbf{e}_j)\right].
-\end{array}
-\end{equation} \end{linenomath*}
-The logarithm improves numerical stability by replacing products
-with summations. The negative facilitates the use of optimisation
-algorithms that are designed to minimise an objective function.
-
-The event locations $\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n$
-are defined by coordinates $\hat{x}$, $\hat{y}$ and $\hat{z}$ where
-the hat indicates use of a local coordinate system. We choose a
-local coordinate system which removes ambiguity associated with
-transformations of the coordinate system. It is necessary to do this
-because the distances between events are invariant for rotations,
-reflections and translations of the seismicity pattern and hence
-cannot be resolved from CWI alone. In defining this coordinate
-system we fix the first event at the origin
-\begin{linenomath*} \begin{equation} 
-\label{eq:coord-const1}
-\mathbf{e}_1 = (0,0,0),
-\end{equation} \end{linenomath*}
-the second event on the positive $\hat{x}$-axis
-\begin{linenomath*} \begin{equation} 
-\label{eq:coord-const2}
-\mathbf{e}_2 = (\hat{x}_2, 0, 0), \hat{x}_2>0
-\end{equation} \end{linenomath*}
-the third on the $\hat{x}-\hat{y}$ plane
-\begin{linenomath*} \begin{equation}
-\label{eq:coord-const3}
-\mathbf{e}_3 = (\hat{x}_3,\hat{y}_3,0), \hat{y}_3>0
-\end{equation} \end{linenomath*}
-and the fourth to
-\begin{linenomath*} \begin{equation} 
-\label{eq:coord-const4}
-\mathbf{e}_4 = (\hat{x}_4,\hat{y}_4,\hat{z}_4), \hat{z}_4>0.
-\end{equation} \end{linenomath*}
-This coordinate system reduces translational (equation \ref{eq:coord-const1})
-and rotational (equations \ref{eq:coord-const2} to \ref{eq:coord-const4}) non-uniqueness
-without loss of generality. It is necessary to work with a local coordinate
-system when using coda-waves alone because the CWI technique constrains only event separation
-between earthquakes. The inclusion of arrival-times in the Combining Arrival-Time 
-and CWI Constraints section 
-allows us to move to a global reference system.
-
-In summary, the posterior $P(\mathbf{e}_1,...,\mathbf{e}_n |
-\widetilde{\mathbf{\delta}}_{CWIN})$ and its negative logarithm $L$
-describe the joint probability of multiple event locations given the
-observed coda-waves. The most likely set of locations is given by
-the minimum of $L$.   In this paper we use the Polak-Ribiere
-technique \citep{dr_Press87a}, a conjugate gradient method, to
-minimize $L$. It uses the derivatives of $L$, derived in Appendix (Derivatives)
-\ref{sec-Appendix-derivatives_ofL}, to guide the
-optimization procedure. Note that when optimizing
-equation \ref{eq:-negative-log} the values of $ln \left[ c \right]$
-and $ln \left[ P(e_i) \right]$ can be ignored because they are
-constant ($ln \left[ P(e_i) \right]$ is constant because we
-consider a uniform prior).
-
-\vspace{2em}
-\begin{centering}
-\section*{Synthetic experiments}
-\end{centering}
-
-\label{sec:benchmarking}
-
-We use synthetic examples in 2D and 3D with 50 earthquakes to test
-the performance of the optimization routine. In these examples the
-synthetic earthquakes are located randomly and CWI data generated
-according to the event separation. It is not necessary to generate
-synthetic waveforms and compute CWI estimates directly because we
-are testing the performance of the optimization routine only. The
-ability of CWI to estimate event separation has been demonstrated
-already \citep{dr_Snieder05a, dr_Robinson07b, dr_Robinson11a}. We
-undertake a complete coda wave location experiment, including the
-calculation of CWI separation estimates, for recorded earthquakes in 
-Relocating Earthquakes on the Calaveras 
-Fault and in Combining Arrival-Time and CWI Constraints.
-
-\vspace{1em}
-\subsection*{Examples 1 and 2 - 2D synthetic experiments}
-
-We design a 2D synthetic acoustic experiment (example 1) to test the 
-performance of our CWI based relative location algorithm by randomly
-selecting $\hat{x}$- and $\hat{y}$-coordinates such that $-50 \leq
-\hat{x}, \hat{y} \leq 50$\,m. These are indicated with triangles in
-Figure \ref{fig-2D50eq-relocation_eg1}.
- We assume a local velocity of $\alpha=3300\,$ms$^{-1}$ between all
-event pairs and a dominant frequency of 2.5$\,$Hz to represent
-waveform data filtered between 1 and 5$\,$Hz. The purpose of these
-examples is to synthetically test the location algorithm. 
-Hence, we do not need to synthetically generate waveforms and compute
-CWI separation estimates, Rather, we begin by synthetically generating 
-the CWI separation estimates directly. \citet{dr_Robinson11a} showed that
-the CWI data are
-defined by the dominant wavelength normalized positive bounded
-Gaussian PDF with statistics $\bar{\mu}_N$ and $\bar{\sigma}_N$. 
-A hypothetical CWI mean is created by
-setting
-\begin{linenomath*} \begin{equation} 
-\label{eq:hypothetical-CWI-mean-optichapt}
-\bar{\mu}_N = \mu_1 \left( \widetilde{\delta}_t \right)
-\end{equation} \end{linenomath*}
-using equation (\ref{eq:mu1}). This assumption ensures that the
-sample mean of hypothetical separation estimates is consistent with
-known CWI biases \citep{dr_Robinson11a}. In example 1 we use
-$\bar{\sigma}_N=0.02$ between all event pairs. Application of our
-optimization procedure on the hypothetical CWI data yields the
-circles in Figure \ref{fig-2D50eq-relocation_eg1}. The optimization
-does not lead to the exact solution due to the addition of noise
-($\bar{\sigma}_N=0.02$) on the hypothetical CWI data. The average
-coordinate error is 2.0\,m  (average location error $\approx$4\,m) 
-which is small compared to the noise of
-$\bar{\sigma}_N=0.02$ which for $v_s=3300$\,ms$^{-1}$ and
-$f_{dom}=2.5$\,Hz corresponds to roughly 25\,m.
-
-\citet{dr_Robinson11a} demonstrates that the noise on CWI estimates
-is often larger than 0.02 and that it increases with event
-separation. Consequently, example 1 is simplistic because we fix
-$\bar{\sigma}_N=0.02$ for all pairs. In example 2 we increase the
-uncertainty and introduce a distance dependance into the
-hypothetical $\bar{\sigma}_N$ by defining
-$\bar{\sigma}_N=\epsilon(\delta_t)$, where
-$\epsilon(\delta_t)$ is the half-width of the errorbars for a
-synthetic acoustic experiment with filtering between 1 and 5\,Hz
-\citep[see Fig. 4(b) of ][]{dr_Robinson11a}. Repeating the
-optimization leads to the circles in Figure
-\ref{fig-2D50eq-relocation_eg3} which have an average coordinate
-error of 2.8\,m (average location error $\approx$9\,m).
-
-Conjugate gradient based optimization techniques are susceptible to
-the presence of local minima. This is because they use the slope of
-the target function to explore the solution space. We explore the
-impact of local minima for our CWI location problem by beginning the
-optimization from 25 randomly chosen starting positions. We observe
-negligble difference in the solutions indicating that neither example 
-is susceptible to local minima.
-
-Three observations can be drawn from the error structure in Figures
-\ref{fig-2D50eq-relocation_eg1} and \ref{fig-2D50eq-relocation_eg3}.
-Firstly, the location errors depicted by gray bars increase between
-examples 1 and 2 with the introduction of larger noise. Secondly,
-the errors are larger for events at greater distances from the
-center. This is because events near the center of the cluster are
-constrained by links from all angles, whereas those on the outside
-are moderated by links from a limited number of directions. This
-observation is analogous to problems associated with poor azimuthal
-coverage in triangulation such as individual earthquake
-location from limited arrival-time data, or GPS positioning with few
-satellites. Our third observation is that the location errors form a
-pattern of circular rotation, despite our attempt to correct for
- rotational non-uniqueness with the local coordinate system.
-
-The local coordinate system works by constraining the location of
-the first three earthquakes. Earthquake 1 is fixed at the origin,
-earthquake 2 on the positive $\hat{x}$-axis and earthquake 3 has
-$\hat{y}>0$. As the number of events increase the strength of these
-constraints on later events weakens allowing small rotations of
-events with respect to each other. That is, even though the
-rotational freedom of the cluster is in principle removed by the
-constraints imposed on the events (see equations
-(\ref{eq:coord-const1}) to (\ref{eq:coord-const3} - equation
-\ref{eq:coord-const4} is needed in 3D only) we observe that in
-practice the presence of noise allows the rotational non-uniqueness
-to reappear. This is because errors align themselves in directions
-least constrained by data. For the CWI technique this ammounts to rotations in 2D.
-The same phenomenon is observed in linear inversion where noise
-creates large spurious model changes in directions of the
-eigenvectors with the smallest singular values \citep{dr_Aster05a}.
- Fortunately, however, combining coda-waves with
-measurements of arrival-times alleviates this problem and facilitates
-the removal of a local coordinate system altogether (see Combining Arrival-Time and 
-CWI Constraints). On balance, however, we gain
-confidence in the optimization procedure due to its stability for
-different starting locations and because of the small average
-coordinate errors of 2.0\,m and 2.8\,m for examples 1 and 2,
-respectively.
-
-\subsection*{Example 3 - The impact of incomplete event pairs in 2D}
-
-Synthetic examples 1 and 2 use 100\% direct linkage between event
-pairs. That is, there is a constraint between each earthquake and
-all other events. In reality, we might expect that the separation
-between some pairs will not be constrained by CWI data due to poor
-signal to noise ratio in the coda for common stations. Obviously,
-the fewer stations that record an event the more likely it is that
-links between it and other events will be broken. In such cases the
-probabilistic distance constraint between a pair of events may only
-exist indirectly through multiple pairs. In this section we consider
-the impact of reduced linkage between event pairs. In example 3, we
-repeat example 2 using 90\%, 80\%, ..., 10\% of the links. 
-That is, we randomly select 10\% of the event pairs and remove the 
-separation estimates between those pairs to create a data set with 90\% 
-linkage. Then, we randomly remove 20\% of the links and so on. 
-This experiment is designed to mimic a realistic recording situation 
-where CWI estimates are not available for all event pairs due to station 
-problems, poor signal-to-noise ratio or any number of other reasons.
-As with the above examples, we undertake the optimization with 25 randomly
-chosen starting locations.
-
-Figure \ref{fig:optimisationresults-2Dsynth} illustrates
-the maximum $\Delta_{max}$ (top) and mean $\Delta_\mu$ (middle) of
-the coordinate error as a function of percentage of earthquake pairs
-that are directly linked by a separation estimate. We show the
-statistics for the `best' optimization solution (thick) and for the
-solution space when all 25 optimizations are considered (thin). In
-the former case the best solution is determined by the set of event
-locations which lead to the smallest value of $L$. The error in the
-best solution is consistent when 30\% or more of the branches are
-used. The errors increase when only 10\% or 20\% of the constraints
-are included. Interestingly, this breakdown around 20\% to 30\%
-coincides with the point where the average number of branches
-required to link an event pair reaches 2 (see
-Fig.\ref{fig:optimisationresults-2Dsynth} (bottom)). Since the
-average number of branches can be computed in advance it can be used
-as an indication of inversion stability prior to optimization. A
-higher breakdown is observed when all 25 solutions are considered
-collectively. For example, the maximum coordinate error
-$\Delta_{max}$ exceeds that for the best solution for linkage
-$\leq$60\% confirming that the optimization is susceptible to local
-minima and that a range of starting points should be considered.
-Some optimizations fail to converge after 1200 iterations when the
-linkage is 60\% or lower. All optimizations fail when the linkage is
-20\% or lower.
-
-The derivatives used in the conjugate gradient method depend on
-events connected by CWI measurements. Consequently, earthquakes that
-are only connected via other events do not `communicate' with each
-other directly. To some extent, this should be adressed during the
-iterative process where location information can spread to events
-which have no direct links. However, the lack of direct connection
-through the gradient could prevent convergence in extreme cases, or
-more likely slow the procedure down. This could explain why some
-examples do not converge after 1200 iterations.
-\citet{dr_VanDecar94a} show that derivative based regularization acts slowly
-through iterative least-squares, because
- every cell in one iteration communicates only with its neighbours, and they demonstrate that this can be
-fixed with preconditioning in some cases. Their findings suggest
-that it may be possible to improve the convergence (stability and/or
-speed) of the CWI optimization by preconditioning.
-
-\subsection*{Example 4 - The impact of incomplete event pairs in 3D}
-
-In Example 4 we expand the optimization routine to 3D by randomly
-picking a set of event locations for 50 earthquakes with
-$-50$\,m$\leq \hat{x},\hat{y},\hat{z} \leq 50$\,m. As in the 2D case
-we assume a local velocity of $v=3300\,$ms$^{-1}$ between all event
-pairs and a dominant frequency of 2.5$\,$Hz to represent
- waveform data filtered between 1 and 5$\,$Hz.
-The hypothetical CWI mean is created using equation
-(\ref{eq:hypothetical-CWI-mean-optichapt}) which ensures consistency
-between the sample mean of hypothetical separation estimates and CWI
-biases. We use a standard deviation for the noisy CWI estimates of
-$\bar{\sigma}_N = \epsilon(\delta_t)$ (where $\epsilon(\delta_t)$ is the same 
-as that used in Examples 2 and 3) and perform the optimization
-using 10\%, 20\%, ..., 100\% of the direct links. In each case we
-repeat the optimization 25 times using randomly chosen starting
-locations. The results are summarised in Figure
-\ref{fig:optimisationresults-3Dsynth}.
-
-When 70\% of the direct constraints are considered all optimization
-results (thin) are consistent with the best solution obtained from
-all 25 starting locations (thick). The
-best solution constrains the event locations down to 30\% of the
-direct links. This is depicted in Figure
-\ref{fig:optimisationresults-3Dsynth} by the absence of the thin and
-thick lines below 60\% and 30\% linkage, respectively.
-The accurate convergence of the best
-solution for cases with 30\% linkage or higher is encouraging for
-the potential of coda wave optimization to constrain earthquake
-location.
-
-\subsection*{Summary of synthetic experiments}
-
-In summary, the synthetic examples demonstrate the ability of coda
-wave data to constrain relative event location using optimization.
-The optimization error is rotational in nature and 
-influenced by the noise on CWI estimates
-with greater $\bar{\sigma}_N$ leading to larger errors in the
-solutions. In 3D, when 70\% or more of the direct branches are used the
-optimizer is stable with no observable difference in the solution
-for 25 randomly chosen starting locations. As the direct linkage
-reduces to 50\% the optimization becomes less stable and the best
-solution from 25 random starting locations is required to find the
-optimal solution. All optimisations fail to converge as the number
-of links decrease below 30\%.
-
-\vspace{2em}
-\begin{centering}
-\section*{Relocating Earthquakes on the Calaveras Fault}
-\end{centering}
-\label{sec:CalaverasLoc-CWIonly}
-
-In this section we relocate 68 earthquakes from the Calaveras Fault,
-California. The 68 earthquakes are selected from the 308 earthquake
-Calaveras example released with the open source Double Difference
-algorithm or hypoDD \citep{dr_Waldhauser00a, dr_Waldhauser01a} [See
-also Data and Resources]. These events are chosen for four
-reasons. Firstly, they are recorded by a large number of stations
-(Fig. \ref{fig:-eqopti-California-Calaveras}) and therefore lend
-themselves to accurate arrival-time location. This makes them ideal
-for assessing the performance of a new location technique. Secondly,
-they are distributed with separations from near zero to hundreds of
-meters making them ideal for application of CWI. Thirdly, Calaveras
-earthquakes have been well researched with several studies having
-relocated events in the region \citep{dr_Waldhauser01a,
-dr_Schaff02a, dr_Waldhauser08a}. Finally, the hypoDD locations for
-these 68 earthquakes align in a streak increasing the likelihood
-that they have near identical source mechanisms, a necessary
-assumption for the application of equation
-\ref{eq:LitReview-g-3d-dc}. The relocations in this paper are sorted
-into four examples as summarised in Table \ref{tab:examples}. Waveforms, 
-cross correlations and separation estimates for example Calaveras event pairs are 
-illustrated by \citet{dr_Robinson11a} an are not repeated her for the sake of brevity.
-
-\subsection*{Example 5 - comparison of CWI, catalogue and hypoDD locations}
-
-Figure \ref{fig-69Calaverasevents_eg1} illustrates three sets of
-locations for the Calaveras earthquakes. The first column shows the
-original catalogue locations for all 308 earthquakes. That is, each event
-is located individually using all available arrival-time data and
-a regional velocity model. The 68 earthquakes of interest in this
-study are differentiated in black. Catalogue locations suggest that
-the 68 earthquakes of interest are spatially widely distributed on the scale of
- Figure \ref{fig-69Calaverasevents_eg1}.
-
-To apply CWI we download available waveforms from the Northern
-California Earthquake Data Center (See Data and Resources).
-Unsuitable waveforms are removed using the conditions summarised in
-Table \ref{tab:-conditions4unsuitablewaveform}. Remaining waveforms
-are filtered between 1 and 5\,Hz and aligned  to $P$ arrivals at
-0\,s. CWI estimates are obtained from 5\,s wide non-overlapping time
-windows between $2.5 < t \leq 20$\,s and used to create
-probabilistic constraints on event separation. We utilize the
-local coordinate system introduced in the Theory Section and find the
-optimum relative locations using Polak-Ribiere optimization.
-
-In this, and the following Calaveras examples, we allow the earthquakes to 
-move freely in all three directions during the inversion despite using the 
-in-fault separation estimates given by equation \ref{eq:LitReview-g-3d-dc}.
-We allow the events to move freely so that we can test the 
-performance of our algorithm without assuming a-priori 
-that the earthquakes are constrained on the same fault plane. 
-We approximate the true event separation using the in-fault separation 
-of equation \ref{eq:LitReview-g-3d-dc} so that we can focus on developing 
-a working algorithm and demonstrate capability 
-without dealing with the complexity of 
-in-fault ($\delta_{\| fault}$) and out-of-fault 
-($\delta_{\perp fault}^2$) displacement. Considering 
-the more complicated formulation of equation \ref{eq:LitReview-fulDC-sep} is
-left for future work. Another potential focus for future work 
-involves refining our algorithm  
-to simultaneously resolve event location and representative fault plane 
-by restricting the events to align in a single (unknown a-priori) plane. 
-That is, for cases where the earthquakes are 
-believed a-priori to be in the same plan.
-
-CWI locations for the 68 events are illustrated in column two of
-Figure \ref{fig-69Calaverasevents_eg1}. Catalogue locations (gray)
-are shown for the remaining 240 earthquakes and are included to ease
-comparison. The third column of Figure
-\ref{fig-69Calaverasevents_eg1} illustrates the locations given by
-hypoDD with Singular Value Decomposition (SVD), absolute arrival
-times and cross correlation computed arrival-time differences.
-
-Absolute locations cannot be found by CWI alone. This is because of
-the non-uniqueness associated with translation, rotation and
-reflection. For the sake of comparison, we arbitrarily choose a
-`master' event and translate our relative locations to align with
-the hypoDD location for that event. This arbitrary translation
-does not change the relative locations. We return to this issue of
-relative versus absolute location in Example 7 by introducing a
-combined arrival-time and coda-wave inversion.
-
-The spatial distribution of the CWI locations is clearly tighter
-than the catalogue locations of column 1. That is, CWI provides an
-independent indication of clustering for the 68 events and to first
-order, similar locations to those from hypoDD (column 3). There is a
-small second order difference between the CWI and hypoDD based
-locations. In particular, the lineation is less clear in the CWI
-locations (column 2) than the hypoDD locations (column 3). Our
-experience suggests that the CWI locations are less supportive of the presence of
-streaks although a complete understanding of these differences is
-left for future work. Our attention now is devoted towards
-understanding how both techniques perform with fewer stations
-(Example 6) and exploring how CWI and arrival-times can be combined
-(Examples 7 and 8).
-
-\subsection*{Example 6 - Dependance on the number of stations}
-
-Accurate location of the Calaveras events is possible using arrival
-phases because of the excellent recording situation in California
-with many stations and strong azimuthal coverage (see Fig.
-\ref{fig:-eqopti-California-Calaveras}). In contrast, a small number
-of stations and poor azimuthal coverage are common limitations when
-trying to locate intraplate clusters. For example, there are only
-four network seismic stations in the South West Seismic Zone of
-Western Australia, a region similar in size to that hosting 805
-stations in Figure \ref{fig:-eqopti-California-Calaveras}.
-
-We explore the impact of poorer recording situations in example 6 by
-re-locating the 68 Calaveras events  using hypoDD and coda-waves
-with a reduced number of stations. We begin with 10 stations and
-repeat the process removing one at a time until a single station
-remains. The 10 stations and there order of removal are shown in Figure
-\ref{fig:-eqopti-Calaveras-substations}.
-
-CWI locations are illustrated in Figure \ref{fig-CWIreducesstats}
-for the inversions with seven, five, four, three, two and one
-station. We observe a high level of consistency between these 6
-inversions and the locations shown in Figure
-\ref{fig-69Calaverasevents_eg1} (column 2) when all stations are
-considered. That is, the coda-wave approach is self-consistent
-regardless of the number of stations available, reinforcing our
-claim that coda-waves can constrain location in what would
-normally be regarded as a poor station network.
-
-Figure \ref{fig-HYPODDreducesstats} illustrates the hypoDD inversion
-results for seven, five and four stations. The arrival-time problem
-is ill-posed for fewer than four stations so it is not possible to
-apply hypoDD with SVD for three or fewer stations.  The hypoDD
-locations are less self-consistent as the number of stations is
-reduced. We observe a general increase in scatter and a higher
-number of stray events outside the cluster when less stations are
-used with hypoDD. Even with seven stations the linear geometry of
-Figure \ref{fig-69Calaverasevents_eg1} (column 3) is less evident.
-
-As the number of stations is reduced neither the CWI nor hypoDD
-techniques are able to re-locate all events. To use the coda
-waves we need at least one pairwise separation constraint to be
-formed from the available stations. This means that for every event
-there must be at least one station that records it, and at least one
-other earthquake, sufficiently well to apply CWI. Fortunately, we can
-make an assessment of this prior to starting the inversion. The top
-panel of Figure \ref{fig-statremoval_summarystats} demonstrates that
-when five or more stations are used, CWI can constrain the location
-of all 68 earthquakes. When less than five stations are used the
-coda-waves constrain a decreasing number of events until at one
-station it is only possible to locate 55 of the 68 events. The
-hypoDD algorithm also fails to locate all events as the number of
-stations is reduced. In the case of hypoDD an event can be
-identified as unconstrainable in one of two stages. Firstly, the
-data are analyzed to ensure that there exist arrival-time
-differences for each event and at least one other earthquake. This
-is analogous to the situation for the coda-wave technique. The
-hypoDD program also has a secondary identification phase in which
-events that can not be located sufficiently well are rejected during the
-inversion. This process is related to the iterative removal of
-outliers described by \citet{dr_Waldhauser00a}. The top panel of
-Figure \ref{fig-statremoval_summarystats} shows that the number of
-events re-located by hypoDD fluctuates between 63 and 28 earthquakes
-for ten to four stations and it demonstrates that the number of
-events located by hypoDD is less than or equal to the number located
-by CWI.
-
-The remaining panels of Figure \ref{fig-statremoval_summarystats}
-illustrate a statistical comparison of the CWI and hypoDD locations 
-with a reduced number of stations to those using hypoDD with all available data. For
-the CWI inversions the mean and maximum coordinate difference is
-consistent regardless of the number of stations considered. In
-contrast, the hypoDD mean and maximum coordinate error fluctuate
-above those for CWI confirming that the hypoDD inversion is less
-stable than CWI with fewer stations.
-
-\vspace{2em}
-\begin{centering}
-\section*{Combining Arrival-Time and CWI Constraints}
-\end{centering}
-\label{sec:CalaverasLoc-CWIandTT}
-In Examples 5 and 6 we compare the location of the Calaveras
-earthquakes using coda-wave and arrival time based constraints
-independently. Since the arrival time (direct or difference) and
-coda-wave data
- come from different sections of the waveform they provide independent constraints on the locations.
- In this section we devise a location algorithm which incorporates
- both CWI and arrival-time data.
-
-We do not propose a new technique for earthquake location using
-arrival-time differences. Rather, we exploit the information created
-by hypoDD with SVD to define a probability density (or posterior)
-function
-\begin{linenomath*} \begin{equation}
-\label{eq-multi-var-Gauss-tt}
-\begin{array}{l}
-P(\mathbf{e}_p|\Delta_{TT})
-\frac{1}{(2\pi)^{3/2}\sqrt{|\Sigma|}} \\
-\hspace{5em} \times \exp
-\left({-\frac{1}{2}\left([\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T
-\Sigma^{-1} [\mathbf{e}_p-\mu_{\mathbf{e}_p}]\right)} \right),
-\end{array}
-\end{equation} \end{linenomath*}
-where
-\begin{linenomath*} \begin{equation}
-\mathbf{e}_p = (x_p,y_p,z_p)^T
-\end{equation} \end{linenomath*}
-is the location of event $p$,
-\begin{linenomath*} \begin{equation}
-\mu_{\mathbf{e}_p} = (\mu_{x_p}, \mu_{y_p},\mu_{z_p})^T
-\end{equation} \end{linenomath*}
-is the most likely location as determined using the arrival-time
-data, and
-\begin{linenomath*} \begin{equation}
-\label{eq:Sigma-expression}
-\Sigma = \left( \begin{array}{ccc} \sigma_{x_p}^2 & 0 & 0\\
-0 &  \sigma_{y_p}^2 & 0 \\
-0 & 0 & \sigma_{z_p}^2  \end{array} \right)
-\end{equation} \end{linenomath*}
-is the covariance matrix. We define the mean location
-$\mu_{\mathbf{e}_p}$ and covariance matrix by the hypoDD optimum
-solution and its uncertainties. It is important to note that hypoDD
-must be used with SVD to obtain useful estimates of $\sigma_{x_p}$,
-$\sigma_{y_p}$ and $\sigma_{z_p}$ because the errors reported by
-conjugate gradient methods (LSQR) are grossly underestimated in
-hypoDD \citep{dr_Waldhauser01a}.
-
-We pose the location problem using the negative log likelihood
-\begin{linenomath*} \begin{equation}
-\label{eq-Lstar-tt-cwi}
-\begin{array}{l}
- L(\mathbf{e}_1, \mathbf{e}_2, ...,
-\mathbf{e}_1, \mathbf{e}_n) = - \sum_{i=1}^n
-ln\left[P(\mathbf{e}_i|\Delta_{TT})\right] \\
-\hspace{6em}  - \sum_{i=1}^{n-1}
-\sum_{j=i+1}^n
-ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right],
-\end{array}
-\end{equation} \end{linenomath*}
-where $(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n)$ is the joint
-location,
-\begin{linenomath*} \begin{equation}
-\label{eq-ttcomponent} \sum_{i=1}^n
-ln\left[P(\mathbf{e}_i|\Delta_{TT})\right]
-\end{equation} \end{linenomath*}
-incorporates the arrival-time constraints and
-\begin{linenomath*} \begin{equation}
-\label{eq-codacomponent} \sum_{i=1}^{n-1} \sum_{j=i+1}^n
-ln\left[P(\delta_{CWIN}|\mathbf{e}_i,\mathbf{e}_j)\right]
-\end{equation} \end{linenomath*}
- the coda-waves.
-
-We must differentiate $L$ to use the Polak-Ribiere conjugate
-gradient technique of \citet{dr_Press87a}. The derivative of
-$L(\mathbf{e}_1, \mathbf{e}_2, ..., \mathbf{e}_n)$ with respect to
-$x_p$ is given by
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\frac{\partial L}{\partial x_p} =  - \frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p}
-- \sum_{i=p+1}^{N} \frac{ \partial \ln
-\left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
-x_p} \\
-\hspace{5em} - \sum_{j=1}^{p-1} \frac{ \partial \ln
-\left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
-x_p}
-\end{array}
-\end{equation} \end{linenomath*}
-where
-\begin{linenomath*} \begin{equation}
-\sum_{i=p+1}^{N} \frac{ \partial \ln
-\left[P(\delta_{CWIN}|\mathbf{e}_p,\mathbf{e}_i)\right]}{\partial
-x_p}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\sum_{j=1}^{p-1} \frac{ \partial \ln
-\left[P(\delta_{CWIN}|\mathbf{e}_j,\mathbf{e}_p)\right]}{\partial
-x_p}
-\end{equation} \end{linenomath*}
-are defined in Appendix \ref{sec-Appendix-derivatives_ofL} and
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial x_p}
-= -\frac{1}{2}[1,0,0]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
-\hspace{9em} -\frac{1}{2}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [1,0,0].
-\end{array}
-\end{equation} \end{linenomath*}
-Similarly, for the derivatives with respect to $y_p$ and $z_p$ we
-have
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial y_p}
-= -\frac{1}{2} [0,1,0]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
-\hspace{9em} -\frac{1}{2}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,1,0]
-\end{array}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\frac{\partial ln\left[P(\mathbf{e}_p|t_{DD})\right]}{\partial z_p}
-= -\frac{1}{2} [0,0,1]^T \Sigma^{-1}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}] \\
-\hspace{9em} -\frac{1}{2}
-[\mathbf{e}_p-\mu_{\mathbf{e}_p}]^T \Sigma^{-1} [0,0,1].
-\end{array}
-\end{equation} \end{linenomath*}
-
-Combining the arrival-time and coda-wave data offers two advantages.
-Firstly, it combines independent constraints on the event locations
-offering further confidence in the resulting solution. Secondly, the
-arrival-time constraints in the form of equation
-(\ref{eq-ttcomponent}) resolve the inherent non-uniqueness
-of the CWI inversion that is associated with translation, rotation and reflection around a global
-coordinate system. This means that it is no longer necessary to use
-a local coordinate system and we can solve directly for location
-with respect to a global reference. Collectively, these advantages
-improve the behavior of the Polak-Ribiere optimization leading to
-faster and more stable convergence. Consequently, we no longer need
-to consider multiple randomly chosen starting locations.
-
-\vspace{1em}
-\subsection*{Example 7 - Combining arrival-time and CWI constraints}
-Figure
-\ref{fig-68Calaverasevents_ttandcoda1} illustrates the earthquake
-locations obtained when we combine the arrival-time and coda-wave
-data using all data (left) and five stations (right). The linear
-features observed in the original hypoDD inversions (see Fig.
-\ref{fig-69Calaverasevents_eg1}) are evident in both cases. However,
-the coda-waves introduce a scatter around these streaks. That is,
-the locations in figure \ref{fig-68Calaverasevents_ttandcoda1}
-result from a trade-off between hypoDD's desire to place the events
-on linear features and the coda-waves voracity to push them away
-from streaks. When all stations are used the hypoDD constraints are
-strong and little off-streak scatter is introduced. As we reduce
-hypoDD's leverage by decreasing the number of stations to five, we
-observe an increase in off-streak scatter resulting from the
-enhanced influence of the coda.
-
-\subsection*{Example 8 - Combining CWI and arrival-times when the arrival-times constrain a limited number of events}
-
-In intraplate regions such as Australia it is common to deploy
-temporary seismometers to monitor aftershocks for significant events
-\citep{dr_Bowman90a, dr_Leonard02a}. Traditionally, these
-deployments facilitate a higher accuracy of location for events
-occuring during the deployment period. Using our combined inversion
-it is possible to re-locate all events by employing the detailed
-arrival-time data when the temporary network is in-situ and using
-coda-waves from network stations when the deployment is absent. The
-hypothesis, to be tested in this section, is that conducting such a
-combined inversion will improve the location accuracy of events
-outside the deployment period.
-
-An estimate of the cummulative number of aftershocks $N(t)$ after
-$t$ days can be modeled by the modified Omori formula
-\begin{linenomath*} \begin{equation}
-\label{eq:CumOmori}
- N(t) = K \frac{c^{1-p} + (t+c)^{1-p}}{p-1}
-\end{equation} \end{linenomath*}
-\citep{dr_Utsu95a}.
-The empirically derived constants, $K$, $C$ and $p$ vary between
-tectonic settings. For example, using recorded aftershocks with
-$M\ge3.2$ of the  Hokkaido-Nansei-Oki, Japan $M_s=7.8$ earthquake of
-12 July 1993, \citet{dr_Utsu95a} obtained maximum likelihood
-estimates for $K$, $p$ and $c$ of 906.5, 1.256 and 1.433,
-respectively.  With these empirically derived values an array
-deployed within 4 days and left for 150 days will record roughly one
-half of the aftershocks occurring within the first 1000 days. That
-is,
-\begin{linenomath*} \begin{equation}
-\frac{N(150+4)-N(4)}{N(1000)} = \frac{2257-934}{2626} \approx 0.5.
-\end{equation} \end{linenomath*}
-This is illustrated in Figure \ref{fig:Omorifigure} which shows
-the best fitting Omori Formula separated into segments before, during 
-and after the pseudo temporary
-deployment.
-
-With this idea of a temporary deployment in mind we have another
-attempt at relocating the Calaveras earthquakes. In Example 8 we
-consider the arrival-time constraints on half (34) of the earthquakes
-and incorporate coda-wave data from a single station for all 68
-earthquakes. The combined inversion is shown in column 1 of Figure
-\ref{fig-68Calaverasevents_ttsubsetandcoda1}. The inversion result
-is similar to the combined inversion when all arrival-time data are
-incorporated (see Fig. \ref{fig-68Calaverasevents_ttandcoda1}). The
-slight increase in scatter observed here can be explained by the
-events with no arrival-time constraints and the tendency of the coda
-to push events away from streaks.
-
-Remarkably, the combined coda-wave and arrival-time inversion locates
-all 68 earthquakes to an accuracy similar to the inversions with all
-data. In contrast when arrival-time data are used alone it is only
-possible to locate the 34 events recorded by the pseudo temporary
-deployment. This
-ability of  coda-waves to constrain the location of events recorded
-by a single station creates new opportunities for understanding
-earthquakes in regions with limited station coverage.
-
-\vspace{2em}
-\begin{centering}
-\section*{Discussion and Conclusions}
-\end{centering}
-
-Coda-wave interferometry is an emerging technique for constraining
-earthquake location. The technique relies on the interference
-between coda-waves of closely located events and is hence useful for
-studying earthquake clusters and/or aftershock sequences. Coda-wave
-constraints are independent of arrival-times and can be used in
-isolation or combination with early onset body waves. The strength
-of coda is that it is possible to constrain earthquake location from
-a single station, an outcome demonstrated most clearly by Figures
-\ref{fig-CWIreducesstats} and
-\ref{fig-68Calaverasevents_ttsubsetandcoda1}.
-
-Coda-wave interferometry offers a new technique for understanding
-earthquakes in intraplate areas with sparse networks and poor
-azimuthal coverage. In particular, the ability to combine coda-wave
-constraints with arrival-times makes it possible to link well
-constrained events from a temporary deployment with those recorded
-outside the deployment period. All that is required to achieve this
-is at least one network station which has recorded sufficient events
-from both periods. CWI facilitates the location of poorly recorded
-events to an accuracy approaching those recorded during the
-temporary deployment and therefore opens new avenues for imaging
-intraplate fault structures and improving our understanding of
-intraplate seismicity and earthquake hazard. Importantly, this analysis 
-can be conducted for any historical aftershock sequence or earthquake swarm
-recorded by a temporay deployment, Our technique is, in that sense, related
-to the retorspective sesimological observation technique of 
-\citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
-on newly installed sensors regardless of whether the event occurs before, 
-during or after the physical installation of the sensor.
-
-Another potential application of CWI is in the area of hydraulic
-fracturing such as hot rock geothermal projects, petroleum reservoir engineering,
-tight gas extraction, CO$_2$ geosequestration and/or underground brine injection.
-Monitoring pumping-induced micro earthquakes
-is a key step in understanding the migration of fluids in such
-reservoirs. There is a trade-off in the ability of surface deployed
-networks to locate events which are small and/or deep. Downhole
-seismic monitoring is likely to play increasingly important roles in
-deep reservoir projects. CWI creates new possibilities to monitor
-pumping induced micro earthquakes from fewer boreholes and hence
-dramatically reduce the costs of reservoir monitoring at large
-depths. It may also be possible to utilize coda for understanding
-hazard in tunneled mining operations where the location of deep
-tunnels prohibits azimuthal coverage of induced events.
-
-\vspace{2em}
-\begin{centering}
-\section*{Data and Resources}
-\end{centering}
-We thank the Northern California Earthquake Data Center (NCEDC) for
-providing the Calaveras data and the Northern California Seismic
-Network (NCSN), U.S. Geological Survey, Menlo Park and Berkeley
-Seismological Laboratory, University of California, Berkeley for
-contributing it to the NCEDC. The waveforms can be downloaded from \\
-http://www.ncedc.org/ncedc/access.html (last accessed August 2012). 
-We also acknowledge Felix
-Waldhauser and William Ellsworth, the authors of the openly
-available Double Difference location algorithm, hypoDD which can be
-downloaded from \\
-http://www.ldeo.columbia.edu/~felixw/hypoDD.html
-(last accessed August 2012).
-The International Sesimological Centre can be found at \\
-http://www.isc.ac.uk/ (last accessed December 2012).
-The National Earthquake
-Information
-Center catalogue can be accessed from \\
-http://earthquake.usgs.gov/earthquakes/eqarchives/epic/
-(last accessed December 2012).
-
-\vspace{2em}
-\begin{centering}
-\section*{Acknowledgments}
-\end{centering}
-
-Geoscience Australia, the Research School of Earth Sciences at The
-Australian National University, and the Center for Wave Phenomena at
-the Colorado School of Mines, are acknowledged for supporting this
-research. The paper is published with permission of the CEO
-Geoscience Australia. Work was conducted as part of an Australian
-Research Council Discovery Project (DP0665111).  This paper has
-benefited significantly from: reviews by Trevor Allen and Clive Collins
-at Geoscience Australia, the BSSA editorial team, Andrew Curtis from 
-the School of GeoSciences at the University of Edinburgh and an anonymous 
-reviewer. The authors have also benefited from comments and advice received from
-Felix Waldhauser on this and earlier research on the application of
-CWI to earthquake location.
-
-%=============================================
-% Bibliography
-\vspace{2em}
-%\bibliography{../refs/drrefs}  %Uncomment when generating bibliography
-
-\newcommand{\areps}{\textit{Ann.\ Rev.\ Earth Planet\ Sci.}}
-\newcommand{\bssa}{\textit{Bull.\ Seism.\ Soc.\ Am.}}
-\newcommand{\eos}{\textit{Eos Trans.\ AGU}} 
-\newcommand{\eps}{\textit{Earth~Planets~Space}}
-\newcommand{\epsl}{\textit{Earth~Planet.\ Sci.\ Lett.}}
-\newcommand{\gca}{\textit{Geochim.\ Cosmochim.\ Acta}}
-\newcommand{\geo}{\textit{Geology}}
-\newcommand{\geop}{\textit{Geophysics}}
-\newcommand{\gji}{\textit{Geophys.\ J.\ Int.}}
-\newcommand{\gjras}{\textit{Geophys.\ J.\ R.\ Astr.\ Soc.}}
-\newcommand{\grl}{\textit{Geophys.\ Res.\ Lett.}}
-\newcommand{\gsab}{\textit{Geol.\ Soc.\ Am.\ Bull.}}
-\newcommand{\gs}{\textit{Geophys.\ Surv.}}
-\newcommand{\jgr}{\textit{J.\ Geophys.\ Res.}}
-\newcommand{\jpo}{\textit{J.\ Phys.\ Oceanogr.}} 
-\newcommand{\jseis}{\textit{J.~Seismology}}
-\newcommand{\mnras}{\textit{Mon.\ Not.\ R.\ astr.\ Soc.}} 
-\newcommand{\pag}{\textit{Pure Appl.\ Geophys.}}
-\newcommand{\pepi}{\textit{Phys.\ Earth Planet.\ Inter.}}
-\newcommand{\rg}{\textit{Rev.\ Geophys.}}
-\newcommand{\tecto}{\textit{Tectonophysics}}
-\newcommand{\jpe}{\textit{J. Phys. Earth}}  % Added by DR
-\newcommand{\srl}{\textit{Seism. Res. Let.}}  % Added by DR
-
-\begin{thebibliography}{45}
-\providecommand{\natexlab}[1]{#1}
-\expandafter\ifx\csname urlstyle\endcsname\relax
-  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
-  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
-  \urlstyle{rm}\Url}\fi
-
-\bibitem[{\textit{Ake et~al.}(2005)\textit{Ake, O'{C}onnell, and
-  Block}}]{dr_Ake05a}
-Ake, J., D.~O'{C}onnell, and L.~Block (2005), Deep-injection and closely
-  monitored induced seismicity at {P}aradox {V}alley, {C}olorado,
-  \bssa, \textit{95}(2),
-  664--683.
-
-\bibitem[{\textit{Aki}(1969)}]{dr_Aki69a}
-Aki, K. (1969), Analysis of the seismic coda of local earthquakes as scattered
-  waves, \jgr, \textit{74}(2), 615--631.
-
-\bibitem[{\textit{Aster et~al.}(2005)\textit{Aster, Borchers, and
-  Thurber}}]{dr_Aster05a}
-Aster, R.~C., B.~Borchers, and C.~H. Thurber (2005), \textit{Parameter
-  estimation and inverse problems}, \textit{International Geophysics Series},
-  vol.~90, Elsevier Academic Press, USA.
-
-\bibitem[{\textit{Bond\'ar et~al.}(2004)\textit{Bond\'ar, Myers, Engdahl, and
-  Bergman}}]{dr_Bondar04a}
-Bond\'ar, I., S.~C. Myers, E.~R. Engdahl, and E.~A. Bergman (2004), Epicentre
-  accuracy based on seismic network criteria, \gji, \textit{156}, 483--496.
-
-\bibitem[{\textit{Bowman et~al.}(1990)\textit{Bowman, Gibson, and
-  Jones}}]{dr_Bowman90a}
-Bowman, J.~R., G.~Gibson, and T.~Jones (1990), Aftershocks of the 1988
-  {J}anuary 22 {T}ennant {C}reek, {A}ustralia intraplate earthquakes: evidence
-  for a complex thrust-fault geometry, \gji, \textit{100}, 87--97.
-
-\bibitem[{\textit{Campbell}(2003)}]{dr_Campbell03a}
-Campbell, K.~W. (2003), Strong motion attenuation, in \textit{International
-  Handbook of Earthquake and Engineering Seismology}, vol.~B, edited by
-  W.~H.~K. Lee, H.~Kanamori, P.~C. Jennings, and C.~Kisslinger, chap.~60, pp.
-  1003--1012, Academic Press, London.
-
-\bibitem[{\textit{Curtis and Snieder}(2002)}]{dr_Curtis02a}
-Curtis, A., and R.~Snieder (2002), Probing the {E}arth's interior with seismic
-  tomography, in \textit{International Handbook of Earthquake Engineering
-  Seismology}, vol.~{A}, edited by W.~H. Lee, H.~Kanamori, P.~C. Jennings, and
-  C.~Kisslinger, chap.~52, pp. 861--874, Academic Press, London.
-
-\bibitem[{\textit{Curtis et~al.}(2012)}]{dr_Curtis12a_EPSL}
-Curtis, A., Behr, Y., Entwistle, E., Galetti, E., Townend J. Bannister, S. (2012),
-The benefit of hindsight in observational science: {R}etrospective
-seismological observations, \epsl, \textit{345--348}, 212--220.
-
-\bibitem[{\textit{Deichmann and Garcia-{F}ernandez}(1992)}]{dr_Deichmann92a}
-Deichmann, N., and M.~Garcia-{F}ernandez (1992), Rupture geometry from
-  high-precision relative hypocentre locations of microearthquake clusters,
-  \gji, \textit{110}, 501--517.
-
-\bibitem[{\textit{Douglas}(1967)}]{dr_Douglas67a}
-Douglas, A. (1967), Joint epicentre determination, \textit{Nature},
-  \textit{215}, 47--48.
-
-\bibitem[{\textit{Frankel et~al.}(2000)\textit{Frankel, Mueller, Barnhard,
-  Leyendecker, Wesson, Harmsen, Klein, Perkins, Dickman, Hanson, and
-  Hopper}}]{dr_Frankel00a}
-Frankel, A.~D., C.~S. Mueller, T.~P. Barnhard, E.~V. Leyendecker, R.~L. Wesson,
-  S.~C. Harmsen, F.~W. Klein, D.~M. Perkins, N.~C. Dickman, S.~L. Hanson, and
-  M.~G. Hopper (2000), {USGS} {N}ational seismic hazard maps,
-  \textit{Earthquake Spectra}, \textit{16}(1), 1--19.
-
-\bibitem[{\textit{Fr\`emont and Malone}(1987)}]{dr_Fremont87a}
-Fr\`emont, M.-J., and S.~D. Malone (1987), High precision relative locations of
-  earthquakes at {M}ount {St.} {H}elens, \jgr, \textit{92}(B10), 10,223--10,236.
-
-\bibitem[{\textit{Got et~al.}(1994)\textit{Got, Fr\`echet, and
-  Klein}}]{dr_Got94a}
-Got, J.-L., J.~Fr\`echet, and F.~W. Klein (1994), Deep fault plane geometry
-  inferred from multiplet relative relocation beneath the south flank of
-  {K}ilauea, \jgr, \textit{99}(B8),
-  15,375--15,386.
-
-\bibitem[{\textit{Gutenberg}(1945)}]{dr_Gutenberg45a}
-Gutenberg, B. (1945), Amplitudes of surface waves and magnitudes of shallow
-  earthquakes, \bssa,
-  \textit{35}, 3--12.
-
-\bibitem[{\textit{Ito}(1985)}]{dr_Ito85a}
-Ito, A. (1985), High resolution relative hypocenters of similar earthquakes by
-  cross-spectral analysis method, \jpe,
-  \textit{33}, 279--294.
-
-\bibitem[{\textit{Kennett et~al.}(1995)\textit{Kennett, Engdahl, and
-  Buland}}]{dr_Kennett95a}
-Kennett, B. L.~N., E.~R. Engdahl, and R.~Buland (1995), Constraints on seismic
-  velocities in the {E}arth from traveltimes, \gji, \textit{122}, 108--124.
-
-\bibitem[{\textit{Kennett et~al.}(2004)\textit{Kennett, Fishwick, and
-  Heintz}}]{dr_Kennett04a}
-Kennett, B. L.~N., S.~Fishwick, and M.~Heintz (2004), Lithospheric structure in
-  the {A}ustralian region - a synthesis of surface wave and body wave studies,
-  \textit{Exploration Geophysics}, \textit{35}, 242--250.
-
-\bibitem[{\textit{Lees}(1998)}]{dr_Lees98a}
-Lees, J.~M. (1998), Multiplet analysis at {C}oso {G}eothermal, \bssa, \textit{88}(5), 1127--1143.
-
-\bibitem[{\textit{Leonard}(2002)}]{dr_Leonard02a}
-Leonard, M. (2002), The {B}urakin {WA} earthquake sequence {S}ept 2000 --
-  {J}une 2002, in \textit{Total Risk Management in the Privatised Era},
-  \textit{Australian Earthquake Engineering Society Conference}, vol. 10th,
-  edited by M.~Griffith, D.~Love, P.~Mc{B}ean, A.~Mc{D}ougall, and B.~Butler,
-  pp. 22(1)--22(5), AEES, University of Adelaide.
-
-\bibitem[{\textit{Nadeau and Mc{E}villy}(1997)}]{dr_Nadeau97a}
-Nadeau, R.~M., and T.~V. Mc{E}villy (1997), Seismological studies at
-  {P}arkfield {V}: {C}haracteristic microearthquake sequences as fault--zone
-  drilling targets, \bssa,
-  \textit{87}(6), 1463--1472.
-
-\bibitem[{\textit{Pavlis}(1992)}]{dr_Pavlis92a}
-Pavlis, G.~L. (1992), Appraising relative earthquake location errors,
-  \bssa, \textit{82}(2),
-  836--859.
-
-\bibitem[{\textit{Press et~al.}(1987)\textit{Press, Flannery, Teukolsky, and
-  Vetterling}}]{dr_Press87a}
-Press, W.~H., B.~P. Flannery, S.~A. Teukolsky, and W.~T. Vetterling (1987),
-  \textit{Numerical Recipes: The Art of Scientific Computing}, Cambridge
-  University Press, USA.
-
-\bibitem[{\textit{Richter}(1935)}]{dr_Richter35a}
-Richter, C.~F. (1935), An instrumental earthquake magnitude scale,
-  \bssa, \textit{25}(1),
-  1--32.
-
-\bibitem[{\textit{Robinson et~al.}(2006)\textit{Robinson, Dhu, and
-  Schneider}}]{dr_Robinson06b}
-Robinson, D., T.~Dhu, and J.~Schneider (2006), Practical probabilistic seismic
-  risk analysis: {A} demonstration of capability, \srl, \textit{77}(4), 452--458.
-
-\bibitem[{\textit{Robinson et~al.}(2007{\natexlab{a}})\textit{Robinson,
-  Sambridge, and Snieder}}]{dr_Robinson07b}
-Robinson, D.~J., M.~Sambridge, and R.~Snieder (2007{\natexlab{a}}), Constraints
-  on coda wave interferometry estimates of source separation: The 2.5d acoustic
-  case, \textit{Exploration Geophysics}, \textit{38}(3), 189--199.
-
-\bibitem[{\textit{Robinson et~al.}(2007{\natexlab{b}})\textit{Robinson,
-  Snieder, and Sambridge}}]{dr_Robinson07c}
-Robinson, D.~J., R.~Snieder, and M.~Sambridge (2007{\natexlab{b}}), Using coda
-  wave interferometry for estimating the variation in source mechanism between
-  double couple events, \jgr, \textit{112},
-  b12302, doi:10.1029/2007JB004925.
-
-\bibitem[{\textit{Robinson et~al.}(2011)\textit{Robinson, Sambridge, and
-  Snieder}}]{dr_Robinson11a}
-Robinson, D.~J., M.~Sambridge, and R.~Snieder (2011), A probabilistic approach
-  for estimating the separation between a pair of earthquakes directly from
-  their coda waves, \jgr, \textit{B04309},
-  1--17.
-
-\bibitem[{\textit{Rubin}(2002)}]{dr_Rubin02a}
-Rubin, A.~M. (2002), Aftershocks of microearthquakes as probes of the mechanics
-  of rupture, \jgr, \textit{107}(B7,2142),
-  10.1029/2001JB000,496.
-
-\bibitem[{\textit{Rubin et~al.}(1999)\textit{Rubin, Gillard, and
-  Got}}]{dr_Rubin99a}
-Rubin, A.~M., D.~Gillard, and J.-L. Got (1999), Streaks of microearthquakes
-  along creeping faults, \textit{Nature}, \textit{400}, 635--641.
-
-\bibitem[{\textit{Schaff et~al.}(2002)\textit{Schaff, Bokelmann, and
-  Beroza}}]{dr_Schaff02a}
-Schaff, D.~P., G.~H.~R. Bokelmann, and G.~C. Beroza (2002), High-resolution
-  image of {C}alaveras {F}ault seismicity, \jgr, \textit{107}(B9), 2186, doi:10.1029/2001JB000,633.
-
-\bibitem[{\textit{Shearer et~al.}(2005)\textit{Shearer, Hauksson, and
-  Lin}}]{dr_Shearer05a}
-Shearer, P., E.~Hauksson, and G.~Lin (2005), Southern {C}alifornia hypocenter
-  relocation with waveform cross-correlation, {P}art 2: {R}esults using
-  source-specific station terms and cluster analysis, \bssa, \textit{95}(3), 904--915.
-  doi:10.1785/0120040,168.
-
-\bibitem[{\textit{Shearer}(1999)}]{dr_Shearer99a}
-Shearer, P.~M. (1999), \textit{Introduction to Seismology}, Cambridge
-  University Press, USA, 260pp.
-
-\bibitem[{\textit{Sipkin}(2002)}]{dr_Sipkin02a}
-Sipkin, S.~A. (2002), {USGS} earthquake moment tensor catalog, in
-  \textit{International Handbook of Earthquake Engineering Seismology},
-  vol.~{A}, edited by W.~H. Lee, H.~Kanamori, P.~C. Jennings, and
-  C.~Kisslinger, chap.~50, pp. 823--825, Academic Press, London.
-
-\bibitem[{\textit{Slunga et~al.}(1995)}]{dr_Slunga95a}
-Slunga, R., R{\"o}gnvaldsson, {S. Th.} and B{\"o}dvarsson, R. (1995),
-Absolute and relative locations of similar events with application to microearthquakes in southern {I}celand,
-\gji,\textit{123}(2),409--419.
-
-\bibitem[{\textit{Snieder}(1999)}]{dr_Snieder99a}
-Snieder, R. (1999), Imaging and averaging in complex media, in \textit{Diffuse
-  waves in complex media}, \textit{NATO Science Series C}, vol. 531, edited by
-  J.~P. Fouque, pp. 405--454, Kluwer Academic Publishers.
-
-\bibitem[{\textit{Snieder}(2006)}]{dr_Snieder06a}
-Snieder, R. (2006), The theory of coda wave interferometry, \pag, 
-\textit{163}, 455--473.
-
-\bibitem[{\textit{Snieder and Vrijlandt}(2005)}]{dr_Snieder05a}
-Snieder, R., and M.~Vrijlandt (2005), Constraining the source separation with
-  coda wave interferometry: Theory and application to earthquake doublets in
-  the {H}ayward {F}ault, {C}alifornia, \jgr, \textit{110}(B04301), doi:10.1029/2004JB003317.
-
-\bibitem[{\textit{Spencer and Gubbins}(1980)}]{dr_Spencer80a}
-Spencer, C., and D.~Gubbins (1980), Travel-time inversion for simultaneous
-  earthquake location and velocity structure determination in laterally varying
-  media, \gjras,
-  \textit{63}, 95--116.
-
-\bibitem[{\textit{Stirling et~al.}(2002)\textit{Stirling, Mc{V}erry, and
-  Berrryman}}]{dr_Stirling02a}
-Stirling, M.~W., G.~H. Mc{V}erry, and K.~R. Berrryman (2002), A new seismic
-  hazard model for {N}ew {Z}ealand, \bssa, \textit{92}(5), 1878--1903.
-
-\bibitem[{\textit{Toro et~al.}(1997)\textit{Toro, Abrahamson, and
-  Schneider}}]{dr_Toro97a}
-Toro, G.~R., N.~A. Abrahamson, and J.~F. Schneider (1997), Model of strong
-  ground motions from earthquakes in {C}entral and {E}astern {N}orth {A}merica:
-  {B}est estimates and uncertainties, \srl,
-  \textit{68}(1), 41--57.
-
-\bibitem[{\textit{Utsu et~al.}(1995)\textit{Utsu, Ogata, and
-  Matsu'ura}}]{dr_Utsu95a}
-Utsu, T., Y.~Ogata, and R.~S. Matsu'ura (1995), The {C}entenary of the {O}mori
-  {F}ormula for a decay law of aftershock activity, \jpe, \textit{43}, 1--33.
-
-\bibitem[{\textit{Van{D}ecar and Snieder}(1994)}]{dr_VanDecar94a}
-Van{D}ecar, J.~C., and R.~Snieder (1994), Obtaining smooth solutions to large
-  linear inverse problems, \textit{Geophysics}, \textit{59}, 818--829.
-
-\bibitem[{\textit{Waldhauser}(2001)}]{dr_Waldhauser01a}
-Waldhauser, F. (2001), hypo{DD} -- a program to compute double-difference
-  hypocenter locations (hypo{DD} version 1.0 - 03/2001), \textit{Open file
-  report 01-113}, United States Geological Survey, Menlo Park, California.
-
-\bibitem[{\textit{Waldhauser and Ellsworth}(2000)}]{dr_Waldhauser00a}
-Waldhauser, F., and W.~L. Ellsworth (2000), A double--difference earthquake
-  location algorithm: method and application to the northern {H}ayward {F}ault,
-  {C}alifornia, \bssa,
-  \textit{90}(6), 1353--1368.
-
-\bibitem[{\textit{Waldhauser and Ellsworth}(2002)}]{dr_Waldhauser02a}
-Waldhauser, F., and W.~L. Ellsworth (2002), Fault structure and mechanics of
-  the {H}ayward {F}ault, {C}alifornia, from double--difference earthquake
-  locations, \jgr, \textit{107}(B3),
-  10.1029/2000JB000,084.
-
-\bibitem[{\textit{Waldhauser and Schaff}(2008)}]{dr_Waldhauser08a}
-Waldhauser, F., and D.~P. Schaff (2008), Large-scale relocation of two decades
-  of {N}orthern {C}alifornia seismicity using cross-correlation and
-  double-difference methods, \jgr,
-  \textit{133}, {B08311, doi10.1029/2007JB005479}.
-
-\bibitem[{\textit{Waldhauser et~al.}(1999)\textit{Waldhauser, Ellsworth, and
-  Cole}}]{dr_Waldhauser99a}
-Waldhauser, F., W.~L. Ellsworth, and A.~Cole (1999), Slip-parallel lineations
-  on the {N}orthern {H}ayward {F}ault, {C}alifornia, \grl, \textit{26}(23), 3525--3528.
-
-\end{thebibliography}
-
-\vspace{2em}
-\begin{centering}
-\section*{Authors' Affiliations, Adresses}
-\end{centering}
-
-\begin{tabular}{lp{0.6\textwidth}}
- & \\
-David Robinson: & Earth Monitoring and Hazard Group \\
- &  Geoscience Australia \\
- & GPO Box \emph{383} \\
- & Canberra ACT \emph{2601} Australia \\
- & E-mail: david.robinson@ga.gov.au\\
- & \\
- & Also at: Research School of Earth Sciences \\
- & Australian National University \\ 
- & Canberra ACT \emph{0200}, Australia \\
- & E-mail: david.robinson@anu.edu.au \\
- & \\
- Malcolm Sambridge: & Research School of Earth Sciences \\
- & Australian National University \\ 
- & Canberra ACT \emph{0200}, Australia \\
-  & \\
-Roel Snieder: & Center for Wave Phenomena and Department of Geophysics \\
- & Colorado School of Mines \\
- & Golden CO \emph{80401-1887}, USA \\
- & \\
-Juerg Hauser: & CSIRO Earth Science and Resource Engineering \\
- & Dick Perry Av \\
- & Kensington WA \emph{6151} Australia
-\end{tabular}
-
-\clearpage
-
-%\begin{centering}
-%\section*{Tables}
-%\end{centering}
-%%=======================================================================================
-% Table 1
-
-\begin{table}
-\caption{Location examples for the 68 Calaveras earthquakes.}
-\label{tab:examples}
-\begin{tabular}{ll}
-\hline
-Example 5 & Comparison of CWI, catalogue and hypoDD \\
- & locations (using all available data). \\
-Example 6 & Exploration of station dependance for CWI and \\
- & hypoDD (using a subset of data). \\
-Example 7 & Combined use of CWI and arrival-time data \\
-& with all and a reduced number of stations. \\
-Example 8 & Combined use of CWI and arrival-time data \\
- & when arrival-times constrain only 50\% of the events. \\
- \hline
-\end{tabular}
-\end{table}
-
-%%=======================================================================================
-% Table 2
-
-\begin{table}
-\caption[Conditions for identifying unsuitable waveforms when
-applying CWI] {Conditions used to identify unsuitable waveforms
-before applying CWI \citep[Originally published as Table
-5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
-\begin{tabular}{|l|p{0.7\textwidth}|}
-\hline
- & \textbf{condition} \\
-\hline
-1 & waveform is clearly corrupted \\
-2 & waveform indicates recording of more then one event \\
-3 & signal to noise ratio is obviously low \\
-4 & there is insufficient coda recorded after the \\
- & first arrivals \\
-5 & there is insufficient recording before the arrivals \\
- &  (needed for accurate noise energy estimate) \\
-\hline
-\end{tabular}
-\end{table}
-
-\clearpage
-
-%\begin{centering}
-%\section*{Figure Captions}
-%\end{centering} 
 %%=======================================================================================
@@
 %\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
-%\includegraphics[width = 20pc]{Figure1_c.eps}
+\includegraphics[width = 20pc]{Figure1_c.eps}
 \caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D
@@
 %\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
-%\includegraphics[width = 20pc]{Figure2_c.eps}
+\includegraphics[width = 20pc]{Figure2_c.eps}
 \caption{Example 2 - Synthetic relocation of 50 earthquakes in 2D
@@
 %\noindent\includegraphics[width=20pc]{diags/synth2Dmulti/ressummary_2Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{Figure3_c.eps}
+\noindent\includegraphics[width=20pc]{Figure3_c.eps}
 \caption{Example 3 - Statistical measures of error in the
@@
 %\noindent\includegraphics[width=20pc]{diags/synth3Dmulti/ressummary_3Dsynth50eq.eps}
-%\noindent\includegraphics[width=20pc]{Figure4_c.eps}
+\noindent\includegraphics[width=20pc]{Figure4_c.eps}
 \caption{Example 4 - Statistical measures of error in the
@@
 %\noindent\includegraphics[width=20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
-%\noindent\includegraphics[width=20pc]{Figure5.eps} 
+\noindent\includegraphics[width=20pc]{Figure5.eps} 
 \caption{Map
@@
 %\includegraphics{diags/CalaverasLoc1_hypoDD_SVD.eps}
-%\includegraphics{Figure6_bw.eps}
+\includegraphics{Figure6_bw.eps}
 \caption{Example 5 - Comparison of relative earthquake locations
@@
 %\noindent\includegraphics[width=20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
-%\noindent\includegraphics[width=20pc]{Figure7.eps} 
+\noindent\includegraphics[width=20pc]{Figure7.eps} 
 \caption{Location
@@
 %\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
-%\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
+\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps}
 \caption{Example 6 - CWI relative locations with reduced stations. 
@@
 %\includegraphics[height = 25pc]{diags/CalaverasLoc3_hypoDD_SVD.eps}
-%\includegraphics[height = 25pc]{Figure9_bw.eps}
+\includegraphics[height = 25pc]{Figure9_bw.eps}
 \caption{Example 6 - HypoDD (SVD) relative locations with reduced
@@
 %\noindent\includegraphics[width=20pc]{diags/CalaverasLoc4_hypoDD_SVD.eps}
-%\noindent\includegraphics[width=20pc]{Figure10_c.eps}
+\noindent\includegraphics[width=20pc]{Figure10_c.eps}
 \caption{Example 6 - Number of constrainable events $nE$ in the CWI
@@
 %\includegraphics{diags/CalaverasLoc5_hypoDD_SVD.eps}
-%\includegraphics{Figure11_bw.eps}
+\includegraphics{Figure11_bw.eps}
 \caption{Example 7 - Combined HypoDD (SVD) and CWI relative
@@
 %\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
-%\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
+\noindent\includegraphics[width = 20pc]{Figure12_c.eps}
 \caption{Modeled cumulative number of aftershocks for the
@@
 %\includegraphics{diags/CalaverasLoc6_hypoDD_SVD.eps}
-%\includegraphics{Figure13_bw.eps}
+\includegraphics{Figure13_bw.eps}
 \caption{Example 8 - Mimicking the deployment of a temporary network
@@
 
-%\clearpage
-%\begin{centering}
-%\section*{Figure Captions}
-%\end{centering} 
-%%=======================================================================================
-
-%Figure 1
-%\noindent\includegraphics[width = 20pc]{Figure1_c.eps} \\
-%\textbf{Figure 1:}
-
-%%=======================================================================================
-
-%Figure 2
-%\clearpage
-%\noindent\includegraphics[width = 20pc]{Figure2_c.eps} \\
-%\textbf{Figure 2:}
-
-%%=======================================================================================
-
-% Figure 3
-%\clearpage
-%\noindent\includegraphics[width=20pc]{Figure3_c.eps} \\
-%\textbf{Figure 3:}
-
-%%=======================================================================================
-
-% Figure 4
-%\clearpage
-%\noindent\includegraphics[width=20pc]{Figure4_c.eps} \\
-%\textbf{Figure 4:}
-
-%%=======================================================================================
-
-% Figure 5
-%\clearpage
-%\noindent\includegraphics[width=20pc]{Figure5.eps} \\
-%\textbf{Figure 5:}
-
-%%=======================================================================================
-% Figure 6
-%\clearpage
-%\includegraphics{Figure6_bw.eps} \\
-%\textbf{Figure 6:}
-
-%%=======================================================================================
-
-% Figure 7
-%\clearpage
-%\noindent\includegraphics[width=20pc]{Figure7.eps} \\
-%\textbf{Figure 7:}
-
-%%=======================================================================================
-
-%Figure 8
-%\textbf{Figure 8:} \noindent\includegraphics[angle=90,height = 50pc]{Figure8_bw.eps} \\
-%\noindent\includegraphics[width= 50pc]{Figure8_bw.eps} \\
-
-%%=========================================================================
-% Figure 9
-%\noindent\includegraphics[height = 25pc]{Figure9_bw.eps} \\
-%\textbf{Figure 9:}
-
-%%=========================================================================
-
-%Figure 10
-%\clearpage
-%\noindent\includegraphics[width=20pc]{Figure10_c.eps} \\
-%\textbf{Figure 10:}
-
-%%=========================================================================
-
-% Figure 11
-%\clearpage
-%\includegraphics{Figure11_bw.eps} \\
-%\textbf{Figure 11:}
-
-%%=========================================================================
-
-% Figure 12
-%\clearpage
-%\noindent\includegraphics[width = 20pc]{Figure12_c.eps} \\
-%\textbf{Figure 12:}
-
-%%=========================================================================
-
-% Figure 13
-%\clearpage
-%\includegraphics{Figure13_bw.eps} \\
-%\textbf{Figure 13:}
-
-%\appendix
-\clearpage
-\begin{centering}
-\section*{Appendix}
-\end{centering}
-
-\vspace{2em}
-
-\appendix
-\subsection*{The Likelihood}
-%\numberwithin{equation}{section}
-\setcounter{equation}{0}
-\renewcommand{\theequation}{A\arabic{equation}}
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-
-\label{sec-Appendix-noisylikelihood}
-
-The likelihood $P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)$
-used in equation (\ref{eq:-bayesian-noisyform}) is given by
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\label{eq-likelihood-int}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t)  =
-A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N)  \\
-\hspace{3em} \times \int_0^\infty
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
-d\widetilde{\delta}_{CWI}
-\end{array}
-\end{equation} \end{linenomath*}
-where $\widetilde{\delta}_{CWI}$ is an estimate of CWI separation in the absence
-of noise,
-\begin{linenomath*} \begin{equation}
-\label{eq:Adefn}
-A(\widetilde{\delta}_t) = \frac{1}{(1-\Phi_{\mu_1,\sigma_1}(0))\sigma_1\sqrt{2\pi} },
-\end{equation} \end{linenomath*}
-\begin{linenomath*} \begin{equation}
-B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})=e^{  \frac{-(\widetilde{\delta}_{CWI}-\mu_1)^2}{2\sigma_1^2} },
-\end{equation} \end{linenomath*}
-\begin{linenomath*} \begin{equation}
-\label{eq:Cdefn}
-C(\bar{\mu}_N, \bar{\sigma}_N) =  \frac{1}{(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0))\sigma_N\sqrt{2\pi}},
-\end{equation} \end{linenomath*}
-\begin{linenomath*} \begin{equation}
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )=e^{  \frac{-(\widetilde{\delta}_{CWI}-\bar{\mu}_N)^2}{2 \bar{\sigma}_N ^2} }
-\end{equation} \end{linenomath*}
-and $\Phi_{\mu,\sigma}(x)$ is the cumulative Gaussian distribution function
-\begin{linenomath*} \begin{equation}
-\label{eq-cummulative-Gaussian}
-\Phi_{\mu,\sigma}(x) = \frac{1}{\sigma \sqrt{2 \pi}}
-\int_{-\infty}^x e^{  \frac{-(s-\mu)^2}{2\sigma^2}  } ds
-\end{equation} \end{linenomath*}
-\citep{dr_Robinson11a}. The parameters $\mu_1$ and $\sigma_1$ used
-in equation (\ref{eq:Adefn}) are defined by the expressions
-\begin{linenomath*} \begin{equation}
-\label{eq:mu1}
-\mu_1(\widetilde{\delta}_t) = a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+a_3
-\widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta_t}^{a_5}+1}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\label{eq:sigma1}
-\sigma_1(\widetilde{\delta}_t) = c + a_1\frac{a_2 \widetilde{\delta}_t^{a_4}+
-a_3 \widetilde{\delta}_t^{a_5}}{a_2 \widetilde{\delta}_t^{a_4}+a_3 \widetilde{\delta}_t^{a_5}+1}
-\end{equation} \end{linenomath*}
-with coefficients $a_1$ to $a_5$ and $c$ defined in Table
-\ref{tab-const4-mu1-sigma1}. The parameters $\bar{\mu}_N$ and
-$\bar{\sigma}_N$ used in equation (\ref{eq:Cdefn}) are obtained by
-finding the values which minimize the difference in a least squares
-sense between the noisy CWI estimates $\widetilde{\delta}_{CWIN}$
-computed from the waveforms and the positively bounded Gaussian
-density function
-\begin{linenomath*} \begin{equation}
-\label{eq-likelihood-noisydata-pdf-orig}
-\begin{array}{l}
-P(\widetilde{\delta}_{CWIN}|\widetilde{\delta}_t,\widetilde{\delta}_{CWI}) \\
-\hspace{5em} = \frac{1}{\left(1-\Phi_{\bar{\mu}_N,\bar{\sigma}_N}(0)\right)\bar{\sigma}_N\sqrt{2\pi}}
-e^{  \frac{-(\widetilde{\delta}_{CWIN}-\bar{\mu}_N)^2}{2\bar{\sigma}_N^2}  }
-\end{array}
-\end{equation} \end{linenomath*}
-with $\widetilde{\delta}_{CWIN} \geq 0$.
-
-%=======================================================
-% Appendix Table
-
-\begin{table}
-\caption{Coefficients for equations (\ref{eq:mu1}) and
-(\ref{eq:sigma1}).} \label{tab-const4-mu1-sigma1}
-\begin{tabular}{|c|c|}
-\hline
-$\mu_1(\widetilde{\delta}_t)$ & $\sigma_1(\widetilde{\delta}_t)$ \\
-\hline
-$a1 = 0.4661$ & $a1 = 0.1441$\\
-$a2 = 48.9697$ & $a2 = 101.0376$\\
-$a3 = 2.4693$ & $a3 = 120.3864$\\
-$a4 = 4.2467$ & $a4 = 2.8430$\\
-$a5 = 1.1619$ & $a5 = 6.0823$ \\
-     & $c = 0.017$ \\
-\hline
-\end{tabular}
-\end{table}
-
-%=======================================================
-
-\vspace{2em}
-%\begin{centering}
-\subsection*{Derivatives}
-%\end{centering}
-
-\label{sec-Appendix-derivatives_ofL}
-
-The derivatives of $L(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$
-\begin{linenomath*} \begin{equation}
-\frac{\partial L}{\partial \hat{x}_1},
-\frac{\partial L}{\partial \hat{y}_1},
- \frac{\partial L}{\partial \hat{z}_1},
-\frac{\partial L}{\partial \hat{x}_2},
-\frac{\partial L}{\partial \hat{y}_2},
-\frac{\partial L}{\partial \hat{z}_2},
-...,
-\frac{\partial L}{\partial \hat{x}_N},
-\frac{\partial L}{\partial \hat{y}_N},
-\frac{\partial L}{\partial \hat{z}_N}
-\end{equation} \end{linenomath*}
-are required by the Polak-Ribiere algorithm. These are used to guide
-the optimization procedure towards the values of
-$(\mathbf{e}_1,\mathbf{e}_2,...,\mathbf{e}_N)$ which minimize $L$.
-
-The equations for the derivatives are convoluted so we build them
-gradually. We start with an expression for $\delta_t$, the
-wavelength normalized separation between two events $\mathbf{e}_p=
-(\hat{x}_p,\hat{y}_p,\hat{z}_p)$ and $\mathbf{e}_q =
-(\hat{x}_q,\hat{y}_q,\hat{z}_q)$
-\begin{linenomath*} \begin{equation}
-\label{eq:deltat4chapt6deriv}
-\delta_t = \frac{f_{dom}}{v_s}\sqrt{(\hat{x}_p-\hat{x}_q)^2 + (\hat{y}_p-\hat{y}_q)^2 +  (\hat{z}_p-\hat{z}_q)^2},
-\end{equation} \end{linenomath*}
-where $f_{dom}$ is the dominant frequency of the waveforms and $v_s$ is the velocity between the events. Expression
-\ref{eq:deltat4chapt6deriv} has derivatives
-\begin{linenomath*} \begin{equation}
-\label{eq-partial-xyz1}
-\begin{array}{l}
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p} = \frac{f_{dom}^2 (\hat{x}_p-\hat{x}_q)}{v_s^2 \widetilde{\delta}_t},
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{y}_p} = \frac{f_{dom}^2 (\hat{y}_p-\hat{y}_q)}{v_s^2 \widetilde{\delta}_t}, \\
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{z}_p} = \frac{f_{dom}^2 (\hat{z}_p-\hat{z}_q)}{v_s^2 \widetilde{\delta}_t},
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_q} = \frac{f_{dom}^2 (\hat{x}_q-\hat{x}_p)}{v_s^2 \widetilde{\delta}_t}, \\
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{y}_q} = \frac{f_{dom}^2 (\hat{y}_q-\hat{y}_p)}{v_s^2 \widetilde{\delta}_t},
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{z}_q} = \frac{f_{dom}^2 (\hat{z}_q-\hat{z}_p)}{v_s^2 \widetilde{\delta}_t}.
-\end{array}
-\end{equation} \end{linenomath*}
-For brevity we focus the following derivation in terms of $\hat{x}_p$. The remaining terms for $\mathbf{e}_p$
-(i.e. $\hat{y}_p$ and $\hat{z}_p$) can be computed
-by following the same procedure. The derivatives for $\mathbf{e}_q$ can be attained by exploiting the symmetry
-\begin{linenomath*} \begin{equation}
-\label{eq:ep2eq-deriv-symmetry}
-\frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_q} = - \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}.
-\end{equation} \end{linenomath*}
-
-The chain rule gives
-\begin{linenomath*} \begin{equation}
-\frac{\partial \mu_1}{\partial \hat{x}_p} = \frac{\partial \mu_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}{\partial \hat{x}_p}
-\end{equation} \end{linenomath*}
-where differentiating equation (\ref{eq:mu1}) gives
-\begin{linenomath*} \begin{equation}
-\label{eq-dmu1-by-dx1}
-\frac{\partial \mu_1}{\partial \widetilde{\delta}_t} = a_1 \frac{a_2 a_4 \widetilde{\delta}_t^{a_4-1} +a_3 a_5 \widetilde{\delta}_t^{a_5-1}}
-{\left(a_2 \widetilde{\delta}_t^{a_4} +a_3 \widetilde{\delta}_t^{a_5} +1 \right)^2}.
-\end{equation} \end{linenomath*}
-Similarly, we have
-\begin{linenomath*} \begin{equation}
-\frac{\partial \sigma_1}{\partial \hat{x}_p} = \frac{\partial \sigma_1}{\partial \widetilde{\delta}_t} \frac{\partial \widetilde{\delta}_t}
-{\partial \hat{x}_p}
-\end{equation} \end{linenomath*}
-where $\frac{\partial \sigma_1}{\partial \widetilde{\delta}_t}$ has the identical form as \ref{eq-dmu1-by-dx1} with different constants
-$a_1,a_2,...,a_5$ (see table \ref{tab-const4-mu1-sigma1}).
-
-The cumulative Gaussian distribution function \ref{eq-cummulative-Gaussian} is
-\begin{linenomath*} \begin{equation}
-\Phi_{\mu_1,\sigma_1}(0) = \frac{1}{\sigma_1 \sqrt{2 \pi}}
-\int_{-\infty}^0 e^{  \frac{-(s-\mu_1)^2}{2\sigma_1^2}  } ds
-\end{equation} \end{linenomath*}
-which has derivative
-\begin{linenomath*} \begin{equation}
-\frac{\partial \Phi_{\mu_1,\sigma_1}(0)}{\partial \hat{x}_p} =
-\frac{ \sigma_1 \int_{-\infty}^0 \frac{\partial g}{\partial \hat{x}_p} e^g ds -
-\frac{\partial \sigma_1}{\partial \hat{x}_p} \int_{-\infty}^0 e^g ds}
-{\sigma_1^2 \sqrt{2 \pi}},
-\end{equation} \end{linenomath*}
-where
-\begin{linenomath*} \begin{equation}
-g = \frac{-(s-\mu_1)^2}{2 \sigma_1^2}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\frac{\partial g}{\partial \hat{x}_p} = \frac{4 \sigma_1^2 (s-\mu_1) \frac{\partial \mu_1}{\partial \hat{x}_p}
-+ 4\sigma_1 \frac{\partial \sigma_1}{\partial \hat{x}_p}(s-\mu_1)^2}
-{4 \sigma_1^4}.
-\end{equation} \end{linenomath*}
-
-Now, we have all the pieces to compute the derivatives of $A=A(\delta_t)$ and $B = B(\delta_t,\delta_{CWI})$ as follows
-\begin{linenomath*} \begin{equation}
-\frac{\partial A} {\partial \hat{x}_p} =
--\frac{ -\frac{\partial  \Phi_{\mu_1,\sigma_1}(0)}{\partial \hat{x}_p} \sigma_1 +
- \left(1- \Phi_{\mu_1,\sigma_1}(0) \right) \frac{\partial \sigma_1}{\partial \hat{x}_p}}
-{\left(1- \Phi_{\mu_1,\sigma_1}(0) \right)^2 \sigma_1^2 \sqrt{2 \pi}}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\frac{\partial B} {\partial \hat{x}_p} = e^h \frac{\partial h}{\partial \hat{x}_p},
-\end{equation} \end{linenomath*}
-where
-\begin{linenomath*} \begin{equation}
-h =  \frac{-(\delta_{CWI}-\mu_1)^2}{2 \sigma_1^2}
-\end{equation} \end{linenomath*}
-and
-\begin{linenomath*} \begin{equation}
-\frac{\partial h}{\partial \hat{x}_p} = \frac{
-4 \sigma_1^2 (\delta_{CWI}-\mu_1) \frac{\partial \mu_1}{\partial \hat{x}_p}
-+ 4(\delta_{CWI}-\mu_1)^2 \sigma_1 \frac{\partial \sigma_1}{\partial \hat{x}_p} }
-{4 \sigma_1^4}.
-\end{equation} \end{linenomath*}
-Finally, we can differentiate the likelihood for an individual event pair
-\begin{linenomath*} \begin{equation}
-\begin{array}{l}
-\frac{\partial P(\delta_{CWIN}|\widetilde{\delta}_t)} {\partial \hat{x}_p}  =
-\frac{\partial A(\widetilde{\delta}_t)}{\partial \hat{x}_p} C(\bar{\mu}_N, \bar{\sigma}_N) \\
-\hspace{2em} \times \int_0^\infty B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
-d\widetilde{\delta}_{CWI} \\
-\hspace{2em} + A(\widetilde{\delta}_t) C(\bar{\mu}_N, \bar{\sigma}_N) \\
-\hspace{2em} \times \int_0^\infty
-\frac{\partial B(\widetilde{\delta}_t,\widetilde{\delta}_{CWI})} {\partial \hat{x}_p}
-D(\widetilde{\delta}_{CWI},\bar{\sigma}_N,\bar{\mu}_N )
-d\widetilde{\delta}_{CWI}
-\end{array}
-\end{equation} \end{linenomath*}
-and for the logarithm we have
-\begin{linenomath*} \begin{equation}
-\frac{ \partial \ln \left[ P(\delta_{CWIN}|\delta_t) \right] } {\partial \hat{x}_p}
-= \frac{1}{P(\delta_{CWIN}|\delta_t)} \frac{\partial P(\delta_{CWIN}|\delta_t)}{\partial \hat{x}_p}.
-\end{equation} \end{linenomath*}
-
-Thus, it follows that the derivative of $L$ with respect to $\hat{x}_p$ is given by
-%\begin{linenomath*} \begin{equation}
-%\label{eq-derivative-Lstar-cwionly22}
-%\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} =
-%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p}
-%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
-%\end{equation} \end{linenomath*}
-\begin{linenomath*} \begin{equation}   
-\label{eq-derivative-Lstar-cwionly}
-\begin{array}{ll}
-\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} = &
-- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p} \\
- & + \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
-\end{array}
-\end{equation} \end{linenomath*}
-%
-%\iftwocol{\begin{eqnarray} \frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} &  = &\\
-%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p} \\
-%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}
-%\end{eqnarray}}
-%{\frac{\partial L(E_1, E_2, ..., E_n)}{\partial \hat{x}_p} =
-%- \sum_{i=p+1}^{N} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_p,E_i)\right]}{\partial \hat{x}_p}
-%+ \sum_{j=1}^{p-1} \frac{ \partial \ln \left[P(\delta_{CWIN}|E_j,E_p)\right]}{\partial \hat{x}_p}}
-%\end{equation} \end{linenomath*} 
-for a uniform prior. The change of sign in the middle (i.e. to
-addition) accounts for the change in order of the events under the
-conditional. Its inclusion here assumes the correct use of $\partial
-\widetilde{\delta}_t / \partial \hat{x}_p$ or $\partial
-\widetilde{\delta}_t / \partial \hat{x}_q$ when evaluating the left
-and right hand terms of the summation. The derivatives shown in this
-section appear complicated but are in practice trivial to compute
-numerically. Confidence in their accuracy is enhanced by
-demonstrating that the optimization procedure converges to the
-correct solution for a number of synthetic problems in 2 and 3
-dimensions.
-
-\clearpage
-
-%\bsp % ``This paper has been produced using the Blackwell
-     %   Publishing GJI \LaTeXe\ class file.''
-
-\label{lastpage}
-
 \end{document}

### 2013-08-03 paper2/paper2.tex
last lot of changes as requested by the BSSA editorial team upon acceptance

@@
 algorithm can be used with cod-waves alone or in tandem with arrival-time 
-data. Synthetic examples in 2D and 3D and real earthquakes on
+data. Synthetic examples (2D and 3D) and real earthquakes on
 the Calaveras Fault, California are used to demonstrate the
@@
 can be conducted for any historical aftershock sequence or earthquake swarm
-recorded by a temporay deployment, Our technique is, in that sense, related
-to the retorspective sesimological observation technique of 
+recorded by a temporay deployment. Our technique is, in that sense, related
+to the retrospective seismological observation technique of 
 \citet{dr_Curtis12a_EPSL} that utilizes interferometry to obtain seismic signals
@@
 % Table 2
-
-\begin{table}
+\clearpage
+\begin{table}[h]
 \caption[Conditions for identifying unsuitable waveforms when
 applying CWI] {Conditions used to identify unsuitable waveforms
-before applying CWI \citep[Originally published as Table
-5][]{dr_Robinson11a}} \label{tab:-conditions4unsuitablewaveform}
+before applying CWI$^*$} \label{tab:-conditions4unsuitablewaveform}
 \begin{tabular}{|l|p{0.7\textwidth}|}
@@
 \end{table}
+$^*$ Originally published as Table
+5 in \citet{dr_Robinson11a}
 
